### 2023-08-08 Documents/wileyNJD-AMS-Doc.tex
Initial commit

\documentclass[AMS,STIX1COL]{WileyNJD-v2}
\usepackage{moreverb}

\newcommand\BibTeX{{\rmfamily B\kern-.05em \textsc{i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\articletype{Article Type}%

\received{<day> <Month>, <year>}
\revised{<day> <Month>, <year>}
\accepted{<day> <Month>, <year>}

%\raggedbottom

\begin{document}

\title{A demonstration of the \LaTeX\ class file for Wiley NJD Journals\protect\thanks{This is an example for title footnote.}}

\author[1]{Author One*}

\author[2,3]{Author Two}

\author[3]{Author Three}

\authormark{AUTHOR ONE \textsc{et al}}

\address[1]{\orgdiv{Org Division}, \orgname{Org name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[2]{\orgdiv{Org Division}, \orgname{Org name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[3]{\orgdiv{Org Division}, \orgname{Org name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*Corresponding author name, Corresponding address. \email{authorone@Email.com}}

\presentaddress{Present address}

\abstract[Abstract]{This paper describes the use of the \LaTeXe\ \textsf{WileyNJD-v2.cls}
class file for setting papers for \emph{Mathematical Methods in the Applied Sciences}.}

\keywords{Class file; \LaTeXe; \emph{Wiley NJD}}

\jnlcitation{\cname{%
\author{Williams K.}, 
\author{B. Hoskins}, 
\author{R. Lee}, 
\author{G. Masato}, and 
\author{T. Woollings}} (\cyear{2016}), 
\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}

\maketitle

\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

\section{Introduction}\label{sec1}

Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{WileyNJD-v2.cls} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in \emph{Wiley NJD Journals}.

The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
\LaTeXe\ interface so that any document which was produced using
the standard \LaTeXe\ \textsf{article} style can easily be
converted to work with the \textsf{WileyNJD-v2} style. However, the
width of text and typesize will vary from that of
\textsf{article.cls}; therefore, \emph{line breaks will change}
and it is likely that displayed mathematics and tabular material
will need re-setting.

In the following sections we describe how to lay out your code to
use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
\emph{Wiley NJD Journals}.

\subsection{Procedure to install fonts}

\begin{enumerate}
\item All font files are available under the Stix-fonts folder 
\item Font installer is available under the same folder Windows-Stix-fontinstaller.exe
\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
\end{enumerate}

\subsection{The Three Golden Rules}

Before we proceed, we would like to
stress \emph{three golden rules} that need to be followed to
enable the most efficient use of your code at the typesetting
stage:
\begin{enumerate}
\item[(i)] keep your own macros to an absolute minimum;

\item[(ii)] as \TeX\ is designed to make sensible spacing
decisions by itself, do \emph{not} use explicit horizontal or
vertical spacing commands, except in a few accepted (mostly
mathematical) situations, such as \verb"\," before a
differential~d, or \verb"\quad" to separate an equation from its
qualifier;

\item[(iii)] follow the \emph{NJD} reference style.
\begin{enumerate}[a.]
\item Chemistry --- Use the ``AMS'' option as \verb"\documentclass[AMS]{WileyNJD-v2.cls}"

\end{enumerate}
\end{enumerate}

\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
on any standard \LaTeXe\ installation. If any of the fonts, class
files or packages it requires are missing from your installation,
they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.

LaTeX document class options

\begin{flushleft}
\begin{enumerate}[a.]
\item STIX1COL--- For STIX font large one column layout use the ``STIX1COL'' option as \verb"\documentclass[AMS,STIX1COL]{WileyNJD-v2}"
\item STIX2COL--- For STIX font large two column layout use the ``STIX2COL'' option as \verb"\documentclass[AMS,STIX2COL]{WileyNJD-v2}"
\item STIXSMALL--- For STIX font small layout use the ``STIXSMALL'' option as \verb"\documentclass[AMS,STIXSMALL]{WileyNJD-v2}"
\end{enumerate}
\end{flushleft}

\section{The Article Header Information}
The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
Figure~\ref{F1}.

\subsection{Remarks}

\begin{enumerate}[(I).]

\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
\item Use \verb"\authormark{}" for running heads.

\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
link names and addresses. The author for correspondence is marked
by ``*'' and \verb"\corres{}" is used to give that
author's address, which will be printed besides abstract, prefaced by
`Correspondence to:'.

\item For submitting a double-spaced manuscript, add
\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"

\item Use \verb"\presentaddress{}" for present address.

\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.

\item For Key words use \verb"\keywords{}".

\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"

\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".

\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"

\item Use \verb"\articletype{<article category}" for article header information

\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.

\end{enumerate}

\begin{figure}[p]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}

\documentclass[AMS,STIX1COL]{WileyNJD-v2}

\articletype{Article Type}%

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\begin{document}

\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}

\author[<address link>]{<Author name><corresponding author*>}

\author[<address link>,<address link>]{Author Name}

\authormark{AUTHOR ONE \textsc{et al}}

\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
\orgaddress{\state{<State name>}, \country{<Country name>}}}
\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
 \orgaddress{\state{<State name>}, \country{<Country name>}}}

\corres{<corresponding author link*> <author name, address.
 \email{<authorone@email.com>}}

\presentaddress{<Present address>}

\abstract[<Abstract heading>]{<Abstract paragraph>}

\keywords{<keyword1>, <keyword2>,...}

\jnlcitation{\cname{%
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>},  and 
\author{<aurhor name>}} (\cyear{<year>}), 
\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}

\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}

\maketitle

\section{Introduction}
.
.
.
\end{boxedverbatim}
\end{center}
\caption{Example for title page.\label{F1}}
\end{figure}

\section{The Body of the Article}

\subsection{Section headings}

\begin{enumerate}[(H1)]
\item Section --- use \verb"\section{}"
\item SubSection--- use \verb"\subsection{}"
\item SubSubSectioin--- use \verb"\subsubsection{}"
\item Paragraph--- use \verb"\paragraph{}"
\item Subparagraph--- use \verb"\subparagraph{}"
\end{enumerate}

\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
functionality of \AmS\/\TeX\ available. We encourage the use of
the \verb"align", \verb"gather" and \verb"multline" environments
for displayed mathematics.

\subsection{Figures and Tables}

\textsf{WileyNJD-v2.cls} uses the
\textsf{graphicx} package for handling figures.

Figures are called in as follows:
\begin{verbatim}
\begin{figure}
\centering
\includegraphics{<figure name>}
\caption{<Figure caption>}
\end{figure}
\end{verbatim}

The standard coding for a table is shown in Figure~\ref{F2}.

\begin{figure}[h]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}
\begin{table}
\caption{<Table caption>}
\centering
\begin{tabular}{<table alignment>}
\toprule
<column headings>\\
\midrule
<table entries
(separated by & as usual)>\\
<table entries>\\
.
.
.\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Source: xxx.
\item[1] xxx.
\item[2] xxx.
\end{tablenotes}
\end{table}
\end{boxedverbatim}
\end{center}
\caption{Example for table layout.\label{F2}}
\end{figure}

\subsection{Cross-referencing}
The use of the \LaTeX\ cross-reference system
for figures, tables, equations, etc., is encouraged
(using \verb"\ref{<name>}" and \verb"\label{<name>}").

\subsection{Box text}

\begin{verbatim}
\begin{boxtext}
\section*{<title>}%
Paragraph
\end{boxtext}
\end{verbatim}

\subsection{List items}

\subsubsection{Enumerate list styles}
\begin{verbatim}
\begin{enumerate}[1]
\item 
\end{enumerate}

\begin{enumerate}[1.]
\item 
\end{enumerate}

\begin{enumerate}[(1)]
\item 
\end{enumerate}

\begin{enumerate}[I]
\item 
\end{enumerate}

\begin{enumerate}[i]
\item 
\end{enumerate}

\begin{enumerate}[a]
\item 
\end{enumerate}

\end{verbatim}

\subsubsection{Bullet list styles}

\begin{verbatim}
\begin{itemize}
\item 
\end{itemize}
\end{verbatim}

\subsubsection{Description list}

\begin{verbatim}
\begin{description}
\item[<entry>] description text.
\end{description}
\end{verbatim}

\subsection{Enunciations}

\begin{verbatim}
\begin{theorem}[<Theorem subhead>]\label{thm1}
<theorem text>. 
\end{theorem}

\begin{proposition}[<proposition subhead>]\label{pro1}
<proposition text>. 
\end{proposition}

\begin{definition}[<definition subhead>]\label{dfn1}
<definition text>. 
\end{definition}

\begin{proof}
<proof text>. 
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm1}]
<proof text>.
\end{proof}

\end{verbatim}

\subsection{Program codes}

Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math. Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math. Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated. Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.  All other code environments are set with normal text font. Refer below example:

\begin{verbatim}
\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
WritE('Pascal keywords.');
\end{lstlisting}
\end{verbatim}

\subsection{Acknowledgements} An Acknowledgements section is started with \verb"\ack" or
\verb"\acks" for \textit{Acknowledgement} or
\textit{Acknowledgements}, respectively. It must be placed just
before the References.

\subsection{Bibliography}

\begin{enumerate}[1]
\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
\end{enumerate}

The normal commands for producing the reference list are:

\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{<x-ref label>}
         <Reference details>
.
.
.
\end{thebibliography}
\end{verbatim}

\subsection{Appendix Section}

\begin{verbatim}
\appendix

\section{Section title of first appendix\label{app1}}
.
.
.

\end{verbatim}

\end{document}

### 2023-08-08 ams/wileyNJD-AMS_2COL.tex
Update title

\documentclass[AMS,STIX2COL]{WileyNJD-v2}

\articletype{Article Type}%

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\raggedbottom

\begin{document}

\title{Improved Morphological Analysis System Through Transformer-based Re-ranking}

\author[1]{Author One*}

\author[2,3]{Author Two}

\author[3]{Author Three}

\authormark{AUTHOR ONE \textsc{et al}}

\address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}

\corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}

\presentaddress{This is sample for present address text this is sample for present address text}

\abstract[Summary]{This is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text.}

\keywords{keyword1, keyword2, keyword3, keyword4}

\JELinfo{classification}

\MSC{Code numbers}

\jnlcitation{\cname{%
\author{Williams K.},
\author{B. Hoskins},
\author{R. Lee},
\author{G. Masato}, and
\author{T. Woollings}} (\cyear{2016}),
\ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}

\maketitle

\footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

\section{Sample for first level head}\label{sec1}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit~\cite{Rothermel1997} Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.
\begin{eqnarray}
s(nT_{s}) &= &s(t)\times \sum\limits_{n=0}^{N-1} \delta (t-nT_{s}) \xleftrightarrow{\mathrm{DFT}}  S \left(\frac{m}{NT_{s}}\right) \nonumber\\
&= &\frac{1}{N} \sum\limits_{n=0}^{N-1} \sum\limits_{k=-N/2}^{N/2-1} s_{k} e^{\mathrm{j}2\pi k\Delta fnT_{s}} e^{-j\frac{2\pi}{N}mn}
\end{eqnarray}

\section{Sample for another first level head \cite{Rothermel1998}}\label{sec2}

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus viverra
fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa ac
quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo \cite{Elbaum2002} Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

Example for bibliography citations cite~\citep{Elbaum2002}, cites~\cite{Allen2011,Yoo2007}

Quisque ullamcorper placerat ipsum. Cras nibh~\cite{Yoo2007,Schulz2012} Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

\begin{figure*}[t]
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{This is the sample figure caption.\label{fig1}}
\end{figure*}

Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.

\begin{figure*}
\centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
\caption{This is the sample figure caption.\label{fig2}}
\end{figure*}

\subsection{Example for second level head}

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit, dictum
in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam vestibulum
fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi. Pellentesque
eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut mi mi, lacinia
sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui. Mauris nibh leo,
facilisis non, adipiscing quis, ultrices a, dui.

Morbi luctus, wisi viverra faucibus pretium, nibh est placerat odio, nec commodo wisi enim eget quam. Quisque
libero justo, consectetuer a, feugiat vitae, porttitor eu, libero. Suspendisse sed mauris vitae elit sollicitudin malesuada.

Maecenas ultricies eros sit amet ante. Ut venenatis velit. Maecenas sed mi eget dui varius euismod. Phasellus aliquet
volutpat odio. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque sit
amet pede ac sem eleifend consectetuer. Nullam elementum, urna vel imperdiet sodales, elit ipsum pharetra ligula,
ac pretium ante justo a nulla. Curabitur tristique arcu eu metus. Vestibulum lectus. Proin mauris. Proin eu nunc eu
urna hendrerit faucibus. Aliquam auctor, pede consequat laoreet varius, eros tellus scelerisque quam, pellentesque
hendrerit ipsum dolor sed augue. Nulla nec lacus.

\begin{quote}
This is an example~\citep{Elbaum2002,Blanchard2015} for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text~\cite{Blanchard2015}. This is an example for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text. This is an example for quote text~\cite{Blanchard2015}. This is an example for quote text. This is an example for quote text. This is an example for quote text.
\end{quote}

\section{Sample for next first level head}\label{sec3}

\subsection{Example for another second level head}

Suspendisse vitae elit. Aliquam arcu neque, ornare in, ullamcorper quis, commodo eu, libero. Fusce sagittis erat at
erat tristique mollis. Maecenas sapien libero, molestie et, lobortis in, sodales eget, dui. Morbi ultrices rutrum lorem.
Nam elementum ullamcorper leo. Morbi dui. Aliquam sagittis. Nunc placerat. Pellentesque tristique sodales est.
Maecenas imperdiet lacinia velit. Cras non urna. Morbi eros pede, suscipit ac, varius vel, egestas non, eros. Praesent
malesuada, diam id pretium elementum, eros sem dictum tortor, vel consectetuer odio sem sed wisi.

Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
Aenean vel lectus. Nunc imperdiet justo nec dolor.

\subsection{Second level head text}

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.

\subsubsection{Third level head text}

Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
Vivamus eu dolor.

Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis
in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
pulvinar in, cursus faucibus, augue.

\begin{boxtext}
\noindent{\bf Example of Boxtext\ }\\
This is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext.
\end{boxtext}

\paragraph{Fourth level head text}

Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
Aenean vel lectus. Nunc imperdiet justo nec dolor.

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.

\subparagraph{Fifth level head text}

Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
Vivamus eu dolor.

in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
pulvinar in, cursus faucibus, augue.

Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor. Donec interdum. Praesent scelerisque. Mae-
cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,
nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Etiam congue neque id dolor.

Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
sed nisl eu sapien cursus rutrum.

Nulla non mauris vitae wisi posuere convallis. Sed eu nulla nec eros scelerisque pharetra. Nullam varius. Etiam
dignissim elementum metus. Vestibulum faucibus, metus sit amet mattis rhoncus, sapien dui laoreet odio, nec ultricies
nibh augue a enim. Fusce in ligula. Quisque at magna et nulla commodo consequat. Proin accumsan imperdiet sem.
Nunc porta. Donec feugiat mi at justo. Phasellus facilisis ipsum quis ante. In ac elit eget ipsum pharetra faucibus.
Maecenas viverra nulla in massa.

Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis

\begin{center}
\begin{table*}[t]%
\caption{This is sample table caption.\label{tab1}}
\centering
\begin{tabular*}{500pt}{@{\extracolsep\fill}lccD{.}{.}{3}c@{\extracolsep\fill}}
\toprule
&\multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{1}}} & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{2}}} \\\cmidrule{2-3}\cmidrule{4-5}
\textbf{col1 head} & \textbf{col2 head}  & \textbf{col3 head}  & \multicolumn{1}{@{}l@{}}{\textbf{col4 head}}  & \textbf{col5 head}   \\
\midrule
col1 text & col2 text  & col3 text  & 12.34  & col5 text\tnote{1}   \\
col1 text & col2 text  & col3 text  & 1.62  & col5 text\tnote{2}   \\
col1 text & col2 text  & col3 text  & 51.809  & col5 text   \\
\bottomrule
\end{tabular*}
\begin{tablenotes}%%[341pt]
\item Source: Example for table source text.
\item[1] Example for a first table footnote.
\item[2] Example for a second table footnote.
\end{tablenotes}
\end{table*}
\end{center}

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

\begin{center}
\begin{table*}[t]%
\centering
\caption{This is sample table caption.\label{tab2}}%
\begin{tabular*}{500pt}{@{\extracolsep\fill}lcccc@{\extracolsep\fill}}
\toprule
\textbf{col1 head} & \textbf{col2 head}  & \textbf{col3 head}  & \textbf{col4 head}  & \textbf{col5 head} \\
\midrule
col1 text & col2 text  & col3 text  & col4 text  & col5 text\tnote{$\dagger$}   \\
col1 text & col2 text  & col3 text  & col4 text  & col5 text   \\
col1 text & col2 text  & col3 text  & col4 text  & col5 text\tnote{$\ddagger$}   \\
\bottomrule
\end{tabular*}
\begin{tablenotes}
\item Source: Example for table source text.
\item[$\dagger$] Example for a first table footnote.
\item[$\ddagger$] Example for a second table footnote.
\end{tablenotes}
\end{table*}
\end{center}

Below is the example~\cite{Rothermel1998,Yoo2007,Schulz2012} for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list. Below is the example for bulleted list\footnote{This is an example for footnote.}:
\begin{itemize}
\item bulleted list entry sample bulleted list entry~\cite{Allen2011} sample list entry text.
\item bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry.
\item bulleted list entry sample bulleted list entry~\cite{Ballen2011} bulleted list entry sample bulleted list entry~\citet{Allen2011} sample list entry text.  bulleted list entry sample bulleted list entry.
\item sample list entry text. sample list entry text.
\end{itemize}

Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.

Below is the sample for description list. Below is the example for description list. Below is the example for description list. Below is the example for description list. Below is the example for description list. Below is the example for description list:\\[12pt]

\noindent\textbf{Description sample:}

\begin{description}
\item[first entry] description text. description text. description text. description text. description text. description text. description text.
\item[second long entry] description text. description text. description text. description text. description text. description text. description text.
\item[third entry] description text. description text. description text. description text. description text.
\item[fourth entry] description text. description text.
\end{description}

\noindent\textbf{Numbered list items sample:}

\begin{enumerate}[1.]
\item First level numbered list entry. sample numbered list entry.

\item First numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry.

\begin{enumerate}[a.]
\item Second level alpabetical list entry. Second level alpabetical list entry. Second level alpabetical list entry~\citet{Allen2011} Second level alpabetical list entry.

\item Second level alpabetical list entry. Second level alpabetical list entry~\citet{Schulz2012,Allen2011,Ballen2011}.

\begin{enumerate}[ii.]
\item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry.

\item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry~\cite{Yoo2007}.
\end{enumerate}

\item Second level alpabetical list entry. Second level alpabetical list entry~\cite{Elbaum2002}.
\end{enumerate}

\item First level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry.

\item Another first level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry.
\end{enumerate}

\noindent\textbf{un-numbered list items sample:}

\begin{enumerate}[]
\item Sample unnumberd list text..
\item Sample unnumberd list text.
\item sample unnumberd list text.
\item Sample unnumberd list text.
\end{enumerate}

\section{Examples for enunciations}\label{sec4}

\begin{theorem}[Theorem subhead]\label{thm1}
Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text. Example theorem text.
\end{theorem}

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

\begin{proposition}
Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text. Example proposition text.
\end{proposition}

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

\begin{definition}[Definition sub head]
Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text. Example definition text.
\end{definition}

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.

\begin{proof}
Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text.
\end{proof}

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

\begin{proof}[Proof of Theorem~\ref{thm1}]
Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text. Example for proof text.
\end{proof}

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor. Donec interdum. Praesent scelerisque. Mae-
cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,

\begin{sidewaystable}%[h]
\caption{Sideways table caption. For decimal alignment refer column 4 to 9 in tabular* preamble.\label{tab3}}%
\begin{tabular*}{\textheight}{@{\extracolsep\fill}lccD{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}@{\extracolsep\fill}}%
\toprule
  & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} &\multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} \\
\midrule
  &col2 text &col3 text &0.7568&1.0530&1.2642&0.9919&1.3541&1.6108 \\
  & &col2 text &12.5701 &19.6603&25.6809&18.0689&28.4865&37.3011 \\
3 &col2 text  & col3 text &0.7426&1.0393&1.2507&0.9095&1.2524&1.4958 \\
  & &col3 text &12.8008&19.9620&26.0324&16.6347&26.0843&34.0765 \\
  & col2 text & col3 text &0.7285&1.0257&1.2374&0.8195&1.1407&1.3691\tnote{*} \\
  & & col3 text &13.0360&20.2690&26.3895&15.0812&23.4932&30.6060\tnote{\dagger} \\
\bottomrule
\end{tabular*}
\begin{tablenotes}%%[\textheight]
\item[*] First sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
\item[$\dagger$] Second sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
\end{tablenotes}
\end{sidewaystable}

\begin{sidewaysfigure}
\centerline{\includegraphics[width=542pt,height=9pc,draft]{empty}}
\caption{Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption.\label{fig3}}
\end{sidewaysfigure}

nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Etiam congue neque id dolor.

\begin{algorithm}
\caption{Pseudocode for our algorithm}\label{alg1}
\begin{algorithmic}
  \For each frame
  \For water particles $f_{i}$
  \State compute fluid flow~\cite{Rothermel1997}
  \State compute fluid--solid interaction~\cite{Allen2011}
  \State apply adhesion and surface tension~\cite{Ballen2011}
  \EndFor
   \For solid particles $s_{i}$
   \For neighboring water particles $f_{j}$
   \State compute virtual water film \\(see Section~\ref{sec3})
   \EndFor
   \EndFor
   \For solid particles $s_{i}$
   \For neighboring water particles $f_{j}$
   \State compute growth direction vector \\(see Section~\ref{sec2})
   \EndFor
   \EndFor
   \For solid particles $s_{i}$
   \For neighboring water particles $f_{j}$
   \State compute $F_{\theta}$ (see Section~\ref{sec1})
   \State compute $CE(s_{i},f_{j})$ \\(see Section~\ref{sec3})
   \If $CE(b_{i}, f_{j})$ $>$ glaze threshold
   \State $j$th water particle's phase $\Leftarrow$ ICE
   \EndIf
   \If $CE(c_{i}, f_{j})$ $>$ icicle threshold
   \State $j$th water particle's phase $\Leftarrow$ ICE
   \EndIf
   \EndFor
   \EndFor
  \EndFor
\end{algorithmic}
\end{algorithm}

Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
Integer porta neque vitae massa~\cite{Rothermel1997,Elbaum2002}. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo~\cite{Elbaum2002} Nulla nisl. Vestibulum
sed nisl eu sapien cursus rutrum.

Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
consectetuer adipiscing elit. Etiam congue neque id dolor.

Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
sed nisl eu sapien cursus rutrum.

\begin{equation}\label{eq23}
 \|\tilde{X}(k)\|^2
 =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
\end{equation}

Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
Aenean vel lectus. Nunc imperdiet justo nec dolor.

Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.

\begin{equation}\label{eq24}
 \|\tilde{X}(k)\|^2
 =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
 \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
\end{equation}

Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.

Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
Vivamus eu dolor.

\section{Conclusions}\label{sec5}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

%\backmatter

\section*{Acknowledgments}
This is acknowledgment text~\cite{Elbaum2002}. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here. This is acknowledgment text. Provide text here.

\subsection*{Author contributions}

This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.

\subsection*{Financial disclosure}

None reported.

\subsection*{Conflict of interest}

The authors declare no potential conflict of interests.

\section*{Supporting information}

The following supporting information is available as part of the online article:

\noindent
\textbf{Figure S1.}
{500{\uns}hPa geopotential anomalies for GC2C calculated against the ERA Interim reanalysis. The period is 1989--2008.}

\noindent
\textbf{Figure S2.}
{The SST anomalies for GC2C calculated against the observations (OIsst).}

\appendix

\section{Section title of first appendix\label{app1}}

Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math. Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math. Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated. Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.  All other code environments are set with normal text font. Refer below example:

\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
WritE('Pascal keywords.');
\end{lstlisting}

\subsection{Subsection title of first appendix\label{app1.1a}}

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

\subsubsection{Subsection title of first appendix\label{app1.1.1a}}

\noindent\textbf{Unnumbered figure}

\begin{center}
\includegraphics[width=7pc,height=8pc,draft]{empty}
\end{center}

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.

Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

\section{Section title of second appendix\label{app2}}%

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.

Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.

%== Figure 4 ==
%% Example for figure inside appendix
\begin{figure}[t]
\centerline{\includegraphics[height=10pc,width=78mm,draft]{empty}}
\caption{This is an example for appendix figure.\label{fig5}}
\end{figure}

\subsection{Subsection title of second appendix\label{app2.1a}}

Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non odio.
Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce sed justo
eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec
pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin et quam.
Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien turpis,
fermentum vel, eleifend faucibus, vehicula eu, lacus.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.

\subsubsection{Subsection title of second appendix\label{app2.1.1a}}

Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
Duis eget orci sit amet orci dignissim rutrum.

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

\begin{center}
\begin{table*}[b]%
\centering
\caption{This is an example of Appendix table showing food requirements of army, navy and airforce.\label{tab4}}%
\begin{tabular*}{300pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
\toprule
\textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
\midrule
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text\\
\bottomrule
\end{tabular*}
\end{table*}
\end{center}

Example for an equation inside appendix
\begin{equation}
\mathcal{L}\quad \mathbf{\mathcal{L}} = i \bar{\psi} \gamma^\mu D_\mu \psi - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi\label{eq25}
\end{equation}

\section{Example of another appendix section\label{app3}}%

This is sample for paragraph text this is sample for paragraph text  this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text

Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

\begin{equation}
\mathcal{L} = i \bar{\psi} \gamma^\mu D_\mu \psi
    - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi
\label{eq26}
\end{equation}

Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
pellentesque felis eu massa.

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

\begin{center}
\begin{tabular*}{250pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
\toprule
\textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
\midrule
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text \\
col1 text & col2 text & col3 text \\
\bottomrule
\end{tabular*}
\end{center}

Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
vitae risus porta vehicula.

Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, evehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.

Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.

\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
\bibliography{wileyNJD-AMS}%

\section*{Author Biography}

\begin{biography}{\includegraphics[width=60pt,height=70pt,draft]{empty}}{\textbf{Author Name.} This is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text this is sample author biography text.}
\end{biography}

\end{document}

### 2023-08-08 ams/wileyNJD-AMS_2COL.tex
Update title and abstract

@@
 
-\title{Improved Morphological Analysis System Through Transformer-based Re-ranking}
+    \title{Improvement of Korean Morphological Analysis System Through Transformer-based Re-ranking}
 
@@
 
-\abstract[Summary]{This is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text this is sample abstract text.}
+    \abstract[Abstract]{
+        %한국어 형태소 분석은 한국어 분석의 첫걸음이라고 할 정도로 기본적이고 중요한 역할을 담당하고 있다.
+        Korean morpheme analysis plays a basic and important role enough to be called the first step in Korean language analysis.
+        %한국어는 교착어의 특성으로 인해 영어처럼 품사 태깅만으로는 분석이 끝나지 않아 자동 분석 시스템 구축에 어려움이 있어왔다.
+        Due to the nature of Korean agglutinative words, it was difficult to build an automatic analysis system because the analysis was not completed with part-of-speech tagging alone, as in English.
+        %또한 형태소분석을 위한 다양한 방법들이 제안되었지만, 딥러닝을 위한 토큰화기로 활용하려는 응용에서는 BPE와 같은 효율적인 방법들이 주로 사용되고 있다.
+        In addition, various methods for morpheme analysis have been proposed, but efficient methods such as BPE are mainly used in applications intended to be used as tokenizers for deep learning.
+        %본 논문에서는 토큰화에서도 사용이 가능한 효율적인 형태소분석 시스템의 성능을 딥러닝 기반의 Multi-Stage 재순위화를 통해 극대화하는 방법에 대해 제안하고자 한다.
+        In this paper, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
+        %재순위화를 통해 순위가 바뀌어진 다수의 다양한 사례들은 추후 Lattice 기반 형태소분석 시스템의 cost matrix를 업데이트함으로 속도를 유지하면서 성능을 개선하는 것이 가능해진다.
+        For a number of various cases whose rankings have been changed through re-ranking, it is possible to improve performance while maintaining speed by updating the cost matrix of the lattice-based morpheme analysis system in the future.
+        %실험을 통해 제안하는 방법을 통해 구어체 모델과 문어체 모델에서 모두 기존보다 오류가 40% 이상 감소됨 보임으로 제안한 방법이 효과적으로 성능을 개선하였음을 보였다.
+        Through experiments, we showed that the proposed method effectively improved performance by reducing errors by more than 40\% in both the spoken language model and the written language model.
+    }
 
@@
                 \toprule
-&\multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{1}}} & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{2}}} \\\cmidrule{2-3}\cmidrule{4-5}
+                & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{1}}} & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{2}}} \\\cmidrule{2-3}\cmidrule{4-5}
                 \textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{@{}l@{}}{\textbf{col4 head}}  & \textbf{col5 head}   \\
@@
 
-\begin{theorem}[Theorem subhead]\label{thm1}
+    \begin{theorem}[Theorem subhead]
+        \label{thm1}
         Example theorem text.
@@
             \toprule
-  & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} &\multicolumn{1}{c}{\textbf{10}} &\multicolumn{1}{c}{\textbf{20}} &\multicolumn{1}{c}{\textbf{30}} \\
+            & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{c}{\textbf{10}} & \multicolumn{1}{c}{\textbf{20}} & \multicolumn{1}{c}{\textbf{30}} & \multicolumn{1}{c}{\textbf{10}} & \multicolumn{1}{c}{\textbf{20}} & \multicolumn{1}{c}{\textbf{30}} \\
             \midrule
-  &col2 text &col3 text &0.7568&1.0530&1.2642&0.9919&1.3541&1.6108 \\
-  & &col2 text &12.5701 &19.6603&25.6809&18.0689&28.4865&37.3011 \\
-3 &col2 text  & col3 text &0.7426&1.0393&1.2507&0.9095&1.2524&1.4958 \\
-  & &col3 text &12.8008&19.9620&26.0324&16.6347&26.0843&34.0765 \\
-  & col2 text & col3 text &0.7285&1.0257&1.2374&0.8195&1.1407&1.3691\tnote{*} \\
-  & & col3 text &13.0360&20.2690&26.3895&15.0812&23.4932&30.6060\tnote{\dagger} \\
+            & col2 text          & col3 text          & 0.7568                          & 1.0530                          & 1.2642                          & 0.9919                          & 1.3541                          & 1.6108                          \\
+            &                    & col2 text          & 12.5701                         & 19.6603                         & 25.6809                         & 18.0689                         & 28.4865                         & 37.3011                         \\
+            3 & col2 text          & col3 text          & 0.7426                          & 1.0393                          & 1.2507                          & 0.9095                          & 1.2524                          & 1.4958                          \\
+            &                    & col3 text          & 12.8008                         & 19.9620                         & 26.0324                         & 16.6347                         & 26.0843                         & 34.0765                         \\
+            & col2 text          & col3 text          & 0.7285                          & 1.0257                          & 1.2374                          & 0.8195                          & 1.1407                          & 1.3691\tnote{*}                 \\
+            &                    & col3 text          & 13.0360                         & 20.2690                         & 26.3895                         & 15.0812                         & 23.4932                         & 30.6060\tnote{\dagger}          \\
             \bottomrule
@@
         \begin{algorithmic}
-  \For each frame
-  \For water particles $f_{i}$
+            \For
+                each frame
+                \For
+                    water particles $f_{i}$
                     \State compute fluid flow~\cite{Rothermel1997}
@@
                 \EndFor
-   \For solid particles $s_{i}$
-   \For neighboring water particles $f_{j}$
+                \For
+                    solid particles $s_{i}$
+                    \For
+                        neighboring water particles $f_{j}$
                         \State compute virtual water film \\(see Section~\ref{sec3})
@@
                 \EndFor
-   \For solid particles $s_{i}$
-   \For neighboring water particles $f_{j}$
+                \For
+                    solid particles $s_{i}$
+                    \For
+                        neighboring water particles $f_{j}$
                         \State compute growth direction vector \\(see Section~\ref{sec2})
@@
                 \EndFor
-   \For solid particles $s_{i}$
-   \For neighboring water particles $f_{j}$
+                \For
+                    solid particles $s_{i}$
+                    \For
+                        neighboring water particles $f_{j}$
                         \State compute $F_{\theta}$ (see Section~\ref{sec1})
                         \State compute $CE(s_{i},f_{j})$ \\(see Section~\ref{sec3})
-   \If $CE(b_{i}, f_{j})$ $>$ glaze threshold
+                        \If
+                            $CE(b_{i}, f_{j})$ $>$ glaze threshold
                             \State $j$th water particle's phase $\Leftarrow$ ICE
                         \EndIf
-   \If $CE(c_{i}, f_{j})$ $>$ icicle threshold
+                        \If
+                            $CE(c_{i}, f_{j})$ $>$ icicle threshold
                             \State $j$th water particle's phase $\Leftarrow$ ICE
@@
 
-\begin{equation}\label{eq23}
+    \begin{equation}
+        \label{eq23}
         \|\tilde{X}(k)\|^2
@@
 
-\begin{equation}\label{eq24}
+    \begin{equation}
+        \label{eq24}
         \|\tilde{X}(k)\|^2
@@
                 col1 text          & col2 text          & col3 text          \\
-col1 text & col2 text & col3 text\\
+                col1 text          & col2 text          & col3 text          \\
                 \bottomrule

### 2023-08-10 ams/wileyNJD-AMS_2COL.tex
Updates from Overleaf

@@
     \abstract[Abstract]{
+        Korean morphological analysis plays a basic and important role enough to be called the first step in Korean language analysis.
+        Due to the nature of Korean agglutinative words, it was difficult to build an automatic analysis system because the analysis was not completed with part-of-speech tagging alone, as in English.
+        In addition, various methods for morphological analysis have been proposed, but efficient methods such as BPE are mainly used in applications intended to be used as tokenizers for deep learning.
+        In this paper, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
+        For a number of various cases whose rankings have been changed through re-ranking, it is possible to improve performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system in the future.
+        Through experiments, we showed that the proposed method effectively improved performance by reducing errors by more than 40\% in both the spoken language model and the written language model.
     %한국어 형태소 분석은 한국어 분석의 첫걸음이라고 할 정도로 기본적이고 중요한 역할을 담당하고 있다.
-        Korean morpheme analysis plays a basic and important role enough to be called the first step in Korean language analysis.
     %한국어는 교착어의 특성으로 인해 영어처럼 품사 태깅만으로는 분석이 끝나지 않아 자동 분석 시스템 구축에 어려움이 있어왔다.
-        Due to the nature of Korean agglutinative words, it was difficult to build an automatic analysis system because the analysis was not completed with part-of-speech tagging alone, as in English.
     %또한 형태소분석을 위한 다양한 방법들이 제안되었지만, 딥러닝을 위한 토큰화기로 활용하려는 응용에서는 BPE와 같은 효율적인 방법들이 주로 사용되고 있다.
-        In addition, various methods for morpheme analysis have been proposed, but efficient methods such as BPE are mainly used in applications intended to be used as tokenizers for deep learning.
     %본 논문에서는 토큰화에서도 사용이 가능한 효율적인 형태소분석 시스템의 성능을 딥러닝 기반의 Multi-Stage 재순위화를 통해 극대화하는 방법에 대해 제안하고자 한다.
-        In this paper, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
     %재순위화를 통해 순위가 바뀌어진 다수의 다양한 사례들은 추후 Lattice 기반 형태소분석 시스템의 cost matrix를 업데이트함으로 속도를 유지하면서 성능을 개선하는 것이 가능해진다.
-        For a number of various cases whose rankings have been changed through re-ranking, it is possible to improve performance while maintaining speed by updating the cost matrix of the lattice-based morpheme analysis system in the future.
     %실험을 통해 제안하는 방법을 통해 구어체 모델과 문어체 모델에서 모두 기존보다 오류가 40% 이상 감소됨 보임으로 제안한 방법이 효과적으로 성능을 개선하였음을 보였다.
-        Through experiments, we showed that the proposed method effectively improved performance by reducing errors by more than 40\% in both the spoken language model and the written language model.
     }
@@
         \author{R. Lee},
-        \author{G. Masato}, and
-        \author{T. Woollings}} (\cyear{2016}),
+        \author{G. Masato}, and \author{T. Woollings}} (\cyear{2016}),
         \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
@@
 
-    \section{Sample for first level head}\label{sec1}
+    \section{Introduction}\label{sec1}
+
+    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of language expression that have an independent meaning in a sentence.
+    In an isolating language like English, this can be done relatively simply by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
+    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
+    Modern, high-performance deep learning methods in natural language processing use a tokenisation process that breaks text into smaller units, and then converts each token into a vector as input to the computational model [Milkolov2013].
+    In this case, the token unit is mainly subword units, and to reflect the characteristics of Korean, subword tokenisation is attempted with separated morphemes in advance. [Song2021]
+    Using the results of morphological analysis for this tokenisation process improves the overall performance of the analysis by reflecting the semantic units of Korean, but requires a highly accurate and fast morphological analyzer.
+
+    %한국어 형태소 분석은 문장 내에서 독립적 의미를 가진 가장 작은 언어표현 단위인 형태소를 찾아 품사를 결정하는 과정이다.
+    %영어와 같은 고립어에서는 기호 및 띄어쓰기로 나뉘어진 단위에 품사 태깅을 하는 것으로 그 과정이 비교적 단순하나, 한국어의 경우 교착어의 특성으로 인해 어미나 조사를 분리해주고 용언 등의 변화형을 원형으로 복원해주는 과정이 필요하다.
+    %또한 다른 한국어 분석 태스크들의 기본 입력이 분리된 형태소인 경우가 많아, 형태소 분석의 정확도는 한국어 분석의 성능에 큰 영향을 미치게 된다.
+    %자연어처리 분야에 높은 성능을 자랑하는 최신의 딥러닝 방법들에서는 텍스트를 작은 단위로 분리하는 토큰화 과정을 거친 뒤, 각 토큰을 벡터로 변환하여 입력으로 사용한다. [Milkolov2013]
+    %이 때의 토큰 단위는 주로 서브워드 단위를 많이 사용하는 추세이고, 한국어의 특성을 반영하여 형태소를 미리 분리한 상태에서 서브워드 토큰화를 시도하기도 한다. [Song2021]
+    %이러한 토큰화 과정에 형태소 분석 결과를 사용하게 되면 한국어의 의미 단위를 반영할 수 있어 전반적인 분석 성능이 좋아지지만, 정확도가 높으면서 빠른 형태소 분석기를 필요로 하게 된다.
+
+    Various approaches have been proposed for morphological analysis, which plays a fundamental and important role in Korean language analysis. [...]
+    In general, when people understand speech or writing, they try to make sense of it using the vocabulary and concepts they know.
+    While there are ways to use rules or dictionaries to reflect this way of understanding [...], the problem is that it becomes difficult to build and maintain a dictionary for vocabulary that appears in every text.
+    Hence, methods for tagging in syllable units without a dictionary have been proposed [...], and studies to improve them have been continuously conducted. [...]
+    From a mechanical point of view, syllable-by-syllable morphological analysis can be done either by tagging syllable-by-syllable and then applying a base form restoration dictionary [...], or by tagging syllable-by-syllable with the base form already restored.
+[...]
+    However, syllable-by-syllable morphological analysis has limitations in that it is difficult to accurately identify the boundaries of morphemes, and it is difficult to learn long-term contextual information as the length of the sequence increases.
+    In this paper, the former is referred to as dictionary-based morphological analysis, and the latter as syllable unit morphological analysis.
+    Both methods also share the limitation that they are trained on a manually labelled corpus and cannot perform accurate analysis of new syllable combinations or morphemes that do not appear in the training corpus.
+    In recent years, with the development of the Internet and the spread of open source and open data, web texts, corpora, language resources, and knowledge shared by various people have accumulated considerably.
+    The reduced cost of building and maintaining a dictionary can be a great opportunity to overcome the limitations of dictionary-based methods.
+
+    %이렇게 한국어 분석에서 기본적이고 중요한 역할을 담당해오는 형태소 분석에 대해서 다양한 접근법들이 제안되어 왔다.
+    %일반적으로 사람들은 말이나 글을 이해할 때 자신이 알고 있는 어휘와 개념들을 이용해서 그것을 이해하려고 한다.
+    %이와 같은 사람들의 이해 방식을 따라 규칙이나 사전을 사용한 방법들이 있었지만, 모든 텍스트에서 등장하는 어휘에 대한 사전을 구축하고 유지하는 것이 어렵게 되는 문제가 있었다.
+    %이에 사전 없이 음절 단위로 태깅하는 방법들이 제안되었고, 계속해서 이를 개선하는 연구들이 진행되어 왔다.
+    %음절 단위 형태소 분석은 기계적인 관점에서 음절 단위로 태깅 후 원형복원 사전을 적용하거나, 원형을 미리 복원한 상태에서 음절 단위로 태깅하는 방법이 있다.
+    %그러나 음절 단위 형태소 분석은 형태소의 경계를 정확하게 파악하기 힘든 면과 시퀀스의 길이가 길어지면서 장기적인 문맥 정보를 학습하기 어려운 면도 있다.
+    %본 논문에서는 전자를 사전 기반 형태소 분석이라 하고, 후자를 음절 단위 형태소 분석이라고 하겠다.
+    %또한 두 방법 모두 수동으로 레이블링된 말뭉치를 기반으로 학습하기 때문에 학습말뭉치에 등장하지 않은 새로운 음절 조합이나 형태소에 대해서는 정확한 분석을 수행하지 못하는 한계가 공통적으로 있다.
+    %최근에는 인터넷의 발전과 함께 오픈소스 및 오픈데이터의 확산 분위기 속에서 다양한 사람들에 의해 공유된 웹텍스트, 말뭉치, 언어자원, 지식 등이 상당히 축적해가고 있다.
+    %이를 통해 사전 구축 및 유지 비용이 줄어들 수 있는 것은 사전 기반 방법의 한계를 극복할 수 있는 좋은 기회가 될 수 있다.
+
+    Against this background, this paper considers how the dictionary-based morphological analysis method used by MeCab, an open software used for Korean and Japanese morphological analysis in tokenisers, an essential tool for preprocessing for deep learning, can be effectively improved through deep learning, and proposes a method.
+    The dictionary-based morphological analysis method[Kudo2004, Na2014] trained by the CRF method[Sutton2012] lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph, and finds the optimal morphological analysis path within it.
+    The process of finding the best path in Lattice uses the Viterbi algorithm[Forney1973], which finds the path that minimises the cost of each morpheme node and the sum of the neighbouring costs of two consecutive morphemes.
+    The main types of errors in these dictionary-based morphological analysis methods are when new words not in the dictionary are used in a sentence, or when the optimal path calculation selects the wrong result due to a bias.
+    For example, it may be less costly to choose one long morpheme than to choose several short ones, but it can sometimes be the wrong analysis.
+    The main motivation for this research is that the path that minimises the sum of all costs for nodes and connections may not be the optimal path.
+
+    %이러한 배경하에서 본 논문에서는 딥러닝을 위한 전처리의 필수 도구인 토큰화기에서 한국어 및 일본어 형태소 분석을 위해 사용되는 공개 소프트웨어인 MeCab에서 사용하는 사전 기반 형태소 분석 방법을 딥러닝을 통해 효과적으로 개선할 수 있는 방법에 대해 고려하고 방법을 제안하고자 한다.
+    %CRF 방법으로 학습하는 사전 기반 형태소 분석 방법은 주어진 문장으로부터 사전에 있는 선택가능한 형태소 후보들을 나열하여 방향성 있는 그래프로 연결한 Lattice 구조를 형성하고, 그 안에서 최적의 형태소 분석 경로를 찾아내는 방법이다.
+    %Lattice에서 최적의 경로를 찾아내는 과정은 Viterbi 알고리즘을 사용하며, 이 때의 경로는 각 형태소 노드에 대한 비용과 연속적인 두 형태소의 인접 비용의 합이 최소가 되는 경로를 찾아내는 것이다.
+    %이러한 사전 기반 형태소 분석 방법에서의 주된 오류 유형은 사전에 없는 새로운 어휘가 문장에서 사용된 경우이거나, 최적 경로 계산 시에 잘못된 편견으로 인해 오분석 결과를 선택한 경우이다.
+    %예를 들면 짧은 형태소 여럿을 선택하는 것보다 하나의 긴 형태소를 선택하는 것이 비용적으로는 적을 수 있지만 때에 따라 잘못된 분석이 될 수도 있다.
+    %이로 인해 노드 및 연결에 대한 모든 비용의 합이 최소가 되는 경로가 최적의 경로가 아닐 수 있다는 점이 본 연구의 주된 동기이다.
+
+    In order to identify the cases where a suboptimal solution is actually the best solution according to the best path calculation, we modified the best path calculation method to generate suboptimal analysis results and check the extent to which they are correct.
+    While there could be a variety of suboptimal choices, we used the method of replacing one morpheme node on the optimal path with nodes ranked 2 through 5.
+    As shown in [Table 1], we were able to confirm the extent to which the analysis performance could be improved by replacing the optimal path with a lower-ranked node.
+    We can think of the problem of finding the actual correct answer among these generated suboptimals as similar to the problem of re-ranking search results in information retrieval.
+    Previously, in [Choi2018], N-Best analysis results generated by the seq2seq model were re-ranked based on a convolutional neural network to improve performance.
+    In this study, reranking was performed using two BERT models of different types and forms as proposed in [Nogueira2019].
+    The experimental results show that the first-stage reranking improves performance by more than 34\% from the previous written and spoken models, and the second-stage reranking with a different type of input and a different kind of pre-trained model further improves performance by more than 40\% the previous written and spoken models.
+
+    %최적 경로 계산 상으로 차선책이 실제적인 최선책인 경우들를 파악하기 위해 본 연구에서는 최적 경로 계산 방법을 수정하여 차선책 분석 결과들을 생성해보고 이들 중에 정답이 있는 정도를 확인하였다.
+    %다양한 차선책 선택 방법이 있을 수 있겠지만, 최적 경로 상에서 하나의 형태소 노드를 2~5순위의 노드로 치환하는 방법을 사용하였다.
+    %[표 1]에서 보는 바와 같이, 최적 경로를 차순위 노드로 치환함으로 분석 성능을 개선할 수 있는 정도를 확인할 수 있었다.
+    %이렇게 생성된 차선책들 중에서 실제 정답을 찾는 문제는 정보검색에서 검색 결과를 재순위화하는 문제와 유사한 것으로 생각해 볼 수 있다.
+    %기존에는 [Choi2018] 연구에서 seq2seq 모델 생성한 N-Best 분석 결과들을 컨볼루션 신경망 기반의 재순위화를 통해 성능을 개선하였다.
+    %본 연구에서는 [Nogueira2019]에서 제안한 것처럼 서로 다른 종류 및 형태로 두 개의 BERT 모델을 사용하여 재순위화를 수행하였다.
+    %실험 결과를 통해, 1단계 재순위화를 통해 문어체와 구어체 모델에서 기존보다 34% 이상 오류가 감소하여 1차로 성능을 개선하였고, 다른 형태의 입력과 다른 종류의 사전학습 모델을 사용한 2단계 재순위화를 수행함으로 추가적으로 기존 보다 오류가 40% 이상 감소한 성능 개선 결과를 확인할 수 있었다.
+
+    Through this method, the performance of the dictionary-based morphological analysis method could be further improved, but the analysis speed slows down when the morphological analysis system is configured including the re-ranking model itself.
+    However, it is possible to use the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in the dictionary, similar to the backpropagation process in a typical neural network.
+    It is also expected that the morphological analysis system with improved connection costs will be able to generate better reranking candidates, which will further improve performance by doing this iteratively.
+    For this, additional research is needed in the future, and in this paper, only the performance improvement through the second-stage re-ranking was covered as the scope of the study.
+    The main contributions of this study are as follows:
+    \begin{itemize}
+        \item 1.
+[Further improvement of dictionary-based morphological analysis method using suboptimal analysis results]: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node, and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
+        \item 2.
+[Extend the performance improvement by introducing a two-stage reranking model]: To improve the performance of dictionary-based analysis by reranking the morphological analysis results, we propose to extend the performance improvement by using different BERT models to perform two rounds of reranking.
+        \item 3.
+[A method for updating connection costs in dictionary and suggestions for future research]: We propose a new method for updating dictionary connection costs based on the results of re-ranked morphological analysis, and provide directions for future research by suggesting improvements and directions for future research.
+    \end{itemize}
+    These contributions provide important insights into the performance improvement of Korean morphological analysis and the direction of future research, and will serve as a useful reference for future researchers.
+
+    %이러한 방법을 통해 사전 기반 형태소 분석 방법의 성능을 추가로 개선할 수 있었으나, 재순위화 모델 자체를 포함하여 형태소 분석 시스템을 구성하게 되면 분석 속도가 느려지는 문제가 발생한다.
+    %그러나 재순위화된 여러 형태소 분석 결과들을 사용해서 일반적인 Neural Network의 Back Propagration과정처럼 사전 상의 형태소 간의 연결 비용을 업데이트하는 방식을 적용해볼 수 있다.
+    %또한 연결 비용이 개선된 형태소 분석 시스템을 통해 더 좋은 재순위화 후보들을 생성할 수 있게 되므로, 이를 반복적으로 수행함으로써 성능을 더욱 개선할 수 있을 것으로도 기대된다.
+    %이에 대해서는 앞으로 추가적인 연구가 필요하며, 본 논문에서는 2단계 재순위화를 통한 성능 개선에 대해서만 연구 범위로 다루었다.
+    %본 연구가 가지는 연구의 주요 기여점은 다음과 같습니다:
+    % 1. **차선 분석 결과를 활용한 사전 기반 형태소 분석 방법의 추가 개선**: 최적 경로를 차순위 노드로 치환하는 방법을 도입하여 성능 개선의 가능성을 탐색하고, 사전 기반 형태소 분석 방법을 딥러닝을 통해 효과적으로 개선할 수 있는 방안을 제안한다.
+    % 2. **2단계 재순위화 모델 도입을 통한 성능 개선 정도 확대**: 형태소 분석 결과의 재순위화를 통해 사전 기반 분석의 성능을 개선하기 위해 서로 다른 BERT 모델을 사용하여 두 차례의 재순위화를 과정을 통해 성능 개선 정도를 확대시킬 수 있는 방안을 제안한다.
+    % 3. **사전 연결 비용의 업데이트 방법 및 향후 연구 제안**: 재순위화된 형태소 분석 결과를 기반으로 사전의 연결 비용을 업데이트하는 새로운 방식을 제안하고, 향후 연구 방향과 개선점을 제시하여 이후 연구에 대한 방향성을 제공한다.
+    %본 논문은 이러한 기여점들을 통해 한국어 형태소 분석의 성능 개선과 연구의 진행 방향에 중요한 통찰을 제공하며, 이후 연구자들에게 유용한 참고자료가 될 것입니다.
+
+    This paper is organised as follows:
+    In section 2, we introduce previous research cases related to this study, and in section 3, we discuss how to configure and train a dictionary-based morphological analysis system.
+    In section 4, we discuss how to generate secondary results of morphological analysis and create re-ranking data, and propose a method to train a two-stage re-ranking model.
+    In section 5, we discuss the results of performance improvement through morphological analysis model and re-ranking model, and in section 6, we discuss error analysis and performance improvement cases.
+    Finally, in section 7, we conclude the paper and discuss the limitations of this study and the direction of future research.
+
+    %본 논문의 구성은 다음과 같다.
+    %2장에서 본 연구와 관련한 이전 연구 사례들을 소개하며, 3장에서는 사전 기반 형태소 분석 시스템을 구성하고 학습하는 방법에 대해 다룬다.
+    %4장에서는 학습된 형태소 분석 모델의 차선 결과들을 생성하여 재순위화 데이터를 만드는 방법에 대해 다루고, 2단계 재순위화 모델을 학습시키는 방법을 제안한다.
+    %5장에서는 형태소 분석 모델 및 재순위화 모델을 통한 성능 개선 실험 결과를 다루고, 6장에서 오류 분석 및 성능 개선 사례들을 살펴본 뒤, 7장에서 본 연구의 결론과 향후 연구를 제시한다.
+
+    \section{Sample for first level head}\label{secX}
 
@@
     Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-    sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
-    leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
+    sit amet tortor gravida placerat.
+Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
+Praesent eget sem vel leo ultrices bibendum.
+Aenean faucibus.
+Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla.
+Curabitur
     auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
@@
     Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus viverra
-    fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa ac
-    quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo \cite{Elbaum2002} Maecenas lacinia. Nam ipsum ligula, eleifend
-    at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-    nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
+    fermentum felis.
+Donec nonummy pellentesque ante.
+Phasellus adipiscing semper elit.
+Proin fermentum massa ac quam.
+Sed diam turpis, molestie vitae, placerat a, molestie nec, leo \cite{Elbaum2002} Maecenas lacinia.
+Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
+Morbi blandit ligula feugiat magna.
+Nunc eleifend consequat lorem.
+Sed lacinia nulla vitae enim.
+Pellentesque tincidunt purus vel magna.
+Integer non enim.
+Praesent euismod nunc eu purus.
+Donec
     bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
@@
     amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-    Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-    quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
+    Nunc elementum fermentum wisi.
+Aenean placerat.
+Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat quam, ac pulvinar elit purus eget enim.
+Nunc vitae tortor.
+Proin tempus nibh sit amet nisl.
+Vivamus quis tortor
     vitae risus porta vehicula.
 
-    Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-    venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-    quam, in hendrerit risus eros eget felis.
+    Fusce mauris.
+Vestibulum luctus nibh at lectus.
+Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac venenatis arcu wisi vel nisl.
+Vestibulum diam.
+Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue quam, in hendrerit risus eros eget felis.
 Maecenas eget erat in sapien mattis porttitor.
@@
 Sed a turpis eu lacus commodo facilisis.
-Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-    vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
+Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et vehicula libero dui cursus dui.
+Mauris tempor ligula sed lacus.
+Duis cursus enim ut augue.
+Cras ac magna.
+Cras nulla.
     Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
@@
 
-    Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-    ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-    eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-    convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
+    Suspendisse vel felis.
+Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu.
+Aenean faucibus pede eu ante.
+Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl.
+Ut lectus eros, malesuada sit amet, fermentum
+    eu, sodales cursus, magna.
+Donec eu purus.
+Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, and convallis elit erat sed nulla.
+Donec luctus.
+Curabitur et nunc.
+Aliquam dolor odio, commodo pretium, ultricies non,
     pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
@@
     Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-    odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
+    odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non-elit. Fusce
     sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
-    Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
-    et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
-    turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
+    Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus.
+Proin et quam.
+Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos.
+Praesent sapien turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
 
@@
     Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit, dictum
-    in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam vestibulum
-    fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi. Pellentesque
+    in, hendrerit sit amet, egestas sed, leo.
+Praesent feugiat sapien aliquet odio.
+Integer vitae justo.
+Aliquam vestibulum fringilla lorem.
+Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus.
+Nulla facilisi.
+Pellentesque
     eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut mi mi, lacinia
@@
 
-    Morbi luctus, wisi viverra faucibus pretium, nibh est placerat odio, nec commodo wisi enim eget quam. Quisque
-    libero justo, consectetuer a, feugiat vitae, porttitor eu, libero. Suspendisse sed mauris vitae elit sollicitudin malesuada.
+    Morbi luctus, wisi viverra faucibus pretium, nibh est placerat odio, nec commodo wisi enim eget quam.
+Quisque libero justo, consectetuer a, feugiat vitae, porttitor eu, libero.
+Suspendisse sed mauris vitae elit sollicitudin malesuada.
 
     Maecenas ultricies eros sit amet ante. Ut venenatis velit. Maecenas sed mi eget dui varius euismod. Phasellus aliquet
-    volutpat odio. Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque sit
-    amet pede ac sem eleifend consectetuer. Nullam elementum, urna vel imperdiet sodales, elit ipsum pharetra ligula,
-    ac pretium ante justo a nulla. Curabitur tristique arcu eu metus. Vestibulum lectus. Proin mauris. Proin eu nunc eu
-    urna hendrerit faucibus. Aliquam auctor, pede consequat laoreet varius, eros tellus scelerisque quam, pellentesque
-    hendrerit ipsum dolor sed augue. Nulla nec lacus.
+    volutpat odio.
+Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque sit amet pede ac sem eleifend consectetuer.
+Nullam elementum, urna vel imperdiet sodales, elit ipsum pharetra ligula,
+    ac pretium ante justo a nulla.
+Curabitur tristique arcu eu metus.
+Vestibulum lectus.
+Proin mauris.
+Proin eu nunc eu urna hendrerit faucibus.
+Aliquam auctor, pede consequat laoreet varius, eros tellus scelerisque quam, pellentesque hendrerit ipsum dolor sed augue.
+Nulla nec lacus.
 
@@
     erat tristique mollis. Maecenas sapien libero, molestie et, lobortis in, sodales eget, dui. Morbi ultrices rutrum lorem.
-    Nam elementum ullamcorper leo. Morbi dui. Aliquam sagittis. Nunc placerat. Pellentesque tristique sodales est.
+    Nam elementum ullamcof aaer leo. Morbi dui. Aliquam sagittis. Nunc placerat. Pellentesque tristique sodales est.
     Maecenas imperdiet lacinia velit. Cras non urna. Morbi eros pede, suscipit ac, varius vel, egestas non, eros. Praesent

### 2023-08-24 paper/ETRIJ.tex
Updates from Overleaf

--- 2023-08-10 ams/wileyNJD-AMS_2COL.tex
@@
         Through experiments, we showed that the proposed method effectively improved performance by reducing errors by more than 40\% in both the spoken language model and the written language model.
+    }
     %한국어 형태소 분석은 한국어 분석의 첫걸음이라고 할 정도로 기본적이고 중요한 역할을 담당하고 있다.
@@
     %실험을 통해 제안하는 방법을 통해 구어체 모델과 문어체 모델에서 모두 기존보다 오류가 40% 이상 감소됨 보임으로 제안한 방법이 효과적으로 성능을 개선하였음을 보였다.
-    }
 
@@
     In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
-    Modern, high-performance deep learning methods in natural language processing use a tokenisation process that breaks text into smaller units, and then converts each token into a vector as input to the computational model [Milkolov2013].
-    In this case, the token unit is mainly subword units, and to reflect the characteristics of Korean, subword tokenisation is attempted with separated morphemes in advance. [Song2021]
+    Modern, high-performance deep learning methods in natural language processing use a tokenisation process that breaks text into smaller units, and then converts each token into a vector as input to the computational model~\cite{Mikolov2013}.
+    In this case, the token unit is mainly subword units, and to reflect the characteristics of Korean, subword tokenisation is attempted with separated morphemes in advance~\cite{Song2021}.
     Using the results of morphological analysis for this tokenisation process improves the overall performance of the analysis by reflecting the semantic units of Korean, but requires a highly accurate and fast morphological analyzer.
@@
     %또한 다른 한국어 분석 태스크들의 기본 입력이 분리된 형태소인 경우가 많아, 형태소 분석의 정확도는 한국어 분석의 성능에 큰 영향을 미치게 된다.
-    %자연어처리 분야에 높은 성능을 자랑하는 최신의 딥러닝 방법들에서는 텍스트를 작은 단위로 분리하는 토큰화 과정을 거친 뒤, 각 토큰을 벡터로 변환하여 입력으로 사용한다. [Milkolov2013]
-    %이 때의 토큰 단위는 주로 서브워드 단위를 많이 사용하는 추세이고, 한국어의 특성을 반영하여 형태소를 미리 분리한 상태에서 서브워드 토큰화를 시도하기도 한다. [Song2021]
+    %자연어처리 분야에 높은 성능을 자랑하는 최신의 딥러닝 방법들에서는 텍스트를 작은 단위로 분리하는 토큰화 과정을 거친 뒤, 각 토큰을 벡터로 변환하여 입력으로 사용한다.
+    %이 때의 토큰 단위는 주로 서브워드 단위를 많이 사용하는 추세이고, 한국어의 특성을 반영하여 형태소를 미리 분리한 상태에서 서브워드 토큰화를 시도하기도 한다.
     %이러한 토큰화 과정에 형태소 분석 결과를 사용하게 되면 한국어의 의미 단위를 반영할 수 있어 전반적인 분석 성능이 좋아지지만, 정확도가 높으면서 빠른 형태소 분석기를 필요로 하게 된다.
@@
     Hence, methods for tagging in syllable units without a dictionary have been proposed [...], and studies to improve them have been continuously conducted. [...]
-    From a mechanical point of view, syllable-by-syllable morphological analysis can be done either by tagging syllable-by-syllable and then applying a base form restoration dictionary [...], or by tagging syllable-by-syllable with the base form already restored.
-[...]
-    However, syllable-by-syllable morphological analysis has limitations in that it is difficult to accurately identify the boundaries of morphemes, and it is difficult to learn long-term contextual information as the length of the sequence increases.
-    In this paper, the former is referred to as dictionary-based morphological analysis, and the latter as syllable unit morphological analysis.
+    From a mechanical point of view, syllable-by-syllable morphological analysis can be done either by tagging syllable-by-syllable and then applying a base form restoration dictionary~\cite{Lee2016}, or by tagging syllable-by-syllable with the base form already restored~\cite{Youn2021}.
+    However, syllable-by-syllable morphological analysis has limitations in that it is difficult to accurately identify the boundaries of morphemes and it is difficult to learn long-term contextual information as the length of the sequence increases.
+    In this paper, the former is referred to as dictionary-based morphological analysis, and the latter is referred to as syllable unit morphological analysis.
     Both methods also share the limitation that they are trained on a manually labelled corpus and cannot perform accurate analysis of new syllable combinations or morphemes that do not appear in the training corpus.
@@
 
-    %이렇게 한국어 분석에서 기본적이고 중요한 역할을 담당해오는 형태소 분석에 대해서 다양한 접근법들이 제안되어 왔다.
+    %이렇게 한국어 분석에서 기본적이고 중요한 역할을 담당해오는 형태소 분석에 대해서 다양한 접근법들이 제안되어 왔다. [...]
     %일반적으로 사람들은 말이나 글을 이해할 때 자신이 알고 있는 어휘와 개념들을 이용해서 그것을 이해하려고 한다.
-    %이와 같은 사람들의 이해 방식을 따라 규칙이나 사전을 사용한 방법들이 있었지만, 모든 텍스트에서 등장하는 어휘에 대한 사전을 구축하고 유지하는 것이 어렵게 되는 문제가 있었다.
-    %이에 사전 없이 음절 단위로 태깅하는 방법들이 제안되었고, 계속해서 이를 개선하는 연구들이 진행되어 왔다.
-    %음절 단위 형태소 분석은 기계적인 관점에서 음절 단위로 태깅 후 원형복원 사전을 적용하거나, 원형을 미리 복원한 상태에서 음절 단위로 태깅하는 방법이 있다.
+    %이와 같은 사람들의 이해 방식을 따라 규칙이나 사전을 사용한 방법들이 있었지만 [...], 모든 텍스트에서 등장하는 어휘에 대한 사전을 구축하고 유지하는 것이 어렵게 되는 문제가 있었다.
+    %이에 사전 없이 음절 단위로 태깅하는 방법들이 제안되었고 [...], 계속해서 이를 개선하는 연구들이 진행되어 왔다. [...]
+    %음절 단위 형태소 분석은 기계적인 관점에서 음절 단위로 태깅 후 원형복원 사전을 적용하거나 [Lee2016], 원형을 미리 복원한 상태에서 음절 단위로 태깅하는 방법이 있다. [2021Youn]
     %그러나 음절 단위 형태소 분석은 형태소의 경계를 정확하게 파악하기 힘든 면과 시퀀스의 길이가 길어지면서 장기적인 문맥 정보를 학습하기 어려운 면도 있다.
@@
 
-    Against this background, this paper considers how the dictionary-based morphological analysis method used by MeCab, an open software used for Korean and Japanese morphological analysis in tokenisers, an essential tool for preprocessing for deep learning, can be effectively improved through deep learning, and proposes a method.
-    The dictionary-based morphological analysis method[Kudo2004, Na2014] trained by the CRF method[Sutton2012] lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph, and finds the optimal morphological analysis path within it.
-    The process of finding the best path in Lattice uses the Viterbi algorithm[Forney1973], which finds the path that minimises the cost of each morpheme node and the sum of the neighbouring costs of two consecutive morphemes.
-    The main types of errors in these dictionary-based morphological analysis methods are when new words not in the dictionary are used in a sentence, or when the optimal path calculation selects the wrong result due to a bias.
+    Against this background, this paper considers how the dictionary-based morphological analysis method used by MeCab [...], an open software used for Korean and Japanese morphological analysis in tokenisers, an essential tool for preprocessing for deep learning, can be effectively improved through deep learning, and proposes a method.
+    The dictionary-based morphological analysis method[Kudo2004, Na2014] trained by the CRF method [Sutton2012] lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph, and finds the optimal morphological analysis path within it.
+    The process of finding the best path in Lattice uses the Viterbi algorithm[Forney1973], which finds the path that minimizes the cost of each morpheme node and the sum of the neighboring costs of two consecutive morphemes.
+    The main types of errors in these dictionary-based morphological analysis methods are when new words not in the dictionary are used in a sentence or when the optimal path calculation selects the wrong result due to a bias.
     For example, it may be less costly to choose one long morpheme than to choose several short ones, but it can sometimes be the wrong analysis.
@@
 
-    %이러한 배경하에서 본 논문에서는 딥러닝을 위한 전처리의 필수 도구인 토큰화기에서 한국어 및 일본어 형태소 분석을 위해 사용되는 공개 소프트웨어인 MeCab에서 사용하는 사전 기반 형태소 분석 방법을 딥러닝을 통해 효과적으로 개선할 수 있는 방법에 대해 고려하고 방법을 제안하고자 한다.
-    %CRF 방법으로 학습하는 사전 기반 형태소 분석 방법은 주어진 문장으로부터 사전에 있는 선택가능한 형태소 후보들을 나열하여 방향성 있는 그래프로 연결한 Lattice 구조를 형성하고, 그 안에서 최적의 형태소 분석 경로를 찾아내는 방법이다.
-    %Lattice에서 최적의 경로를 찾아내는 과정은 Viterbi 알고리즘을 사용하며, 이 때의 경로는 각 형태소 노드에 대한 비용과 연속적인 두 형태소의 인접 비용의 합이 최소가 되는 경로를 찾아내는 것이다.
+    %이러한 배경하에서 본 논문에서는 딥러닝을 위한 전처리의 필수 도구인 토큰화기에서 한국어 및 일본어 형태소 분석을 위해 사용되는 공개 소프트웨어인 MeCab [...]에서 사용하는 사전 기반 형태소 분석 방법을 딥러닝을 통해 효과적으로 개선할 수 있는 방법에 대해 고려하고 방법을 제안하고자 한다.
+    %CRF 방법으로 학습하는 사전 기반 형태소 분석 방법[Kudo2004, Na2014]은 주어진 문장으로부터 사전에 있는 선택가능한 형태소 후보들을 나열하여 방향성 있는 그래프로 연결한 Lattice 구조를 형성하고, 그 안에서 최적의 형태소 분석 경로를 찾아내는 방법이다.
+    %Lattice에서 최적의 경로를 찾아내는 과정은 Viterbi 알고리즘[Forney1973]을 사용하며, 이 때의 경로는 각 형태소 노드에 대한 비용과 연속적인 두 형태소의 인접 비용의 합이 최소가 되는 경로를 찾아내는 것이다.
     %이러한 사전 기반 형태소 분석 방법에서의 주된 오류 유형은 사전에 없는 새로운 어휘가 문장에서 사용된 경우이거나, 최적 경로 계산 시에 잘못된 편견으로 인해 오분석 결과를 선택한 경우이다.
@@
     Previously, in [Choi2018], N-Best analysis results generated by the seq2seq model were re-ranked based on a convolutional neural network to improve performance.
-    In this study, reranking was performed using two BERT models of different types and forms as proposed in [Nogueira2019].
+    In this study, re-ranking was performed using two BERT models of different types and forms as proposed in ~\cite{Nogueira2019}.
     The experimental results show that the first-stage reranking improves performance by more than 34\% from the previous written and spoken models, and the second-stage reranking with a different type of input and a different kind of pre-trained model further improves performance by more than 40\% the previous written and spoken models.
@@
 
-    Through this method, the performance of the dictionary-based morphological analysis method could be further improved, but the analysis speed slows down when the morphological analysis system is configured including the re-ranking model itself.
+    Through this method, the performance of the dictionary-based morphological analysis method could be further improved, but the overall analysis time increases when the morphological analysis system is configured including the re-ranking model itself.
     However, it is possible to use the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in the dictionary, similar to the backpropagation process in a typical neural network.
@@
     The main contributions of this study are as follows:
-    \begin{itemize}
-        \item 1.
-[Further improvement of dictionary-based morphological analysis method using suboptimal analysis results]: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node, and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
-        \item 2.
-[Extend the performance improvement by introducing a two-stage reranking model]: To improve the performance of dictionary-based analysis by reranking the morphological analysis results, we propose to extend the performance improvement by using different BERT models to perform two rounds of reranking.
-        \item 3.
-[A method for updating connection costs in dictionary and suggestions for future research]: We propose a new method for updating dictionary connection costs based on the results of re-ranked morphological analysis, and provide directions for future research by suggesting improvements and directions for future research.
-    \end{itemize}
+    \begin{enumerate}
+        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node, and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
+        \item \textbf{Extend the performance improvement by introducing a two-stage re-ranking model}: To improve the performance of dictionary-based analysis by reranking the morphological analysis results, we propose to extend the performance improvement by using different BERT models to perform two rounds of reranking.
+        \item \textbf{A method for updating connection costs in dictionary and suggestions for future research}: We propose a new method for updating dictionary connection costs based on the results of re-ranked morphological analysis, and provide directions for future research by suggesting improvements and directions for future research.
+    \end{enumerate}
     These contributions provide important insights into the performance improvement of Korean morphological analysis and the direction of future research, and will serve as a useful reference for future researchers.
 
-    %이러한 방법을 통해 사전 기반 형태소 분석 방법의 성능을 추가로 개선할 수 있었으나, 재순위화 모델 자체를 포함하여 형태소 분석 시스템을 구성하게 되면 분석 속도가 느려지는 문제가 발생한다.
+    %이러한 방법을 통해 사전 기반 형태소 분석 방법의 성능을 추가로 개선할 수 있었으나, 재순위화 모델 자체를 포함하여 형태소 분석 시스템을 구성하게 되면 전체적인 분석 시간이 늘어나는 문제가 발생한다.
     %그러나 재순위화된 여러 형태소 분석 결과들을 사용해서 일반적인 Neural Network의 Back Propagration과정처럼 사전 상의 형태소 간의 연결 비용을 업데이트하는 방식을 적용해볼 수 있다.
@@
 
-    This paper is organised as follows:
-    In section 2, we introduce previous research cases related to this study, and in section 3, we discuss how to configure and train a dictionary-based morphological analysis system.
-    In section 4, we discuss how to generate secondary results of morphological analysis and create re-ranking data, and propose a method to train a two-stage re-ranking model.
-    In section 5, we discuss the results of performance improvement through morphological analysis model and re-ranking model, and in section 6, we discuss error analysis and performance improvement cases.
-    Finally, in section 7, we conclude the paper and discuss the limitations of this study and the direction of future research.
+    This paper is organized as follows:
+    In Section 2, we introduce previous research cases related to this study, and in Section 3, we discuss how to configure and train a dictionary-based morphological analysis system.
+    In Section 4, we discuss how to generate secondary results of morphological analysis and create re-ranking data, and propose a method to train a two-stage re-ranking model.
+    In Section 5, we discuss the results of performance improvement through morphological analysis model and re-ranking model, and in Section 6, we discuss error analysis and performance improvement cases.
+    Finally, in Section 7, we conclude the paper and discuss the limitations of this study and the direction of future research.
 
@@
 
-    \section{Sample for first level head}\label{secX}
+    \section{Related Work}\label{sec2}
 
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit~\cite{Rothermel1997} Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
-    felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
-    vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-    Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-    sit amet tortor gravida placerat.
-Integer sapien est, iaculis in, pretium quis, viverra ac, nunc.
-Praesent eget sem vel leo ultrices bibendum.
-Aenean faucibus.
-Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla.
-Curabitur
-    auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-    Duis eget orci sit amet orci dignissim rutrum.
-    \begin{eqnarray}
-        s(nT_{s}) &= &s(t)\times \sum\limits_{n=0}^{N-1} \delta (t-nT_{s}) \xleftrightarrow{\mathrm{DFT}}  S \left(\frac{m}{NT_{s}}\right) \nonumber\\
-        &= &\frac{1}{N} \sum\limits_{n=0}^{N-1} \sum\limits_{k=-N/2}^{N/2-1} s_{k} e^{\mathrm{j}2\pi k\Delta fnT_{s}} e^{-j\frac{2\pi}{N}mn}
-    \end{eqnarray}
+    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of language expression that have an independent meaning in a sentence.
+    In an isolating language like English, this can be done relatively simply by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
+    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
 
-    \section{Sample for another first level head \cite{Rothermel1998}}\label{sec2}
+    %본 연구와 관련한 이전 연구 사례들을 소개
 
-    Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus viverra
-    fermentum felis.
-Donec nonummy pellentesque ante.
-Phasellus adipiscing semper elit.
-Proin fermentum massa ac quam.
-Sed diam turpis, molestie vitae, placerat a, molestie nec, leo \cite{Elbaum2002} Maecenas lacinia.
-Nam ipsum ligula, eleifend at, accumsan nec, suscipit a, ipsum.
-Morbi blandit ligula feugiat magna.
-Nunc eleifend consequat lorem.
-Sed lacinia nulla vitae enim.
-Pellentesque tincidunt purus vel magna.
-Integer non enim.
-Praesent euismod nunc eu purus.
-Donec
-    bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-    pellentesque felis eu massa.
+    \section{Dictionary-Based Morphological Analysis Model}\label{sec3}
 
-    Example for bibliography citations cite~\citep{Elbaum2002}, cites~\cite{Allen2011,Yoo2007}
+    A representative corpus for training Korean morphological analysis models is the Sejong Morphological Analysis Corpus (also known as the Sejong Corpus).
+    The Sejong corpus was built as a major output of the 21st Century Sejong Project with 15 million words [Choi2008] and is the most used corpus for Korean morphological analysis research.
+    Since then, the limitations of the Sejong corpus have been discussed [Kim2010], Ulsan University has released a morphological analysis corpus that corrects errors in the Sejong corpus [AIOpen], and the National Institute of the Korean Language released the newly built corpus in 2018 through a large-scale Korean corpus construction project, including plans for corpus maintenance and construction.
+[Kim2018]
+    For morphological analysis, a morphological analysis corpus of 3 million words, including spoken language, was built through the morphological analysis corpus construction project [2019Kim].
 
-    Quisque ullamcorper placerat ipsum. Cras nibh~\cite{Yoo2007,Schulz2012} Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-    amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-    Nunc elementum fermentum wisi.
-Aenean placerat.
-Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat quam, ac pulvinar elit purus eget enim.
-Nunc vitae tortor.
-Proin tempus nibh sit amet nisl.
-Vivamus quis tortor
-    vitae risus porta vehicula.
+    %한국어 형태소 분석 모델을 학습하기 위한 대표적인 말뭉치로는 세종 형태의미분석 말뭉치(세종 코퍼스로도 알려짐)가 있다.
+    %세종 코퍼스는 21세기 세종 프로젝트의 주요한 결과물로 1500만 어절 규모로 구축되었으며 [2008최민우], 한국어 형태소 분석 연구에서 가장 많이 사용하는 말뭉치이다.
+    %이후 세종 코퍼스의 한계들이 거론이 되었고 [2010김일환], 울산대학교에서는 세종 코퍼스의 오류를 교정한 형태의미분석 말뭉치를 배포하였으며 [AIOpen], 국립국어원에서는 2018년에 대규모 한국어 말뭉치 구축 사업을 통해 말뭉치 정비 및 구축 계획을 포함하여 새롭게 구축한 말뭉치들을 공개하였다. [2018김한샘]
+    %형태소 분석에 관해서는 형태 분석 말뭉치 구축 사업 [2019김일환]을 통해 구어를 포함한 300만 어절 규모의 형태 분석 말뭉치가 구축되었다.
 
-    Fusce mauris.
-Vestibulum luctus nibh at lectus.
-Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac venenatis arcu wisi vel nisl.
-Vestibulum diam.
-Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue quam, in hendrerit risus eros eget felis.
-Maecenas eget erat in sapien mattis porttitor.
-Vestibulum porttitor.
-Nulla facilisi.
-Sed a turpis eu lacus commodo facilisis.
-Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et vehicula libero dui cursus dui.
-Mauris tempor ligula sed lacus.
-Duis cursus enim ut augue.
-Cras ac magna.
-Cras nulla.
-    Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-    \begin{figure*}[t]
-        \centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
-        \caption{This is the sample figure caption.\label{fig1}}
-    \end{figure*}
-
-    Suspendisse vel felis.
-Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu.
-Aenean faucibus pede eu ante.
-Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl.
-Ut lectus eros, malesuada sit amet, fermentum
-    eu, sodales cursus, magna.
-Donec eu purus.
-Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, and convallis elit erat sed nulla.
-Donec luctus.
-Curabitur et nunc.
-Aliquam dolor odio, commodo pretium, ultricies non,
-    pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-    Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-    odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non-elit. Fusce
-    sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
-    Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus.
-Proin et quam.
-Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos.
-Praesent sapien turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-    \begin{figure*}
-        \centerline{\includegraphics[width=342pt,height=9pc,draft]{empty}}
-        \caption{This is the sample figure caption.\label{fig2}}
-    \end{figure*}
-
-    \subsection{Example for second level head}
-
-    Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit, dictum
-    in, hendrerit sit amet, egestas sed, leo.
-Praesent feugiat sapien aliquet odio.
-Integer vitae justo.
-Aliquam vestibulum fringilla lorem.
-Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus.
-Nulla facilisi.
-Pellentesque
-    eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut mi mi, lacinia
-    sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui. Mauris nibh leo,
-    facilisis non, adipiscing quis, ultrices a, dui.
-
-    Morbi luctus, wisi viverra faucibus pretium, nibh est placerat odio, nec commodo wisi enim eget quam.
-Quisque libero justo, consectetuer a, feugiat vitae, porttitor eu, libero.
-Suspendisse sed mauris vitae elit sollicitudin malesuada.
-
-    Maecenas ultricies eros sit amet ante. Ut venenatis velit. Maecenas sed mi eget dui varius euismod. Phasellus aliquet
-    volutpat odio.
-Vestibulum ante ipsum primis in faucibus orci luctus et ultrices posuere cubilia Curae; Pellentesque sit amet pede ac sem eleifend consectetuer.
-Nullam elementum, urna vel imperdiet sodales, elit ipsum pharetra ligula,
-    ac pretium ante justo a nulla.
-Curabitur tristique arcu eu metus.
-Vestibulum lectus.
-Proin mauris.
-Proin eu nunc eu urna hendrerit faucibus.
-Aliquam auctor, pede consequat laoreet varius, eros tellus scelerisque quam, pellentesque hendrerit ipsum dolor sed augue.
-Nulla nec lacus.
-
-    \begin{quote}
-        This is an example~\citep{Elbaum2002,Blanchard2015} for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text~\cite{Blanchard2015}.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text~\cite{Blanchard2015}.
-This is an example for quote text.
-This is an example for quote text.
-This is an example for quote text.
-    \end{quote}
-
-    \section{Sample for next first level head}\label{sec3}
-
-    \subsection{Example for another second level head}
-
-    Suspendisse vitae elit. Aliquam arcu neque, ornare in, ullamcorper quis, commodo eu, libero. Fusce sagittis erat at
-    erat tristique mollis. Maecenas sapien libero, molestie et, lobortis in, sodales eget, dui. Morbi ultrices rutrum lorem.
-    Nam elementum ullamcof aaer leo. Morbi dui. Aliquam sagittis. Nunc placerat. Pellentesque tristique sodales est.
-    Maecenas imperdiet lacinia velit. Cras non urna. Morbi eros pede, suscipit ac, varius vel, egestas non, eros. Praesent
-    malesuada, diam id pretium elementum, eros sem dictum tortor, vel consectetuer odio sem sed wisi.
-
-    Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
-    augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
-    ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
-    Aenean vel lectus. Nunc imperdiet justo nec dolor.
-
-    \subsection{Second level head text}
-
-    Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-    eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-    facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-    a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-    convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-
-    \subsubsection{Third level head text}
-
-    Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
-    justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
-    sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
-    in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-    Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
-    lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
-    purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
-    In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
-    Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
-    porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
-    Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
-    Vivamus eu dolor.
-
-    Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
-    tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
-    ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis
-    in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
-    eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
-    pulvinar in, cursus faucibus, augue.
-
-    \begin{boxtext}
-        \noindent{\bf Example of Boxtext\ }\\
-        This is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext this is sample for boxtext.
-    \end{boxtext}
-
-    \paragraph{Fourth level head text}
-
-    Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
-    augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
-    ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
-    Aenean vel lectus. Nunc imperdiet justo nec dolor.
-
-    Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-    eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-    facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-    a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-    convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-
-    \subparagraph{Fifth level head text}
-
-    Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
-    tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
-    est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
-    urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-    Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
-    lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
-    purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
-    In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
-    Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
-    porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
-    Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
-    Vivamus eu dolor.
-
-    in faucibus orci luctus et ultrices posuere cubilia Curae; Proin ut est. Aliquam odio. Pellentesque massa turpis, cursus
-    eu, euismod nec, tempor congue, nulla. Duis viverra gravida mauris. Cras tincidunt. Curabitur eros ligula, varius ut,
-    pulvinar in, cursus faucibus, augue.
-
-    Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor. Donec interdum. Praesent scelerisque. Mae-
-    cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
-    elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,
-    nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
-    consectetuer adipiscing elit. Etiam congue neque id dolor.
-
-    Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
-    adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
-    Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
-    faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
-    taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
-    Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
-    sed nisl eu sapien cursus rutrum.
-
-    Nulla non mauris vitae wisi posuere convallis. Sed eu nulla nec eros scelerisque pharetra. Nullam varius. Etiam
-    dignissim elementum metus. Vestibulum faucibus, metus sit amet mattis rhoncus, sapien dui laoreet odio, nec ultricies
-    nibh augue a enim. Fusce in ligula. Quisque at magna et nulla commodo consequat. Proin accumsan imperdiet sem.
-    Nunc porta. Donec feugiat mi at justo. Phasellus facilisis ipsum quis ante. In ac elit eget ipsum pharetra faucibus.
-    Maecenas viverra nulla in massa.
-
-    Nulla in ipsum. Praesent eros nulla, congue vitae, euismod ut, commodo a, wisi. Pellentesque habitant morbi
-    tristique senectus et netus et malesuada fames ac turpis egestas. Aenean nonummy magna non leo. Sed felis erat,
-    ullamcorper in, dictum non, ultricies ut, lectus. Proin vel arcu a odio lobortis euismod. Vestibulum ante ipsum primis
-
-    \begin{center}
-        \begin{table*}[t]%
-            \caption{This is sample table caption.\label{tab1}}
-            \centering
-            \begin{tabular*}{500pt}{@{\extracolsep\fill}lccD{.}{.}{3}c@{\extracolsep\fill}}
-                \toprule
-                & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{1}}} & \multicolumn{2}{@{}c@{}}{\textbf{Spanned heading\tnote{2}}} \\\cmidrule{2-3}\cmidrule{4-5}
-                \textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{@{}l@{}}{\textbf{col4 head}}  & \textbf{col5 head}   \\
-                \midrule
-                col1 text          & col2 text          & col3 text          & 12.34                                        & col5 text\tnote{1} \\
-                col1 text          & col2 text          & col3 text          & 1.62                                         & col5 text\tnote{2} \\
-                col1 text          & col2 text          & col3 text          & 51.809                                       & col5 text          \\
-                \bottomrule
-            \end{tabular*}
-            \begin{tablenotes}%%[341pt]
-                \item Source: Example for table source text.
-                \item[1] Example for a first table footnote.
-                \item[2] Example for a second table footnote.
-            \end{tablenotes}
-        \end{table*}
-    \end{center}
-
-    Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-    venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-    quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-    facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-    vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-    Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-    \begin{center}
-        \begin{table*}[t]%
-            \centering
-            \caption{This is sample table caption.\label{tab2}}%
-            \begin{tabular*}{500pt}{@{\extracolsep\fill}lcccc@{\extracolsep\fill}}
-                \toprule
-                \textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} & \textbf{col4 head} & \textbf{col5 head}          \\
-                \midrule
-                col1 text          & col2 text          & col3 text          & col4 text          & col5 text\tnote{$\dagger$}  \\
-                col1 text          & col2 text          & col3 text          & col4 text          & col5 text                   \\
-                col1 text          & col2 text          & col3 text          & col4 text          & col5 text\tnote{$\ddagger$} \\
-                \bottomrule
-            \end{tabular*}
-            \begin{tablenotes}
-                \item Source: Example for table source text.
-                \item[$\dagger$] Example for a first table footnote.
-                \item[$\ddagger$] Example for a second table footnote.
-            \end{tablenotes}
-        \end{table*}
-    \end{center}
-
-    Below is the example~\cite{Rothermel1998,Yoo2007,Schulz2012} for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list.
-Below is the example for bulleted list\footnote{This is an example for footnote.}:
-    \begin{itemize}
-        \item bulleted list entry sample bulleted list entry~\cite{Allen2011} sample list entry text.
-        \item bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry. bulleted list entry sample bulleted list entry.
-        \item bulleted list entry sample bulleted list entry~\cite{Ballen2011} bulleted list entry sample bulleted list entry~\citet{Allen2011} sample list entry text.
-bulleted list entry sample bulleted list entry.
-        \item sample list entry text. sample list entry text.
-    \end{itemize}
-
-    Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-    ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-    eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-    convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-    pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-    Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-    odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
-    sed justo eu urna porta tincidunt.
-Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat.
-Morbi quis dolor.
-Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus.
-Proin
-    et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
-    turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-    Below is the sample for description list.
-Below is the example for description list.
-Below is the example for description list.
-Below is the example for description list.
-Below is the example for description list.
-Below is the example for description list:\\[12pt]
-
-    \noindent\textbf{Description sample:}
-
-    \begin{description}
-        \item[first entry] description text. description text. description text. description text. description text. description text. description text.
-        \item[second long entry] description text. description text. description text. description text. description text. description text. description text.
-        \item[third entry] description text. description text. description text. description text. description text.
-        \item[fourth entry] description text. description text.
-    \end{description}
-
-    \noindent\textbf{Numbered list items sample:}
-
-    \begin{enumerate}[1.]
-        \item First level numbered list entry. sample numbered list entry.
-
-        \item First numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry.
-
-        \begin{enumerate}[a.]
-            \item Second level alpabetical list entry. Second level alpabetical list entry. Second level alpabetical list entry~\citet{Allen2011} Second level alpabetical list entry.
-
-            \item Second level alpabetical list entry. Second level alpabetical list entry~\citet{Schulz2012,Allen2011,Ballen2011}.
-
-            \begin{enumerate}[ii.]
-                \item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry.
-
-                \item Third level lowercase roman numeral list entry. Third level lowercase roman numeral list entry~\cite{Yoo2007}.
-            \end{enumerate}
-
-            \item Second level alpabetical list entry. Second level alpabetical list entry~\cite{Elbaum2002}.
-        \end{enumerate}
-
-        \item First level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry.
-
-        \item Another first level numbered list entry. sample numbered list entry. Numbered list entry. sample numbered list entry. Numbered list entry.
-    \end{enumerate}
-
-    \noindent\textbf{un-numbered list items sample:}
-
-    \begin{enumerate}[]
-        \item Sample unnumberd list text..
-        \item Sample unnumberd list text.
-        \item sample unnumberd list text.
-        \item Sample unnumberd list text.
-    \end{enumerate}
-
-    \section{Examples for enunciations}\label{sec4}
-
-    \begin{theorem}[Theorem subhead]
-        \label{thm1}
-        Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-Example theorem text.
-    \end{theorem}
-
-    Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-    amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-    Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-    quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-    vitae risus porta vehicula.
-
-    Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-    venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-    quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-    facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-    vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-    Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-    \begin{proposition}
-        Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-Example proposition text.
-    \end{proposition}
-
-    Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-    viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-    ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-    at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-    nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-    bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-    pellentesque felis eu massa.
-
-    Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-    amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-    Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-    quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-    vitae risus porta vehicula.
-
-    \begin{definition}[Definition sub head]
-        Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-Example definition text.
-    \end{definition}
-
-    Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non
-    odio. Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce
-    sed justo eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor.
-    Donec pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin
-    et quam. Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien
-    turpis, fermentum vel, eleifend faucibus, vehicula eu, lacus.
-
-    Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-    dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-    vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-    Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
-    mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
-    Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.
-
-    \begin{proof}
-        Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-    \end{proof}
-
-    Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-    pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-    vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-    a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-    urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-    Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-    viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-    ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-    at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-    nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-    bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-    pellentesque felis eu massa.
-
-    \begin{proof}[Proof of Theorem~\ref{thm1}]
-        Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-Example for proof text.
-    \end{proof}
-
-    Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-    eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-    facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-    a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-    convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-    Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra tortor. Sed fringilla
-    justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue est scelerisque
-    sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas urna mi, suscipit
-    in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-    Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-    dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-    vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-    Pellentesque eget lectus.
-Proin eu metus.
-Sed porttitor.
-In hac habitasse platea dictumst.
-Suspendisse eu lectus.
-Ut Curabitur tellus magna, porttitor a, commodo a, commodo in, tortor.
-Donec interdum.
-Praesent scelerisque.
-Mae-
-    cenas posuere sodales odio. Vivamus metus lacus, varius quis, imperdiet quis, rhoncus a, turpis. Etiam ligula arcu,
-    elementum a, venenatis quis, sollicitudin sed, metus. Donec nunc pede, tincidunt in, venenatis vitae, faucibus vel,
-
-    \begin{sidewaystable}%[h]
-        \caption{Sideways table caption. For decimal alignment refer column 4 to 9 in tabular* preamble.\label{tab3}}%
-        \begin{tabular*}{\textheight}{@{\extracolsep\fill}lccD{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}D{.}{.}{4}@{\extracolsep\fill}}%
-            \toprule
-            & \textbf{col2 head} & \textbf{col3 head} & \multicolumn{1}{c}{\textbf{10}} & \multicolumn{1}{c}{\textbf{20}} & \multicolumn{1}{c}{\textbf{30}} & \multicolumn{1}{c}{\textbf{10}} & \multicolumn{1}{c}{\textbf{20}} & \multicolumn{1}{c}{\textbf{30}} \\
-            \midrule
-            & col2 text          & col3 text          & 0.7568                          & 1.0530                          & 1.2642                          & 0.9919                          & 1.3541                          & 1.6108                          \\
-            &                    & col2 text          & 12.5701                         & 19.6603                         & 25.6809                         & 18.0689                         & 28.4865                         & 37.3011                         \\
-            3 & col2 text          & col3 text          & 0.7426                          & 1.0393                          & 1.2507                          & 0.9095                          & 1.2524                          & 1.4958                          \\
-            &                    & col3 text          & 12.8008                         & 19.9620                         & 26.0324                         & 16.6347                         & 26.0843                         & 34.0765                         \\
-            & col2 text          & col3 text          & 0.7285                          & 1.0257                          & 1.2374                          & 0.8195                          & 1.1407                          & 1.3691\tnote{*}                 \\
-            &                    & col3 text          & 13.0360                         & 20.2690                         & 26.3895                         & 15.0812                         & 23.4932                         & 30.6060\tnote{\dagger}          \\
-            \bottomrule
-        \end{tabular*}
-        \begin{tablenotes}%%[\textheight]
-            \item[*] First sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
-            \item[$\dagger$] Second sideways table footnote. Sideways table footnote. Sideways table footnote. Sideways table footnote.
-        \end{tablenotes}
-    \end{sidewaystable}
-
-    \begin{sidewaysfigure}
-        \centerline{\includegraphics[width=542pt,height=9pc,draft]{empty}}
-        \caption{Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption. Sideways figure caption.\label{fig3}}
-    \end{sidewaysfigure}
-
-    nibh. Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
-    consectetuer adipiscing elit. Etiam congue neque id dolor.
-
-    \begin{algorithm}
-        \caption{Pseudocode for our algorithm}\label{alg1}
-        \begin{algorithmic}
-            \For
-                each frame
-                \For
-                    water particles $f_{i}$
-                    \State compute fluid flow~\cite{Rothermel1997}
-                    \State compute fluid--solid interaction~\cite{Allen2011}
-                    \State apply adhesion and surface tension~\cite{Ballen2011}
-                \EndFor
-                \For
-                    solid particles $s_{i}$
-                    \For
-                        neighboring water particles $f_{j}$
-                        \State compute virtual water film \\(see Section~\ref{sec3})
-                    \EndFor
-                \EndFor
-                \For
-                    solid particles $s_{i}$
-                    \For
-                        neighboring water particles $f_{j}$
-                        \State compute growth direction vector \\(see Section~\ref{sec2})
-                    \EndFor
-                \EndFor
-                \For
-                    solid particles $s_{i}$
-                    \For
-                        neighboring water particles $f_{j}$
-                        \State compute $F_{\theta}$ (see Section~\ref{sec1})
-                        \State compute $CE(s_{i},f_{j})$ \\(see Section~\ref{sec3})
-                        \If
-                            $CE(b_{i}, f_{j})$ $>$ glaze threshold
-                            \State $j$th water particle's phase $\Leftarrow$ ICE
-                        \EndIf
-                        \If
-                            $CE(c_{i}, f_{j})$ $>$ icicle threshold
-                            \State $j$th water particle's phase $\Leftarrow$ ICE
-                        \EndIf
-                    \EndFor
-                \EndFor
-            \EndFor
-        \end{algorithmic}
-    \end{algorithm}
-
-    Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
-    adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
-    Integer porta neque vitae massa~\cite{Rothermel1997,Elbaum2002}. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
-    faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
-    taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
-    Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo~\cite{Elbaum2002} Nulla nisl. Vestibulum
-    sed nisl eu sapien cursus rutrum.
-
-    Pellentesque wisi. Nullam malesuada. Morbi ut tellus ut pede tincidunt porta. Lorem ipsum dolor sit amet,
-    consectetuer adipiscing elit. Etiam congue neque id dolor.
-
-    Donec et nisl at wisi luctus bibendum. Nam interdum tellus ac libero. Sed sem justo, laoreet vitae, fringilla at,
-    adipiscing ut, nibh. Maecenas non sem quis tortor eleifend fermentum. Etiam id tortor ac mauris porta vulputate.
-    Integer porta neque vitae massa. Maecenas tempus libero a libero posuere dictum. Vestibulum ante ipsum primis in
-    faucibus orci luctus et ultrices posuere cubilia Curae; Aenean quis mauris sed elit commodo placerat. Class aptent
-    taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Vivamus rhoncus tincidunt libero.
-    Etiam elementum pretium justo. Vivamus est. Morbi a tellus eget pede tristique commodo. Nulla nisl. Vestibulum
-    sed nisl eu sapien cursus rutrum.
-
-    \begin{equation}
-        \label{eq23}
-        \|\tilde{X}(k)\|^2
-        =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
-        \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
-    \end{equation}
-
-    Sed feugiat. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Ut pellentesque
-    augue sed urna. Vestibulum diam eros, fringilla et, consectetuer eu, nonummy id, sapien. Nullam at lectus. In sagittis
-    ultrices mauris. Curabitur malesuada erat sit amet massa. Fusce blandit. Aliquam erat volutpat. Aliquam euismod.
-    Aenean vel lectus. Nunc imperdiet justo nec dolor.
-
-    Etiam euismod. Fusce facilisis lacinia dui. Suspendisse potenti. In mi erat, cursus id, nonummy sed, ullamcorper
-    eget, sapien. Praesent pretium, magna in eleifend egestas, pede pede pretium lorem, quis consectetuer tortor sapien
-    facilisis magna. Mauris quis magna varius nulla scelerisque imperdiet. Aliquam non quam. Aliquam porttitor quam
-    a lacus. Praesent vel arcu ut tortor cursus volutpat. In vitae pede quis diam bibendum placerat. Fusce elementum
-    convallis neque. Sed dolor orci, scelerisque ac, dapibus nec, ultricies ut, mi. Duis nec dui quis leo sagittis commodo.
-
-    \begin{equation}
-        \label{eq24}
-        \|\tilde{X}(k)\|^2
-        =\frac{\left\|\sum\limits_{i=1}^{p}\tilde{Y}_i(k)+\sum\limits_{j=1}^{q}\tilde{Z}_j(k) \right\|^2}{(p+q)^2}
-        \leq\frac{\sum\limits_{i=1}^{p}\left\|\tilde{Y}_i(k)\right\|^2+\sum\limits_{j=1}^{q}\left\|\tilde{Z}_j(k)\right\|^2 }{p+q}.
-    \end{equation}
-
-    Aliquam lectus. Vivamus leo. Quisque ornare tellus ullamcorper nulla. Mauris porttitor pharetra
-    tortor. Sed fringilla justo sed mauris. Mauris tellus. Sed non leo. Nullam elementum, magna in cursus sodales, augue
-    est scelerisque sapien, venenatis congue nulla arcu et pede. Ut suscipit enim vel sapien. Donec congue. Maecenas
-    urna mi, suscipit in, placerat ut, vestibulum ut, massa. Fusce ultrices nulla et nisl.
-
-    Etiam ac leo a risus tristique nonummy. Donec dignissim tincidunt nulla. Vestibulum rhoncus molestie odio. Sed
-    lobortis, justo et pretium lobortis, mauris turpis condimentum augue, nec ultricies nibh arcu pretium enim. Nunc
-    purus neque, placerat id, imperdiet sed, pellentesque nec, nisl. Vestibulum imperdiet neque non sem accumsan laoreet.
-    In hac habitasse platea dictumst. Etiam condimentum facilisis libero. Suspendisse in elit quis nisl aliquam dapibus.
-    Pellentesque auctor sapien. Sed egestas sapien nec lectus. Pellentesque vel dui vel neque bibendum viverra. Aliquam
-    porttitor nisl nec pede. Proin mattis libero vel turpis. Donec rutrum mauris et libero. Proin euismod porta felis.
-    Nam lobortis, metus quis elementum commodo, nunc lectus elementum mauris, eget vulputate ligula tellus eu neque.
-    Vivamus eu dolor.
-
-    \section{Conclusions}\label{sec5}
-
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
-    felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
-    vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-    Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-    sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
-    leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
-    auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-    Duis eget orci sit amet orci dignissim rutrum.
-
-    Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-    pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-    vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-    a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-    urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-%\backmatter
-
-    \section*{Acknowledgments}
-    This is acknowledgment text~\cite{Elbaum2002}.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-This is acknowledgment text.
-Provide text here.
-
-    \subsection*{Author contributions}
-
-    This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text. This is an author contribution text.
-
-    \subsection*{Financial disclosure}
-
-    None reported.
-
-    \subsection*{Conflict of interest}
-
-    The authors declare no potential conflict of interests.
-
-    \section*{Supporting information}
-
-    The following supporting information is available as part of the online article:
-
-    \noindent
-    \textbf{Figure S1.}
-    {500{\uns}hPa geopotential anomalies for GC2C calculated against the ERA Interim reanalysis. The period is 1989--2008.}
-
-    \noindent
-    \textbf{Figure S2.}
-    {The SST anomalies for GC2C calculated against the observations (OIsst).}
-
-    \appendix
-
-    \section{Section title of first appendix\label{app1}}
-
-    Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math.
-Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math.
-Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated.
-Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.
-All other code environments are set with normal text font.
-Refer below example:
-
-    \begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
-for i:=maxint to 0 do
-begin
-{ do nothing }
-end;
-Write('Case insensitive ');
-WritE('Pascal keywords.');
-    \end{lstlisting}
-
-    \subsection{Subsection title of first appendix\label{app1.1a}}
-
-    Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-    pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-    vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-    a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-    urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
-
-    Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-    viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-    ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-    at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-    nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-    bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-    pellentesque felis eu massa.
-
-    \subsubsection{Subsection title of first appendix\label{app1.1.1a}}
-
-    \noindent\textbf{Unnumbered figure}
-
-    \begin{center}
-        \includegraphics[width=7pc,height=8pc,draft]{empty}
-    \end{center}
-
-    Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-    venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-    quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-    facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-    vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-
-    Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-    Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-    ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-    eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-    convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-    pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-    \section{Section title of second appendix\label{app2}}%
-
-    Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-    venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-    quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-    facilisi. Sed a turpis eu lacus commodo facilisis. Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, et
-    vehicula libero dui cursus dui. Mauris tempor ligula sed lacus. Duis cursus enim ut augue. Cras ac magna. Cras nulla.
-
-    Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-    Suspendisse vel felis. Ut lorem lorem, interdum eu, tincidunt sit amet, laoreet vitae, arcu. Aenean faucibus pede eu
-    ante. Praesent enim elit, rutrum at, molestie non, nonummy vel, nisl. Ut lectus eros, malesuada sit amet, fermentum
-    eu, sodales cursus, magna. Donec eu purus. Quisque vehicula, urna sed ultricies auctor, pede lorem egestas dui, et
-    convallis elit erat sed nulla. Donec luctus. Curabitur et nunc. Aliquam dolor odio, commodo pretium, ultricies non,
-    pharetra in, velit. Integer arcu est, nonummy in, fermentum faucibus, egestas vel, odio.
-
-%== Figure 4 ==
-%% Example for figure inside appendix
     \begin{figure}[t]
-        \centerline{\includegraphics[height=10pc,width=78mm,draft]{empty}}
-        \caption{This is an example for appendix figure.\label{fig5}}
+        \centerline{\includegraphics[width=0.5\textwidth]{img/fig1}}
+        \caption{The transformation of a single sentence in the Korean morphology tagged corpus into a single training sample}\label{fig:sample}
     \end{figure}
 
-    \subsection{Subsection title of second appendix\label{app2.1a}}
+    In order to train a dictionary-based morpheme analysis model, it is necessary to make the morpheme tagged corpus, which is previously expressed in lemma form, into a form that includes boundary information between morphemes in surface form.
+    In this process, a string alignment method that considers the difference between the lemma form and the surface form in the Korean morphological analysis corpus is essential.
+    In this study, string alignment was performed with the Smith-Waterman algorithm using a scoring matrix based on the similarity in the grapheme unit of Korean letters for each word pair.
+    (See Figure~\ref{fig:sample})
+    One aligned sentence with morpheme tag can be transformed into one training sample for dictionary-based morphological analysis.
+    In the tabular data at the bottom of Figure~\ref{fig:sample}, each line becomes a unit constituting a lexicon, the first four columns are used for feature generation and the last four columns used for post-lemmatization.
 
-    Sed commodo posuere pede. Mauris ut est. Ut quis purus. Sed ac odio. Sed vehicula hendrerit sem. Duis non odio.
-    Morbi ut dui. Sed accumsan risus eget odio. In hac habitasse platea dictumst. Pellentesque non elit. Fusce sed justo
-    eu urna porta tincidunt. Mauris felis odio, sollicitudin sed, volutpat a, ornare ac, erat. Morbi quis dolor. Donec
-    pellentesque, erat ac sagittis semper, nunc dui lobortis purus, quis congue purus metus ultricies tellus. Proin et quam.
-    Class aptent taciti sociosqu ad litora torquent per conubia nostra, per inceptos hymenaeos. Praesent sapien turpis,
-    fermentum vel, eleifend faucibus, vehicula eu, lacus.
+    %사전 기반 형태소 분석 모델을 학습하기 위해서는 기존에 lemma form으로 표현되어 있는 morpheme tagged corpus를 surface form에서의 형태소 간의 경계 정보가 포함된 형태로 만들어 줄 필요가 있다.
+    %이 과정 내에서 한국어 형태 분석 말뭉치 내의 lemma form과 surface form 간의 차이를 고려한 string alignment 방법이 핵심적으로 필요하게 된다.
+    %본 연구에서는 각 어절 쌍에 대해서 한국어 글자의 자소 단위에서의 유사도에 기반한 scoring matrix를 사용한 Smith-Waterman 알고리즘으로 문자열 정렬을 수행하였다.
+    %(Figure~\ref{fig:sample} 참조)
+    %하나의 aligned sentence with morpheme tag는 하나의 training sample for dictionary-based morphological analysis로 변형될 수 있게 된다.
+    %Figure~\ref{fig:sample}의 하단에 있는 표 형태의 데이터에서 각 줄은 lexicon을 구성하는 단위가 되며, 전반의 4개 열은 feature generation에 사용되고 후반의 4개 열은 post-lemmatization에 사용된다.
 
-    Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-    dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-    vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-    Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
-    mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
-    Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.
+    \section{Transformer-based Re-ranking Model}\label{sec4}
 
-    \subsubsection{Subsection title of second appendix\label{app2.1.1a}}
+    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of language expression that have an independent meaning in a sentence.
+    In an isolating language like English, this can be done relatively simply by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
+    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
 
-    Lorem ipsum dolor sit amet, consectetuer adipiscing elit. Ut purus elit, vestibulum ut, placerat ac, adipiscing vitae,
-    felis. Curabitur dictum gravida mauris. Nam arcu libero, nonummy eget, consectetuer id, vulputate a, magna. Donec
-    vehicula augue eu neque. Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas.
-    Mauris ut leo. Cras viverra metus rhoncus sem. Nulla et lectus vestibulum urna fringilla ultrices. Phasellus eu tellus
-    sit amet tortor gravida placerat. Integer sapien est, iaculis in, pretium quis, viverra ac, nunc. Praesent eget sem vel
-    leo ultrices bibendum. Aenean faucibus. Morbi dolor nulla, malesuada eu, pulvinar at, mollis ac, nulla. Curabitur
-    auctor semper nulla. Donec varius orci eget risus. Duis nibh mi, congue eu, accumsan eleifend, sagittis quis, diam.
-    Duis eget orci sit amet orci dignissim rutrum.
+    %학습된 형태소 분석 모델의 차선 결과들을 생성하여 재순위화 데이터를 만드는 방법
 
-    Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-    pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-    vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-    a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-    urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
+    \section{Experimental Results}\label{sec5}
 
-    \begin{center}
-        \begin{table*}[b]%
-            \centering
-            \caption{This is an example of Appendix table showing food requirements of army, navy and airforce.\label{tab4}}%
-            \begin{tabular*}{300pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
-                \toprule
-                \textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
-                \midrule
-                col1 text          & col2 text          & col3 text          \\
-                col1 text          & col2 text          & col3 text          \\
-                col1 text          & col2 text          & col3 text          \\
-                \bottomrule
-            \end{tabular*}
-        \end{table*}
-    \end{center}
+    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of language expression that have an independent meaning in a sentence.
+    In an isolating language like English, this can be done relatively simply by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
+    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
 
-    Example for an equation inside appendix
-    \begin{equation}
-        \mathcal{L}\quad \mathbf{\mathcal{L}} = i \bar{\psi} \gamma^\mu D_\mu \psi - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi\label{eq25}
-    \end{equation}
+    %형태소 분석 모델 및 재순위화 모델을 통한 성능 개선 실험 결과
 
-    \section{Example of another appendix section\label{app3}}%
+    \section{Error Analysis and Case Studies}\label{sec6}
 
-    This is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text this is sample for paragraph text
+    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of language expression that have an independent meaning in a sentence.
+    In an isolating language like English, this can be done relatively simply by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
+    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
 
-    Nam dui ligula, fringilla a, euismod sodales, sollicitudin vel, wisi. Morbi auctor lorem non justo. Nam lacus libero,
-    pretium at, lobortis vitae, ultricies et, tellus. Donec aliquet, tortor sed accumsan bibendum, erat ligula aliquet magna,
-    vitae ornare odio metus a mi. Morbi ac orci et nisl hendrerit mollis. Suspendisse ut massa. Cras nec ante. Pellentesque
-    a nulla. Cum sociis natoque penatibus et magnis dis parturient montes, nascetur ridiculus mus. Aliquam tincidunt
-    urna. Nulla ullamcorper vestibulum turpis. Pellentesque cursus luctus mauris.
+    %오류 분석 및 성능 개선 사례들
 
-    Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-    viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-    ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-    at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-    nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-    bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-    pellentesque felis eu massa.
+    \section{Conclusion}\label{sec7}
 
-    \begin{equation}
-        \mathcal{L} = i \bar{\psi} \gamma^\mu D_\mu \psi
-        - \frac{1}{4} F_{\mu\nu}^a F^{a\mu\nu} - m \bar{\psi} \psi
-        \label{eq26}
-    \end{equation}
+    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of language expression that have an independent meaning in a sentence.
+    In an isolating language like English, this can be done relatively simply by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
+    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
 
-    Nulla malesuada porttitor diam. Donec felis erat, congue non, volutpat at, tincidunt tristique, libero. Vivamus
-    viverra fermentum felis. Donec nonummy pellentesque ante. Phasellus adipiscing semper elit. Proin fermentum massa
-    ac quam. Sed diam turpis, molestie vitae, placerat a, molestie nec, leo. Maecenas lacinia. Nam ipsum ligula, eleifend
-    at, accumsan nec, suscipit a, ipsum. Morbi blandit ligula feugiat magna. Nunc eleifend consequat lorem. Sed lacinia
-    nulla vitae enim. Pellentesque tincidunt purus vel magna. Integer non enim. Praesent euismod nunc eu purus. Donec
-    bibendum quam in tellus. Nullam cursus pulvinar lectus. Donec et mi. Nam vulputate metus eu enim. Vestibulum
-    pellentesque felis eu massa.
+    %결론과 향후 연구
 
-    Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-    amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-    Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-    quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-    vitae risus porta vehicula.
-
-    \begin{center}
-        \begin{tabular*}{250pt}{@{\extracolsep\fill}lcc@{\extracolsep\fill}}%
-            \toprule
-            \textbf{col1 head} & \textbf{col2 head} & \textbf{col3 head} \\
-            \midrule
-            col1 text          & col2 text          & col3 text          \\
-            col1 text          & col2 text          & col3 text          \\
-            col1 text          & col2 text          & col3 text          \\
-            \bottomrule
-        \end{tabular*}
-    \end{center}
-
-    Quisque ullamcorper placerat ipsum. Cras nibh. Morbi vel justo vitae lacus tincidunt ultrices. Lorem ipsum dolor sit
-    amet, consectetuer adipiscing elit. In hac habitasse platea dictumst. Integer tempus convallis augue. Etiam facilisis.
-    Nunc elementum fermentum wisi. Aenean placerat. Ut imperdiet, enim sed gravida sollicitudin, felis odio placerat
-    quam, ac pulvinar elit purus eget enim. Nunc vitae tortor. Proin tempus nibh sit amet nisl. Vivamus quis tortor
-    vitae risus porta vehicula.
-
-    Fusce mauris. Vestibulum luctus nibh at lectus. Sed bibendum, nulla a faucibus semper, leo velit ultricies tellus, ac
-    venenatis arcu wisi vel nisl. Vestibulum diam. Aliquam pellentesque, augue quis sagittis posuere, turpis lacus congue
-    quam, in hendrerit risus eros eget felis. Maecenas eget erat in sapien mattis porttitor. Vestibulum porttitor. Nulla
-    facilisi.
-Sed a turpis eu lacus commodo facilisis.
-Morbi fringilla, wisi in dignissim interdum, justo lectus sagittis dui, evehicula libero dui cursus dui.
-Mauris tempor ligula sed lacus.
-Duis cursus enim ut augue.
-Cras ac magna.
-Cras nulla.
-    Nulla egestas. Curabitur a leo. Quisque egestas wisi eget nunc. Nam feugiat lacus vel est. Curabitur consectetuer.
-
-    Pellentesque habitant morbi tristique senectus et netus et malesuada fames ac turpis egestas. Donec odio elit,
-    dictum in, hendrerit sit amet, egestas sed, leo. Praesent feugiat sapien aliquet odio. Integer vitae justo. Aliquam
-    vestibulum fringilla lorem. Sed neque lectus, consectetuer at, consectetuer sed, eleifend ac, lectus. Nulla facilisi.
-    Pellentesque eget lectus. Proin eu metus. Sed porttitor. In hac habitasse platea dictumst. Suspendisse eu lectus. Ut
-    mi mi, lacinia sit amet, placerat et, mollis vitae, dui. Sed ante tellus, tristique ut, iaculis eu, malesuada ac, dui.
-    Mauris nibh leo, facilisis non, adipiscing quis, ultrices a, dui.
-
-    \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
-    \bibliography{wileyNJD-AMS}%
+    %\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
+    \bibliography{WileyNJD-AMS}
 

### 2023-09-05 contents/draft.tex
Updates from Overleaf

\documentclass[AMS,STIX2COL]{WileyNJD-v2}

\articletype{Article Type}
\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}
\raggedbottom

\begin{document}
    \title{Improvement of Korean Morphological Analysis System \\Through Transformer-based Re-ranking}

    \author[1]{Author One*}
    \author[2,3]{Author Two}
    \author[3]{Author Three}
    \authormark{AUTHOR ONE \textsc{et al}}

    \address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
    \address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
    \address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
    \corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
    \presentaddress{This is sample for present address text this is sample for present address text}

    \abstract[Abstract]{Korean morphological analysis plays a basic and important role enough to be called the first step in Korean language analysis. Due to the nature of Korean agglutinative words, it was difficult to build an automatic analysis system because the analysis was not completed with part-of-speech tagging alone, as in English. In addition, various methods for morphological analysis have been proposed, but efficient methods such as BPE are mainly used in applications intended to be used as tokenizers for deep learning. In this paper, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning. For a number of various cases whose rankings have been changed through re-ranking, it is possible to improve performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system in the future. Through experiments, we showed that the proposed method effectively improved performance by reducing errors by more than 30\% in both the spoken language model and the written language model.}
    \keywords{Korean morphological analysis, natural language understanding, deep learing, pretrained transformer encoder, re-ranking}

    \JELinfo{classification}
    \MSC{Code numbers}
    \jnlcitation{\cname{
        \author{Williams K.},
        \author{B. Hoskins},
        \author{R. Lee},
        \author{G. Masato}, and \author{T. Woollings}} (\cyear{2016}),
        \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
    \maketitle
    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}

    \begin{center}
        \begin{table*}[t]
            \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
            \centering
            \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
                \toprule
                & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
                alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
                \midrule
                no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
                secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
                tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
                quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
                quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
                \bottomrule
            \end{tabular*}
            \begin{tablenotes}
                \footnotesize
                \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
                \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
            \end{tablenotes}
        \end{table*}
    \end{center}

    \section{Introduction}\label{sec:intro}

    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of linguistic expression that have an independent meaning in a sentence.
    In an isolating language like English, this can be done relatively easily by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
    Modern high-performance deep learning methods in natural language processing use a tokenization process that breaks text into smaller units, and then converts each token into a vector as an input to the computational model~\cite{Mikolov2013}.
    In this case, the token unit is mainly subword units, and to reflect the characteristics of Korean, subword tokenization with separated morphemes is attempted in advance~\cite{SongHJ2021}.
    Using the results of morphological analysis for this tokenization process improves the overall performance of the analysis by reflecting the semantic units of Korean, but requires a highly accurate and fast morphological analyzer.

    Various approaches have been proposed for morphological analysis, which plays a fundamental and important role in Korean language analysis~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
    In general, when people understand speech or writing, they try to make sense of it using the vocabulary and concepts they know.
    While there are ways to use rules or dictionaries to reflect this way of understanding~\cite{KwonHC1991}, the problem is that it becomes difficult to build and maintain a dictionary for vocabulary that appears in every text.
    Therefore, methods for tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016}, and studies to improve them have been carried out continuously~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
    From a mechanical point of view, syllable-by-syllable morphological analysis can be done either by tagging syllable-by-syllable and then applying a base form restoration dictionary~\cite{ShimKS2011, LeeCH2016}, or by tagging syllable-by-syllable with the base form already restored~\cite{YounJY2021}.
    However, syllable-by-syllable morphological analysis has limitations in that it is difficult to accurately identify morpheme boundaries, and it is difficult to learn long-term contextual information as the length of the sequence increases.
    In this paper, the former is referred to as dictionary-based morphological analysis, and the latter is referred to as syllable-unit morphological analysis.
    Both methods also share the limitation that they are trained on a manually labeled corpus and cannot accurately analyze new syllable combinations or morphemes that do not appear in the training corpus.
    In recent years, with the development of the Internet and the spread of open source and open data, web texts, corpora, language resources, and knowledge shared by different people have accumulated significantly.
    The reduced cost of building and maintaining a dictionary can be a great opportunity to overcome the limitations of dictionary-based methods.

    Against this background, this paper considers how the dictionary-based morphological analysis method used by MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis in tokenizers, an essential preprocessing tool for deep learning, can be effectively improved by deep learning, and proposes a method.
    The dictionary-based morphological analysis method~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018} trained by the CRF method~\cite{Lafferty2001} lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph, and finds the optimal morphological analysis path within it.
    The process of finding the best path in the lattice uses the Viterbi algorithm~\cite{Viterbi1967}, which finds the path that minimizes the cost of each morpheme node and the sum of the neighborhood costs of two consecutive morphemes.
    The main types of errors in these dictionary-based morphological analysis methods are when new words not in the dictionary are used in a sentence, or when the optimal path calculation selects the wrong result due to a bias.
    For example, it may be less costly to select one long morpheme than several short morphemes, but it may sometimes be the wrong analysis.
    The main motivation for this research is that the path that minimizes the sum of all costs for nodes and links may not be the optimal path.

    In order to identify the cases where a suboptimal solution is actually the best solution according to the best path calculation, we modified the best path calculation method to generate suboptimal analysis results and check the extent to which they are correct.
    While there are many different ways to choose the next best path, we used the method of replacing a morpheme node on the optimal path with a lower ranked node.
    As shown in Table~\ref{tab:maximum-performance}, we were able to confirm the extent to which analysis performance could be improved by replacing the optimal path with a lower-ranked node.
    We can think of the problem of finding the actual correct answer among these generated suboptimals as similar to the problem of re-ranking search results in information retrieval~\cite{BaeYJ2021}.
    Previously, in ~\cite{ChoiYS2018}, the N-best analysis results generated by the seq2seq model were re-ranked based on a convolutional neural network to improve performance.
    In this study, the re-ranking was performed using two BERT models of different types and forms as proposed in ~\cite{Nogueira2019}.
    The experimental results show that the first stage re-ranking improves the performance by more than 20\% over the previous written and spoken models, and the second stage re-ranking with a different type of input and a different type of pre-trained model further improves the performance by more than 30\% over the previous written and spoken models.

    With this method, the performance of the dictionary-based morphological analysis method could be further improved, but the overall analysis time increases when the morphological analysis system is configured including the re-ranking model itself.
    However, it is possible to use the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in the dictionary, similar to the backpropagation process in a typical neural network.
    It is also expected that the morphological analysis system with improved connection costs will be able to generate better re-ranking candidates, which will further improve performance by doing so iteratively.
    Further research is needed for this in the future, and in this paper, only the performance improvement through the second stage re-ranking was covered as the scope of the study.
    The main contributions of this study are as follows:
    \begin{enumerate}
        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node, and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To improve the performance of dictionary-based analysis by re-ranking the morphological analysis results, we propose to extend the performance improvement by using different BERT models to perform two rounds of re-ranking.
        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We propose a new method for updating connection costs in dictionaries based on the results of reranked morphological analysis, and provide directions for future research by suggesting improvements and directions for future research.
    \end{enumerate}
    These contributions provide important insights into the performance improvement of Korean morphological analysis and the direction of future research, and will serve as a useful reference for future researchers.

    This paper is organized as follows:
    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study, and in Section ~\ref{sec:morphological-analysis-model}, we discuss how to configure and train a dictionary-based morphological analysis system.
    In Section ~\ref{sec:re-ranking-model}, we discuss how to generate secondary results of morphological analysis and produce re-ranking data, and propose a method for training a two-stage re-ranking model.
    In Section ~\ref{sec:results}, we discuss the results of performance improvement by morphological analysis model and re-ranking model.
    Finally, in Section ~\ref{sec:conclusion}, we conclude the paper and discuss the limitations of this study and the direction of future research.

    \begin{figure*}[t]
        \centerline{\includegraphics[width=0.75\textwidth]{fig1.1}}
        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}\label{fig:sample}
    \end{figure*}

    \section{Related Work}\label{sec:related-work}

    Korean morphological analysis has seen an influx of various methodologies over the years~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}. The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to come up with inventive solutions, many of which have laid the groundwork for future research.

    \subsection{Traditional Dictionary-based Approaches}\label{subsec2.1}
    The earliest attempts at Korean morphological analysis heavily depended on rule-based systems and dictionary-based methods~\cite{KwonHC1991}. These methodologies essentially employed predefined sets of linguistic rules or large dictionaries to detect morphemes and determine parts of speech. One of the most significant advantages of such an approach is its deterministic nature, which can lead to high accuracy when the input text closely adheres to the rules or dictionaries used. However, they are notably challenging to scale and update, particularly with the constant evolution of the language and emergence of new words. The dynamic nature of language, especially in the age of the internet, has made maintaining comprehensive dictionaries labor-intensive.

    \subsection{Syllable-unit Morphological Analysis}\label{subsec2.2}
    In an attempt to bypass the limitations of dictionary-dependence, syllable-by-syllable morphological analysis emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}. This method either tags each syllable and then applies a base form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}. One notable drawback is the challenge in accurately pinpointing morpheme boundaries. Furthermore, as sequences increase in length, the system finds it increasingly challenging to understand long-term contextual data.

    \subsection{Deep Learning and Tokenization}\label{subsec2.3}
    The advent of deep learning has reshaped the landscape of Korean morphological analysis. High-performance deep learning models in NLP now employ tokenization, dividing the text into smaller units and then converting these tokens into vectors as an input to the computational model~\cite{Mikolov2013}. Especially significant is the attempt to conduct subword tokenization, incorporating separated morphemes to cater to Korean linguistic characteristics. In particular, it is noteworthy that we attempted to tokenize subwords by incorporating segmented morphemes to suit the linguistic characteristics of Korean, and it is known that incorporating accurate morpheme analysis results into tokenization can improve overall analysis performance.

    However, with the progression of technology and accessibility to vast amounts of data, the possibility of integrating dictionary-based methods with deep learning techniques emerged. As motivated in our study, MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis, utilized dictionary-based morphological analysis trained by the CRF method~\cite{Lafferty2001}. This method attempts to find the optimal morphological analysis path by forming a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018}. The amalgamation of dictionary-based methods with deep learning, as explored in our research, signifies the latest stride in this journey, aiming to harness the strengths of both approaches. Future research avenues include refining these hybrid methods and further exploring the capabilities of end-to-end models for this complex task.

    \begin{figure*}[t]
        \centerline{\includegraphics[width=0.9\textwidth]{fig2.1}}
        \caption{Example of lattice construction and decoding result and secondary path generation}\label{fig:lattice}
    \end{figure*}

    \section{Morphological Analysis Model}\label{sec:morphological-analysis-model}

    \subsection{Korean Morphological Analysis Corpora}\label{subsec3.1}

    A representative corpus for training Korean morphological analysis models is the Sejong Morphological Analysis Corpus, often referred to as the Sejong Corpus. The Sejong Corpus, a major output of the 21st Century Sejong Project, contains 15 million words and remains a mainstay of Korean morphological analysis research~\cite{ChoeMW2008}.

    Subsequent efforts have extended and refined this foundational work. The University of Ulsan, addressing the limitations of the Sejong corpus~\cite{KimIH2010}, introduced [UCorpus], an expanded corpus of 63 million words. This expanded corpus not only added new data, but also corrected errors in the original Sejong corpus~\cite{UCorpusHG}. To take this a step further, the National Institute of the Korean Language launched a massive Korean corpus construction project in 2018. The fruits of this labor, a corpus called <Everyone Corpus>, were released to the public in 2020~\cite{EveryoneCorpus}. A special offshoot of this project produced a morpheme-tagged corpus of 3 million words, including spoken language~\cite{KimIH2019}.

    \subsection{Training Example Transformation}\label{subsec3.2}

    In order to effectively train a dictionary-based morpheme analysis model, the morpheme-tagged corpus, typically represented in lemma form, needs to be transformed to include boundary information between morphemes in its surface form. Crucial to this transformation is string alignment, a process that accounts for discrepancies between lemma and surface forms in the Korean morphological analysis corpus.

    In this research, string alignment was performed using the Smith-Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}). Each aligned sentence containing a morpheme tag can be converted into a training sample tailored for dictionary-based morphological analysis.

    The resulting table data in Figure~\ref{fig:sample} illustrates this process. Here, each row acts as a lexical unit. The first four columns contribute to feature generation, while the last four columns facilitate post-lemmatization. Using the above morphological corpus, a large number of training samples can be generated according to the process shown in Figure~\ref{fig:sample}. Except for the evaluation samples, the remaining sentences are used to train the dictionary-based morphological analysis model via the CRF algorithm. The output of this training allows the calculation of the costs associated with each morpheme node and the linking of two consecutive morphemes. This in turn allows the discovery of the optimal path using the Viterbi algorithm.

    \begin{figure*}[t]
        \centerline{\includegraphics[width=0.9\textwidth]{fig3.0}}
        \caption{Two-stage re-ranking model for Korean morphological analysis}\label{fig:ranking}
    \end{figure*}

    \subsection{Lattice Construction and Decoding}\label{subsec3.3}

    Figure~\ref{fig:lattice} shows a snapshot of the lattice structure, an integral part of morphological analysis. Part (1) shows a fragment of the lattice structure formed when the example sentence from Figure~\ref{fig:sample} is entered. Meanwhile, part (2) shows the optimal path as determined by the Viterbi algorithm.

    However, the path inferred by the trained model may differ from the correct solution constructed by a human. The nodes marked with stars in part (1) represent the correct nodes. The upper left number of each node indicates the ranking of the nodes accessible at each decoding point. It can be seen that the choices made at certain moments can deviate from the correct solution. In order to improve the performance of the analysis, it is imperative to develop mechanisms to correct these discrepancies.

    \section{Re-ranking Model}\label{sec:re-ranking-model}

    \subsection{Motivation and Background}\label{subsec4.1}

    While dictionary-based morphological analysis offers significant advances in Korean language processing, its optimal paths occasionally diverge from the correct solutions that humans understand. This divergence underscores the need for a model that re-evaluates these primary results and reorients them to achieve higher accuracy. This method, called "re-ranking," involves generating multiple analyses of an input and then reordering them based on a new set of criteria or models, thereby improving the overall quality of the results.

    \subsection{Secondary Path Generation}\label{subsec4.2}

    Before re-ranking can begin, multiple analyses, typically referred to as N-best paths, of the input sentence are generated.
    This involves extracting the top N analyses from the lattice structure in general.
    In this study, a novel approach has been introduced to generate secondary paths, as shown in part (3) of Figure~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
    Encouragingly, some of these secondary paths provided alternatives that reconciled incorrect answers with the correct ones.
    Similarly, paths modified by favoring the third-best node were called tertiary paths, and this naming convention continued for subsequent paths.
    In our preliminary test, the secondary paths, including the optimal and some suboptimal paths, were shown to cover the majority of correct morphological analyses as measured by human judgments. (See Table~\ref{tab:maximum-performance})

    \subsection{BERT-based Re-ranking}\label{subsec4.3}

    BERT (Bidirectional Encoder to Transformer Representation) models~\cite{Devlin2019} have revolutionized many natural language processing tasks by understanding the context in which words appear in text. In this study, we attempt to leverage the power of BERT to reorder the generated secondary paths. We labeled the generated secondary paths with scores related to morphological analysis performance in order to fine-tune a pre-trained BERT model specialized for Korean with a large amount of Korean text. After pre-testing several scoring methods on a modest scale, we found that using scores based on the degree of error, rather than scores based on accuracy, to widen the gap between correct and incorrect answers is effective for learning.

    Once the BERT model has been fine-tuned and trained for the reranking task, it will be able to predict a reranking score for each path in the secondary path list. This means that, taking into account the context, morphological organization, and other essential linguistic features of the path, the model will assign a score for each path. The paths are then re-ranked according to this score, and the path with the highest score is selected as the best morphological analysis result.

    \begin{table*}[]
        \caption{Statistics on full data for training and evaluating three morphological analysis models}\label{tab:data-statistics}
        \centering
        \begin{tabular*}{500pt}{@{\extracolsep\fill}|c|c|rrr|rrr|@{\extracolsep\fill}}
            \toprule
            \multicolumn{2}{|c|}{\multirow{2}{*}{\textbf{Corpus}}} & \multicolumn{3}{c|}{\textbf{Training Set}} & \multicolumn{3}{c|}{\textbf{Test Set}} \\
            \cmidrule{3-5} \cmidrule{6-8}
            \multicolumn{2}{|c|}{~} & sentences & eojeols & morphemes & sentences & eojeols & morphemes \\
            \midrule
            \multicolumn{2}{|c|}{Sejong Corpus} & 194,822 & 2,681,582 & 6,033,785 & 49,922 & 678,578 & 1,527,803 \\
            \midrule
            \multirow{3}{*}{UCorpus}         & written     & 4,998,560 & 57,393,332 & 127,171,473 & 53,003 & 598,413 & 1,325,419 \\
            ~                                & semi-spoken & 334,061   & 2,960,146  & 6,468,494   & 38,960 & 332,285 & 726,398   \\
            ~                                & spoken      & 429,215   & 2,295,940  & 5,584,494   & 62,399 & 279,545 & 691,542   \\
            \midrule
            \multirow{2}{*}{Everyone Corpus} & written     & 129,352   & 1,713,367  & 3,944,118   & 14,442 & 191,223 & 440,052   \\
            ~                                & spoken      & 137,869   & 714,021    & 1,440,746   & 19,789 & 85,316  & 170,523   \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \subsection{Two-stage Re-ranking}\label{subsec4.4}

    Given the complexity of the Korean language, a single reranking step does not always yield the most accurate results. Therefore, we propose a two-step reranking approach, as in ~\cite{Nogueira2019}.

    In the first step, we re-rank the secondary paths generated using the BERT model as described in section ~\ref{subsec4.3}. In the second step, we introduce another BERT variant that is optimized for a different set of linguistic features or trained on a different dataset. This allows us to perform a fine-grained re-evaluation, further refining the list and pushing the more contextually accurate paths to the top.

    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage performs a first reranking, taking as input a secondary path in morphologically tagged lemma form. It then performs a second reranking, again taking as input the path reranked in stage 1 and the original input sentence. This is done to improve the effectiveness, since it didn't work very well when given the same type of input.

    \subsection{Iterative Updatability}\label{subsec4.5}

    The re-ranked paths are then integrated with the original dictionary-based morphological analysis. The connection costs between morphemes in the dictionary are updated based on feedback from the re-ranking model. Over time, this feedback loop ensures that the morphological analysis model becomes more closely aligned with human understanding and minimizes discrepancies in optimal path selection.

    \section{Experimental Results}\label{sec:results}

    In our effort to enhance Korean morphological analysis, we evaluated the performance of the proposed deep learning integrated dictionary-based morphological analysis method. This section presents the results of the experimental evaluation, taking into account the improvement over conventional methods and the effectiveness of our re-ranking model.

    \subsection{Setup and Data}\label{subsec5.1}

    For our experiments, we used the Sejong corpus (the version used in ~\cite{NaSH2014, NaSH2015, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone Corpus\cite{EveryoneCorpus}. For comparison with previous studies, the Sejong corpus was trained with a single model without separation. UCorpus and Everyone Corpus provided separate spoken corpus consisting of drama scripts and broadcast dialogues, while UCorpus separated documents that were thought to be close to spoken language and further organized them into a semi-spoken corpus. Because UCorpus and Everyone Corpus have synergistic effects when trained together, we trained the models separately for written and spoken language, rather than separating them by source. The statistics of the full data for the three types of models are presented in Table~\ref{tab:data-statistics}, and due to the large volume of UCorpus, we randomly selected some of them for the actual model training.

    We transformed this organized morphological corpus with the training example transformation process described in section ~\ref{subsec3.2} to generate samples for training a dictionary-based morphological analysis model.

    \begin{table*}[]
        \caption{Performance comparison between morphological analysis systems without Re-ranking}\label{tab:performance-without-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System} & \multicolumn{2}{c}{Sejong} & \multicolumn{2}{c}{UCorpus (written)} & \multicolumn{2}{c}{Everyone Corpus (written)} \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
            \toprule
            \multirow{2}{*}{System} & \multicolumn{2}{c}{UCorpus (semi-spoken)} & \multicolumn{2}{c}{UCorpus (spoken)} & \multicolumn{2}{c}{Everyone Corpus (spoken)} \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \subsection{Evaluation Metrics}\label{subsec5.2}

    To measure the accuracy of the morphological analysis model, the correctness of the N-Best path, and the ranking accuracy of the reranking model, we used eojeol accuracy and morpheme F1 scores as evaluation metrics. To verify that they actually produced correct morphological analysis results, we measured the degree of agreement with human annotation on aforementioned corpus. However, due to the slightly different criteria and style of the annotators who labeled the different kinds of corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
    \begin{itemize}
        \item Sentences containing unanalyzable tags (NF, NA, NV) were excluded from both training and evaluation.
        \item As for the tagsets, we excluded 3 unanalyzable tags from the 45 Sejong tagsets and used 42 tagsets.
        \item Each tag output by the MeCab-ko system was converted to the corresponding tag in the Sejong tagset.
        \item Chinese characters were converted to Chinese character tags (SH) even if they were semantically used as nouns, and consecutive Chinese characters were converted to a single morpheme.
        \item Similarly, symbol, numeral, ending, and postposition in the same tag were converted to a single morpheme, and decimal expressions were treated as a single morpheme, including the midpoint and the numbers before and after.
        \item If the first lemma letter of the ending is `[eo]', `[yeo]', or `[ah]', it is unified as `[eo]', and if it is `[eot]', `[yeo]', or `[ass]', it is unified as `[eot]'. %`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeo]', or `았[ass]'
        \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus.
        \item As mentioned in ~\cite{KimIH2010}, connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
        \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, so we did not distinguish between them. %`것[geot]' and `거[geo]'
        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes, so we evaluated them without distinguishing between them.
        \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective, and human annotators have slightly different standards, so they were also evaluated without distinguishing them.
    \end{itemize}

    \subsection{Basic Performance}\label{subsec5.3}

    First, we compared the initial results of the dictionary-based morphological analysis model trained with the method described in Section ~\ref{sec:morphological-analysis-model} with MeCab and syllable-based morphological analysis systems. (See Table~\ref{tab:performance-without-reranking}) The results show that the dictionary-based method we implemented is better than the existing MeCab system, but it is different from human judgment due to the limitations mentioned above, and it does not reach the performance of existing syllable-based morphological analysis systems. We also found that the compatibility between the Sejong corpus and other corpora is not good, as the model trained on the Sejong corpus has guaranteed performance when evaluated on the Sejong corpus, and some performance degradation occurs on other corpora.

    \begin{table*}[]
        \caption{Performance comparison between morphological analysis systems with Two-staage Re-ranking}\label{tab:performance-with-reranking}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{System} & \multicolumn{2}{c}{Sejong} & \multicolumn{2}{c}{UC+EC (written)} & \multicolumn{2}{c}{UC+EC (spoken)} \\
            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
            & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            \hspace{2mm}MeCab-ko                          & 89.17                      & 93.06                        & 87.83                      & 92.19                        & 84.62                      & 89.60                        \\
            \hspace{2mm}Syllable-based                    & 91.95                      & 95.16                        & 97.42                      & 98.39                        & 95.53                      & \textbf{97.08}               \\
            \hspace{2mm}Dictionary-based (without rerank) & 95.23                      & 97.08                        & 96.59                      & 97.94                        & 93.49                      & 95.73                        \\
            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63                      & 97.84                        & 97.50                      & 98.44                        & 94.77                      & 96.62                        \\
            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}             & \textbf{98.01}               & \textbf{97.75}             & \textbf{98.60}               & \textbf{95.56}             & \textbf{97.08}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \subsection{Re-ranking Performance}\label{subsec5.4}

    Upon integrating the BERT-based re-ranking model, we observed a substantial enhancement in performance. Table~\ref{tab:maximum-performance} demonstrated that the re-ranking model was able to identify a better path in a significant proportion of cases. The first-stage re-ranking itself exhibited a performance improvement of over 20\% compared to traditional models. The subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by over 30\%.

    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:re-ranking-model} and compared the performance.
    Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well on other Korean language understanding tasks, were used to fine-tune the re-ranking model. KPF-BERT receives Korean sentences as input, ETRI-ELECTRA receives morphological tagged sentence as input, and ETRI-RoBERTa receives morpheme-separated sentences as input. In the case of KPF-BERT and ETRI-RoBERTa, there may be problems with model learning due to the separation of morpheme tags into letter units during the tokenization process when the morpheme analysis results are received as input and reranked, so the morpheme tags of the mid-level classification unit were added as new tokens, and then training was performed.
    As shown in Figure~\ref{fig:ranking}, for these three types of pre-trained language models, we first performed training with a re-ranking model using only the morphological analysis results, and then we performed training with a second re-ranking model using the top five morphological analysis results from the first re-ranking results along with the input sentences for other types of pre-trained language models. This is because preliminary tests have shown that given the same kind of model or the same kind of input, a model that is almost identical to the previously trained model is trained and performance is no longer improved.

    The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone corpus. For the large number of sentences, we adopt a floating-point 16-bit technique while using four GPUs for distributed training, and were able to significantly reduce the time required to train.
    In addition, the minibatch size was 120 with a max sequence length of 384 because the first reranking uses only the morphological analysis results as input, and the minibatch size was 40 with a max sequence length of 512 because the original input sentences are given as input along with the first morphological analysis results. And the learning rate was set to $2 \times 10^{-5}$ and AdamW is used as an optimization algorithm.

    Table~\ref{tab:performance-with-reranking} shows that incorporating the reranking model significantly improves performance compared to no reranking. The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is shown as 29\%, 27\%, and 20\% for the Sejong corpus, the combined written corpus, and the combined spoken corpus, respectively, with the first round of reranking, and the second round of reranking improved the performance more by increasing the rate to 34\%, 34\%, and 32\%, respectively.
    These performance improvements show that the dictionary-based morphological analysis model outperforms traditional syllable-based morphological analysis systems, including many pre- and post-processing rule and dictionaries.

    \begin{table*}[]
        \caption{Comparison of performance differences with previous studies}\label{tab:differences-with-previous-studies}
        \begin{tabular*}{500pt}{@{\extracolsep\fill}ccc|cc@{\extracolsep\fill}}
            \toprule
            \multirow{2}{*}{Authors} & \multirow{2}{*}{Model} & \multirow{2}{*}{Data (train, test)} & \multicolumn{2}{c}{Performance} \\
            \cmidrule{4-5}
            ~                                     & ~                                          & ~                                           & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
            \midrule
            Na, 2015~\cite{NaSH2015}              & CRF++, HMM                                 & Sejong 200k, 50k sentences                  & 95.22                      & 97.21                        \\
            Lee et al., 2016~\cite{LeeCH2016}     & Structural SVM                             & Sejong 666k, 74k eojeols                    & 96.41                      & -                            \\
            Li et al., 2017~\cite{Li2017}         & Seq2seq (GRU-based)                        & Sejong 90k, 10k sentences                   & 95.33                      & 97.15                        \\
            Na and Kim, 2018~\cite{NaSH2018}      & Lattice + HMM                              & Sejong 200k, 50k sentences                  & 96.35                      & 97.74                        \\
            Min et al., 2019~\cite{MinJW2019}     & Seq2seq (Transition-based)                 & Sejong 200k, 50k sentences                  & 96.34                      & 97.68                        \\
            Song and Park, 2019~\cite{SongHJ2019} & Seq2seq (BiLSTM-based)                     & Sejong 200k, 50k sentences                  & 95.68                      & 97.43                        \\
            Youn et al, 2021~\cite{YounJY2021}    & Seq2seq (BERT-based)                       & Sejong 675k, 75k sentences                  & 95.99                      & 97.94                        \\
            Shin et al, 2023~\cite{ShinHJ2023}    & Transformer(En) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
            \midrule
            Proposed (without rerank)             & \multirow{3}{*}{Lattice + Transformer(En)} & \multirow{3}{*}{Sejong 194k, 10k sentences} & 95.23                      & 97.08                        \\
            Proposed (1-stage rerank)             & ~                                          & ~                                           & 96.63                      & 97.84                        \\
            Proposed (2-stage rerank)             & ~                                          & ~                                           & \textbf{96.87}             & \textbf{98.01}               \\
            \bottomrule
        \end{tabular*}
    \end{table*}

    \subsection{Comparison to Other Studies}\label{subsec5.5}

    We found that the proposed transformer-based reranking technique consistently improves the results of existing morphological analysis models. These results open up new possibilities in the area of Korean morphological analysis by further improving the results of existing traditional machine learning models.
    Finally, since the results of the major related works proposed in the literature are mostly conducted on the Sejong corpus, we would like to compare the performance improvement of the Sejong corpus with the results of previous studies.

    We found that the proposed transformer-based reranking technique consistently improves the results of existing morphological analysis models. These results confirm that it opens up new possibilities by further improving the results of existing traditional machine learning models in the field of Korean morphological analysis. Finally, since the results of the major related studies proposed in the literature were mostly conducted on the Sejong corpus, we would like to compare the performance improvement of the Sejong corpus with the results of previous studies. Although it is difficult to make a direct comparison due to slight differences in implementation conditions and evaluation criteria, it can be seen that the proposed dictionary-based morphological analysis model is not up to the latest research results, but by incorporating a re-ranking model, it can secure performance that is comparable to the existing research.

    However, the entire morphological analysis model including the reranking model is not suitable for real-time processing, but it is expected that by reflecting the cases whose ranks are changed through the reranking model as feedback to the dictionary-based morphological analysis model, it is possible to obtain near-improved morphological analysis performance. The improved dictionary-based morphological analysis model can then be used as input to the reranking model, so it is expected that a gradually improving morphological analysis model can be obtained through this iterative feedback loop.

    \section{Conclusion}\label{sec:conclusion}

    This research signifies a progressive stride in the realm of Korean morphological analysis by seamlessly merging conventional dictionary-based techniques with advanced deep learning methodologies. Our findings indicate that while relying solely on dictionary-based morphological analysis does not surpass the efficacy of some existing models, the integration of a BERT-based re-ranking system notably enhances the accuracy, establishing a new standard in this domain.

    While the enhancement in performance comes at the cost of augmented computational demand, the introduced methodology offers an intriguing avenue for continuous enhancements. This innovative amalgamation of classical dictionary approaches and cutting-edge machine learning methodologies paves the way for groundbreaking advancements in the intricate and multifaceted domain of Korean linguistic processing.

    Future endeavors in this domain should emphasize refining this harmonious integration to achieve even higher precision in morphological analysis while optimizing computational efficiency. Moreover, our observations hint at the potential of employing a probabilistic model to discern areas where inaccuracies are likely to arise, enabling the retrieval of more accurate interpretations from a narrower candidate pool. The parallels between this initiative and the challenges of translation quality estimation suggest that insights from the latter could further inform and bolster the efficacy of our approach.

    %\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
    \bibliography{references}

\end{document}

### 2023-11-19 contents/draft.tex
Updates from Overleaf

@@
 \begin{document}
-    \title{Improvement of Korean Morphological Analysis System \\Through Transformer-based Re-ranking}
+    \title{Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking}
 
@@
 
-    \abstract[Abstract]{Korean morphological analysis plays a basic and important role enough to be called the first step in Korean language analysis.
-Due to the nature of Korean agglutinative words, it was difficult to build an automatic analysis system because the analysis was not completed with part-of-speech tagging alone, as in English.
-In addition, various methods for morphological analysis have been proposed, but efficient methods such as BPE are mainly used in applications intended to be used as tokenizers for deep learning.
-In this paper, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
-For a number of various cases whose rankings have been changed through re-ranking, it is possible to improve performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system in the future.
-Through experiments, we showed that the proposed method effectively improved performance by reducing errors by more than 30\% in both the spoken language model and the written language model.}
-    \keywords{Korean morphological analysis, natural language understanding, deep learing, pretrained transformer encoder, re-ranking}
+    \abstract[Abstract]{Korean morphological analysis is a fundamental step in analyzing the Korean language.
+Owing to the nature of Korean agglutinative words, building an automatic analysis system is difficult because parts-of-speech tagging independently is insufficient to complete analysis, as in English.
+In addition, various methods for morphological analysis have been proposed; however, efficient methods, such as BPE (Byte Pair Encoding), are mainly used in applications intended to be used as tokenizers for deep learning.
+In this study, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
+For cases whose rankings have been changed through re-ranking, it is feasible to improve the performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system.
+Through experiments, we demonstrate that the proposed method effectively improves performance via reducing errors by over 30\% in both spoken and written language models.}
+    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}
 
@@
 
-    Korean morphological analysis is the process of determining parts of speech by finding morphemes, which are the smallest units of linguistic expression that have an independent meaning in a sentence.
-    In an isolating language like English, this can be done relatively easily by tagging parts of speech sequentially, but in Korean, the nature of the agglutinative language requires separating endings or investigatives and restoring inflections to their original form.
-    In addition, since the basic input of other Korean analysis tasks is often a separated morpheme, the accuracy of morphological analysis greatly affects the performance of Korean analysis.
-    Modern high-performance deep learning methods in natural language processing use a tokenization process that breaks text into smaller units, and then converts each token into a vector as an input to the computational model~\cite{Mikolov2013}.
-    In this case, the token unit is mainly subword units, and to reflect the characteristics of Korean, subword tokenization with separated morphemes is attempted in advance~\cite{SongHJ2021}.
-    Using the results of morphological analysis for this tokenization process improves the overall performance of the analysis by reflecting the semantic units of Korean, but requires a highly accurate and fast morphological analyzer.
+    Korean morphological analysis is the process of determining parts of speech by identifying morphemes, which are the smallest units of linguistic expression with independent meanings in a sentence.
+    In an isolating language, such as English, this identification can be achieved relatively easily by tagging parts of speech sequentially.
+However, in Korean, the nature of the agglutinative language requires separating endings or postpositions and restoring inflections to their original form.
+    In addition, because the basic input of other Korean analysis tasks is often a separate morpheme, the accuracy of the morphological analysis significantly affects the performance of Korean analysis.
+    Modern high-performance deep learning methods in natural language processing (NLP) use a tokenization process that breaks the text into smaller units and converts each token into a vector as an input to the computational model~\cite{Mikolov2013}.
+    Here, the token unit is mainly a subword unit, and to reflect the characteristics of a Korean subword, tokenization with separate morphemes is attempted in advance~\cite{SongHJ2021}.
+    Using the results of the morphological analysis for this tokenization process improves the overall performance of the analysis by reflecting the semantic units of Korean.
+This requires a highly accurate and fast morphological analyzer.
 
-    Various approaches have been proposed for morphological analysis, which plays a fundamental and important role in Korean language analysis~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
-    In general, when people understand speech or writing, they try to make sense of it using the vocabulary and concepts they know.
-    While there are ways to use rules or dictionaries to reflect this way of understanding~\cite{KwonHC1991}, the problem is that it becomes difficult to build and maintain a dictionary for vocabulary that appears in every text.
-    Therefore, methods for tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016}, and studies to improve them have been carried out continuously~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
-    From a mechanical point of view, syllable-by-syllable morphological analysis can be done either by tagging syllable-by-syllable and then applying a base form restoration dictionary~\cite{ShimKS2011, LeeCH2016}, or by tagging syllable-by-syllable with the base form already restored~\cite{YounJY2021}.
-    However, syllable-by-syllable morphological analysis has limitations in that it is difficult to accurately identify morpheme boundaries, and it is difficult to learn long-term contextual information as the length of the sequence increases.
-    In this paper, the former is referred to as dictionary-based morphological analysis, and the latter is referred to as syllable-unit morphological analysis.
-    Both methods also share the limitation that they are trained on a manually labeled corpus and cannot accurately analyze new syllable combinations or morphemes that do not appear in the training corpus.
-    In recent years, with the development of the Internet and the spread of open source and open data, web texts, corpora, language resources, and knowledge shared by different people have accumulated significantly.
-    The reduced cost of building and maintaining a dictionary can be a great opportunity to overcome the limitations of dictionary-based methods.
+    Various approaches have been proposed for morphological analysis, which is crucial in Korean language analysis~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
+    In general, when people understand speech or written text, they attempt to make sense of it using vocabulary and concepts that they are familiar with.
+    While there are approaches to use rules or dictionaries to reflect this understanding~\cite{KwonHC1991}, it becomes difficult to build and maintain a dictionary for the vocabulary that appears in each text.
+    Therefore, methods for tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016} and studies have been conducted to improve them ~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
+    From a mechanical perspective, syllable-by-syllable morphological analysis can be performed either by tagging syllable-by-syllable and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016}, or by tagging syllable-by-syllable with the base form already restored~\cite{YounJY2021}.
+    However, syllable-by-syllable morphological analysis has limitations, in that it is difficult to accurately identify morpheme boundaries and learn long-term contextual information as the length of the sequence increases.
+    In this study, the former is referred to as dictionary-based morphological analysis and the latter as syllable-unit morphological analysis.
+    Both methods are trained on a manually labeled corpus and cannot accurately analyze new syllable combinations or morphemes that do not appear in the training corpus.
+    Recently, with the development of the Internet and the spread of open sources as well as open data, web texts, corpora, language resources, and knowledge shared by different people have accumulated significantly.
+    The reduced cost of building and maintaining a dictionary provides a significant opportunity to overcome the limitations of dictionary-based methods.
 
-    Against this background, this paper considers how the dictionary-based morphological analysis method used by MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis in tokenizers, an essential preprocessing tool for deep learning, can be effectively improved by deep learning, and proposes a method.
-    The dictionary-based morphological analysis method~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018} trained by the CRF method~\cite{Lafferty2001} lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph, and finds the optimal morphological analysis path within it.
-    The process of finding the best path in the lattice uses the Viterbi algorithm~\cite{Viterbi1967}, which finds the path that minimizes the cost of each morpheme node and the sum of the neighborhood costs of two consecutive morphemes.
-    The main types of errors in these dictionary-based morphological analysis methods are when new words not in the dictionary are used in a sentence, or when the optimal path calculation selects the wrong result due to a bias.
-    For example, it may be less costly to select one long morpheme than several short morphemes, but it may sometimes be the wrong analysis.
-    The main motivation for this research is that the path that minimizes the sum of all costs for nodes and links may not be the optimal path.
+    Against this background, this study considers how the dictionary-based morphological analysis method used by MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis in tokenizers, which is an essential preprocessing tool for deep learning, can be effectively improved, and a method is proposed.
+    The dictionary-based morphological analysis method~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018} trained by the CRF (Conditional Random Fields) method~\cite{Lafferty2001} lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph and determines the optimal morphological analysis path within it.
+    The process of determining the optimal path in the lattice uses the Viterbi algorithm~\cite{Viterbi1967}, which determines the path that minimizes the cost of each morpheme node and the sum of the neighborhood costs of two consecutive morphemes.
+    The main types of errors in these dictionary-based morphological analysis methods occur when new words that are not in the dictionary are used in a sentence, or when the optimal path calculation selects the incorrect result owing to bias.
+    For example, it may be cost-effective to select one long morpheme than several short morphemes, but this may often lead to an incorrect analysis.
+    The main motivation for this study was that the path that minimizes the costs for the nodes and links may not be the optimal path.
 
-    In order to identify the cases where a suboptimal solution is actually the best solution according to the best path calculation, we modified the best path calculation method to generate suboptimal analysis results and check the extent to which they are correct.
-    While there are many different ways to choose the next best path, we used the method of replacing a morpheme node on the optimal path with a lower ranked node.
-    As shown in Table~\ref{tab:maximum-performance}, we were able to confirm the extent to which analysis performance could be improved by replacing the optimal path with a lower-ranked node.
-    We can think of the problem of finding the actual correct answer among these generated suboptimals as similar to the problem of re-ranking search results in information retrieval~\cite{BaeYJ2021}.
-    Previously, in ~\cite{ChoiYS2018}, the N-best analysis results generated by the seq2seq model were re-ranked based on a convolutional neural network to improve performance.
-    In this study, the re-ranking was performed using two BERT models of different types and forms as proposed in ~\cite{Nogueira2019}.
-    The experimental results show that the first stage re-ranking improves the performance by more than 20\% over the previous written and spoken models, and the second stage re-ranking with a different type of input and a different type of pre-trained model further improves the performance by more than 30\% over the previous written and spoken models.
+    To identify cases in which a suboptimal solution is actually the best solution according to the best path calculation, we modified the best path calculation method to generate suboptimal analysis results and verified the extent to which they are correct.
+    Although there are numerous different approaches to select the next-best path, we used the method of replacing a morpheme node on the optimal path with a lower-ranked node.
+    As shown in Table~\ref{tab:maximum-performance}, we confirm the extent to which the analysis performance can be improved by replacing the optimal path with a lower-ranked node.
+    We can consider the problem of finding the correct answer among the generated sub-optimals, similar to the problem of re-ranking search results in information retrieval~\cite{BaeYJ2021}.
+    In ~\cite{ChoiYS2018}, the N-best analysis results generated by the seq2seq model were re-ranked based on a convolutional neural network to improve the performance.
+    In this study, re-ranking was performed using two BERT models of different types and forms, as proposed in ~\cite{Nogueira2019}.
+    Experimental results show that first-stage re-ranking improves the performance by over 20\% over previously written and spoken models, and second-stage re-ranking with a different type of input and a different type of pre-trained model further improves the performance by more than 30\% over previously written and spoken models.
 
-    With this method, the performance of the dictionary-based morphological analysis method could be further improved, but the overall analysis time increases when the morphological analysis system is configured including the re-ranking model itself.
-    However, it is possible to use the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in the dictionary, similar to the backpropagation process in a typical neural network.
+    With this method, the performance of the dictionary-based morphological analysis method could be further improved; however, the overall analysis time increased when the morphological analysis system was configured, including the re-ranking model itself.
+    However, it is feasible to use the results of multiple reranked morpheme analyses to update the connection costs between morphemes in a dictionary, similar to the backpropagation process in a typical neural network.
     It is also expected that the morphological analysis system with improved connection costs will be able to generate better re-ranking candidates, which will further improve performance by doing so iteratively.
-    Further research is needed for this in the future, and in this paper, only the performance improvement through the second stage re-ranking was covered as the scope of the study.
-    The main contributions of this study are as follows:
+    Further research is required in the future.
+    In this study, only performance improvement using the second-stage re-ranking was covered as the scope of the study.
+    The main contributions of this study are as follows.
     \begin{enumerate}
-        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node, and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
-        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To improve the performance of dictionary-based analysis by re-ranking the morphological analysis results, we propose to extend the performance improvement by using different BERT models to perform two rounds of re-ranking.
-        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We propose a new method for updating connection costs in dictionaries based on the results of reranked morphological analysis, and provide directions for future research by suggesting improvements and directions for future research.
+        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
+        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To improve the performance of dictionary-based analysis by re-ranking the morphological analysis results, we propose extending the performance improvement using different BERT models to perform two rounds of re-ranking.
+        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We propose a new method for updating dictionary connection costs based on re-ranked morphological analysis results.
+We also outline directions for future research, suggesting potential improvements.
     \end{enumerate}
@@
 
-    This paper is organized as follows:
-    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study, and in Section ~\ref{sec:morphological-analysis-model}, we discuss how to configure and train a dictionary-based morphological analysis system.
-    In Section ~\ref{sec:re-ranking-model}, we discuss how to generate secondary results of morphological analysis and produce re-ranking data, and propose a method for training a two-stage re-ranking model.
-    In Section ~\ref{sec:results}, we discuss the results of performance improvement by morphological analysis model and re-ranking model.
-    Finally, in Section ~\ref{sec:conclusion}, we conclude the paper and discuss the limitations of this study and the direction of future research.
+    The remainder of this paper is organized as follows.
+    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
+In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
+    In Section ~\ref{sec:re-ranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
+    In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
+    Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.
 
@@
 
-    Korean morphological analysis has seen an influx of various methodologies over the years~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
-The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to come up with inventive solutions, many of which have laid the groundwork for future research.
+    Korean morphological analyses have seen an influx of various methodologies in recent years~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
+The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to develop inventive solutions, many of which have laid the groundwork for future research.
 
     \subsection{Traditional Dictionary-based Approaches}\label{subsec2.1}
-    The earliest attempts at Korean morphological analysis heavily depended on rule-based systems and dictionary-based methods~\cite{KwonHC1991}.
-These methodologies essentially employed predefined sets of linguistic rules or large dictionaries to detect morphemes and determine parts of speech.
-One of the most significant advantages of such an approach is its deterministic nature, which can lead to high accuracy when the input text closely adheres to the rules or dictionaries used.
-However, they are notably challenging to scale and update, particularly with the constant evolution of the language and emergence of new words.
-The dynamic nature of language, especially in the age of the internet, has made maintaining comprehensive dictionaries labor-intensive.
+    The earliest attempts at Korean morphological analysis relied heavily on rule- and dictionary-based methods~\cite{KwonHC1991}.
+These methodologies employ predefined sets of linguistic rules or large dictionaries to detect morphemes and determine parts of speech.
+One of the most significant advantages of this approach is its deterministic nature, which can lead to high accuracy when the input text closely adheres to the rules or dictionaries used.
+However, it is challenging to scale and update them, particularly with the constant evolution of language and the emergence of new words.
+The dynamic nature of language, particularly in the Internet age, has made the maintenance of comprehensive dictionaries labor-intensive.
 
     \subsection{Syllable-unit Morphological Analysis}\label{subsec2.2}
-    In an attempt to bypass the limitations of dictionary-dependence, syllable-by-syllable morphological analysis emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
-This method either tags each syllable and then applies a base form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}.
-One notable drawback is the challenge in accurately pinpointing morpheme boundaries.
-Furthermore, as sequences increase in length, the system finds it increasingly challenging to understand long-term contextual data.
+    To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
+This method either tags each syllable and then applies a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}.
+One notable drawback is the challenge of accurately pinpointing morpheme boundaries.
+Furthermore, as the sequences increase in length, the system finds it increasingly challenging to understand long-term contextual data.
 
     \subsection{Deep Learning and Tokenization}\label{subsec2.3}
-    The advent of deep learning has reshaped the landscape of Korean morphological analysis.
-High-performance deep learning models in NLP now employ tokenization, dividing the text into smaller units and then converting these tokens into vectors as an input to the computational model~\cite{Mikolov2013}.
-Especially significant is the attempt to conduct subword tokenization, incorporating separated morphemes to cater to Korean linguistic characteristics.
-In particular, it is noteworthy that we attempted to tokenize subwords by incorporating segmented morphemes to suit the linguistic characteristics of Korean, and it is known that incorporating accurate morpheme analysis results into tokenization can improve overall analysis performance.
+    The advent of deep learning has reshaped the Korean morphological analysis landscape.
+High-performance deep learning models in NLP employ tokenization, dividing the text into smaller units and then converting these tokens into vectors as an input to the computational model~\cite{Mikolov2013}.
+The attempt to conduct subword tokenization, incorporating separate morphemes to cater to Korean linguistic characteristics is particularly significant.
+Incorporating accurate morpheme analysis results into tokenization can improve overall analysis performance.
 
-    However, with the progression of technology and accessibility to vast amounts of data, the possibility of integrating dictionary-based methods with deep learning techniques emerged.
+    With advancements in technology and access to large datasets, the potential to integrate dictionary-based methods with deep learning techniques has emerged.
 As motivated in our study, MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis, utilized dictionary-based morphological analysis trained by the CRF method~\cite{Lafferty2001}.
 This method attempts to find the optimal morphological analysis path by forming a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018}.
-The amalgamation of dictionary-based methods with deep learning, as explored in our research, signifies the latest stride in this journey, aiming to harness the strengths of both approaches.
-Future research avenues include refining these hybrid methods and further exploring the capabilities of end-to-end models for this complex task.
+The amalgamation of dictionary-based methods with deep learning, as explored in our research, signifies the latest strides in this journey aimed at harnessing the strengths of both approaches.
+Future research avenues include refining these hybrid methods and exploring the capabilities of end-to-end models.
 
@@
 
-    A representative corpus for training Korean morphological analysis models is the Sejong Morphological Analysis Corpus, often referred to as the Sejong Corpus.
-The Sejong Corpus, a major output of the 21st Century Sejong Project, contains 15 million words and remains a mainstay of Korean morphological analysis research~\cite{ChoeMW2008}.
+    A representative corpus for training Korean morphological analysis models is the Sejong morphological analysis corpus, which is often referred to as the Sejong corpus.
+The Sejong corpus, a major output of the 21st Century Sejong Project, contains 15 million words and is the mainstay of Korean morphological analysis research~\cite{ChoeMW2008}.
 
     Subsequent efforts have extended and refined this foundational work.
-The University of Ulsan, addressing the limitations of the Sejong corpus~\cite{KimIH2010}, introduced [UCorpus], an expanded corpus of 63 million words.
-This expanded corpus not only added new data, but also corrected errors in the original Sejong corpus~\cite{UCorpusHG}.
-To take this a step further, the National Institute of the Korean Language launched a massive Korean corpus construction project in 2018.
+The University of Ulsan addressed the limitations of the Sejong corpus~\cite{KimIH2010} and introduced [UCorpus], an expanded corpus of 63 million words.
+This expanded corpus not only adds new data but also corrects errors in the original Sejong corpus~\cite{UCorpusHG}.
+To further extend this step, the National Institute of Korean Language launched a massive Korean corpus construction project in 2018.
 The fruits of this labor, a corpus called <Everyone Corpus>, were released to the public in 2020~\cite{EveryoneCorpus}.
-A special offshoot of this project produced a morpheme-tagged corpus of 3 million words, including spoken language~\cite{KimIH2019}.
+A special offshoot of this project produced a morpheme-tagged corpus of three million words, including spoken languages ~\cite{KimIH2019}.
 
@@
 
-    In order to effectively train a dictionary-based morpheme analysis model, the morpheme-tagged corpus, typically represented in lemma form, needs to be transformed to include boundary information between morphemes in its surface form.
-Crucial to this transformation is string alignment, a process that accounts for discrepancies between lemma and surface forms in the Korean morphological analysis corpus.
+    To train a dictionary-based morpheme analysis model effectively, the morpheme-tagged corpus, typically represented in lemma form, must be transformed to include the boundary information between morphemes in its surface form.
+Crucial to this transformation is string alignment, a process that accounts for the discrepancies between lemma forms and surface forms in the Korean morphological analysis corpus.
 
-    In this research, string alignment was performed using the Smith-Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}).
-Each aligned sentence containing a morpheme tag can be converted into a training sample tailored for dictionary-based morphological analysis.
+    In this study, string alignment was performed using the Smith--Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}).
+Each aligned sentence containing a morpheme tag was converted into a training sample tailored for dictionary-based morphological analysis.
 
-    The resulting table data in Figure~\ref{fig:sample} illustrates this process.
-Here, each row acts as a lexical unit.
-The first four columns contribute to feature generation, while the last four columns facilitate post-lemmatization.
-Using the above morphological corpus, a large number of training samples can be generated according to the process shown in Figure~\ref{fig:sample}.
-Except for the evaluation samples, the remaining sentences are used to train the dictionary-based morphological analysis model via the CRF algorithm.
-The output of this training allows the calculation of the costs associated with each morpheme node and the linking of two consecutive morphemes.
-This in turn allows the discovery of the optimal path using the Viterbi algorithm.
+    The resulting table in Figure~\ref{fig:sample} illustrates this process.
+Each row acts as a lexical unit.
+The first four columns contribute to feature generation, whereas the last four columns facilitate post-lemmatization.
+Using the morphological corpus above, a large number of training samples can be generated according to the process shown in Figure~\ref{fig:sample}.
+With the exception of the evaluation samples, the remaining sentences were used to train the dictionary-based morphological analysis model using the CRF algorithm.
+The output of this training allowed the calculation of the costs associated with each morpheme node and the linking of two consecutive morphemes.
+This, in turn, allowed the discovery of an optimal path using the Viterbi algorithm.
 
@@
 
-    Figure~\ref{fig:lattice} shows a snapshot of the lattice structure, an integral part of morphological analysis.
-Part (1) shows a fragment of the lattice structure formed when the example sentence from Figure~\ref{fig:sample} is entered.
-Meanwhile, part (2) shows the optimal path as determined by the Viterbi algorithm.
+    Figure~\ref{fig:lattice} presents a snapshot of the lattice structure, which is an integral part of the morphological analysis.
+(1) shows a fragment of the lattice structure formed when the example sentence in Figure~\ref{fig:sample} is entered.
+(2) shows the optimal path determined using the Viterbi algorithm.
 
-    However, the path inferred by the trained model may differ from the correct solution constructed by a human.
-The nodes marked with stars in part (1) represent the correct nodes.
-The upper left number of each node indicates the ranking of the nodes accessible at each decoding point.
-It can be seen that the choices made at certain moments can deviate from the correct solution.
-In order to improve the performance of the analysis, it is imperative to develop mechanisms to correct these discrepancies.
+    However, the path inferred by the trained model may differ from the correct solution constructed by humans.
+The nodes marked with stars in (1) represent correct nodes.
+The upper-left number of each node indicates the ranking of the nodes accessible at each decoding point.
+The choices made at certain moments deviate from the correct solution.
+To improve analytical performance, mechanisms to correct these discrepancies must developed.
 
@@
 
-    While dictionary-based morphological analysis offers significant advances in Korean language processing, its optimal paths occasionally diverge from the correct solutions that humans understand.
-This divergence underscores the need for a model that re-evaluates these primary results and reorients them to achieve higher accuracy.
+    Although dictionary-based morphological analysis offers significant advances, its optimal paths occasionally diverge from the correct solutions that humans understand.
+This divergence underscores the need for a model that reevaluates these primary results and reorients them to achieve higher accuracy.
 This method, called "re-ranking," involves generating multiple analyses of an input and then reordering them based on a new set of criteria or models, thereby improving the overall quality of the results.
@@
 
-    Before re-ranking can begin, multiple analyses, typically referred to as N-best paths, of the input sentence are generated.
-    This involves extracting the top N analyses from the lattice structure in general.
-    In this study, a novel approach has been introduced to generate secondary paths, as shown in part (3) of Figure~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
-    Encouragingly, some of these secondary paths provided alternatives that reconciled incorrect answers with the correct ones.
-    Similarly, paths modified by favoring the third-best node were called tertiary paths, and this naming convention continued for subsequent paths.
-    In our preliminary test, the secondary paths, including the optimal and some suboptimal paths, were shown to cover the majority of correct morphological analyses as measured by human judgments.
-(See Table~\ref{tab:maximum-performance})
+    Before reranking begins, multiple analyses, typically referred to as the N-best paths, of the input sentence are generated.
+This involves extracting the top N atoms from the lattice structure.
+In this study, a novel approach is introduced to generate secondary paths, as shown in (3) of Figure~\ref{fig:lattice}, by selecting the second-best node rather than each best node constituting the path from the best-path result.
+Some of these secondary paths provided alternatives that reconciled incorrect with correct answers.
+Similarly, paths modified by favoring the third-best node were called tertiary paths, and this naming convention was continued for subsequent paths.
+In our preliminary test, the secondary paths, including the optimal and suboptimal paths, were shown to cover the majority of the correct morphological analyses as measured through human evaluations.
+(Refer to Table~\ref{tab:maximum-performance}).
 
@@
 
-    BERT (Bidirectional Encoder to Transformer Representation) models~\cite{Devlin2019} have revolutionized many natural language processing tasks by understanding the context in which words appear in text.
+    Bidirectional Encoder Representations from Transformers (BERT) models~\cite{Devlin2019} have revolutionized many natural language processing tasks by understanding the context in which words appear in text.
 In this study, we attempt to leverage the power of BERT to reorder the generated secondary paths.
-We labeled the generated secondary paths with scores related to morphological analysis performance in order to fine-tune a pre-trained BERT model specialized for Korean with a large amount of Korean text.
-After pre-testing several scoring methods on a modest scale, we found that using scores based on the degree of error, rather than scores based on accuracy, to widen the gap between correct and incorrect answers is effective for learning.
+We labeled the generated secondary paths with scores related to the morphological analysis performance to fine-tune a pre-trained BERT model specialized for Koreans with excess amount Korean text.
+After pre-testing several scoring methods on a modest scale, we found that using scores based on the degree of error rather than scores based on accuracy by widen the gap between correct and incorrect answers is effective for learning.
 
-    Once the BERT model has been fine-tuned and trained for the reranking task, it will be able to predict a reranking score for each path in the secondary path list.
-This means that, taking into account the context, morphological organization, and other essential linguistic features of the path, the model will assign a score for each path.
-The paths are then re-ranked according to this score, and the path with the highest score is selected as the best morphological analysis result.
+    Once the BERT model is fine-tuned and trained for the re-ranking task, it can predict a re-ranking score for each path in the secondary path list.
+This implies that considering the context, morphological organization, and other essential linguistic features of the path, the model assigns a score to each path.
+The paths were then re-ranked according to this score, and the path with the highest score was selected for the best morphological analysis.
 
@@
 
-    Given the complexity of the Korean language, a single reranking step does not always yield the most accurate results.
-Therefore, we propose a two-step reranking approach, as in ~\cite{Nogueira2019}.
+    Given the complexity of the Korean language, a single re-ranking step does not constantly yield accurate results.
+Therefore, we propose a two-step re-ranking approach as described in ~\cite{Nogueira2019}.
 
-    In the first step, we re-rank the secondary paths generated using the BERT model as described in section ~\ref{subsec4.3}.
-In the second step, we introduce another BERT variant that is optimized for a different set of linguistic features or trained on a different dataset.
-This allows us to perform a fine-grained re-evaluation, further refining the list and pushing the more contextually accurate paths to the top.
+    In the first step, we re-rank the secondary paths generated using the BERT model, as described in Section ~\ref{subsec4.3}.
+In the second step, we introduced another BERT variant that was optimized for a different set of linguistic features or trained on a different dataset.
+This allowed us to perform a fine-grained re-evaluation, further refine the list, and push more contextually accurate paths to the top.
 
-    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage performs a first reranking, taking as input a secondary path in morphologically tagged lemma form.
-It then performs a second reranking, again taking as input the path reranked in stage 1 and the original input sentence.
-This is done to improve the effectiveness, since it didn't work very well when given the same type of input.
-
-    \subsection{Iterative Updatability}\label{subsec4.5}
-
-    The re-ranked paths are then integrated with the original dictionary-based morphological analysis.
-The connection costs between morphemes in the dictionary are updated based on feedback from the re-ranking model.
-Over time, this feedback loop ensures that the morphological analysis model becomes more closely aligned with human understanding and minimizes discrepancies in optimal path selection.
+    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage performs the first re-ranking, taking as input a secondary path in morphologically tagged lemma form.
+It then performs a second re-ranking, again taking as input the path re-ranked in stage 1 and the original input sentence.
+This was conducted to improve effectiveness, as it was ineffective given the same type of input.
 
@@
 
-    In our effort to enhance Korean morphological analysis, we evaluated the performance of the proposed deep learning integrated dictionary-based morphological analysis method.
-This section presents the results of the experimental evaluation, taking into account the improvement over conventional methods and the effectiveness of our re-ranking model.
+    We evaluated the performance of the proposed deep learning-integrated dictionary-based morphological analysis method.
+This section presents the results of the experimental evaluation considering the improvements over conventional methods and the effectiveness of our re-ranking model.
 
@@
 
-    For our experiments, we used the Sejong corpus (the version used in ~\cite{NaSH2014, NaSH2015, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone Corpus\cite{EveryoneCorpus}.
-For comparison with previous studies, the Sejong corpus was trained with a single model without separation.
-UCorpus and Everyone Corpus provided separate spoken corpus consisting of drama scripts and broadcast dialogues, while UCorpus separated documents that were thought to be close to spoken language and further organized them into a semi-spoken corpus.
-Because UCorpus and Everyone Corpus have synergistic effects when trained together, we trained the models separately for written and spoken language, rather than separating them by source.
-The statistics of the full data for the three types of models are presented in Table~\ref{tab:data-statistics}, and due to the large volume of UCorpus, we randomly selected some of them for the actual model training.
+    For our experiments, we used the Sejong corpus (versions used in ~\cite{NaSH2014, NaSH2015, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone Corpus\cite{EveryoneCorpus}.
+For comparison with previous studies, the Sejong corpus was trained using a single model without separation.
+The UCorpus and Everyone Corpus provided a separate spoken corpus with drama scripts and broadcast dialogues, while UCorpus separated documents that were considered to be close to spoken language and further organized them into a semi-spoken corpus.
+Because UCorpus and Everyone Corpus have synergistic effects when trained concurrently, we trained the models separately for written and spoken language rather than separating them by source.
+The statistics of the full data for the three types of models are presented in Table~\ref{tab:data-statistics}.
+Because of the large volume of UCorpus, we randomly selected some of them to train the actual model.
 
-    We transformed this organized morphological corpus with the training example transformation process described in section ~\ref{subsec3.2} to generate samples for training a dictionary-based morphological analysis model.
+    We transformed this organized morphological corpus using the training–example transformation process described in Section ~\ref{subsec3.2} to generate samples for training the dictionary-based morphological analysis model.
 
     \begin{table*}[]
-        \caption{Performance comparison between morphological analysis systems without Re-ranking}\label{tab:performance-without-reranking}
+        \caption{Performance comparison between morphological analysis systems without re-ranking}\label{tab:performance-without-reranking}
         \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
@@
 
-    To measure the accuracy of the morphological analysis model, the correctness of the N-Best path, and the ranking accuracy of the reranking model, we used eojeol accuracy and morpheme F1 scores as evaluation metrics.
-To verify that they actually produced correct morphological analysis results, we measured the degree of agreement with human annotation on aforementioned corpus.
-However, due to the slightly different criteria and style of the annotators who labeled the different kinds of corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
+    To measure the accuracy of the morphological analysis model, correctness of the N-best path, and ranking accuracy of the reranking model, we used the eojeol accuracy and morpheme F1 scores as evaluation metrics.
+To verify that they produced the correct morphological analysis results, we measured the degree of agreement with human annotations on the corpus.
+However, owing to the slightly different criteria and styles of the annotators who labeled the different types of corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
     \begin{itemize}
-        \item Sentences containing unanalyzable tags (NF, NA, NV) were excluded from both training and evaluation.
-        \item As for the tagsets, we excluded 3 unanalyzable tags from the 45 Sejong tagsets and used 42 tagsets.
+        \item Sentences containing unanalyzable tags (NF, NA, and NV) were excluded from both training and evaluation.
+        \item As for the tagsets, we excluded three unanalyzable tags from the 45 Sejong tagsets and used 42 tagsets.
         \item Each tag output by the MeCab-ko system was converted to the corresponding tag in the Sejong tagset.
@@
 %`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeo]', or `았[ass]'
-        \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus.
-        \item As mentioned in ~\cite{KimIH2010}, connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
-        \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, so we did not distinguish between them.
+        \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus only.
+        \item As mentioned in ~\cite{KimIH2010}, connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, to ensure that we evaluated them without distinguishing them.
+        \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, hence, we did not distinguish between them.
 %`것[geot]' and `거[geo]'
-        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes, so we evaluated them without distinguishing between them.
-        \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective, and human annotators have slightly different standards, so they were also evaluated without distinguishing them.
+        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes, hence, we evaluated them without distinguishing between them.
+        \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective.
+Human annotators have slightly different standards, and thus they were also evaluated without distinguishing the nouns.
     \end{itemize}
@@
 
-    First, we compared the initial results of the dictionary-based morphological analysis model trained with the method described in Section ~\ref{sec:morphological-analysis-model} with MeCab and syllable-based morphological analysis systems.
-(See Table~\ref{tab:performance-without-reranking}) The results show that the dictionary-based method we implemented is better than the existing MeCab system, but it is different from human judgment due to the limitations mentioned above, and it does not reach the performance of existing syllable-based morphological analysis systems.
-We also found that the compatibility between the Sejong corpus and other corpora is not good, as the model trained on the Sejong corpus has guaranteed performance when evaluated on the Sejong corpus, and some performance degradation occurs on other corpora.
+    First, we compared the initial results of the dictionary-based morphological analysis model trained using the method described in Section ~\ref{sec:morphological-analysis-model} with those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
+The results show that the dictionary-based method implemented is superior to the existing MeCab system, but it differs from human evaluations owing to the limitations mentioned above, and it does not reach the performance of existing syllable-based morphological analysis systems.
+We also found that the compatibility between the Sejong corpus and other corpora is poor, as the model trained on the Sejong corpus has guaranteed performance when evaluated on the Sejong corpus, and some performance degradation occurs on other corpora.
 
     \begin{table*}[]
-        \caption{Performance comparison between morphological analysis systems with Two-staage Re-ranking}\label{tab:performance-with-reranking}
+        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}\label{tab:performance-with-reranking}
         \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
@@
 
-    Upon integrating the BERT-based re-ranking model, we observed a substantial enhancement in performance.
-Table~\ref{tab:maximum-performance} demonstrated that the re-ranking model was able to identify a better path in a significant proportion of cases.
-The first-stage re-ranking itself exhibited a performance improvement of over 20\% compared to traditional models.
-The subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by over 30\%.
+    Upon integrating the BERT-based re-ranking model, we observed substantial performance enhancement.
+Table~\ref{tab:performance-with-reranking} shows that the re-ranking model identified a better path in a significant proportion of cases.
+The first-stage re-ranking exhibited a performance improvement of over 20\% compared with traditional models.
+The subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
 
-    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:re-ranking-model} and compared the performance.
-    Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well on other Korean language understanding tasks, were used to fine-tune the re-ranking model.
-KPF-BERT receives Korean sentences as input, ETRI-ELECTRA receives morphological tagged sentence as input, and ETRI-RoBERTa receives morpheme-separated sentences as input.
-In the case of KPF-BERT and ETRI-RoBERTa, there may be problems with model learning due to the separation of morpheme tags into letter units during the tokenization process when the morpheme analysis results are received as input and reranked, so the morpheme tags of the mid-level classification unit were added as new tokens, and then training was performed.
-    As shown in Figure~\ref{fig:ranking}, for these three types of pre-trained language models, we first performed training with a re-ranking model using only the morphological analysis results, and then we performed training with a second re-ranking model using the top five morphological analysis results from the first re-ranking results along with the input sentences for other types of pre-trained language models.
-This is because preliminary tests have shown that given the same kind of model or the same kind of input, a model that is almost identical to the previously trained model is trained and performance is no longer improved.
+    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:re-ranking-model} and compared its performances.
+    Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well in other Korean language understanding tasks, were used to fine-tune the re-ranking model.
+KPF-BERT received Korean sentences as input, ETRI-ELECTRA received morphologically tagged sentences as input, and ETRI-RoBERTa receives morpheme-separated sentences as input.
+For KPF-BERT and ETRI-RoBERTa, there may be problems with model learning because of the separation of morpheme tags into letter units during the tokenization process when the morpheme analysis results were received as input and re-ranked, hence, the morpheme tags of the mid-level classification unit were added as new tokens, and then training was performed.
+    As shown in Figure~\ref{fig:ranking}, for these three types of pre-trained language models, we first performed training with a re-ranking model using only the morphological analysis results and then performed training with a second re-ranking model using the top five morphological analysis results from the first re-ranking results along with the input sentences for other types of pre-trained language models.
+Preliminary tests indicate that using the same type of model or input results in a nearly identical retrained model, with no further improvement in performance.
 
     The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone corpus.
-For the large number of sentences, we adopt a floating-point 16-bit technique while using four GPUs for distributed training, and were able to significantly reduce the time required to train.
-    In addition, the minibatch size was 120 with a max sequence length of 384 because the first reranking uses only the morphological analysis results as input, and the minibatch size was 40 with a max sequence length of 512 because the original input sentences are given as input along with the first morphological analysis results.
-And the learning rate was set to $2 \times 10^{-5}$ and AdamW is used as an optimization algorithm.
+For a large number of sentences, we adopted a floating-point 16-bit technique while using four GPUs for distributed training and significantly reduced the time required for training.
+    In addition, the minibatch size was 120 with a maximum sequence length of 384 because the first re-ranking uses only the morphological analysis results as input.
+The minibatch size was 40 with a maximum sequence length of 512 because the original input sentences were given as input along with the first morphological analysis results.
+The learning rate was set to $2 \times 10^{-5}$ and AdamW is used as the optimization algorithm.
 
-    Table~\ref{tab:performance-with-reranking} shows that incorporating the reranking model significantly improves performance compared to no reranking.
-The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is shown as 29\%, 27\%, and 20\% for the Sejong corpus, the combined written corpus, and the combined spoken corpus, respectively, with the first round of reranking, and the second round of reranking improved the performance more by increasing the rate to 34\%, 34\%, and 32\%, respectively.
-    These performance improvements show that the dictionary-based morphological analysis model outperforms traditional syllable-based morphological analysis systems, including many pre- and post-processing rule and dictionaries.
+    Table~\ref{tab:performance-with-reranking} shows that incorporating the re-ranking model significantly improves the performance compared with no re-ranking.
+The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is shown as 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking, and the second round of re-ranking improved the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
+    These performance improvements demonstrate that the dictionary-based morphological analysis model outperforms traditional syllable-based morphological analysis systems, including numerous pre- and post-processing rules and dictionaries.
 
@@
 
-    We found that the proposed transformer-based reranking technique consistently improves the results of existing morphological analysis models.
-These results open up new possibilities in the area of Korean morphological analysis by further improving the results of existing traditional machine learning models.
-    Finally, since the results of the major related works proposed in the literature are mostly conducted on the Sejong corpus, we would like to compare the performance improvement of the Sejong corpus with the results of previous studies.
+    We found that the proposed transformer-based re-ranking technique consistently improved the results of the existing morphological analysis models.
+These results open new possibilities in the area of Korean morphological analysis by further improving the results of existing traditional machine learning models.
+    Finally, because the results of the major related works proposed in the literature were mostly conducted on the Sejong corpus, we compared the performance improvement of the Sejong corpus with the results of previous studies.
 
-    We found that the proposed transformer-based reranking technique consistently improves the results of existing morphological analysis models.
-These results confirm that it opens up new possibilities by further improving the results of existing traditional machine learning models in the field of Korean morphological analysis.
-Finally, since the results of the major related studies proposed in the literature were mostly conducted on the Sejong corpus, we would like to compare the performance improvement of the Sejong corpus with the results of previous studies.
-Although it is difficult to make a direct comparison due to slight differences in implementation conditions and evaluation criteria, it can be seen that the proposed dictionary-based morphological analysis model is not up to the latest research results, but by incorporating a re-ranking model, it can secure performance that is comparable to the existing research.
+    We found that the proposed transformer-based re-ranking technique consistently improved the results of the existing morphological analysis models.
+These results confirm that it opens up new possibilities by further improving the results of existing traditional machine-learning models in the field of Korean morphological analysis.
+Finally, because the major related studies proposed in the literature were mostly conducted on the Sejong corpus, we compared the performance improvement of the Sejong corpus with the results of previous studies.
+Although it is difficult to make a direct comparison because of slight differences in implementation conditions and evaluation criteria.
+The proposed dictionary-based morphological analysis model is not up to the latest research results; however, by incorporating a re-ranking model, it can secure a performance that is comparable to existing research.
 
-    However, the entire morphological analysis model including the reranking model is not suitable for real-time processing, but it is expected that by reflecting the cases whose ranks are changed through the reranking model as feedback to the dictionary-based morphological analysis model, it is possible to obtain near-improved morphological analysis performance.
-The improved dictionary-based morphological analysis model can then be used as input to the reranking model, so it is expected that a gradually improving morphological analysis model can be obtained through this iterative feedback loop.
+    The entire morphological analysis model, including the re-ranking model, is not suitable for real-time processing.
+However, it is expected that by reflecting the cases whose ranks are changed through the re-ranking model as feedback to the dictionary-based morphological analysis model, it will be feasible to obtain near-improved morphological analysis performance.
+The improved dictionary-based morphological analysis model can then be used as input to the re-ranking model; therefore, it is expected that a gradually improvement in morphological analysis model can be obtained through this iterative feedback loop.
 
@@
 
-    This research signifies a progressive stride in the realm of Korean morphological analysis by seamlessly merging conventional dictionary-based techniques with advanced deep learning methodologies.
-Our findings indicate that while relying solely on dictionary-based morphological analysis does not surpass the efficacy of some existing models, the integration of a BERT-based re-ranking system notably enhances the accuracy, establishing a new standard in this domain.
+    This study signifies a progressive stride in Korean morphological analysis by seamlessly merging conventional dictionary-based techniques with advanced deep learning methodologies.
+Our findings indicate that while relying solely on dictionary-based morphological analysis does not surpass the efficacy of some existing models, the integration of a BERT-based re-ranking system notably enhances accuracy, establishing a new standard in this domain.
 
-    While the enhancement in performance comes at the cost of augmented computational demand, the introduced methodology offers an intriguing avenue for continuous enhancements.
-This innovative amalgamation of classical dictionary approaches and cutting-edge machine learning methodologies paves the way for groundbreaking advancements in the intricate and multifaceted domain of Korean linguistic processing.
+    While the performance improvement increases computational demand, the introduced methodology provides a promising avenue for continuous enhancement.
+This innovative amalgamation of classical dictionary approaches and cutting-edge machine-learning methodologies paves the way for groundbreaking advancements in the intricate and multifaceted domains of Korean linguistic processing.
 
-    Future endeavors in this domain should emphasize refining this harmonious integration to achieve even higher precision in morphological analysis while optimizing computational efficiency.
-Moreover, our observations hint at the potential of employing a probabilistic model to discern areas where inaccuracies are likely to arise, enabling the retrieval of more accurate interpretations from a narrower candidate pool.
-The parallels between this initiative and the challenges of translation quality estimation suggest that insights from the latter could further inform and bolster the efficacy of our approach.
+    Future endeavors in this domain should emphasize the refinement of this harmonious integration to achieve even higher precision in morphological analysis while optimizing computational efficiency.
+Moreover, our observations indicate the potential for employing a probabilistic model to discern areas where inaccuracies are likely to arise, thus enabling the retrieval of more accurate interpretations from a narrower candidate pool.
+The parallels between this initiative and the challenges of translation quality estimation suggest that insights from the latter can bolster the efficacy of our approach.
 
-    %\nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
     \bibliography{references}

### 2023-11-24 contents/draft.tex
Enter Key

@@
 
-    \abstract[Abstract]{Korean morphological analysis is a fundamental step in analyzing the Korean language.
+    \abstract[Abstract]{
+        Korean morphological analysis is a fundamental step in analyzing the Korean language.
         Owing to the nature of Korean agglutinative words, building an automatic analysis system is difficult because parts-of-speech tagging independently is insufficient to complete analysis, as in English.
@@
         For cases whose rankings have been changed through re-ranking, it is feasible to improve the performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system.
-Through experiments, we demonstrate that the proposed method effectively improves performance via reducing errors by over 30\% in both spoken and written language models.}
+        Through experiments, we demonstrate that the proposed method effectively improves performance via reducing errors by over 30\% in both spoken and written language models.
+    }
     \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}
@@
 
-    We transformed this organized morphological corpus using the training–example transformation process described in Section ~\ref{subsec3.2} to generate samples for training the dictionary-based morphological analysis model.
+    We transformed this organized morphological corpus using the training-example transformation process described in Section ~\ref{subsec3.2} to generate samples for training the dictionary-based morphological analysis model.
 

### 2023-11-27 contents/draft.tex
Misspelling: yeo -> yeot

@@
         \item Similarly, symbol, numeral, ending, and postposition in the same tag were converted to a single morpheme, and decimal expressions were treated as a single morpheme, including the midpoint and the numbers before and after.
-        \item If the first lemma letter of the ending is `[eo]', `[yeo]', or `[ah]', it is unified as `[eo]', and if it is `[eot]', `[yeo]', or `[ass]', it is unified as `[eot]'.
-%`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeo]', or `았[ass]'
+        \item If the first lemma letter of the ending is `[eo]', `[yeo]', or `[ah]', it is unified as `[eo]', and if it is `[eot]', `[yeot]', or `[ass]', it is unified as `[eot]'.
+%`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeot]', or `았[ass]'
         \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus only.

### 2023-11-27 contents/draft.tex
Remove redundancy in 5.5

@@
     We found that the proposed transformer-based re-ranking technique consistently improved the results of the existing morphological analysis models.
-    These results open new possibilities in the area of Korean morphological analysis by further improving the results of existing traditional machine learning models.
-    Finally, because the results of the major related works proposed in the literature were mostly conducted on the Sejong corpus, we compared the performance improvement of the Sejong corpus with the results of previous studies.
-
-    We found that the proposed transformer-based re-ranking technique consistently improved the results of the existing morphological analysis models.
     These results confirm that it opens up new possibilities by further improving the results of existing traditional machine-learning models in the field of Korean morphological analysis.

### 2023-11-28 contents/draft.tex
Table 2에 전체 데이터 통계 포함 Table 2를 앞으로 보냄 [Related Work] 섹션을 뒤로 보냄

@@
 \documentclass[AMS,STIX2COL]{WileyNJD-v2}
+\usepackage{makecell}
 
@@
 
-    \begin{center}
-        \begin{table*}[t]
-            \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
+    \begin{table*}[]
+        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}\label{tab:data-statistics}
         \centering
-            \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
+        \begin{tabular*}{500pt}{@{\extracolsep{\fill}}m{10mm}m{8mm}m{10mm}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{9mm}m{9mm}m{10mm}@{}}
             \toprule
-                & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
-                alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
+            \multirow{2}{*}{Corpus}                       & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
+            \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
+            ~                                             & ~                      & Sentences & Eojeols    & Morphs\newline/Sent & Sentences & Eojeols    & Morphs\newline/Sent & Sentences & Eojeols & Morphs\newline/Sent \\
             \midrule
-                no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
-                secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
-                tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
-                quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
-                quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
+            Sejong\newline Corpus                         & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
+            \midrule
+            \multirow{3}{*}{UCorpus}                      & written                & 5,456,101 & 62,462,158 & 25.1                & 4,998,560 & 57,393,332 & 25.4                & 53,003    & 598,413 & 25.0                \\
+            ~                                             & semi-spoken            & 393,770   & 3,401,444  & 18.4                & 334,061   & 2,960,146  & 19.4                & 38,960    & 332,285 & 18.6                \\
+            ~                                             & spoken                 & 627,380   & 2,819,427  & 10.9                & 429,215   & 2,295,940  & 13.0                & 62,399    & 279,545 & 11.1                \\
+            \midrule
+            \multirow{2}{*}{\makecell{Everyone \\Corpus}} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
+            ~                                             & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
             \bottomrule
         \end{tabular*}
-            \begin{tablenotes}
-                \footnotesize
-                \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
-                \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
-            \end{tablenotes}
+
     \end{table*}
-    \end{center}
 
@@
 
+    \begin{table*}[t]
+        \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
+        \centering
+        \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
+            \toprule
+            & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
+            alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
+            \midrule
+            no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
+            secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
+            tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
+            quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
+            quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
+            \bottomrule
+        \end{tabular*}
+        \begin{tablenotes}
+            \footnotesize
+            \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
+            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
+        \end{tablenotes}
+    \end{table*}
+
     To identify cases in which a suboptimal solution is actually the best solution according to the best path calculation, we modified the best path calculation method to generate suboptimal analysis results and verified the extent to which they are correct.
@@
     The remainder of this paper is organized as follows.
-    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
     In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
@@
     In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
+    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
     Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.
@@
     \end{figure*}
-
-    \section{Related Work}\label{sec:related-work}
-
-    Korean morphological analyses have seen an influx of various methodologies in recent years~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
-    The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to develop inventive solutions, many of which have laid the groundwork for future research.
-
-    \subsection{Traditional Dictionary-based Approaches}\label{subsec2.1}
-    The earliest attempts at Korean morphological analysis relied heavily on rule- and dictionary-based methods~\cite{KwonHC1991}.
-    These methodologies employ predefined sets of linguistic rules or large dictionaries to detect morphemes and determine parts of speech.
-    One of the most significant advantages of this approach is its deterministic nature, which can lead to high accuracy when the input text closely adheres to the rules or dictionaries used.
-    However, it is challenging to scale and update them, particularly with the constant evolution of language and the emergence of new words.
-    The dynamic nature of language, particularly in the Internet age, has made the maintenance of comprehensive dictionaries labor-intensive.
-
-    \subsection{Syllable-unit Morphological Analysis}\label{subsec2.2}
-    To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
-    This method either tags each syllable and then applies a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}.
-    One notable drawback is the challenge of accurately pinpointing morpheme boundaries.
-    Furthermore, as the sequences increase in length, the system finds it increasingly challenging to understand long-term contextual data.
-
-    \subsection{Deep Learning and Tokenization}\label{subsec2.3}
-    The advent of deep learning has reshaped the Korean morphological analysis landscape.
-    High-performance deep learning models in NLP employ tokenization, dividing the text into smaller units and then converting these tokens into vectors as an input to the computational model~\cite{Mikolov2013}.
-    The attempt to conduct subword tokenization, incorporating separate morphemes to cater to Korean linguistic characteristics is particularly significant.
-    Incorporating accurate morpheme analysis results into tokenization can improve overall analysis performance.
-
-    With advancements in technology and access to large datasets, the potential to integrate dictionary-based methods with deep learning techniques has emerged.
-    As motivated in our study, MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis, utilized dictionary-based morphological analysis trained by the CRF method~\cite{Lafferty2001}.
-    This method attempts to find the optimal morphological analysis path by forming a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018}.
-    The amalgamation of dictionary-based methods with deep learning, as explored in our research, signifies the latest strides in this journey aimed at harnessing the strengths of both approaches.
-    Future research avenues include refining these hybrid methods and exploring the capabilities of end-to-end models.
 
@@
     The paths were then re-ranked according to this score, and the path with the highest score was selected for the best morphological analysis.
-
-    \begin{table*}[]
-        \caption{Statistics on full data for training and evaluating three morphological analysis models}\label{tab:data-statistics}
-        \centering
-        \begin{tabular*}{500pt}{@{\extracolsep\fill}|c|c|rrr|rrr|@{\extracolsep\fill}}
-            \toprule
-            \multicolumn{2}{|c|}{\multirow{2}{*}{\textbf{Corpus}}} & \multicolumn{3}{c|}{\textbf{Training Set}} & \multicolumn{3}{c|}{\textbf{Test Set}} \\
-            \cmidrule{3-5} \cmidrule{6-8}
-            \multicolumn{2}{|c|}{~} & sentences & eojeols & morphemes & sentences & eojeols & morphemes \\
-            \midrule
-            \multicolumn{2}{|c|}{Sejong Corpus} & 194,822 & 2,681,582 & 6,033,785 & 49,922 & 678,578 & 1,527,803 \\
-            \midrule
-            \multirow{3}{*}{UCorpus}         & written     & 4,998,560 & 57,393,332 & 127,171,473 & 53,003 & 598,413 & 1,325,419 \\
-            ~                                & semi-spoken & 334,061   & 2,960,146  & 6,468,494   & 38,960 & 332,285 & 726,398   \\
-            ~                                & spoken      & 429,215   & 2,295,940  & 5,584,494   & 62,399 & 279,545 & 691,542   \\
-            \midrule
-            \multirow{2}{*}{Everyone Corpus} & written     & 129,352   & 1,713,367  & 3,944,118   & 14,442 & 191,223 & 440,052   \\
-            ~                                & spoken      & 137,869   & 714,021    & 1,440,746   & 19,789 & 85,316  & 170,523   \\
-            \bottomrule
-        \end{tabular*}
-    \end{table*}
 
@@
 
+    \section{Related Work}\label{sec:related-work}
+
+    Korean morphological analyses have seen an influx of various methodologies in recent years~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
+    The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to develop inventive solutions, many of which have laid the groundwork for future research.
+
+    \subsection{Traditional Dictionary-based Approaches}\label{subsec2.1}
+    The earliest attempts at Korean morphological analysis relied heavily on rule- and dictionary-based methods~\cite{KwonHC1991}.
+    These methodologies employ predefined sets of linguistic rules or large dictionaries to detect morphemes and determine parts of speech.
+    One of the most significant advantages of this approach is its deterministic nature, which can lead to high accuracy when the input text closely adheres to the rules or dictionaries used.
+    However, it is challenging to scale and update them, particularly with the constant evolution of language and the emergence of new words.
+    The dynamic nature of language, particularly in the Internet age, has made the maintenance of comprehensive dictionaries labor-intensive.
+
+    \subsection{Syllable-unit Morphological Analysis}\label{subsec2.2}
+    To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
+    This method either tags each syllable and then applies a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}.
+    One notable drawback is the challenge of accurately pinpointing morpheme boundaries.
+    Furthermore, as the sequences increase in length, the system finds it increasingly challenging to understand long-term contextual data.
+
+    \subsection{Deep Learning and Tokenization}\label{subsec2.3}
+    The advent of deep learning has reshaped the Korean morphological analysis landscape.
+    High-performance deep learning models in NLP employ tokenization, dividing the text into smaller units and then converting these tokens into vectors as an input to the computational model~\cite{Mikolov2013}.
+    The attempt to conduct subword tokenization, incorporating separate morphemes to cater to Korean linguistic characteristics is particularly significant.
+    Incorporating accurate morpheme analysis results into tokenization can improve overall analysis performance.
+
+    With advancements in technology and access to large datasets, the potential to integrate dictionary-based methods with deep learning techniques has emerged.
+    As motivated in our study, MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis, utilized dictionary-based morphological analysis trained by the CRF method~\cite{Lafferty2001}.
+    This method attempts to find the optimal morphological analysis path by forming a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018}.
+    The amalgamation of dictionary-based methods with deep learning, as explored in our research, signifies the latest strides in this journey aimed at harnessing the strengths of both approaches.
+    Future research avenues include refining these hybrid methods and exploring the capabilities of end-to-end models.
+
     \section{Conclusion}\label{sec:conclusion}

### 2023-11-28 contents/draft.tex
Table 1과 Table 2의 등장 순서 변경 [Korean Morphological Analysis Corpora]장의 내용 개정!

@@
 
-    \begin{table*}[]
-        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}\label{tab:data-statistics}
+    \begin{table*}[t]
+        \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
         \centering
-        \begin{tabular*}{500pt}{@{\extracolsep{\fill}}m{10mm}m{8mm}m{10mm}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{9mm}m{9mm}m{10mm}@{}}
+        \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
             \toprule
-            \multirow{2}{*}{Corpus}                       & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
-            \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-            ~                                             & ~                      & Sentences & Eojeols    & Morphs\newline/Sent & Sentences & Eojeols    & Morphs\newline/Sent & Sentences & Eojeols & Morphs\newline/Sent \\
+            & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
+            alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
             \midrule
-            Sejong\newline Corpus                         & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
-            \midrule
-            \multirow{3}{*}{UCorpus}                      & written                & 5,456,101 & 62,462,158 & 25.1                & 4,998,560 & 57,393,332 & 25.4                & 53,003    & 598,413 & 25.0                \\
-            ~                                             & semi-spoken            & 393,770   & 3,401,444  & 18.4                & 334,061   & 2,960,146  & 19.4                & 38,960    & 332,285 & 18.6                \\
-            ~                                             & spoken                 & 627,380   & 2,819,427  & 10.9                & 429,215   & 2,295,940  & 13.0                & 62,399    & 279,545 & 11.1                \\
-            \midrule
-            \multirow{2}{*}{\makecell{Everyone \\Corpus}} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
-            ~                                             & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
+            no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
+            secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
+            tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
+            quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
+            quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
             \bottomrule
         \end{tabular*}
-
+        \begin{tablenotes}
+            \footnotesize
+            \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
+            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
+        \end{tablenotes}
     \end{table*}
@@
 
-    \begin{table*}[t]
-        \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
+    \begin{table*}[]
+        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}\label{tab:data-statistics}
         \centering
-        \begin{tabular*}{500pt}{@{\extracolsep\fill}cccD{.}{.}{3}c@{\extracolsep\fill}}
+        \begin{tabular*}{500pt}{@{\extracolsep{\fill}}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{9mm}m{9mm}m{10mm}@{}}
             \toprule
-            & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
-            alternative range & eojeol accuracy & average number of alternative & \multicolumn{1}{@{}l@{}}{eojeol accuracy}  & average number of alternative \\
+            \multirow{2}{*}{Corpus}                         & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
+            \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
+            ~                                               & ~                      & sentences & eojeols    & morphs\newline/sent & sentences & eojeols    & morphs\newline/sent & sentences & eojeols & morphs\newline/sent \\
             \midrule
-            no alternative    & 96.36           & 1.0                           & 92.54                                     & 1.0                           \\
-            secondary         & 98.74           & 25.7                          & 97.27                                     & 12.9                          \\
-            tertiary          & 98.96           & 47.8                          & 97.81                                     & 23.6                          \\
-            quarternary       & 99.01           & 69.6                          & 97.95                                     & 34.2                          \\
-            quinary           & 99.02           & 91.1                          & 98.01                                     & 44.5                          \\
+            Sejong\newline Corpus                           & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
+            \midrule
+            \multirow{3}{*}{UCorpus}                        & written                & 5,456,101 & 62,462,158 & 25.1                & 4,998,560 & 57,393,332 & 25.4                & 53,003    & 598,413 & 25.0                \\
+            ~                                               & semi-spoken            & 393,770   & 3,401,444  & 18.4                & 334,061   & 2,960,146  & 19.4                & 38,960    & 332,285 & 18.6                \\
+            ~                                               & spoken                 & 627,380   & 2,819,427  & 10.9                & 429,215   & 2,295,940  & 13.0                & 62,399    & 279,545 & 11.1                \\
+            \midrule
+            \multirow{2}{*}{\makecell{Everyone's \\Corpus}} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
+            ~                                               & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
             \bottomrule
         \end{tabular*}
-        \begin{tablenotes}
-            \footnotesize
-            \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
-            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone Corpus (4,800 sentences total)
-        \end{tablenotes}
     \end{table*}
@@
 
-    A representative corpus for training Korean morphological analysis models is the Sejong morphological analysis corpus, which is often referred to as the Sejong corpus.
-    The Sejong corpus, a major output of the 21st Century Sejong Project, contains 15 million words and is the mainstay of Korean morphological analysis research~\cite{ChoeMW2008}.
+    In this study, we used three major corpora to train and evaluate Korean morphological analysis models, each of which has unique characteristics and serves different research purposes.
 
-    Subsequent efforts have extended and refined this foundational work.
-    The University of Ulsan addressed the limitations of the Sejong corpus~\cite{KimIH2010} and introduced [UCorpus], an expanded corpus of 63 million words.
-    This expanded corpus not only adds new data but also corrects errors in the original Sejong corpus~\cite{UCorpusHG}.
-    To further extend this step, the National Institute of Korean Language launched a massive Korean corpus construction project in 2018.
-    The fruits of this labor, a corpus called <Everyone Corpus>, were released to the public in 2020~\cite{EveryoneCorpus}.
-    A special offshoot of this project produced a morpheme-tagged corpus of three million words, including spoken languages ~\cite{KimIH2019}.
+    \textbf{Sejong Corpus}: Originating from the 21st Century Sejong Project, this corpus consists of a total of 15 million eojeols, including the raw untagged corpus, and forms the backbone of Korean morphological analysis research~\cite{ChoeMW2008}.
+    It provides a wide variety of linguistic patterns and structures that are important for baseline training and validation of morphological analysis models, and has been used for performance comparisons with other studies.
+    In most of the previous studies, only a part of the Sejong corpus was used for experiments, and in this study, we used the dataset provided by the researchers in ~\cite{NaSH2014}.
+
+    \textbf{UCorpus (University of Ulsan Corpus)}~\cite{UCorpusHG}: This is an extension of the Sejong corpus, which is constantly being maintained and added to by the University of Ulsan, significantly increasing its volume to 63 million eojeols and testing the adaptability and accuracy of the model to a wider range of data.
+    The expansion includes corrections to previously raised errors ~\cite{KimIH2010} and a number of annotation outputs for new data, providing a substantial basis for comprehensive linguistic analysis.
+
+    \textbf{Everyone's Corpus}~\cite{EveryoneCorpus}: Launched by the National Institute of the Korean Language in 2020, the Everybody's Corpus enriches the data landscape with web texts and spoken language materials that reflect contemporary language use~\cite{KimIH2019}.
+    This modern corpus reflects the dynamic evolution of the Korean language and is playing a pivotal role in improving models for capturing the nuances of current Korean usage.
+
+    Table~\ref{tab:data-statistics} details the specific number of sentences and words in each corpus, and the data subsets extracted for model training and evaluation.
+    During the training data conversion process, we first removed duplicate sentences and excluded sentences with annotation errors or other problems.
+    We can see that many duplicate sentences occur, especially in spoken language.
 

### 2023-11-28 contents/draft.tex
Everyone Corpus -> Everyone's Corpus

@@
             \toprule
-            & \multicolumn{2}{@{}c@{}}{\textbf{Written Language Evaluation Set}} & \multicolumn{2}{@{}c@{}}{\textbf{Spoken Language Evaluation Set}} \\\cmidrule{2-3}\cmidrule{4-5}
+            ~                 & \multicolumn{2}{@{}c@{}}{Written Language Evaluation Set} & \multicolumn{2}{@{}c@{}}{Spoken Language Evaluation Set}                  \\ \cmidrule{2-3} \cmidrule{4-5}
             alternative range & eojeol accuracy & average number of alternative           & \multicolumn{1}{@{}l@{}}{eojeol accuracy} & average number of alternative \\
@@
     This divergence underscores the need for a model that reevaluates these primary results and reorients them to achieve higher accuracy.
-    This method, called "re-ranking," involves generating multiple analyses of an input and then reordering them based on a new set of criteria or models, thereby improving the overall quality of the results.
+    This method, called re-ranking, involves generating multiple analyses of an input and then reordering them based on a new set of criteria or models, thereby improving the overall quality of the results.
 
@@
 
-    For our experiments, we used the Sejong corpus (versions used in ~\cite{NaSH2014, NaSH2015, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone Corpus\cite{EveryoneCorpus}.
+    For our experiments, we used the Sejong corpus (versions used in ~\cite{NaSH2014, NaSH2015, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone's Corpus\cite{EveryoneCorpus}.
     For comparison with previous studies, the Sejong corpus was trained using a single model without separation.
-    The UCorpus and Everyone Corpus provided a separate spoken corpus with drama scripts and broadcast dialogues, while UCorpus separated documents that were considered to be close to spoken language and further organized them into a semi-spoken corpus.
-    Because UCorpus and Everyone Corpus have synergistic effects when trained concurrently, we trained the models separately for written and spoken language rather than separating them by source.
+    The UCorpus and Everyone's Corpus provided a separate spoken corpus with drama scripts and broadcast dialogues, while UCorpus separated documents that were considered to be close to spoken language and further organized them into a semi-spoken corpus.
+    Because UCorpus and Everyone's Corpus have synergistic effects when trained concurrently, we trained the models separately for written and spoken language rather than separating them by source.
     The statistics of the full data for the three types of models are presented in Table~\ref{tab:data-statistics}.
@@
             \toprule
-            \multirow{2}{*}{System} & \multicolumn{2}{c}{Sejong} & \multicolumn{2}{c}{UCorpus (written)} & \multicolumn{2}{c}{Everyone Corpus (written)} \\
+            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
             \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
-            & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
+            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
             \midrule
@@
             \toprule
-            \multirow{2}{*}{System} & \multicolumn{2}{c}{UCorpus (semi-spoken)} & \multicolumn{2}{c}{UCorpus (spoken)} & \multicolumn{2}{c}{Everyone Corpus (spoken)} \\
+            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
             \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
-            & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
+            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
             \midrule
@@
             \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
-            & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
+            ~                                             & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
             \midrule
@@
 
-    The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone corpus.
+    The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
     For a large number of sentences, we adopted a floating-point 16-bit technique while using four GPUs for distributed training and significantly reduced the time required for training.

### 2023-11-28 contents/draft.tex
Table 5 앞 장으로 이동 subsection 레이블 변경

@@
 
-    \subsection{Korean Morphological Analysis Corpora}\label{subsec3.1}
+    \subsection{Korean Morphological Analysis Corpora}\label{subsec:korean-morphological-analysis-corpora}
 
@@
 
-    \subsection{Training Example Transformation}\label{subsec3.2}
+    \subsection{Training Example Transformation}\label{subsec:training-example-transformation}
 
@@
 
-    \subsection{Lattice Construction and Decoding}\label{subsec3.3}
+    \subsection{Lattice Construction and Decoding}\label{subsec:lattice-construction-and-decoding}
 
@@
 
-    \section{Re-ranking Model}\label{sec:re-ranking-model}
+    \section{Re-ranking Model}\label{sec:reranking-model}
 
-    \subsection{Motivation and Background}\label{subsec4.1}
+    \subsection{Motivation and Background}\label{subsec:motivation-and-background}
 
@@
 
-    \subsection{Secondary Path Generation}\label{subsec4.2}
+    \subsection{Secondary Path Generation}\label{subsec:secondary-path-generation}
 
@@
 
-    \subsection{BERT-based Re-ranking}\label{subsec4.3}
+    \subsection{BERT-based Re-ranking}\label{subsec:bert-based-reranking}
 
@@
 
-    \subsection{Two-stage Re-ranking}\label{subsec4.4}
+    \subsection{Two-stage Re-ranking}\label{subsec:two-stage-reranking}
 
@@
 
-    In the first step, we re-rank the secondary paths generated using the BERT model, as described in Section ~\ref{subsec4.3}.
+    In the first step, we re-rank the secondary paths generated using the BERT model, as described in Section ~\ref{subsec:bert-based-reranking}.
     In the second step, we introduced another BERT variant that was optimized for a different set of linguistic features or trained on a different dataset.
@@
 
-    \subsection{Setup and Data}\label{subsec5.1}
+    \subsection{Setup and Data}\label{subsec:setup-and-data}
 
@@
 
-    We transformed this organized morphological corpus using the training-example transformation process described in Section ~\ref{subsec3.2} to generate samples for training the dictionary-based morphological analysis model.
+    We transformed this organized morphological corpus using the training-example transformation process described in Section ~\ref{subsec:training-example-transformation} to generate samples for training the dictionary-based morphological analysis model.
 
@@
 
-    \subsection{Evaluation Metrics}\label{subsec5.2}
+    \subsection{Evaluation Metrics}\label{subsec:evaluation-metrics}
 
@@
 
-    \subsection{Basic Performance}\label{subsec5.3}
+    \subsection{Basic Performance}\label{subsec:basic-performance}
 
@@
 
-    \subsection{Re-ranking Performance}\label{subsec5.4}
+    \subsection{Re-ranking Performance}\label{subsec:reranking-performance}
 
@@
 
-    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:re-ranking-model} and compared its performances.
+    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:reranking-model} and compared its performances.
     Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well in other Korean language understanding tasks, were used to fine-tune the re-ranking model.
@@
     Preliminary tests indicate that using the same type of model or input results in a nearly identical retrained model, with no further improvement in performance.
-
-    The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
-    For a large number of sentences, we adopted a floating-point 16-bit technique while using four GPUs for distributed training and significantly reduced the time required for training.
-    In addition, the minibatch size was 120 with a maximum sequence length of 384 because the first re-ranking uses only the morphological analysis results as input.
-    The minibatch size was 40 with a maximum sequence length of 512 because the original input sentences were given as input along with the first morphological analysis results.
-    The learning rate was set to $2 \times 10^{-5}$ and AdamW is used as the optimization algorithm.
-
-    Table~\ref{tab:performance-with-reranking} shows that incorporating the re-ranking model significantly improves the performance compared with no re-ranking.
-    The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is shown as 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking, and the second round of re-ranking improved the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
-    These performance improvements demonstrate that the dictionary-based morphological analysis model outperforms traditional syllable-based morphological analysis systems, including numerous pre- and post-processing rules and dictionaries.
 
@@
 
-    \subsection{Comparison to Other Studies}\label{subsec5.5}
+    The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
+    For a large number of sentences, we adopted a floating-point 16-bit technique while using four GPUs for distributed training and significantly reduced the time required for training.
+    In addition, the minibatch size was 120 with a maximum sequence length of 384 because the first re-ranking uses only the morphological analysis results as input.
+    The minibatch size was 40 with a maximum sequence length of 512 because the original input sentences were given as input along with the first morphological analysis results.
+    The learning rate was set to $2 \times 10^{-5}$ and AdamW is used as the optimization algorithm.
+
+    Table~\ref{tab:performance-with-reranking} shows that incorporating the re-ranking model significantly improves the performance compared with no re-ranking.
+    The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is shown as 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking, and the second round of re-ranking improved the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
+    These performance improvements demonstrate that the dictionary-based morphological analysis model outperforms traditional syllable-based morphological analysis systems, including numerous pre- and post-processing rules and dictionaries.
+
+    \subsection{Comparison to Other Studies}\label{subsec:comparison-to-other-studies}
 
@@
 
-    \subsection{Traditional Dictionary-based Approaches}\label{subsec2.1}
+    \subsection{Traditional Dictionary-based Approaches}\label{subsec:traditional-dictionary-based-approaches}
     The earliest attempts at Korean morphological analysis relied heavily on rule- and dictionary-based methods~\cite{KwonHC1991}.
@@
 
-    \subsection{Syllable-unit Morphological Analysis}\label{subsec2.2}
+    \subsection{Syllable-unit Morphological Analysis}\label{subsec:syllable-unit-morphological-analysis}
     To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
@@
 
-    \subsection{Deep Learning and Tokenization}\label{subsec2.3}
+    \subsection{Deep Learning and Tokenization}\label{subsec:deep-learning-and-tokenization}
     The advent of deep learning has reshaped the Korean morphological analysis landscape.

### 2023-11-28 contents/draft.tex
Fix ref label!: re-ranking -> reranking

@@
     In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
-    In Section ~\ref{sec:re-ranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
+    In Section ~\ref{sec:reranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
     In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.

### 2023-11-28 contents/draft.tex
Revise Abstract!

@@
     \abstract[Abstract]{
-        Korean morphological analysis is a fundamental step in analyzing the Korean language.
-        Owing to the nature of Korean agglutinative words, building an automatic analysis system is difficult because parts-of-speech tagging independently is insufficient to complete analysis, as in English.
-        In addition, various methods for morphological analysis have been proposed; however, efficient methods, such as BPE (Byte Pair Encoding), are mainly used in applications intended to be used as tokenizers for deep learning.
-        In this study, we propose a method to maximize the performance of an efficient morphological analysis system that can be used for tokenization through multi-stage re-ranking based on deep learning.
-        For cases whose rankings have been changed through re-ranking, it is feasible to improve the performance while maintaining speed by updating the cost matrix of the lattice-based morphological analysis system.
-        Through experiments, we demonstrate that the proposed method effectively improves performance via reducing errors by over 30\% in both spoken and written language models.
+        This study presents a novel approach to Korean morphological analysis by integrating a Transformer-based re-ranking method into a dictionary-based morphological analysis system.
+        A significant advancement in this research is the effective utilization of the BERT model's re-ranking, which has brought innovations in the broader field of natural language processing.
+        This enhancement is achieved through a two-stage re-ranking process: the first stage involves fine-tuning a BERT model using only the results of morphological analysis, and the second stage fine-tunes a different type of BERT model using the re-ranked results along with the original text.
+        This method effectively improves the performance of dictionary-based morphological analysis, which previously lagged behind syllable-based analysis in terms of accuracy.
+        The integration of deep learning with traditional morphological analysis represents a significant advancement in providing more powerful and efficient tools for language processing tasks.
+        According to our results, there is a substantial improvement in eojeol accuracy and morpheme F1 scores compared to previous methods.
+        This study not only sets a new standard in Korean language processing but also paves the way for further advancements in applying deep learning to linguistic analysis.
     }

### 2023-11-28 contents/draft.tex
Add Table 6: Overview of Recent Korean Morphological Analysis Methods

@@
             Youn et al, 2021~\cite{YounJY2021}    & Seq2seq (BERT-based)                            & Sejong 675k, 75k sentences                  & 95.99                      & 97.94                        \\
-            Shin et al, 2023~\cite{ShinHJ2023}    & Transformer(En) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
+            Shin et al, 2023~\cite{ShinHJ2023}    & Transformer(Encoder) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
             \midrule
-            Proposed (without rerank)             & \multirow{3}{*}{Lattice + Transformer(En)} & \multirow{3}{*}{Sejong 194k, 10k sentences} & 95.23                      & 97.08                        \\
+            Proposed (without rerank)             & \multirow{3}{*}{Lattice + Transformer(Encoder)} & \multirow{3}{*}{Sejong 194k, 10k sentences} & 95.23                      & 97.08                        \\
             Proposed (1-stage rerank)             & ~                                               & ~                                           & 96.63                      & 97.84                        \\
@@
     The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to develop inventive solutions, many of which have laid the groundwork for future research.
+    Table~\ref{tab:overview-of-recent-korean-morphological-analysis-methods} provides a concise comparison of the methodologies and key concepts of key studies that are directly or indirectly related to this research, giving a brief overview of the different methods of morphological analysis.
+
+    \begin{table}[h!]
+        \centering
+        % LaTeX에서 표 안의 글자 크기를 조절하려면, 해당 표의 내용을 글자 크기를 변경하는 명령어로 감싸면 됩니다.
+        % 예를 들어, \tiny, \small, \footnotesize, \scriptsize 등의 명령어를 사용할 수 있습니다.
+        % 이 명령어들은 각각 다른 크기의 글자를 생성합니다.
+        \footnotesize
+        \caption{Overview of Recent Korean Morphological Analysis Methods}
+        \label{tab:overview-of-recent-korean-morphological-analysis-methods}
+        \begin{tabular}{|p{10mm}|p{32mm}|p{32mm}|}
+            \hline
+            \textbf{Authors} & \textbf{Methodology} & \textbf{Key Concepts} \\
+            \hline
+            Na et al., 2014~\cite{NaSH2014}
+            & Lattice-based discriminative approach creating a morpheme lattice for POS tagging and morphological analysis
+            & Lattice-based analysis, morpheme segmentation, structured classification \\
+            \hline
+            Na and Kim, 2018~\cite{NaSH2018}
+            & Phrase-based model for morphological analysis integrating phrases with CRFs
+            & Phrase-based modeling, CRFs, discriminative modeling \\
+            \hline
+            Shim, 2011~\cite{ShimKS2011}
+            & Syllable-based POS tagging method avoiding morphological analysis by employing CRF models
+            & Syllable-based POS tagging, CRF models, lexical and contextual probabilities \\
+            \hline
+            Lee, 2013~\cite{LeeCK2013}
+            & Joint model using structural SVM for concurrent word spacing and POS tagging
+            & Joint modeling, word spacing, POS tagging, structural SVM, error propagation \\
+            \hline
+            Lee et al., 2016~\cite{LeeCH2016}
+            & Hybrid algorithm combining machine learning with a pre-analyzed dictionary for syllable-based POS tagging
+            & Hybrid algorithm, syllable-based POS tagging, machine learning, CRF \\
+            \hline
+            Kim et al., 2016~\cite{KimHM2016}
+            & Method utilizing Bi-LSTM-CRF for POS tagging with input based on syllable distribution patterns
+            & Syllable-based POS tagging, bi-directional LSTM, CRFs, POS distribution vectors \\
+            \hline
+            Li et al., 2017~\cite{Li2017}
+            & End-to-end sequence-to-sequence model with convolutional features for morphological analysis and POS tagging
+            & Sequence-to-sequence model, convolutional features, morphological analysis, POS tagging \\
+            \hline
+            Kim and Choi, 2018~\cite{KimSW2018}
+            & Integrated model using Bi-LSTM-CRF for simultaneous word spacing and POS tagging
+            & Bidirectional LSTM, CRF, word spacing, POS tagging, syllable-based analysis \\
+            \hline
+            Choi and Lee, 2018~\cite{ChoiYS2018}
+            & Reranking model post-processing seq2seq outputs with morpheme-unit embedding and n-grams to reorder results
+            & Seq2seq model, reranking, morpheme-unit embedding, beam search, n-grams \\
+            \hline
+            Min et al., 2019~\cite{MinJW2019}
+            & Neural transition-based model for end-to-end morpheme segmentation and POS tagging
+            & Neural transition-based learning, end-to-end model, morpheme segmentation, POS tagging \\
+            \hline
+            Kim et al., 2019~\cite{KimHM2019}
+            & Syllable distribution pattern utilization with Bi-LSTM-CRF for morphological analysis and POS tagging
+            & Syllable distribution patterns, Bi-LSTM-CRF, morphological analysis, POS tagging \\
+            \hline
+            Song and Park, 2019~\cite{SongHJ2019}
+            & Tied sequence-to-sequence multi-task model for morpheme processing and POS tagging
+            & Multi-task learning, POS tagging, Morpheme generation, Sequence-to-sequence model \\
+            \hline
+            Song and Park, 2020~\cite{SongHJ2020}
+            & Two-step POS tagging using an encoder-decoder architecture for morpheme generation followed by sequence labeling
+            & POS Tagging, Morpheme Generation, Encoder-Decoder Architecture, Sequence Labeling \\
+            \hline
+            Youn and Lee, 2021~\cite{YounJY2021}
+            & Two-step deep learning-based pipeline model for morpheme restoration and POS tagging with BERT
+            & Deep Learning, Sequence-to-Sequence, BERT, Morpheme Restoration, POS Tagging \\
+            \hline
+            Shin and Lee, 2023~\cite{ShinHJ2023}
+            & Syllable-Based Multi-POSMORPH Annotation approach
+            & Syllable distribution patterns, Multi-POSMORPH tags, Transformer encoder, BiLSTM \\
+            \hline
+        \end{tabular}
+    \end{table}
 
@@
     \subsection{Syllable-unit Morphological Analysis}\label{subsec:syllable-unit-morphological-analysis}
-    To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
+    To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, Li2017, KimSW2018, ChoiYS2018, MinJW2019, KimHM2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
     This method either tags each syllable and then applies a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}.

### 2023-11-28 contents/draft.tex
Update minor
* Introduction:   - previously -> existing   - Further research is required in the future와 다음 문장을 합침 * NaSH2015: CRF++, Lattice-based HMM * Overview of Recent Korean Morphological Analysis Methods   - Add NaSH2015 * Deep Learning and Tokenization:   - Split 2 subsections: Recent Deep Learning Approaches, Integrating Dictionary-based and Deep Learning Approaches * Recent Deep Learning Approaches   - 기존 딥러닝 연구와의 차별점 기술 * Integrating Dictionary-based and Deep Learning Approaches   - 서론에서의 전개와 일맥상통하도록 보강

--- 2023-11-28 contents/draft.tex
@@
     Against this background, this study considers how the dictionary-based morphological analysis method used by MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis in tokenizers, which is an essential preprocessing tool for deep learning, can be effectively improved, and a method is proposed.
-    The dictionary-based morphological analysis method~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018} trained by the CRF (Conditional Random Fields) method~\cite{Lafferty2001} lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph and determines the optimal morphological analysis path within it.
+    The dictionary-based morphological analysis method~\cite{Kudo2004, NaSH2014, NaSH2018} trained by the CRF (Conditional Random Fields) method~\cite{Lafferty2001} lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph and determines the optimal morphological analysis path within it.
     The process of determining the optimal path in the lattice uses the Viterbi algorithm~\cite{Viterbi1967}, which determines the path that minimizes the cost of each morpheme node and the sum of the neighborhood costs of two consecutive morphemes.
@@
     In this study, re-ranking was performed using two BERT models of different types and forms, as proposed in ~\cite{Nogueira2019}.
-    Experimental results show that first-stage re-ranking improves the performance by over 20\% over previously written and spoken models, and second-stage re-ranking with a different type of input and a different type of pre-trained model further improves the performance by more than 30\% over previously written and spoken models.
+    Experimental results show that first-stage re-ranking improves the performance by over 20\% over existing written and spoken models, and second-stage re-ranking with a different type of input and a different type of pre-trained model further improves the performance by more than 30\% over existing written and spoken models.
 
@@
     It is also expected that the morphological analysis system with improved connection costs will be able to generate better re-ranking candidates, which will further improve performance by doing so iteratively.
-    Further research is required in the future.
-    In this study, only performance improvement using the second-stage re-ranking was covered as the scope of the study.
+    Further research is needed on this, and this study was limited to performance improvements with two-stage reranking.
+
     The main contributions of this study are as follows.
@@
             \midrule
-            Na, 2015~\cite{NaSH2015}              & CRF++, HMM                                 & Sejong 200k, 50k sentences                  & 95.22                      & 97.21                        \\
+            Na, 2015~\cite{NaSH2015}              & CRF++, Lattice-based HMM                        & Sejong 200k, 50k sentences                  & 95.22                      & 97.21                        \\
             Lee et al., 2016~\cite{LeeCH2016}     & Structural SVM                                  & Sejong 666k, 74k eojeols                    & 96.41                      & -                            \\
@@
     The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to develop inventive solutions, many of which have laid the groundwork for future research.
+    Table~\ref{tab:overview-of-recent-korean-morphological-analysis-methods} provides a concise comparison of the methodologies and key concepts of key studies that are directly or indirectly related to this research, giving a brief overview of the different methods of morphological analysis.
+
+    \begin{table}[h!]
+        \centering
+        \footnotesize % OR use \tiny, \small, \footnotesize, \scriptsize
+        \caption{Overview of Recent Korean Morphological Analysis Methods}
+        \label{tab:overview-of-recent-korean-morphological-analysis-methods}
+        \begin{tabular}{|p{10mm}|p{24mm}|p{40mm}|}
+            \hline
+            \textbf{Study}                        & \textbf{Methodology}                                   & \textbf{Key Concepts}                                                                                             \\
+            \hline
+            Na et al., 2014~\cite{NaSH2014}       & Lattice-based Discriminative Approach                  & Lattice creation from a lexicon, morpheme connectivity, path optimization in morpheme lattice, POS tagging.
+\\
+            \hline
+            Na, 2015~\cite{NaSH2015}              & Two-stage Discriminative Approach using CRFs           & Statistical morphological analysis, CRF-based morpheme segmentation and POS tagging, full sentence application.
+\\
+            \hline
+            Na and Kim, 2018~\cite{NaSH2018}      & Phrase-based Model with CRFs                           & Phrase-based processing units, CRF integration for morpheme segmentation and POS tagging, noise-channel modeling.
+\\
+            \hline
+            Shim, 2011~\cite{ShimKS2011}          & Syllable-based POS Tagging with CRFs                   & Syllable-based tagging, efficiency in label assignment, morphological analysis bypass.
+\\
+            \hline
+            Lee, 2013~\cite{LeeCK2013}            & Joint Model with Structural SVM                        & Word spacing and POS tagging joint modeling, error propagation reduction, structural SVM application.
+\\
+            \hline
+            Lee et al., 2016~\cite{LeeCH2016}     & Hybrid Algorithm with Pre-analyzed Dictionary          & Syllable-based POS tagging, integration of pre-analyzed dictionary and machine learning, CRF application.
+\\
+            \hline
+            Kim et al., 2016~\cite{KimHM2016}     & POS Tagging with Bi-LSTM-CRFs                          & Syllable pattern input, bi-directional LSTM and CRF for POS tagging, morpheme ambiguity handling.
+\\
+            \hline
+            Li et al., 2017~\cite{Li2017}         & Sequence-to-Sequence Model with Convolutional Features & Seq2seq model with convolutional features for morphological analysis, POS tagging.
+\\
+            \hline
+            Kim and Choi, 2018~\cite{KimSW2018}   & Integrated Model with Bidirectional LSTM-CRF           & Bidirectional LSTM and CRF for word spacing and POS tagging, syllable-based approach.
+\\
+            \hline
+            Choi and Lee, 2018~\cite{ChoiYS2018}  & Reranking Model with Seq2Seq Outputs                   & Seq2Seq model reranking, morpheme-unit embedding, n-gram based morpheme reordering.
+\\
+            \hline
+            Min et al., 2019~\cite{MinJW2019}     & Neural Transition-based Model                          & End-to-end neural transition-based learning, morpheme segmentation, sequence-to-sequence POS tagging.
+\\
+            \hline
+            Kim et al., 2019~\cite{KimHM2019}     & Syllable Distribution Patterns with Bi-LSTM-CRF        & Utilization of syllable distribution, Bi-LSTM-CRF for morphological analysis and POS tagging.
+\\
+            \hline
+            Song and Park, 2019~\cite{SongHJ2019} & Tied Sequence-to-Sequence Multi-task Model             & Multi-task learning for morpheme processing and POS tagging, pointer-generator and CRF network integration.
+\\
+            \hline
+            Song and Park, 2020~\cite{SongHJ2020} & Two-step Korean POS Tagger with Encoder-Decoder        & Encoder-decoder architecture for morpheme generation, sequence labeling for POS tagging.
+\\
+            \hline
+            Youn and Lee, 2021~\cite{YounJY2021}  & Two-step Deep Learning-based Pipeline Model            & Deep learning sequence-to-sequence models, BERT for morpheme restoration and POS tagging.
+\\
+            \hline
+            Shin and Lee, 2023~\cite{ShinHJ2023}  & Syllable-Based Multi-POSMORPH Annotation               & Syllable distribution patterns, Multi-POSMORPH tagging, Transformer encoder, BiLSTM usage.
+\\
+            \hline
+        \end{tabular}
+    \end{table}
 
@@
 
-    \subsection{Deep Learning and Tokenization}\label{subsec:deep-learning-and-tokenization}
-    The advent of deep learning has reshaped the Korean morphological analysis landscape.
-    High-performance deep learning models in NLP employ tokenization, dividing the text into smaller units and then converting these tokens into vectors as an input to the computational model~\cite{Mikolov2013}.
-    The attempt to conduct subword tokenization, incorporating separate morphemes to cater to Korean linguistic characteristics is particularly significant.
-    Incorporating accurate morpheme analysis results into tokenization can improve overall analysis performance.
+    \subsection{Recent Deep Learning Approaches}\label{subsec:recent-deep-learning-approaches}
+    The incorporation of deep learning into Korean morphological analysis has brought significant advancements to the field.
+    Existing deep learning methods typically employ architectures like Bidirectional Long Short-Term Memory (Bi-LSTM) networks, Convolutional Neural Networks (CNNs), and Transformer-based models.
+    These approaches focus on understanding language context and sequence, utilizing the ability of these models to capture long-range dependencies and intricate patterns in text data.
+    For example, Bi-LSTM-CRF models, extensively used for sequence labeling in morphological analysis, leverage LSTM's capacity to remember long-term dependencies and CRF's proficiency in sequence prediction.
 
-    With advancements in technology and access to large datasets, the potential to integrate dictionary-based methods with deep learning techniques has emerged.
-    As motivated in our study, MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis, utilized dictionary-based morphological analysis trained by the CRF method~\cite{Lafferty2001}.
-    This method attempts to find the optimal morphological analysis path by forming a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2015, NaSH2018}.
-    The amalgamation of dictionary-based methods with deep learning, as explored in our research, signifies the latest strides in this journey aimed at harnessing the strengths of both approaches.
-    Future research avenues include refining these hybrid methods and exploring the capabilities of end-to-end models.
+    In contrast, our method innovatively integrates the re-ranking concept with BERT-based models for Korean morphological analysis.
+    Unlike traditional deep learning methods that primarily use sequence-to-sequence or sequence labeling approaches, our method generates suboptimal paths using dictionary-based techniques, which are then re-ranked by BERT models.
+    This dual approach, leveraging BERT's contextual understanding, allows for a more detailed and accurate morphological analysis.
+    The distinction of our approach lies in its ability to address the complexities of the Korean language.
+    By generating and re-ranking suboptimal paths, our method can identify and rectify anomalies that standard deep learning models may miss.
+    This innovative strategy combines the precision of dictionary-based methods with the contextual comprehension of BERT models, marking a significant advancement in the field, especially for languages with intricate morphological structures like Korean.
+
+    \subsection{Integrating Dictionary-based and Deep Learning Approaches}\label{subsec:integrating-dictionary-based-and-deep-learning-approaches}
+    Tokenisation, a fundamental process in NLP deep learning models, involves breaking down text into smaller units and converting these tokens into vectors for computational processing.
+    For Korean, with its complex morphological characteristics, tokenisation that respects morpheme boundaries is crucial.
+    This is because it can not only accurately capture the linguistic nuances of Korean, but also improve the overall performance of deep learning models.
+    This is especially important given the agglutinative nature of Korean, where words are formed by combining morphemes with different semantic and syntactic information.
+
+    In this respect, the combination of dictionary-based morphological analysis methods and deep learning approaches used by MeCab~\cite{MeCab}, a fast and lightweight morphological analyser used for tokenisation of Korean and Japanese, is quite useful.
+    The dictionary-based morphological analysis used here uses a model trained with CRFs to form a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2018} to identify the optimal path for morphological analysis.
+    While this method provides a degree of accuracy and speed, it does not achieve the high accuracy achieved by modern deep learning.
+
+    Our research sought to bridge this gap by effectively combining these dictionary-based morphological analysis methods with the contextual understanding capabilities of deep learning.
+    Future research should continue to refine these hybrid methods to explore the possibility of end-to-end models that seamlessly combine the strengths of traditional dictionary-based analysis with the adaptive capabilities of deep learning.
+    This direction promises significant advances in morphological analysis and will further push the boundaries of Korean language processing.
 

### 2023-11-29 contents/draft.tex
Update minor

@@
 
-    In this study, string alignment was performed using the Smith--Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}).
+    In this study, string alignment was performed using the Smith-Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}).
 Each aligned sentence containing a morpheme tag was converted into a training sample tailored for dictionary-based morphological analysis.

### 2023-11-29 contents/draft.tex
* \subsection{Motivation and Background} 제목만 제거 * \section{Re-ranking Model} 뒷부분과 \section{Experimental Results} 앞부분 내용 보완!

@@
 
-    \subsection{Motivation and Background}\label{subsec:motivation-and-background}
-
     Although dictionary-based morphological analysis offers significant advances, its optimal paths occasionally diverge from the correct solutions that humans understand.
@@
 
+    In summary, the re-ranking model represents a significant advancement in our approach to Korean morphological analysis.
+    By leveraging BERT-based models, we anticipate a marked improvement in accuracy, especially in complex linguistic scenarios.
+    The next section will present our experimental setup and results, providing crucial empirical evidence for the efficacy of the re-ranking model in practical applications.
+
     \section{Experimental Results}\label{sec:results}
+
+    Having developed the re-ranking model as a theoretical framework for enhancing Korean morphological analysis, we now turn to empirical validation.
+    This section outlines our experimental setup, designed meticulously to test the performance of our model.
+    Through these experiments, we aim to demonstrate not just the model's accuracy but also its practical applicability in handling the nuances of Korean language processing.
 

### 2023-11-29 contents/draft.tex
* Add Table: Training Options and Software Information for Re-ranking Model

@@
     \begin{table*}[t]
-        \caption{Maximum performance of alternative paths as correct answers}\label{tab:maximum-performance}
+        \caption{Maximum performance of alternative paths as correct answers}
+        \label{tab:maximum-performance}
         \centering
@@
     \begin{table*}[]
-        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}\label{tab:data-statistics}
+        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}
+        \label{tab:data-statistics}
         \centering
@@
         \centerline{\includegraphics[width=0.75\textwidth]{fig1.1}}
-        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}\label{fig:sample}
+        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
+        \label{fig:sample}
     \end{figure*}
@@
         \centerline{\includegraphics[width=0.9\textwidth]{fig2.1}}
-        \caption{Example of lattice construction and decoding result and secondary path generation}\label{fig:lattice}
+        \caption{Example of lattice construction and decoding result and secondary path generation}
+        \label{fig:lattice}
     \end{figure*}
@@
         \centerline{\includegraphics[width=0.9\textwidth]{fig3.0}}
-        \caption{Two-stage re-ranking model for Korean morphological analysis}\label{fig:ranking}
+        \caption{Two-stage re-ranking model for Korean morphological analysis}
+        \label{fig:ranking}
     \end{figure*}
@@
     \begin{table*}[]
-        \caption{Performance comparison between morphological analysis systems without re-ranking}\label{tab:performance-without-reranking}
+        \caption{Performance comparison between morphological analysis systems without re-ranking}
+        \label{tab:performance-without-reranking}
         \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
@@
     \begin{table*}[]
-        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}\label{tab:performance-with-reranking}
+        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
+        \label{tab:performance-with-reranking}
         \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
@@
     \end{table*}
+
+    \begin{table}[h]
+        \centering
+        \footnotesize
+        \caption{Training Options and Software Information for Re-ranking Model}
+        \label{tab:training-options}
+        \begin{tabular}{|p{24mm}|p{25mm}|p{25mm}|}
+            \hline
+            ~                     & \textbf{First-Stage}                & \textbf{Second-Stage}                                        \\ \hline
+            Input Type            & Only Morphological Analysis Results & First Morphological Analysis Results and Original Input Sentences \\ \hline
+            Max Sequence Length   & 384                                 & 512                                                               \\ \hline
+            Minibatch Size        & 120                                 & 40                                                                \\ \hline
+            Training Epochs       & 5                                   & 7                                                                 \\ \hline
+            Devices Used          & \multicolumn{2}{l|}{4 GPUs}                                                                             \\ \hline
+            Distribution Strategy & \multicolumn{2}{l|}{ddp}                                                                                \\ \hline
+            FP Precision          & \multicolumn{2}{l|}{16-bit}                                                                             \\ \hline
+            Learning Rate         & \multicolumn{2}{l|}{$2 \times 10^{-5}$}                                                                 \\ \hline
+            LR Scheduler          & \multicolumn{2}{l|}{ExponentialLR (gamma=0.9)}                                                          \\ \hline
+            Optimizer Type        & \multicolumn{2}{l|}{AdamW}                                                                              \\ \hline
+            PyTorch               & \multicolumn{2}{l|}{version 2.0.1}                                                                      \\ \hline
+            PyTorch Lightning     & \multicolumn{2}{l|}{version 2.0.6}                                                                      \\ \hline
+            Transformers          & \multicolumn{2}{l|}{version 4.31.0}                                                                     \\ \hline
+        \end{tabular}
+    \end{table}
 
@@
     \begin{table*}[]
-        \caption{Comparison of performance differences with previous studies}\label{tab:differences-with-previous-studies}
+        \caption{Comparison of performance differences with previous studies}
+        \label{tab:differences-with-previous-studies}
         \begin{tabular*}{500pt}{@{\extracolsep\fill}ccc|cc@{\extracolsep\fill}}
@@
     The minibatch size was 40 with a maximum sequence length of 512 because the original input sentences were given as input along with the first morphological analysis results.
-    The learning rate was set to $2 \times 10^{-5}$ and AdamW is used as the optimization algorithm.
+    See Table~\ref{tab:training-options} for information on other training options and software tools used in the implementation of re-ranking models.
 

### 2023-11-29 contents/draft.tex
No \usepackage{makecell} * Table 정리

@@
 \documentclass[AMS,STIX2COL]{WileyNJD-v2}
-\usepackage{makecell}
 
@@
 
-    \begin{table*}[]
+    \begin{table*}[h]
+        \centering
+        \footnotesize
         \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}
         \label{tab:data-statistics}
-        \centering
-        \begin{tabular*}{500pt}{@{\extracolsep{\fill}}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{10mm}m{12mm}m{8mm}m{9mm}m{9mm}m{10mm}@{}}
+        \begin{tabular}{m{20mm}m{14mm}m{10mm}m{12mm}m{10mm}m{10mm}m{12mm}m{10mm}m{10mm}m{12mm}m{10mm}}
             \toprule
@@
             \midrule
-            Sejong\newline Corpus                           & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
+            Sejong Corpus                      & written                & 854,475   & 10,052,869 & 26.8                & 194,822   & 2,681,582  & 31.0                & 49,922    & 678,578 & 30.6                \\
             \midrule
@@
             \midrule
-            \multirow{2}{*}{\makecell{Everyone's \\Corpus}} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
+            \multirow{2}{*}{Everyone's Corpus} & written                & 150,082   & 2,000,213  & 30.4                & 129,352   & 1,713,367  & 30.5                & 14,442    & 191,223 & 30.5                \\
             ~                                  & spoken                 & 221,371   & 1,006,287  & 8.7                 & 137,869   & 714,021    & 10.5                & 19,789    & 85,316  & 8.6                 \\
             \bottomrule
-        \end{tabular*}
+        \end{tabular}
     \end{table*}
@@
 
-    \begin{table*}[]
-        \caption{Performance comparison between morphological analysis systems without re-ranking}
-        \label{tab:performance-without-reranking}
-        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
-            \toprule
-            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
-            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
-            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
-            \midrule
-            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
-            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
-            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
-            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
-            \toprule
-            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
-            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
-            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
-            \midrule
-            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
-            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
-            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
-            \bottomrule
-        \end{tabular*}
-    \end{table*}
-
     \subsection{Evaluation Metrics}\label{subsec:evaluation-metrics}
@@
 
-    \begin{table*}[]
+    \begin{table*}[h]
+        \caption{Performance comparison between morphological analysis systems without re-ranking}
+        \label{tab:performance-without-reranking}
+        \begin{tabular*}{500pt}{@{\extracolsep\fill}c|cccccc@{\extracolsep\fill}}
+            \toprule
+            \multirow{2}{*}{System}                & \multicolumn{2}{c}{Sejong}                                & \multicolumn{2}{c}{UCorpus (written)}                     & \multicolumn{2}{c}{Everyone's Corpus (written)}           \\
+            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
+            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
+            \midrule
+            \hspace{2mm}MeCab-ko                   & 89.17                      & 93.06                        & 87.88                      & 92.32                        & 87.77                      & 92.05                        \\
+            \hspace{2mm}Syllable-based (written)   & 91.95                      & 95.16                        & \textbf{96.84}             & \textbf{97.97}               & \textbf{98.00}             & \textbf{98.82}               \\
+            \hspace{2mm}Dictionary-based (written) & 90.99                      & 94.58                        & 96.33                      & 97.74                        & 96.85                      & 98.14                        \\
+            \hspace{2mm}Dictionary-based (Sejong)  & \textbf{95.23}             & \textbf{97.08}               & 90.18                      & 94.19                        & 91.30                      & 94.79                        \\
+            \toprule
+            \multirow{2}{*}{System}                & \multicolumn{2}{c}{UCorpus (semi-spoken)}                 & \multicolumn{2}{c}{UCorpus (spoken)}                      & \multicolumn{2}{c}{Everyone's Corpus (spoken)}            \\
+            \cmidrule{2-3} \cmidrule{4-5} \cmidrule{6-7}
+            ~                                      & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} & \multicolumn{1}{c}{eojeol} & \multicolumn{1}{c}{morpheme} \\
+            \midrule
+            \hspace{2mm}MeCab-ko                   & 86.85                      & 91.38                        & 81.75                      & 87.90                        & 85.28                      & 89.52                        \\
+            \hspace{2mm}Syllable-based (spoken)    & \textbf{96.56}             & \textbf{97.65}               & \textbf{94.89}             & \textbf{96.76}               & \textbf{95.14}             & \textbf{96.82}               \\
+            \hspace{2mm}Dictionary-based (spoken)  & 94.98                      & 96.65                        & 93.02                      & 95.71                        & 92.47                      & 94.83                        \\
+            \bottomrule
+        \end{tabular*}
+    \end{table*}
+
+    \begin{table*}[h]
         \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
@@
 
-    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:reranking-model} and compared its performances.
-    Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well in other Korean language understanding tasks, were used to fine-tune the re-ranking model.
-    KPF-BERT received Korean sentences as input, ETRI-ELECTRA received morphologically tagged sentences as input, and ETRI-RoBERTa receives morpheme-separated sentences as input.
-    For KPF-BERT and ETRI-RoBERTa, there may be problems with model learning because of the separation of morpheme tags into letter units during the tokenization process when the morpheme analysis results were received as input and re-ranked, hence, the morpheme tags of the mid-level classification unit were added as new tokens, and then training was performed.
-    As shown in Figure~\ref{fig:ranking}, for these three types of pre-trained language models, we first performed training with a re-ranking model using only the morphological analysis results and then performed training with a second re-ranking model using the top five morphological analysis results from the first re-ranking results along with the input sentences for other types of pre-trained language models.
-    Preliminary tests indicate that using the same type of model or input results in a nearly identical retrained model, with no further improvement in performance.
-
     \begin{table*}[]
@@
             \toprule
-            \multirow{2}{*}{Authors}              & \multirow{2}{*}{Model}                          & \multirow{2}{*}{Data (train, test)}         & \multicolumn{2}{c}{Performance}                           \\
+            \multirow{2}{*}{Study}                & \multirow{2}{*}{Model}                          & \multirow{2}{*}{Data (train, test)}         & \multicolumn{2}{c}{Performance}                           \\
             \cmidrule{4-5}
@@
     \end{table*}
+
+    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:reranking-model} and compared its performances.
+    Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well in other Korean language understanding tasks, were used to fine-tune the re-ranking model.
+    KPF-BERT received Korean sentences as input, ETRI-ELECTRA received morphologically tagged sentences as input, and ETRI-RoBERTa receives morpheme-separated sentences as input.
+    For KPF-BERT and ETRI-RoBERTa, there may be problems with model learning because of the separation of morpheme tags into letter units during the tokenization process when the morpheme analysis results were received as input and re-ranked, hence, the morpheme tags of the mid-level classification unit were added as new tokens, and then training was performed.
+    As shown in Figure~\ref{fig:ranking}, for these three types of pre-trained language models, we first performed training with a re-ranking model using only the morphological analysis results and then performed training with a second re-ranking model using the top five morphological analysis results from the first re-ranking results along with the input sentences for other types of pre-trained language models.
+    Preliminary tests indicate that using the same type of model or input results in a nearly identical retrained model, with no further improvement in performance.
 

### 2023-12-02 contents/draft.tex
Apply revision by soomgo: Introduction

@@
 
-    Korean morphological analysis is the process of determining parts of speech by identifying morphemes, which are the smallest units of linguistic expression with independent meanings in a sentence.
-    In an isolating language, such as English, this identification can be achieved relatively easily by tagging parts of speech sequentially.
-    However, in Korean, the nature of the agglutinative language requires separating endings or postpositions and restoring inflections to their original form.
-    In addition, because the basic input of other Korean analysis tasks is often a separate morpheme, the accuracy of the morphological analysis significantly affects the performance of Korean analysis.
-    Modern high-performance deep learning methods in natural language processing (NLP) use a tokenization process that breaks the text into smaller units and converts each token into a vector as an input to the computational model~\cite{Mikolov2013}.
-    Here, the token unit is mainly a subword unit, and to reflect the characteristics of a Korean subword, tokenization with separate morphemes is attempted in advance~\cite{SongHJ2021}.
-    Using the results of the morphological analysis for this tokenization process improves the overall performance of the analysis by reflecting the semantic units of Korean.
-    This requires a highly accurate and fast morphological analyzer.
+    Korean morphological analysis involves determining parts of speech by identifying morphemes, the smallest units of linguistic expression with independent meanings in a sentence.
+    Unlike isolating languages like English, where sequential tagging suffices, Korean, being agglutinative, requires separating endings or postpositions and restoring inflections.
+    The accuracy of morphological analysis significantly impacts Korean analysis performance since many tasks rely on separate morphemes as their basic input.
+    Modern deep learning methods in natural language processing use tokenization, breaking text into smaller units and converting each into a vector for computational models~\cite{Mikolov2013}.
+    For Korean, where subword units are crucial, attempting tokenization with separate morphemes in advance reflects the language's characteristics~\cite{SongHJ2021}.
+    Incorporating morphological analysis results into this process enhances overall performance, capturing the semantic units of Korean.
+    To accomplish this, we need a morphological analyzer that is not only highly accurate but also operates swiftly.
 
-    Various approaches have been proposed for morphological analysis, which is crucial in Korean language analysis~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
-    In general, when people understand speech or written text, they attempt to make sense of it using vocabulary and concepts that they are familiar with.
-    While there are approaches to use rules or dictionaries to reflect this understanding~\cite{KwonHC1991}, it becomes difficult to build and maintain a dictionary for the vocabulary that appears in each text.
-    Therefore, methods for tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016} and studies have been conducted to improve them ~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
-    From a mechanical perspective, syllable-by-syllable morphological analysis can be performed either by tagging syllable-by-syllable and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016}, or by tagging syllable-by-syllable with the base form already restored~\cite{YounJY2021}.
-    However, syllable-by-syllable morphological analysis has limitations, in that it is difficult to accurately identify morpheme boundaries and learn long-term contextual information as the length of the sequence increases.
-    In this study, the former is referred to as dictionary-based morphological analysis and the latter as syllable-unit morphological analysis.
-    Both methods are trained on a manually labeled corpus and cannot accurately analyze new syllable combinations or morphemes that do not appear in the training corpus.
-    Recently, with the development of the Internet and the spread of open sources as well as open data, web texts, corpora, language resources, and knowledge shared by different people have accumulated significantly.
-    The reduced cost of building and maintaining a dictionary provides a significant opportunity to overcome the limitations of dictionary-based methods.
+    Several approaches have been suggested for morphological analysis, a critical aspect of Korean language comprehension~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
+    Typically, when individuals grasp spoken or written language, they try to comprehend it through familiar vocabulary and concepts.
+    While some approaches rely on rules or dictionaries to capture this understanding~\cite{KwonHC1991}, constructing and updating dictionaries for varied text vocabularies can be challenging.
+    As a result, methods focusing on tagging syllable units without a dictionary have been proposed~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016} and studied for enhancement~\cite{KimSW2018, ChoiYS2018, KimHM2019, MinJW2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
+    Mechanically, syllable-by-syllable morphological analysis can be achieved by either tagging syllables and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or by tagging syllables with the base form pre-restored~\cite{YounJY2021}.
+    However, this approach has limitations, struggling with precise morpheme boundary identification and struggling to grasp long-term contextual information as the sequence lengthens.
+    In this study, the former is termed dictionary-based morphological analysis, and the latter is syllable-unit morphological analysis.
+    Both methods are trained on manually labeled corpora, facing challenges in accurately analyzing new syllable combinations or morphemes absent in the training data.
+    The evolution of the Internet, open sources, and shared knowledge has led to substantial accumulations of web texts, corpora, language resources, offering an opportunity to overcome the constraints of dictionary-based methods due to reduced costs in dictionary construction and maintenance.
 
-    Against this background, this study considers how the dictionary-based morphological analysis method used by MeCab~\cite{MeCab}, an open software for Korean and Japanese morphological analysis in tokenizers, which is an essential preprocessing tool for deep learning, can be effectively improved, and a method is proposed.
-    The dictionary-based morphological analysis method~\cite{Kudo2004, NaSH2014, NaSH2018} trained by the CRF (Conditional Random Fields) method~\cite{Lafferty2001} lists the candidate morphemes in the dictionary from a given sentence to form a lattice structure connected by a directed graph and determines the optimal morphological analysis path within it.
-    The process of determining the optimal path in the lattice uses the Viterbi algorithm~\cite{Viterbi1967}, which determines the path that minimizes the cost of each morpheme node and the sum of the neighborhood costs of two consecutive morphemes.
-    The main types of errors in these dictionary-based morphological analysis methods occur when new words that are not in the dictionary are used in a sentence, or when the optimal path calculation selects the incorrect result owing to bias.
-    For example, it may be cost-effective to select one long morpheme than several short morphemes, but this may often lead to an incorrect analysis.
-    The main motivation for this study was that the path that minimizes the costs for the nodes and links may not be the optimal path.
+    Given this context, our study aims to enhance the effectiveness of the dictionary-based morphological analysis method employed by MeCab~\cite{MeCab}, an open-source tool for Korean and Japanese morphological analysis commonly used as a crucial preprocessing tool for deep learning.
+    The method, trained through Conditional Random Fields (CRF)~\cite{Lafferty2001}, generates a lattice structure from a given sentence, connecting candidate morphemes in the dictionary through a directed graph.
+    Subsequently, the optimal morphological analysis path is determined within this lattice structure~\cite{Kudo2004, NaSH2014, NaSH2018}.
+    The Viterbi algorithm~\cite{Viterbi1967} is employed in this process, minimizing the cost associated with each morpheme node and the sum of neighborhood costs for consecutive morphemes to identify the optimal path.
+
+    In these dictionary-based morphological analysis methods, the primary errors stem from encountering new words absent in the dictionary within a sentence or when biases lead to the selection of an incorrect result during optimal path calculation.
+    For instance, opting for one long morpheme over several short ones might be cost-effective but often results in an inaccurate analysis.
+    The main impetus behind our study is the recognition that the path minimizing costs for nodes and links may not always align with the optimal path.
+    In response, we propose methods to address these challenges and improve the accuracy of the morphological analysis process.
 
@@
 
-    To identify cases in which a suboptimal solution is actually the best solution according to the best path calculation, we modified the best path calculation method to generate suboptimal analysis results and verified the extent to which they are correct.
-    Although there are numerous different approaches to select the next-best path, we used the method of replacing a morpheme node on the optimal path with a lower-ranked node.
-    As shown in Table~\ref{tab:maximum-performance}, we confirm the extent to which the analysis performance can be improved by replacing the optimal path with a lower-ranked node.
-    We can consider the problem of finding the correct answer among the generated sub-optimals, similar to the problem of re-ranking search results in information retrieval~\cite{BaeYJ2021}.
-    In ~\cite{ChoiYS2018}, the N-best analysis results generated by the seq2seq model were re-ranked based on a convolutional neural network to improve the performance.
-    In this study, re-ranking was performed using two BERT models of different types and forms, as proposed in ~\cite{Nogueira2019}.
-    Experimental results show that first-stage re-ranking improves the performance by over 20\% over existing written and spoken models, and second-stage re-ranking with a different type of input and a different type of pre-trained model further improves the performance by more than 30\% over existing written and spoken models.
+    To pinpoint instances where a suboptimal solution may, in fact, be the best choice according to the best path calculation, we modified the best path calculation method to yield suboptimal analysis results and assessed their accuracy.
+    While various approaches exist for selecting the next-best path, we opted for the method of substituting a morpheme node on the optimal path with a lower-ranked node.
+    Table~\ref{tab:maximum-performance} illustrates the degree to which analysis performance can be enhanced by replacing the optimal path with a lower-ranked node.
+    This problem is analogous to the challenge of re-ranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.
 
-    With this method, the performance of the dictionary-based morphological analysis method could be further improved; however, the overall analysis time increased when the morphological analysis system was configured, including the re-ranking model itself.
-    However, it is feasible to use the results of multiple reranked morpheme analyses to update the connection costs between morphemes in a dictionary, similar to the backpropagation process in a typical neural network.
-    It is also expected that the morphological analysis system with improved connection costs will be able to generate better re-ranking candidates, which will further improve performance by doing so iteratively.
-    Further research is needed on this, and this study was limited to performance improvements with two-stage reranking.
+    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were re-ranked based on a convolutional neural network to enhance performance.
+    In our study, we employed re-ranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
+    Experimental results reveal that first-stage re-ranking improves performance by over 20\% compared to existing written and spoken models.
+    Furthermore, second-stage re-ranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.
 
-    The main contributions of this study are as follows.
+    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the re-ranking model itself.
+    However, a promising avenue for future exploration lies in utilizing the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
+    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior re-ranking candidates, potentially enabling iterative performance improvements.
+    While this study focused on two-stage re-ranking, further research is essential to fully explore this potential.
+
+    The primary contributions of this study can be summarized as follows:
     \begin{enumerate}
-        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We explore the possibility of performance improvement by introducing a method to replace the optimal path with a suboptimal node and propose a method to effectively improve the dictionary-based morphological analysis method through deep learning.
-        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To improve the performance of dictionary-based analysis by re-ranking the morphological analysis results, we propose extending the performance improvement using different BERT models to perform two rounds of re-ranking.
-        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We propose a new method for updating dictionary connection costs based on re-ranked morphological analysis results.
-We also outline directions for future research, suggesting potential improvements.
+        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace the optimal path with a suboptimal node.
+Additionally, we propose an effective approach to enhance the dictionary-based morphological analysis method through deep learning.
+        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To further enhance the performance of dictionary-based analysis through re-ranking, we suggest extending the improvement using different BERT models and conducting two rounds of re-ranking.
+        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We present a novel method for updating dictionary connection costs based on re-ranked morphological analysis results.
+Furthermore, we outline directions for future research, suggesting potential enhancements.
     \end{enumerate}
-    These contributions provide important insights into the performance improvement of Korean morphological analysis and the direction of future research, and will serve as a useful reference for future researchers.
+    These contributions provide valuable insights into advancing the performance of Korean morphological analysis and offer guidance for future researchers.
 
-    The remainder of this paper is organized as follows.
-    In Section ~\ref{sec:morphological-analysis-model}, we discuss configuring and training a dictionary-based morphological analysis system.
-    In Section ~\ref{sec:reranking-model}, we discuss the generation of secondary results of morphological analysis, produce re-ranking data, and propose a method for training a two-stage re-ranking model.
-    In Section ~\ref{sec:results}, we discuss the results of the performance improvement using the morphological analysis and re-ranking models.
-    In Section ~\ref{sec:related-work}, we introduce previous research cases related to this study.
-    Finally, in Section ~\ref{sec:conclusion}, we conclude the study and discuss its limitations and directions for future research.
+    The subsequent sections of this paper are organized as follows:
+    Section ~\ref{sec:morphological-analysis-model} discusses the configuration and training of a dictionary-based morphological analysis system.
+    Section ~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of re-ranking data, and the proposal of a method for training a two-stage re-ranking model.
+    Section ~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and re-ranking models.
+    Section ~\ref{sec:related-work} introduces previous research cases related to this study.
+    Finally, in Section ~\ref{sec:conclusion}, we conclude the study, discuss its limitations, and suggest directions for future research.
 

### 2023-12-02 contents/draft.tex
Apply revision by soomgo: Section 2 and 3

@@
 
-    In this study, we used three major corpora to train and evaluate Korean morphological analysis models, each of which has unique characteristics and serves different research purposes.
+    In this study, three major corpora were utilized to train and evaluate Korean morphological analysis models, each serving distinct research purposes and possessing unique characteristics:
 
-    \textbf{Sejong Corpus}: Originating from the 21st Century Sejong Project, this corpus consists of a total of 15 million eojeols, including the raw untagged corpus, and forms the backbone of Korean morphological analysis research~\cite{ChoeMW2008}.
-    It provides a wide variety of linguistic patterns and structures that are important for baseline training and validation of morphological analysis models, and has been used for performance comparisons with other studies.
-    In most of the previous studies, only a part of the Sejong corpus was used for experiments, and in this study, we used the dataset provided by the researchers in ~\cite{NaSH2014}.
+    \textbf{Sejong Corpus}: Originating from the 21st Century Sejong Project, this corpus comprises a total of 15 million eojeols, including the raw untagged corpus~\cite{ChoeMW2008}.
+    It forms the backbone of Korean morphological analysis research, offering a diverse array of linguistic patterns and structures crucial for baseline training and validation of morphological analysis models.
+    The Sejong Corpus has been widely used for performance comparisons with other studies.
+    For our experiments, we utilized the dataset used by researchers of ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.
 
-    \textbf{UCorpus (University of Ulsan Corpus)}~\cite{UCorpusHG}: This is an extension of the Sejong corpus, which is constantly being maintained and added to by the University of Ulsan, significantly increasing its volume to 63 million eojeols and testing the adaptability and accuracy of the model to a wider range of data.
-    The expansion includes corrections to previously raised errors ~\cite{KimIH2010} and a number of annotation outputs for new data, providing a substantial basis for comprehensive linguistic analysis.
+    \textbf{UCorpus (University of Ulsan Corpus)}~\cite{UCorpusHG}: An extension of the Sejong corpus, the UCorpus is continually maintained and expanded by the University of Ulsan.
+    It has significantly grown in volume, reaching 63 million eojeols.
+    This extension tests the adaptability and accuracy of the model across a broader range of data.
+    Corrections to previously identified errors ~\cite{KimIH2010} and additional annotations for new data contribute to its value, providing a comprehensive basis for linguistic analysis.
 
-    \textbf{Everyone's Corpus}~\cite{EveryoneCorpus}: Launched by the National Institute of the Korean Language in 2020, the Everybody's Corpus enriches the data landscape with web texts and spoken language materials that reflect contemporary language use~\cite{KimIH2019}.
-    This modern corpus reflects the dynamic evolution of the Korean language and is playing a pivotal role in improving models for capturing the nuances of current Korean usage.
+    \textbf{Everyone's Corpus}~\cite{EveryoneCorpus}: Launched by the National Institute of the Korean Language in 2020, the Everyone's Corpus enriches the data landscape with contemporary web texts and spoken language materials~\cite{KimIH2019}.
+    This modern corpus reflects the dynamic evolution of the Korean language, playing a pivotal role in improving models to capture the nuances of current Korean usage.
 
-    Table~\ref{tab:data-statistics} details the specific number of sentences and words in each corpus, and the data subsets extracted for model training and evaluation.
-    During the training data conversion process, we first removed duplicate sentences and excluded sentences with annotation errors or other problems.
-    We can see that many duplicate sentences occur, especially in spoken language.
+    Table~\ref{tab:data-statistics} presents specific details regarding the number of sentences and words in each corpus, along with the data subsets used for model training and evaluation.
+    In the process of converting training data, we initially removed duplicate sentences and excluded those with annotation errors or other issues.
+    Notably, a substantial occurrence of duplicate sentences was observed, particularly in spoken language datasets.
 
@@
 
-    To train a dictionary-based morpheme analysis model effectively, the morpheme-tagged corpus, typically represented in lemma form, must be transformed to include the boundary information between morphemes in its surface form.
-    Crucial to this transformation is string alignment, a process that accounts for the discrepancies between lemma forms and surface forms in the Korean morphological analysis corpus.
+    To effectively train a dictionary-based morpheme analysis model, the morpheme-tagged corpus, typically represented in lemma form, needs transformation to include boundary information between morphemes in its surface form.
+    This transformation relies on string alignment, addressing discrepancies between lemma forms and surface forms in the Korean morphological analysis corpus.
 
-    In this study, string alignment was performed using the Smith-Waterman algorithm, which uses a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as shown in Figure~\ref{fig:sample}).
-Each aligned sentence containing a morpheme tag was converted into a training sample tailored for dictionary-based morphological analysis.
+    In this study, we employed the Smith-Waterman algorithm for string alignment.
+    This algorithm utilizes a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as depicted in Figure~\ref{fig:sample}).
+    Each aligned sentence containing a morpheme tag was then converted into a training sample tailored for dictionary-based morphological analysis.
 
     The resulting table in Figure~\ref{fig:sample} illustrates this process.
-    Each row acts as a lexical unit.
-    The first four columns contribute to feature generation, whereas the last four columns facilitate post-lemmatization.
-    Using the morphological corpus above, a large number of training samples can be generated according to the process shown in Figure~\ref{fig:sample}.
-    With the exception of the evaluation samples, the remaining sentences were used to train the dictionary-based morphological analysis model using the CRF algorithm.
-    The output of this training allowed the calculation of the costs associated with each morpheme node and the linking of two consecutive morphemes.
-    This, in turn, allowed the discovery of an optimal path using the Viterbi algorithm.
+    Each row functions as a lexical unit, with the first four columns contributing to feature generation and the last four columns facilitating post-lemmatization.
+    Leveraging the morphological corpus, a substantial number of training samples were generated following the process illustrated in Figure~\ref{fig:sample}.
+    Except for the evaluation samples, the remaining sentences were employed to train the dictionary-based morphological analysis model using the CRF algorithm.
+    The output of this training facilitated the calculation of costs associated with each morpheme node and the linking of two consecutive morphemes, enabling the determination of an optimal path using the Viterbi algorithm.
 
@@
 
-    Figure~\ref{fig:lattice} presents a snapshot of the lattice structure, which is an integral part of the morphological analysis.
-    (1) shows a fragment of the lattice structure formed when the example sentence in Figure~\ref{fig:sample} is entered.
-    (2) shows the optimal path determined using the Viterbi algorithm.
+    In Figure~\ref{fig:lattice}, a snapshot of the lattice structure crucial to morphological analysis is presented.
+    (1) displays a portion of the lattice structure formed when inputting the example sentence from Figure~\ref{fig:sample}.
+    (2) illustrates the optimal path determined through the Viterbi algorithm.
 
-    However, the path inferred by the trained model may differ from the correct solution constructed by humans.
+    However, it's essential to note that the path predicted by the trained model might differ from the correct solution crafted by humans.
     The nodes marked with stars in (1) represent correct nodes.
-    The upper-left number of each node indicates the ranking of the nodes accessible at each decoding point.
-    The choices made at certain moments deviate from the correct solution.
-    To improve analytical performance, mechanisms to correct these discrepancies must developed.
+    The upper-left number of each node indicates the ranking of accessible nodes at each decoding point.
+    Choices made at certain moments deviate from the correct solution.
+    To enhance analytical performance, mechanisms must be developed to correct these discrepancies.
 
@@
 
-    Although dictionary-based morphological analysis offers significant advances, its optimal paths occasionally diverge from the correct solutions that humans understand.
-    This divergence underscores the need for a model that reevaluates these primary results and reorients them to achieve higher accuracy.
-    This method, called re-ranking, involves generating multiple analyses of an input and then reordering them based on a new set of criteria or models, thereby improving the overall quality of the results.
+    While dictionary-based morphological analysis provides substantial advancements, it is not immune to instances where its optimal paths deviate from the correct solutions perceived by humans.
+    This deviation emphasizes the necessity for a model that reexamines these initial results and adjusts them to enhance accuracy.
+    This approach, known as re-ranking, entails producing multiple analyses of an input and subsequently rearranging them using a new set of criteria or models, thereby elevating the overall quality of the results.
 
@@
 
-    Before reranking begins, multiple analyses, typically referred to as the N-best paths, of the input sentence are generated.
-    This involves extracting the top N atoms from the lattice structure.
-    In this study, a novel approach is introduced to generate secondary paths, as shown in (3) of Figure~\ref{fig:lattice}, by selecting the second-best node rather than each best node constituting the path from the best-path result.
-    Some of these secondary paths provided alternatives that reconciled incorrect with correct answers.
-    Similarly, paths modified by favoring the third-best node were called tertiary paths, and this naming convention was continued for subsequent paths.
-    In our preliminary test, the secondary paths, including the optimal and suboptimal paths, were shown to cover the majority of the correct morphological analyses as measured through human evaluations.
-    (Refer to Table~\ref{tab:maximum-performance}).
+    Before the re-ranking process initiates, multiple analyses, commonly referred to as N-best paths, of the input sentence are generated.
+    This involves extracting the top N candidates from the lattice structure.
+    In our study, a novel approach is introduced to produce secondary paths, as depicted in (3) of Figure~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
+    Some of these secondary paths offered alternatives that reconciled incorrect answers with correct ones.
+    Similarly, paths modified by favoring the third-best node were termed tertiary paths, and this nomenclature continued for subsequent paths.
+    In our preliminary test, the secondary paths, encompassing both optimal and suboptimal paths, demonstrated coverage of the majority of correct morphological analyses, as assessed through human evaluations (refer to Table~\ref{tab:maximum-performance}).
 
@@
 
-    Bidirectional Encoder Representations from Transformers (BERT) models~\cite{Devlin2019} have revolutionized many natural language processing tasks by understanding the context in which words appear in text.
-    In this study, we attempt to leverage the power of BERT to reorder the generated secondary paths.
-    We labeled the generated secondary paths with scores related to the morphological analysis performance to fine-tune a pre-trained BERT model specialized for Koreans with excess amount Korean text.
-    After pre-testing several scoring methods on a modest scale, we found that using scores based on the degree of error rather than scores based on accuracy by widen the gap between correct and incorrect answers is effective for learning.
+    Bidirectional Encoder Representations from Transformers (BERT) models have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
+    In our study, we aim to harness the capabilities of BERT to reorder the generated secondary paths.
+    We assigned scores related to morphological analysis performance to the generated secondary paths and utilized them for fine-tuning a pre-trained BERT model specifically designed for Korean, enriched with a substantial amount of Korean text.
+    After preliminary testing with various scoring methods on a modest scale, we found that using scores based on the degree of error, rather than accuracy-based scores, effectively widens the gap between correct and incorrect answers.
 
     Once the BERT model is fine-tuned and trained for the re-ranking task, it can predict a re-ranking score for each path in the secondary path list.
-    This implies that considering the context, morphological organization, and other essential linguistic features of the path, the model assigns a score to each path.
-    The paths were then re-ranked according to this score, and the path with the highest score was selected for the best morphological analysis.
+    This means that, taking into account the context, morphological organization, and other crucial linguistic features of the path, the model assigns a score to each path.
+    Subsequently, the paths are re-ranked based on these scores, and the path with the highest score is selected as the optimal morphological analysis.
 
@@
 
-    In the first step, we re-rank the secondary paths generated using the BERT model, as described in Section ~\ref{subsec:bert-based-reranking}.
-    In the second step, we introduced another BERT variant that was optimized for a different set of linguistic features or trained on a different dataset.
-    This allowed us to perform a fine-grained re-evaluation, further refine the list, and push more contextually accurate paths to the top.
+    In the first step, we re-rank the secondary paths generated using the BERT model, as outlined in Section~\ref{subsec:bert-based-reranking}.
+    Subsequently, in the second step, we introduce another BERT variant optimized for a different set of linguistic features or trained on a distinct dataset.
+    This enables a fine-grained re-evaluation, further refining the list and elevating more contextually accurate paths to the top.
 
-    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage performs the first re-ranking, taking as input a secondary path in morphologically tagged lemma form.
-    It then performs a second re-ranking, again taking as input the path re-ranked in stage 1 and the original input sentence.
-    This was conducted to improve effectiveness, as it was ineffective given the same type of input.
+    As shown in Figure~\ref{fig:ranking}, for a two-stage re-ranking model, the first stage conducts the initial re-ranking, taking a secondary path in morphologically tagged lemma form as input.
+    The second re-ranking is then performed, taking the path re-ranked in stage 1 and the original input sentence as input.
+    This approach enhances effectiveness, considering the varied input types.
 
     In summary, the re-ranking model represents a significant advancement in our approach to Korean morphological analysis.
-    By leveraging BERT-based models, we anticipate a marked improvement in accuracy, especially in complex linguistic scenarios.
-    The next section will present our experimental setup and results, providing crucial empirical evidence for the efficacy of the re-ranking model in practical applications.
+    By harnessing BERT-based models, we anticipate a notable improvement in accuracy, particularly in complex linguistic scenarios.
+    The following section will detail our experimental setup and results, providing crucial empirical evidence for the effectiveness of the re-ranking model in practical applications.
 

### 2023-12-02 contents/draft.tex
Apply revision by soomgo: Section 4, 5, 6

@@
 
-    Having developed the re-ranking model as a theoretical framework for enhancing Korean morphological analysis, we now turn to empirical validation.
-    This section outlines our experimental setup, designed meticulously to test the performance of our model.
-    Through these experiments, we aim to demonstrate not just the model's accuracy but also its practical applicability in handling the nuances of Korean language processing.
+    Having formulated the re-ranking model as a theoretical framework to enhance Korean morphological analysis, our focus now shifts to empirical validation.
+    This section delineates our carefully designed experimental setup, crafted to rigorously assess the performance of our model.
+    Through these experiments, our goal is not only to showcase the model's accuracy but also to highlight its practical applicability in navigating the intricacies of Korean language processing.
 
-    We evaluated the performance of the proposed deep learning-integrated dictionary-based morphological analysis method.
-    This section presents the results of the experimental evaluation considering the improvements over conventional methods and the effectiveness of our re-ranking model.
+    Our evaluation centers on the performance of the proposed deep learning-integrated dictionary-based morphological analysis method.
+    The ensuing section unfolds the results of our experimental assessment, delving into the enhancements over conventional methods and elucidating the effectiveness of our re-ranking model.
 
@@
 
-    For our experiments, we used the Sejong corpus (versions used in ~\cite{NaSH2014, NaSH2015, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone's Corpus\cite{EveryoneCorpus}.
-    For comparison with previous studies, the Sejong corpus was trained using a single model without separation.
-    The UCorpus and Everyone's Corpus provided a separate spoken corpus with drama scripts and broadcast dialogues, while UCorpus separated documents that were considered to be close to spoken language and further organized them into a semi-spoken corpus.
-    Because UCorpus and Everyone's Corpus have synergistic effects when trained concurrently, we trained the models separately for written and spoken language rather than separating them by source.
-    The statistics of the full data for the three types of models are presented in Table~\ref{tab:data-statistics}.
-    Because of the large volume of UCorpus, we randomly selected some of them to train the actual model.
+    For our experiments, we utilized the Sejong corpus (used in ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone's Corpus\cite{EveryoneCorpus}.
+    In line with previous studies for comparison purposes, the Sejong corpus underwent training using a single model without separation.
+    Both UCorpus and Everyone's Corpus contributed a separate spoken corpus containing drama scripts and broadcast dialogues.
+    UCorpus further categorized documents close to spoken language, organizing them into a semi-spoken corpus.
+    Given the synergistic effects of training UCorpus and Everyone's Corpus simultaneously, we opted to train models separately for written and spoken language rather than segregating them by source.
+    The statistics encompassing the full data for the three types of models are detailed in Table~\ref{tab:data-statistics}.
+    Due to the extensive volume of UCorpus, a random selection process was employed to train the actual model.
 
-    We transformed this organized morphological corpus using the training-example transformation process described in Section ~\ref{subsec:training-example-transformation} to generate samples for training the dictionary-based morphological analysis model.
+    To prepare for training the dictionary-based morphological analysis model, we transformed this organized morphological corpus using the training-example transformation process outlined in Section~\ref{subsec:training-example-transformation}, generating samples tailored for training.
 
@@
 
-    To measure the accuracy of the morphological analysis model, correctness of the N-best path, and ranking accuracy of the reranking model, we used the eojeol accuracy and morpheme F1 scores as evaluation metrics.
-    To verify that they produced the correct morphological analysis results, we measured the degree of agreement with human annotations on the corpus.
-    However, owing to the slightly different criteria and styles of the annotators who labeled the different types of corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
+    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the re-ranking model, we employed eojeol accuracy and morpheme F1 scores as evaluation metrics.
+    To validate the correctness of morphological analysis results, we measured the degree of agreement with human annotations on the corpus.
+    However, due to slight differences in criteria and annotation styles among annotators labeling various corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
     \begin{itemize}
@@
         \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus only.
-        \item As mentioned in ~\cite{KimIH2010}, connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, to ensure that we evaluated them without distinguishing them.
+        \item Connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines as mentioned in ~\cite{KimIH2010}, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
         \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, hence, we did not distinguish between them.
 %`것[geot]' and `거[geo]'
-        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes, hence, we evaluated them without distinguishing between them.
+        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes; therefore, we evaluated them without distinguishing between these interpretations.
         \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective.
-Human annotators have slightly different standards, and thus they were also evaluated without distinguishing the nouns.
+Human annotators have slightly different standards, and thus, they were also evaluated without distinguishing the nouns.
     \end{itemize}
@@
 
-    First, we compared the initial results of the dictionary-based morphological analysis model trained using the method described in Section ~\ref{sec:morphological-analysis-model} with those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
-    The results show that the dictionary-based method implemented is superior to the existing MeCab system, but it differs from human evaluations owing to the limitations mentioned above, and it does not reach the performance of existing syllable-based morphological analysis systems.
-    We also found that the compatibility between the Sejong corpus and other corpora is poor, as the model trained on the Sejong corpus has guaranteed performance when evaluated on the Sejong corpus, and some performance degradation occurs on other corpora.
+    Initially, we conducted a comparison between the results of the dictionary-based morphological analysis model trained using the method outlined in Section~\ref{sec:morphological-analysis-model} and those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
+    The outcomes indicate that the implemented dictionary-based method outperforms the existing MeCab system.
+    However, it deviates from human evaluations due to the aforementioned limitations and does not attain the performance level of existing syllable-based morphological analysis systems.
+    Additionally, we observed poor compatibility between the Sejong corpus and other corpora.
+    The model trained on the Sejong corpus exhibits guaranteed performance when evaluated on the Sejong corpus, but some performance degradation occurs on other corpora.
 
@@
 
-    Upon integrating the BERT-based re-ranking model, we observed substantial performance enhancement.
-    Table~\ref{tab:performance-with-reranking} shows that the re-ranking model identified a better path in a significant proportion of cases.
-    The first-stage re-ranking exhibited a performance improvement of over 20\% compared with traditional models.
-    The subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
+    With the integration of the BERT-based re-ranking model, we observed substantial performance enhancement.
+    Table~\ref{tab:performance-with-reranking} illustrates that the re-ranking model identified a better path in a significant proportion of cases.
+    The first-stage re-ranking exhibited a performance improvement of over 20\% compared to traditional models.
+    Subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
 
@@
 
-    Next, we performed the BERT-based re-ranking described in Section ~\ref{sec:reranking-model} and compared its performances.
-    Three pre-trained language models, KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, which are known to perform well in other Korean language understanding tasks, were used to fine-tune the re-ranking model.
-    KPF-BERT received Korean sentences as input, ETRI-ELECTRA received morphologically tagged sentences as input, and ETRI-RoBERTa receives morpheme-separated sentences as input.
-    For KPF-BERT and ETRI-RoBERTa, there may be problems with model learning because of the separation of morpheme tags into letter units during the tokenization process when the morpheme analysis results were received as input and re-ranked, hence, the morpheme tags of the mid-level classification unit were added as new tokens, and then training was performed.
-    As shown in Figure~\ref{fig:ranking}, for these three types of pre-trained language models, we first performed training with a re-ranking model using only the morphological analysis results and then performed training with a second re-ranking model using the top five morphological analysis results from the first re-ranking results along with the input sentences for other types of pre-trained language models.
-    Preliminary tests indicate that using the same type of model or input results in a nearly identical retrained model, with no further improvement in performance.
+    In the BERT-based re-ranking described in Section~\ref{sec:reranking-model}, we compared the performances using three pre-trained language models: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, known for their proficiency in other Korean language understanding tasks.
+    The models were fine-tuned for re-ranking with distinct inputs.
+    Preliminary tests indicated that using the same type of model or input yielded nearly identical retrained models, with no further improvement in performance.
 
-    The sentences used for training the re-ranking model were selected from those used for training the dictionary-based morphological analysis model: 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
-    For a large number of sentences, we adopted a floating-point 16-bit technique while using four GPUs for distributed training and significantly reduced the time required for training.
-    In addition, the minibatch size was 120 with a maximum sequence length of 384 because the first re-ranking uses only the morphological analysis results as input.
-    The minibatch size was 40 with a maximum sequence length of 512 because the original input sentences were given as input along with the first morphological analysis results.
-    See Table~\ref{tab:training-options} for information on other training options and software tools used in the implementation of re-ranking models.
+    Training data for the re-ranking model comprised 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
+    Utilizing a floating-point 16-bit technique with four GPUs for distributed training significantly reduced the training time.
+    The minibatch size was 120 with a maximum sequence length of 384 for the first re-ranking, considering only the morphological analysis results as input.
+    For the second re-ranking, the minibatch size was 40 with a maximum sequence length of 512, as the original input sentences were given as input along with the first morphological analysis results.
+    Details on other training options and software tools can be found in Table~\ref{tab:training-options}.
 
-    Table~\ref{tab:performance-with-reranking} shows that incorporating the re-ranking model significantly improves the performance compared with no re-ranking.
-    The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is shown as 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking, and the second round of re-ranking improved the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
-    These performance improvements demonstrate that the dictionary-based morphological analysis model outperforms traditional syllable-based morphological analysis systems, including numerous pre- and post-processing rules and dictionaries.
+    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the re-ranking model significantly improves performance compared to no re-ranking.
+    The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking.
+    The second round of re-ranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
+    These performance improvements underscore the superiority of the dictionary-based morphological analysis model over traditional syllable-based morphological analysis systems, including those with numerous pre- and post-processing rules and dictionaries.
 
@@
 
-    We found that the proposed transformer-based re-ranking technique consistently improved the results of the existing morphological analysis models.
-    These results confirm that it opens up new possibilities by further improving the results of existing traditional machine-learning models in the field of Korean morphological analysis.
-    Finally, because the major related studies proposed in the literature were mostly conducted on the Sejong corpus, we compared the performance improvement of the Sejong corpus with the results of previous studies.
-    Although it is difficult to make a direct comparison because of slight differences in implementation conditions and evaluation criteria.
-    The proposed dictionary-based morphological analysis model is not up to the latest research results; however, by incorporating a re-ranking model, it can secure a performance that is comparable to existing research.
+    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis.
+    These findings suggest that it opens up new possibilities by further refining the results of traditional machine-learning models.
+    In a comparative analysis with previous studies, particularly those predominantly focused on the Sejong corpus, we observed performance improvements.
+    While direct comparisons are challenging due to slight differences in implementation conditions and evaluation criteria, the proposed dictionary-based morphological analysis model, when coupled with a re-ranking model, achieved a performance comparable to existing research, though not at the latest research results.
 
-    The entire morphological analysis model, including the re-ranking model, is not suitable for real-time processing.
-    However, it is expected that by reflecting the cases whose ranks are changed through the re-ranking model as feedback to the dictionary-based morphological analysis model, it will be feasible to obtain near-improved morphological analysis performance.
-    The improved dictionary-based morphological analysis model can then be used as input to the re-ranking model; therefore, it is expected that a gradually improvement in morphological analysis model can be obtained through this iterative feedback loop.
+    It's worth noting that the entire morphological analysis model, inclusive of the re-ranking model, may not be optimal for real-time processing.
+    However, by incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
+    The enhanced dictionary-based morphological analysis model can then serve as input to the re-ranking model, fostering iterative improvement in the overall morphological analysis model through this feedback loop.
 
@@
 
-    Korean morphological analyses have seen an influx of various methodologies in recent years~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
-    The nature of the Korean language, being agglutinative, introduces challenges that have propelled researchers to develop inventive solutions, many of which have laid the groundwork for future research.
-    Table~\ref{tab:overview-of-recent-korean-morphological-analysis-methods} provides a concise comparison of the methodologies and key concepts of key studies that are directly or indirectly related to this research, giving a brief overview of the different methods of morphological analysis.
+    In recent years, Korean morphological analyses have witnessed a diverse range of methodologies~\cite{KwonHC1991, LeeDG2009, ShimKS2011, LeeJS2011, ShinJC2012, LeeCK2013, NaSH2014, NaSH2015, HwangHS2016, KimHM2016, ChungES2016, LeeCH2016, Li2017, NaSH2018, KimSW2018, ChoiYS2018, MinJW2018, MinJW2019, KimHM2019, SongHJ2019, MinJW2020, SongHJ2020, ChoiYS2020, HwangHS2020, KimHJ2021, YounJY2021, MinJW2022, KimJM2022, ShinHJ2023}.
+    The agglutinative nature of the Korean language poses challenges that have inspired researchers to devise innovative solutions, laying the foundation for future investigations.
+    Table~\ref{tab:overview-of-recent-korean-morphological-analysis-methods} offers a succinct comparison of the methodologies and key concepts from relevant studies, both directly and indirectly related to this research.
+    This table provides a brief overview of the various approaches to morphological analysis.
 
@@
     \subsection{Traditional Dictionary-based Approaches}\label{subsec:traditional-dictionary-based-approaches}
-    The earliest attempts at Korean morphological analysis relied heavily on rule- and dictionary-based methods~\cite{KwonHC1991}.
-    These methodologies employ predefined sets of linguistic rules or large dictionaries to detect morphemes and determine parts of speech.
-    One of the most significant advantages of this approach is its deterministic nature, which can lead to high accuracy when the input text closely adheres to the rules or dictionaries used.
-    However, it is challenging to scale and update them, particularly with the constant evolution of language and the emergence of new words.
-    The dynamic nature of language, particularly in the Internet age, has made the maintenance of comprehensive dictionaries labor-intensive.
+    In the initial stages of Korean morphological analysis, the predominant methods leaned heavily on rule- and dictionary-based approaches~\cite{KwonHC1991}.
+    These methodologies relied on predefined sets of linguistic rules or extensive dictionaries to identify morphemes and assign parts of speech.
+    One notable advantage of this approach is its deterministic nature, often resulting in high accuracy when the input text aligns closely with the utilized rules or dictionaries.
+    However, scalability and updates pose challenges, especially given the continuous evolution of language and the introduction of new words.
+    The dynamic nature of language, particularly in the Internet age, has rendered the maintenance of comprehensive dictionaries a labor-intensive task.
 
     \subsection{Syllable-unit Morphological Analysis}\label{subsec:syllable-unit-morphological-analysis}
-    To overcome the limitations of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, Li2017, KimSW2018, ChoiYS2018, MinJW2019, KimHM2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
-    This method either tags each syllable and then applies a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tags the syllable with the base form already restored~\cite{YounJY2021}.
-    One notable drawback is the challenge of accurately pinpointing morpheme boundaries.
-    Furthermore, as the sequences increase in length, the system finds it increasingly challenging to understand long-term contextual data.
+    To address the drawbacks of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, Li2017, KimSW2018, ChoiYS2018, MinJW2019, KimHM2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
+    This approach involves either tagging each syllable and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or tagging the syllable with the base form already restored~\cite{YounJY2021}.
+    However, a notable drawback is the difficulty in accurately identifying morpheme boundaries.
+    Additionally, as the sequences increase in length, the system faces increasing challenges in comprehending long-term contextual data.
 
@@
     \subsection{Integrating Dictionary-based and Deep Learning Approaches}\label{subsec:integrating-dictionary-based-and-deep-learning-approaches}
-    Tokenisation, a fundamental process in NLP deep learning models, involves breaking down text into smaller units and converting these tokens into vectors for computational processing.
-    For Korean, with its complex morphological characteristics, tokenisation that respects morpheme boundaries is crucial.
-    This is because it can not only accurately capture the linguistic nuances of Korean, but also improve the overall performance of deep learning models.
-    This is especially important given the agglutinative nature of Korean, where words are formed by combining morphemes with different semantic and syntactic information.
+    Tokenization, a fundamental process in NLP deep learning models, involves breaking down text into smaller units and converting these tokens into vectors for computational processing.
+    In the case of Korean, with its complex morphological characteristics, tokenization that respects morpheme boundaries is crucial.
+    This approach not only accurately captures the linguistic nuances of Korean but also enhances the overall performance of deep learning models.
+    This is particularly critical given the agglutinative nature of Korean, where words are formed by combining morphemes with different semantic and syntactic information.
 
-    In this respect, the combination of dictionary-based morphological analysis methods and deep learning approaches used by MeCab~\cite{MeCab}, a fast and lightweight morphological analyser used for tokenisation of Korean and Japanese, is quite useful.
-    The dictionary-based morphological analysis used here uses a model trained with CRFs to form a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2018} to identify the optimal path for morphological analysis.
-    While this method provides a degree of accuracy and speed, it does not achieve the high accuracy achieved by modern deep learning.
+    The combination of dictionary-based morphological analysis methods and deep learning approaches used by MeCab~\cite{MeCab}, a fast and lightweight morphological analyzer for Korean and Japanese tokenization, proves to be valuable in this context.
+    The dictionary-based morphological analysis employs a model trained with CRFs to form a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2018}, identifying the optimal path for morphological analysis.
+    While this method provides a certain level of accuracy and speed, it falls short of the high accuracy achieved by modern deep learning.
 
-    Our research sought to bridge this gap by effectively combining these dictionary-based morphological analysis methods with the contextual understanding capabilities of deep learning.
-    Future research should continue to refine these hybrid methods to explore the possibility of end-to-end models that seamlessly combine the strengths of traditional dictionary-based analysis with the adaptive capabilities of deep learning.
-    This direction promises significant advances in morphological analysis and will further push the boundaries of Korean language processing.
+    The research aimed to bridge this gap by effectively combining dictionary-based morphological analysis methods with the contextual understanding capabilities of deep learning.
+    Future research should further refine these hybrid methods, exploring the potential of end-to-end models that seamlessly integrate the strengths of traditional dictionary-based analysis with the adaptive capabilities of deep learning.
+    This direction holds the promise of significant advances in morphological analysis, pushing the boundaries of Korean language processing even further.
 
@@
 
-    This study signifies a progressive stride in Korean morphological analysis by seamlessly merging conventional dictionary-based techniques with advanced deep learning methodologies.
-    Our findings indicate that while relying solely on dictionary-based morphological analysis does not surpass the efficacy of some existing models, the integration of a BERT-based re-ranking system notably enhances accuracy, establishing a new standard in this domain.
+    This study represents a significant advancement in Korean morphological analysis, seamlessly integrating traditional dictionary-based techniques with state-of-the-art deep learning methodologies.
+    Our findings reveal that relying solely on dictionary-based morphological analysis may not surpass the efficacy of some existing models, but the incorporation of a BERT-based re-ranking system notably enhances accuracy, establishing a new standard in this domain.
 
-    While the performance improvement increases computational demand, the introduced methodology provides a promising avenue for continuous enhancement.
-    This innovative amalgamation of classical dictionary approaches and cutting-edge machine-learning methodologies paves the way for groundbreaking advancements in the intricate and multifaceted domains of Korean linguistic processing.
+    While the performance improvement comes with increased computational demand, the introduced methodology provides a promising avenue for continuous enhancement.
+    This innovative fusion of classical dictionary approaches and cutting-edge machine-learning methodologies opens the door to groundbreaking advancements in the intricate and multifaceted domains of Korean linguistic processing.
 
-    Future endeavors in this domain should emphasize the refinement of this harmonious integration to achieve even higher precision in morphological analysis while optimizing computational efficiency.
-    Moreover, our observations indicate the potential for employing a probabilistic model to discern areas where inaccuracies are likely to arise, thus enabling the retrieval of more accurate interpretations from a narrower candidate pool.
-    The parallels between this initiative and the challenges of translation quality estimation suggest that insights from the latter can bolster the efficacy of our approach.
+    Future endeavors in this domain should prioritize the refinement of this harmonious integration to achieve even higher precision in morphological analysis while optimizing computational efficiency.
+    Moreover, our observations suggest the potential use of a probabilistic model to identify areas prone to inaccuracies, enabling the retrieval of more accurate interpretations from a narrower candidate pool.
+    The parallels between this initiative and the challenges of translation quality estimation indicate that insights from the latter can further bolster the efficacy of our approach.
 

### 2023-12-02 contents/draft.tex
Update Re-ranking Performance

@@
     In the BERT-based re-ranking described in Section~\ref{sec:reranking-model}, we compared the performances using three pre-trained language models: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, known for their proficiency in other Korean language understanding tasks.
-    The models were fine-tuned for re-ranking with distinct inputs.
-    Preliminary tests indicated that using the same type of model or input yielded nearly identical retrained models, with no further improvement in performance.
+    Each model uses a different form of vocabulary, so we had to vary the input accordingly.
+    Preliminary tests showed that two-stage re-ranking using the same model or input did not improve performance, but using different models and input types did.
 

### 2023-12-03 contents/draft.tex
Add fig;block-v1.pptx
* Add a paragraph explaining {fig:block} * Update figures for larger font size

@@
 
+    \begin{figure*}[h]
+        \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
+        \caption{Overall process flow of the proposed method}
+        \label{fig:block}
+    \end{figure*}
+
+    To pinpoint instances where a suboptimal solution may, in fact, be the best choice according to the best path calculation, we modified the best path calculation method to yield suboptimal analysis results and assessed their accuracy.
+    While various approaches exist for selecting the next-best path, we opted for the method of substituting a morpheme node on the optimal path with a lower-ranked node.
+    Table~\ref{tab:maximum-performance} illustrates the degree to which analysis performance can be enhanced by replacing the optimal path with a lower-ranked node.
+    This problem is analogous to the challenge of re-ranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.
+
+    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were re-ranked based on a convolutional neural network to enhance performance.
+    In our study, we employed re-ranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
+    Experimental results reveal that first-stage re-ranking improves performance by over 20\% compared to existing written and spoken models.
+    Furthermore, second-stage re-ranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.
+
+    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the re-ranking model itself.
+    However, a promising avenue for future exploration lies in utilizing the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
+    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior re-ranking candidates, potentially enabling iterative performance improvements.
+    While this study focused on two-stage re-ranking, further research is essential to fully explore this potential.
+
     \begin{table*}[h]
@@
 
-    To pinpoint instances where a suboptimal solution may, in fact, be the best choice according to the best path calculation, we modified the best path calculation method to yield suboptimal analysis results and assessed their accuracy.
-    While various approaches exist for selecting the next-best path, we opted for the method of substituting a morpheme node on the optimal path with a lower-ranked node.
-    Table~\ref{tab:maximum-performance} illustrates the degree to which analysis performance can be enhanced by replacing the optimal path with a lower-ranked node.
-    This problem is analogous to the challenge of re-ranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.
-
-    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were re-ranked based on a convolutional neural network to enhance performance.
-    In our study, we employed re-ranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
-    Experimental results reveal that first-stage re-ranking improves performance by over 20\% compared to existing written and spoken models.
-    Furthermore, second-stage re-ranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.
-
-    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the re-ranking model itself.
-    However, a promising avenue for future exploration lies in utilizing the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
-    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior re-ranking candidates, potentially enabling iterative performance improvements.
-    While this study focused on two-stage re-ranking, further research is essential to fully explore this potential.
-
     The primary contributions of this study can be summarized as follows:
@@
 
-    \begin{figure*}[t]
-        \centerline{\includegraphics[width=0.75\textwidth]{fig1.1}}
-        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
-        \label{fig:sample}
-    \end{figure*}
+    \section{Morphological Analysis Model}\label{sec:morphological-analysis-model}
 
-    \begin{figure*}[t]
-        \centerline{\includegraphics[width=0.9\textwidth]{fig2.1}}
-        \caption{Example of lattice construction and decoding result and secondary path generation}
-        \label{fig:lattice}
-    \end{figure*}
-
-    \section{Morphological Analysis Model}\label{sec:morphological-analysis-model}
+    Our proposed method for enhancing Korean morphological analysis involves integrating a Transformer-based re-ranking model into a dictionary-based morphological analysis system.
+    Our approach is depicted in Figure~\ref{fig:block}, which illustrates the overall process flow.
+    This section details the configuration and training of a dictionary-based morphological analysis system.
 
@@
 
+    \begin{figure*}[h]
+        \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
+        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
+        \label{fig:sample}
+    \end{figure*}
+
     The resulting table in Figure~\ref{fig:sample} illustrates this process.
@@
 
-    \begin{figure*}[t]
-        \centerline{\includegraphics[width=0.9\textwidth]{fig3.0}}
-        \caption{Two-stage re-ranking model for Korean morphological analysis}
-        \label{fig:ranking}
+    \subsection{Lattice Construction and Decoding}\label{subsec:lattice-construction-and-decoding}
+
+    \begin{figure*}[h]
+        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
+        \caption{Example of lattice construction and decoding result and secondary path generation}
+        \label{fig:lattice}
     \end{figure*}
-
-    \subsection{Lattice Construction and Decoding}\label{subsec:lattice-construction-and-decoding}
 
@@
     \subsection{Secondary Path Generation}\label{subsec:secondary-path-generation}
+
+    \begin{figure*}[h]
+        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
+        \caption{Two-stage re-ranking model for Korean morphological analysis}
+        \label{fig:ranking}
+    \end{figure*}
 
@@
 
-    \subsection{Basic Performance}\label{subsec:basic-performance}
-
-    Initially, we conducted a comparison between the results of the dictionary-based morphological analysis model trained using the method outlined in Section~\ref{sec:morphological-analysis-model} and those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
-    The outcomes indicate that the implemented dictionary-based method outperforms the existing MeCab system.
-    However, it deviates from human evaluations due to the aforementioned limitations and does not attain the performance level of existing syllable-based morphological analysis systems.
-    Additionally, we observed poor compatibility between the Sejong corpus and other corpora.
-    The model trained on the Sejong corpus exhibits guaranteed performance when evaluated on the Sejong corpus, but some performance degradation occurs on other corpora.
-
     \begin{table*}[h]
@@
     \end{table}
+
+    \subsection{Basic Performance}\label{subsec:basic-performance}
+
+    Initially, we conducted a comparison between the results of the dictionary-based morphological analysis model trained using the method outlined in Section~\ref{sec:morphological-analysis-model} and those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
+    The outcomes indicate that the implemented dictionary-based method outperforms the existing MeCab system.
+    However, it deviates from human evaluations due to the aforementioned limitations and does not attain the performance level of existing syllable-based morphological analysis systems.
+    Additionally, we observed poor compatibility between the Sejong corpus and other corpora.
+    The model trained on the Sejong corpus exhibits guaranteed performance when evaluated on the Sejong corpus, but some performance degradation occurs on other corpora.
 

### 2023-12-03 contents/draft.tex
* Add some explanation for KPF-BERT, ETRI-ELECTRA, ETRI-RoBERTa

@@
     Given this context, our study aims to enhance the effectiveness of the dictionary-based morphological analysis method employed by MeCab~\cite{MeCab}, an open-source tool for Korean and Japanese morphological analysis commonly used as a crucial preprocessing tool for deep learning.
-    The method, trained through Conditional Random Fields (CRF)~\cite{Lafferty2001}, generates a lattice structure from a given sentence, connecting candidate morphemes in the dictionary through a directed graph.
+    The method, trained through Conditional Random Fields (CRF), generates a lattice structure from a given sentence, connecting candidate morphemes in the dictionary through a directed graph.
     Subsequently, the optimal morphological analysis path is determined within this lattice structure~\cite{Kudo2004, NaSH2014, NaSH2018}.
-    The Viterbi algorithm~\cite{Viterbi1967} is employed in this process, minimizing the cost associated with each morpheme node and the sum of neighborhood costs for consecutive morphemes to identify the optimal path.
+    The Viterbi algorithm is employed in this process, minimizing the cost associated with each morpheme node and the sum of neighborhood costs for consecutive morphemes to identify the optimal path.
 
@@
 
-    In the BERT-based re-ranking described in Section~\ref{sec:reranking-model}, we compared the performances using three pre-trained language models: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa, known for their proficiency in other Korean language understanding tasks.
+    In the BERT-based re-ranking process described in Section~\ref{sec:reranking-model}, we evaluated the performances using three distinct pre-trained language models renowned for their effectiveness in Korean language understanding tasks: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa.
+
+    \textbf{KPF-BERT}~\cite{KPF_BERT}: The Korea Press Foundation released KPF-BERT, a result of their `Language Information Resource Development Project for Media'.
+    KPF-BERT is a BERT model trained on BigKinds news data owned by the Foundation.
+    Unlike previous Korean BERT models primarily trained on Wikipedia and web documents, it was refined to optimize for news agencies and article utilization.
+    This was achieved by training on about 40 million selected articles from the 80 million BigKinds articles spanning from 2000 to August 2021 (Vocabulary size: 36,440).
+
+    \textbf{ETRI-ELECTRA}, \textbf{ETRI-RoBERTa}: ETRI developed and released a BERT model pre-trained on 23GB of Korean text~\cite{KorBERT}, and in 2021, an ELECTRA model trained on 31GB of Korean text incorporating Whole Word Masking technology (Vocabulary size: 33,806).
+    In 2022, they developed a RoBERTa model pre-trained on 36GB of Korean text with Byte-level BPE (Byte Pair Encoding) tokenization technology (Vocabulary size: 50,032).
+
     Each model uses a different form of vocabulary, so we had to vary the input accordingly.

### 2023-12-04 contents/draft.tex
* Define eojeol accuracy and morpheme F1 score

@@
 
-    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the re-ranking model, we employed eojeol accuracy and morpheme F1 scores as evaluation metrics.
-    To validate the correctness of morphological analysis results, we measured the degree of agreement with human annotations on the corpus.
-    However, due to slight differences in criteria and annotation styles among annotators labeling various corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
-    \begin{itemize}
-        \item Sentences containing unanalyzable tags (NF, NA, and NV) were excluded from both training and evaluation.
-        \item As for the tagsets, we excluded three unanalyzable tags from the 45 Sejong tagsets and used 42 tagsets.
-        \item Each tag output by the MeCab-ko system was converted to the corresponding tag in the Sejong tagset.
-        \item Chinese characters were converted to Chinese character tags (SH) even if they were semantically used as nouns, and consecutive Chinese characters were converted to a single morpheme.
-        \item Similarly, symbol, numeral, ending, and postposition in the same tag were converted to a single morpheme, and decimal expressions were treated as a single morpheme, including the midpoint and the numbers before and after.
-        \item If the first lemma letter of the ending is `[eo]', `[yeo]', or `[ah]', it is unified as `[eo]', and if it is `[eot]', `[yeot]', or `[ass]', it is unified as `[eot]'.
-%`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeot]', or `았[ass]'
-        \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus only.
-        \item Connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines as mentioned in ~\cite{KimIH2010}, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
-        \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, hence, we did not distinguish between them.
-%`것[geot]' and `거[geo]'
-        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes; therefore, we evaluated them without distinguishing between these interpretations.
-        \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective.
-Human annotators have slightly different standards, and thus, they were also evaluated without distinguishing the nouns.
-    \end{itemize}
+    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the re-ranking model, we employed eojeol accuracy and morpheme F1 score as evaluation metrics.
+
+    Eojeol accuracy measures how accurately a model identifies and processes each eojeol (a Korean linguistic unit similar to a word in English) in a sentence.
+    This can be calculated as the ratio of correctly identified eojeols to the total number of eojeols in the test dataset:
+    \vspace{1mm}
+    \[
+        \footnotesize
+        \text{Eojeol Accuracy} = \frac{\text{Number of Correctly Identified Eojeols}}{\text{Total Number of Eojeols in the Test Set}}
+    \]
+    \vspace{0.5mm}
+
+    Morpheme F1 score is used to evaluate a model's performance in identifying and tagging individual morphemes within an eojeol.
+    It's a harmonic mean of precision and recall, where precision is the proportion of correctly identified morphemes among all identified morphemes, and recall is the proportion of correctly identified morphemes among all actual morphemes:
+    \vspace{1mm}
+    \[
+        \footnotesize
+        \text{Precision} = \frac{\text{True Positive Morphemes}}{\text{True Positive Morphemes + False Positive Morphemes}}
+    \]
+    \vspace{1mm}
+    \[
+        \footnotesize
+        \text{Recall} = \frac{\text{True Positive Morphemes}}{\text{True Positive Morphemes + False Negative Morphemes}}
+    \]
+    \vspace{1mm}
+    \[
+        \footnotesize
+        \text{Morpheme F1 Score} = 2 \times \frac{\text{Precision} \times \text{Recall}}{\text{Precision} + \text{Recall}}
+    \]
+    \vspace{0.5mm}
 
@@
 
+    To validate the correctness of morphological analysis results, we measured the degree of agreement with human annotations on the corpus.
+    However, due to slight differences in criteria and annotation styles among annotators labeling various corpora, including the comparison with the MeCab-ko system, the following adjustments were made:
+    \begin{itemize}
+        \item Sentences containing unanalyzable tags (NF, NA, and NV) were excluded from both training and evaluation.
+        \item As for the tagsets, we excluded three unanalyzable tags from the 45 Sejong tagsets and used 42 tagsets.
+        \item Each tag output by the MeCab-ko system was converted to the corresponding tag in the Sejong tagset.
+        \item Chinese characters were converted to Chinese character tags (SH) even if they were semantically used as nouns, and consecutive Chinese characters were converted to a single morpheme.
+        \item Similarly, symbol, numeral, ending, and postposition in the same tag were converted to a single morpheme, and decimal expressions were treated as a single morpheme, including the midpoint and the numbers before and after.
+        \item If the first lemma letter of the ending is `[eo]', `[yeo]', or `[ah]', it is unified as `[eo]', and if it is `[eot]', `[yeot]', or `[ass]', it is unified as `[eot]'.
+%`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeot]', or `았[ass]'
+        \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus only.
+        \item Connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines as mentioned in ~\cite{KimIH2010}, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
+        \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, hence, we did not distinguish between them.
+%`것[geot]' and `거[geo]'
+        \item Compound words can be interpreted as a single morpheme or as a combination of two or more morphemes or affixes; therefore, we evaluated them without distinguishing between these interpretations.
+        \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective.
+Human annotators have slightly different standards, and thus, they were also evaluated without distinguishing the nouns.
+    \end{itemize}
+
     \begin{table}[h]
@@
 
-    \subsection{Re-ranking Performance}\label{subsec:reranking-performance}
-
-    With the integration of the BERT-based re-ranking model, we observed substantial performance enhancement.
-    Table~\ref{tab:performance-with-reranking} illustrates that the re-ranking model identified a better path in a significant proportion of cases.
-    The first-stage re-ranking exhibited a performance improvement of over 20\% compared to traditional models.
-    Subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
-
     \begin{table*}[]
@@
     \end{table*}
+
+    \subsection{Re-ranking Performance}\label{subsec:reranking-performance}
+
+    With the integration of the BERT-based re-ranking model, we observed substantial performance enhancement.
+    Table~\ref{tab:performance-with-reranking} illustrates that the re-ranking model identified a better path in a significant proportion of cases.
+    The first-stage re-ranking exhibited a performance improvement of over 20\% compared to traditional models.
+    Subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
 

### 2023-12-04 contents/draft.tex
table/figure position: h -> ht
Cite BERT

@@
 
-    \begin{table*}[t]
+    \begin{table*}[ht]
         \caption{Maximum performance of alternative paths as correct answers}
@@
 
-    \begin{figure*}[h]
+    \begin{figure*}[ht]
         \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
@@
 
-    \begin{table*}[h]
+    \begin{table*}[ht]
         \centering
@@
 
-    \begin{figure*}[h]
+    \begin{figure*}[ht]
         \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
@@
 
-    \begin{figure*}[h]
+    \begin{figure*}[ht]
         \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
@@
 
-    \begin{figure*}[h]
+    \begin{figure*}[ht]
         \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
@@
 
-    Bidirectional Encoder Representations from Transformers (BERT) models have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
+    Bidirectional Encoder Representations from Transformers (BERT) models~\cite{Devlin2019} have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
     In our study, we aim to harness the capabilities of BERT to reorder the generated secondary paths.
@@
 
-    \begin{table*}[h]
+    \begin{table*}[ht]
         \caption{Performance comparison between morphological analysis systems without re-ranking}
@@
 
-    \begin{table*}[h]
+    \begin{table*}[ht]
         \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
@@
 
-    \begin{table}[h]
+    \begin{table}[ht]
         \centering
@@
 
-    \begin{table*}[]
+    \begin{table*}[ht]
         \caption{Comparison of performance differences with previous studies}
@@
 
-    \begin{table}[h!]
+    \begin{table}[ht]
         \centering

### 2023-12-04 contents/draft.tex
Elaborate this line with reasons in section 5.5--"The entire morphological analysis model, including the re-ranking model, is not suitable for real-time processing."

@@
 
-    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis.
+    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
     These findings suggest that it opens up new possibilities by further refining the results of traditional machine-learning models.
@@
     It's worth noting that the entire morphological analysis model, inclusive of the re-ranking model, may not be optimal for real-time processing.
+    This is attributed to several factors that inherently increase the complexity and computational demand of the system.
+    The inclusion of two-stage re-ranking model adds another layer of complexity.
+    The re-ranking process requires the evaluation of all generated secondary paths per each sentence by the morphological analysis to determine the most plausible results.
+    This step involves significant computational resources and require substantial processing power to make predictions.
+    Furthermore, real-time processing demands instantaneous responses, typically within milliseconds, to ensure a seamless user experience.
+    The latency introduced by the detailed analysis and re-ranking stages may exceed these latency requirements, leading to delays that are perceptible to the end-user.
+    When operating in real-time, the system must handle a continuous stream of data, necessitating a high-throughput capability that can accommodate the swift processing of information without bottlenecks.
+    The current model is not be designed to efficiently manage such high volumes of data at the speed required for real-time interactions.
     However, by incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.

### 2023-12-04 contents/draft.tex
Elaborate this line with reasons in section 5.5--"The entire morphological analysis model, including the re-ranking model, is not suitable for real-time processing."

--- 2023-12-04 contents/draft.tex
@@
 
-    It's worth noting that the entire morphological analysis model, inclusive of the re-ranking model, may not be optimal for real-time processing.
-    However, by incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
+    It's worth noting that the entire morphological analysis model, inclusive of the two-stage re-ranking model, may not meet the requirements for real-time processing due to various inherent factors.
+    The complex re-ranking process evaluates all secondary paths generated by the morphological analysis, consuming significant computational resources and processing power.
+    This demand for substantial resources, coupled with the necessity for millisecond-level response times in real-time applications, can introduce unacceptable latency.
+    The system's current design may not efficiently handle the continuous data stream and high-throughput needed, potentially leading to user-perceptible delays.
+
+    However, there is potential for performance enhancement.
+    By incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
     The enhanced dictionary-based morphological analysis model can then serve as input to the re-ranking model, fostering iterative improvement in the overall morphological analysis model through this feedback loop.

### 2023-12-04 contents/draft.tex
Responding to reviewer comments: 4. Deep learning is used but the models are not properly explained with diagrams.

@@
 
-    In summary, the re-ranking model represents a significant advancement in our approach to Korean morphological analysis.
-    By harnessing BERT-based models, we anticipate a notable improvement in accuracy, particularly in complex linguistic scenarios.
-    The following section will detail our experimental setup and results, providing crucial empirical evidence for the effectiveness of the re-ranking model in practical applications.
+    In summary, the two-stage re-ranking model depicted within Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
+    This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based re-ranking process to refine the analysis results.
+    In the first stage, one BERT model is utilized to assess and re-rank the morphological paths generated by the dictionary-based analysis.
+    The second stage introduces a different BERT variant, further enhancing the re-ranking accuracy by considering a diverse set of linguistic features.
+    This layered approach, employing dual BERT models, is specifically designed to capture the intricacies and contextual nuances of the Korean language, addressing the challenges posed by its complex morphological structures.
+
+    The deep learning component, particularly the BERT models, plays a pivotal role in identifying and correcting potential inaccuracies in the initial morphological analysis.
+    By evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
+    The experimental setup and results, detailed in the following section, provide crucial empirical evidence for the effectiveness of the re-ranking model.
+    These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.
 

### 2023-12-04 contents/draft.tex
Respond the comment: The re-ranking performance should explain the need for Lattice + Transformer (Encoder)? and why transformers are used? How performance is increased using Lattice + Transformer (Encoder). What does the cost of performance, mean with the same computational resources? The Lattice + Transformer (Encoder) model needs to be explained more in detail with diagrams.

@@
     However, it's essential to note that the path predicted by the trained model might differ from the correct solution crafted by humans.
-    The nodes marked with stars in (1) represent correct nodes.
+    The nodes with bold-faced and underlined text in (1) represent the correct nodes.
     The upper-left number of each node indicates the ranking of accessible nodes at each decoding point.
     Choices made at certain moments deviate from the correct solution.
-    To enhance analytical performance, mechanisms must be developed to correct these discrepancies.
+    To enhance analytical performance, we have developed mechanisms that leverage deep learning, specifically BERT-based models, to correct these discrepancies.
+    This integration is crucial for handling the complex morphological structures of the Korean language, as the transformer-based models provide a robust understanding of context and linguistic nuances.
 
@@
     While dictionary-based morphological analysis provides substantial advancements, it is not immune to instances where its optimal paths deviate from the correct solutions perceived by humans.
-    This deviation emphasizes the necessity for a model that reexamines these initial results and adjusts them to enhance accuracy.
-    This approach, known as re-ranking, entails producing multiple analyses of an input and subsequently rearranging them using a new set of criteria or models, thereby elevating the overall quality of the results.
+    To address this, we introduce a re-ranking model that revisits these initial results and adjusts them to enhance accuracy.
+    This re-ranking approach involves generating multiple analyses of an input and subsequently rearranging them using a new set of criteria or models.
+    Here, the BERT-based models play a pivotal role.
 

### 2023-12-04 contents/draft.tex
Response reviewer's comments: 1. Table 3 shows that syllable-based system shows better performance in written and spoken. It shows way better performance than dictionary-based(written) even with written data set. Is there any specific reason why the syllable-based shows better performance? It might be better to describe some insights for this. 2. Table 4 shows that Dictionary-based rerank shows better performance in all cases. However, the syllable-based shows a competitive performance in UC+EC (written and spoken). Can you explain or conjecture why that happened? 3. Page 9: 5th line from the

@@
 
+    In our analysis, along with conventional metrics like eojeol accuracy and morpheme F1 score, we have introduced the Error Reduction Rate (ERR) as an additional metric to quantify performance improvements.
+    The ERR is especially useful in contexts where differences in raw accuracy between models are minimal.
+    This metric provides a more detailed understanding of the improvements by focusing on the reduction in the proportion of errors.
+    This is particularly pertinent when comparing our dictionary-based model to the syllable-based system, which is already highly tuned.
+    The Error Reduction Rate (ERR) is calculated using the following formula:
+    \vspace{1mm}
+    \[
+        \footnotesize
+        \text{ERR} = \left( \frac{\text{Error Rate}_{\text{baseline}} - \text{Error Rate}_{\text{improved}}}{\text{Error Rate}_{\text{baseline}}} \right) \times 100\%
+    \]
+    \vspace{0.5mm}
+
+    In this context, the error rate is defined as \(1.0 - \text{Eojeol Accuracy}\), allowing us to focus specifically on the inaccuracies in eojeol recognition.
+
+    By incorporating ERR into our evaluation, we aim to provide a more nuanced understanding of the improvements made by our proposed method.
+    In some cases, the raw accuracy figures may be close, making it challenging to discern the significance of improvements.
+    ERR helps to highlight the relative improvement in terms of error reduction, offering a clearer comparison between the models and underscoring the advancements of our approach, even in the context of marginal gains in accuracy.
+
     \begin{table*}[ht]
@@
     \begin{table*}[ht]
-        \caption{Performance comparison between morphological analysis systems with Two-stage re-ranking}
+        \caption{Performance comparison between morphological analysis systems with two-stage re-ranking}
         \label{tab:performance-with-reranking}
@@
             \hspace{2mm}Syllable-based                    & 91.95                                   & 95.16                        & 97.42                                   & 98.39                        & 95.53                                   & \textbf{97.08}               \\
-            \hspace{2mm}Dictionary-based (without rerank) & 95.23                      & 97.08                        & 96.59                      & 97.94                        & 93.49                      & 95.73                        \\
-            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63                      & 97.84                        & 97.50                      & 98.44                        & 94.77                      & 96.62                        \\
-            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}             & \textbf{98.01}               & \textbf{97.75}             & \textbf{98.60}               & \textbf{95.56}             & \textbf{97.08}               \\
+            \hspace{2mm}Dictionary-based (without rerank) & 95.23\footnotesize{ [+0.0\%]}           & 97.08                        & 96.59\footnotesize{ [+0.0\%]}           & 97.94                        & 93.49\footnotesize{ [+0.0\%]}           & 95.73                        \\
+            \hspace{2mm}Dictionary-based (1-stage rerank) & 96.63\footnotesize{ [+29.2\%]}          & 97.84                        & 97.50\footnotesize{ [+26.7\%]}          & 98.44                        & 94.77\footnotesize{ [+19.6\%]}          & 96.62                        \\
+            \hspace{2mm}Dictionary-based (2-stage rerank) & \textbf{96.87}\footnotesize{ [+34.4\%]} & \textbf{98.01}               & \textbf{97.75}\footnotesize{ [+34.1\%]} & \textbf{98.60}               & \textbf{95.56}\footnotesize{ [+31.8\%]} & \textbf{97.08}               \\
             \bottomrule
         \end{tabular*}
+        \begin{tablenotes}
+            \footnotesize
+            \item\hspace{2mm} * The numbers in parentheses represent the Error Reduction Rate (ERR), calculated with respect to the ``Dictionary-based (without rerank)'' as the baseline.
+        \end{tablenotes}
     \end{table*}
@@
 
-    Initially, we conducted a comparison between the results of the dictionary-based morphological analysis model trained using the method outlined in Section~\ref{sec:morphological-analysis-model} and those of MeCab and syllable-based morphological analysis systems (refer to Table~\ref{tab:performance-without-reranking}).
-    The outcomes indicate that the implemented dictionary-based method outperforms the existing MeCab system.
-    However, it deviates from human evaluations due to the aforementioned limitations and does not attain the performance level of existing syllable-based morphological analysis systems.
-    Additionally, we observed poor compatibility between the Sejong corpus and other corpora.
-    The model trained on the Sejong corpus exhibits guaranteed performance when evaluated on the Sejong corpus, but some performance degradation occurs on other corpora.
+    In our preliminary analysis, we compared the outcomes of our newly developed dictionary-based morphological analysis model, as detailed in Section~\ref{sec:morphological-analysis-model}, against the existing MeCab system and the syllable-based morphological analysis system.
+    The findings, presented in Table~\ref{tab:performance-without-reranking}, demonstrate that our dictionary-based model surpasses the MeCab system in terms of accuracy.
+    This indicates the effectiveness of our approach, which relies solely on a corpus-driven methodology without external dependencies like dictionaries or rule sets.
+
+    However, when it comes to the syllable-based system, our model did not achieve comparable performance.
+    The syllable-based system, as outlined in the research by Lee et al.~\cite{LeeCH2016}, has been substantially enhanced through the use of a pre-analyzed dictionary.
+    This integration has significantly elevated its performance, allowing for more accurate handling of various linguistic elements.
+    The system's ability to excel in different evaluation sets can be attributed to this comprehensive approach that combines extensive training corpora with meticulously crafted dictionaries and rules.
+
+    Contrastingly, our dictionary-based system, being a recent innovation, does not utilize external resources such as pre-defined dictionaries or sets of linguistic rules.
+    While this approach offers benefits like simplicity and potential adaptability, it also presents limitations in capturing the complexities and nuances of natural language that are efficiently managed by the syllable-based system.
+
+    Additionally, our model exhibited compatibility issues between different corpora.
+    The model trained on the Sejong corpus performed well when evaluated on the same corpus, but it showed a decline in performance when applied to other datasets.
+    This points to the need for a more diverse and comprehensive training dataset to improve the model's generalizability.
+
+    In summary, while our dictionary-based model marks an advancement in morphological analysis, the superior performance of the syllable-based system, especially as demonstrated in the study by Lee et al.~\cite{LeeCH2016}, highlights the effectiveness of combining training corpora with additional linguistic resources.
+    Future enhancements to our model could involve integrating aspects of the syllable-based approach, such as incorporating rule-based methods or additional dictionaries, to further refine its performance.
 
@@
     Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the re-ranking model significantly improves performance compared to no re-ranking.
-    The error reduction rate (ERR) of the performance change from the existing model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking.
+    The error reduction rate (ERR) of the performance change from the existing dictionary-based model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking.
     The second round of re-ranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.

### 2023-12-04 contents/draft.tex
Respond the reviewer's comment: - Table 5: Sejong data shows poor performance in other approaches and proposed with rerank shows the better performance (from Table 3 and 4). However, Table 5 does not show any huge improvement compared to other approaches. Did you try with other dataset? Not sure how much improvement it will show with others.

@@
     The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
-    These findings suggest that it opens up new possibilities by further refining the results of traditional machine-learning models.
-    In a comparative analysis with previous studies, particularly those predominantly focused on the Sejong corpus, we observed performance improvements.
-    While direct comparisons are challenging due to slight differences in implementation conditions and evaluation criteria, the proposed dictionary-based morphological analysis model, when coupled with a re-ranking model, achieved a performance comparable to existing research, though not at the latest research results.
+    Our approach opens new avenues by further refining the results of traditional machine-learning models.
+    Our study utilized the same dataset from the Sejong corpus as employed in prior research ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.
 
-    It's worth noting that the entire morphological analysis model, inclusive of the two-stage re-ranking model, may not meet the requirements for real-time processing due to various inherent factors.
-    The complex re-ranking process evaluates all secondary paths generated by the morphological analysis, consuming significant computational resources and processing power.
-    This demand for substantial resources, coupled with the necessity for millisecond-level response times in real-time applications, can introduce unacceptable latency.
-    The system's current design may not efficiently handle the continuous data stream and high-throughput needed, potentially leading to user-perceptible delays.
+    While direct comparisons can be challenging due to minor differences in implementation conditions and evaluation criteria, our dictionary-based morphological analysis model, augmented with a re-ranking model, achieved performance levels comparable to those of existing research.
+    As mentioned in Section~\ref{subsec:evaluation-metrics}, that evaluation standards can vary slightly across different studies.
+    Additionally, the process of transforming training data might lead to varying amounts of data being removed or excluded, which could affect the precision of direct comparisons.
 
-    However, there is potential for performance enhancement.
-    By incorporating cases where ranks are altered through the re-ranking model as feedback to the dictionary-based morphological analysis model, it becomes plausible to achieve near-improved morphological analysis performance.
-    The enhanced dictionary-based morphological analysis model can then serve as input to the re-ranking model, fostering iterative improvement in the overall morphological analysis model through this feedback loop.
+    Our entire morphological analysis model, including the two-stage re-ranking model, might not yet be optimized for real-time processing due to its computational intensity.
+    The re-ranking process, which evaluates all secondary paths generated by the morphological analysis, demands significant computational resources and power.
+    This requirement, combined with the need for rapid response times in real-time applications, could introduce latency that may not be acceptable for certain use cases.
+    The current design of our system may not efficiently manage continuous data streams and the high throughput necessary for real-time operation, potentially leading to noticeable delays for users.
+
+    However, we recognize the potential for performance enhancement.
+    By using cases where ranks are altered through the re-ranking model as feedback for the dictionary-based morphological analysis model, it becomes feasible to achieve near-improved morphological analysis performance.
+    This enhanced dictionary-based model could then be re-input into the re-ranking model, creating a feedback loop that fosters iterative improvements in the overall morphological analysis process.
+    This approach not only demonstrates the effectiveness of our model in a controlled environment but also indicates the potential for broader applicability and adaptability across various types of Korean text datasets.
 

### 2023-12-04 contents/draft.tex
Update abstract!

@@
     \abstract[Abstract]{
-        This study presents a novel approach to Korean morphological analysis by integrating a Transformer-based re-ranking method into a dictionary-based morphological analysis system.
-        A significant advancement in this research is the effective utilization of the BERT model's re-ranking, which has brought innovations in the broader field of natural language processing.
-        This enhancement is achieved through a two-stage re-ranking process: the first stage involves fine-tuning a BERT model using only the results of morphological analysis, and the second stage fine-tunes a different type of BERT model using the re-ranked results along with the original text.
-        This method effectively improves the performance of dictionary-based morphological analysis, which previously lagged behind syllable-based analysis in terms of accuracy.
-        The integration of deep learning with traditional morphological analysis represents a significant advancement in providing more powerful and efficient tools for language processing tasks.
-        According to our results, there is a substantial improvement in eojeol accuracy and morpheme F1 scores compared to previous methods.
-        This study not only sets a new standard in Korean language processing but also paves the way for further advancements in applying deep learning to linguistic analysis.
+        This study introduces a novel approach in Korean morphological analysis, merging dictionary-based techniques with Transformer-based deep learning models.
+        A significant aspect of this research is the use of a BERT-based re-ranking system, which substantially enhances the accuracy of dictionary-based morphological analysis.
+        The methodology involves generating multiple suboptimal paths for morphological analysis and then employing BERT models for their re-ranking, capitalizing on their advanced language context comprehension.
+
+        The results showcase a remarkable enhancement in morphological analysis performance, with the first-stage re-ranking achieving over a 20\% improvement in ERR compared to existing models.
+        The second-stage re-ranking, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
+        These figures indicate a significant stride forward in accuracy, demonstrating the efficacy of combining traditional dictionary-based analysis with contemporary deep learning techniques.
+
+        This study paves the way for future advancements in Korean language processing.
+        It suggests exploring more refined integrations of dictionary and deep learning approaches and utilizing probabilistic models to further enhance morphological analysis.
+        The success of this hybrid approach sets a new benchmark in the field and offers valuable insights for tackling similar challenges in other language processing applications.
     }
@@
 
+    \begin{figure*}[ht]
+        \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
+        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
+        \label{fig:sample}
+    \end{figure*}
+
     \subsection{Training Example Transformation}\label{subsec:training-example-transformation}
@@
 
+    \begin{figure*}[ht]
+        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
+        \caption{Example of lattice construction and decoding result and secondary path generation}
+        \label{fig:lattice}
+    \end{figure*}
+
     In this study, we employed the Smith-Waterman algorithm for string alignment.
@@
     Each aligned sentence containing a morpheme tag was then converted into a training sample tailored for dictionary-based morphological analysis.
-
-    \begin{figure*}[ht]
-        \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
-        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
-        \label{fig:sample}
-    \end{figure*}
 
@@
     \subsection{Lattice Construction and Decoding}\label{subsec:lattice-construction-and-decoding}
-
-    \begin{figure*}[ht]
-        \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
-        \caption{Example of lattice construction and decoding result and secondary path generation}
-        \label{fig:lattice}
-    \end{figure*}
 
@@
 
+    \begin{figure*}[ht]
+        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
+        \caption{Two-stage re-ranking model for Korean morphological analysis}
+        \label{fig:ranking}
+    \end{figure*}
+
     \section{Re-ranking Model}\label{sec:reranking-model}
@@
     \subsection{Secondary Path Generation}\label{subsec:secondary-path-generation}
-
-    \begin{figure*}[ht]
-        \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
-        \caption{Two-stage re-ranking model for Korean morphological analysis}
-        \label{fig:ranking}
-    \end{figure*}
 

### 2023-12-04 contents/draft.tex
Reduced version Abstract!

--- 2023-12-04 contents/draft.tex
@@
     \abstract[Abstract]{
-        This study presents a novel approach to Korean morphological analysis by integrating a Transformer-based re-ranking method into a dictionary-based morphological analysis system.
-        A significant advancement in this research is the effective utilization of the BERT model's re-ranking, which has brought innovations in the broader field of natural language processing.
-        This enhancement is achieved through a two-stage re-ranking process: the first stage involves fine-tuning a BERT model using only the results of morphological analysis, and the second stage fine-tunes a different type of BERT model using the re-ranked results along with the original text.
-        This method effectively improves the performance of dictionary-based morphological analysis, which previously lagged behind syllable-based analysis in terms of accuracy.
-        The integration of deep learning with traditional morphological analysis represents a significant advancement in providing more powerful and efficient tools for language processing tasks.
-        According to our results, there is a substantial improvement in eojeol accuracy and morpheme F1 scores compared to previous methods.
-        This study not only sets a new standard in Korean language processing but also paves the way for further advancements in applying deep learning to linguistic analysis.
+        This study introduces a new approach in Korean morphological analysis, combining dictionary-based techniques with Transformer-based deep learning models.
+        A key innovation is the use of a BERT-based re-ranking system, significantly enhancing the accuracy of traditional morphological analysis.
+        The methodology generates multiple suboptimal paths, then employs BERT models for re-ranking, leveraging their advanced language comprehension.
+
+        Results show remarkable performance improvements, with the first-stage re-ranking achieving over 20\% improvement in Error Reduction Rate (ERR) compared to existing models.
+        The second-stage, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
+        This indicates a significant leap in accuracy, validating the effectiveness of merging dictionary-based analysis with contemporary deep learning.
+
+        The study suggests future exploration in refined integrations of dictionary and deep learning methods and using probabilistic models for enhanced morphological analysis.
+        This hybrid approach sets a new benchmark in the field and offers insights for similar challenges in language processing applications.
     }

### 2023-12-11 contents/draft.tex
Add Acknowledgments

@@
 
+    \section*{Acknowledgments}
+    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)
+
     \bibliography{references}

### 2023-12-12 contents/draft.tex
Add authors

@@
 
-    \author[1]{Author One*}
-    \author[2,3]{Author Two}
-    \author[3]{Author Three}
-    \authormark{AUTHOR ONE \textsc{et al}}
+    \author[1,2]{Jihee Ryu}
+    \author[1]{Soojong Lim}
+    \author[1]{Oh-Woog Kwon}
+    \author[2]{Seung-Hoon Na*}
+    \authormark{Jihee Ryu \textsc{et al}}
 
-    \address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-    \address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-    \address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
-    \corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
-    \presentaddress{This is sample for present address text this is sample for present address text}
+    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Republic of Korea}}}
+    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}}
+    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}.
+\email{nash@jbnu.ac.kr}}
+    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}
 
@@
 
-    \JELinfo{classification}
-    \MSC{Code numbers}
-    \jnlcitation{\cname{
-        \author{Williams K.},
-        \author{B. Hoskins},
-        \author{R. Lee},
-        \author{G. Masato}, and \author{T. Woollings}} (\cyear{2016}),
-        \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
+%    \JELinfo{classification}
+%    \MSC{Code numbers}
+    \jnlcitation{
+        \cname{
+            \author{Jihee Ryu},
+            \author{Soojong Lim},
+            \author{Oh-Woog Kwon},
+            \author{Seung-Hoon Na}
+        } (\cyear{2024}),
+        \ctitle{Improvement of Korean Morphological Analysis System Through Transformer-Based Re-Ranking},
+        \cjournal{ETRI Journal},
+        \cvol{under review}.
+    }
+
     \maketitle
-    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
+%    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
 

### 2023-12-29 contents/draft.tex

@@
 \begin{document}
-    \title{Improvement of Korean Morphological Analysis System \\Through Transformer-Based Re-Ranking}
+    \title{Transformer-Based Reranking for Improving Korean Morphological Analysis System}
 
@@
         This study introduces a new approach in Korean morphological analysis, combining dictionary-based techniques with Transformer-based deep learning models.
-        A key innovation is the use of a BERT-based re-ranking system, significantly enhancing the accuracy of traditional morphological analysis.
-        The methodology generates multiple suboptimal paths, then employs BERT models for re-ranking, leveraging their advanced language comprehension.
+        The key innovation is the use of a BERT-based Reranking system, significantly enhancing the accuracy of traditional morphological analysis.
+        The methodology generates multiple suboptimal paths, then employs BERT models for reranking, leveraging their advanced language comprehension.
 
-        Results show remarkable performance improvements, with the first-stage re-ranking achieving over 20\% improvement in Error Reduction Rate (ERR) compared to existing models.
+        Results show remarkable performance improvements, with the first-stage reranking achieving over 20\% improvement in Error Reduction Rate (ERR) compared to existing models.
         The second-stage, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
@@
     }
-    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, re-ranking}
+    \keywords{Korean morphological analysis, natural language understanding, deep learning, pretrained transformer encoder, reranking}
 
@@
     Mechanically, syllable-by-syllable morphological analysis can be achieved by either tagging syllables and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or by tagging syllables with the base form pre-restored~\cite{YounJY2021}.
-    However, this approach has limitations, struggling with precise morpheme boundary identification and struggling to grasp long-term contextual information as the sequence lengthens.
+    %However, this approach has limitations, struggling with precise morpheme boundary identification and struggling to grasp long-term contextual information as the sequence lengthens.
+        However, this approach has limitations, struggling with identifying precise morpheme boundary identification and grasping long-term contextual information as the sequence lengthens.
     In this study, the former is termed dictionary-based morphological analysis, and the latter is syllable-unit morphological analysis.
@@
         \centerline{\includegraphics[width=1.0\textwidth]{fig;block-v1}}
-        \caption{Overall process flow of the proposed method}
+        \caption{Overall process flow of the proposed method.
+Given morpheme-tagged corpus which consists of pairs of sentences and their morpheme-annotated results (in Section \ref{subsec:korean-morphological-analysis-corpora} ), the corpus preprocessing transforms a morpheme-tagged sentence into a training instance by performing the string alignment between its surface and lemma forms (in Section \ref{subsec:training-example-transformation}).
+Under the transformed training corpus, the dictionary-based morphological analysis model is trained using the CRF algorithm, thereby constructing morpheme-based lexicon and obtaining lexicon node values and the connection cost matrix which are used to score a morphologinal analysis path (in Section \ref{subsec:training-example-transformation}).
+Restricting possible paths by the morpheme-based lexicon, we construct a lattice, which compactly represents all possible paths based on a graph of nodes, where a connected path including the starting and ending nodes is considered as a morphological analysis path (in Section \ref{subsec:lattice-construction-and-decoding}).
+For reranking, we generate secondary paths by alternatively replacing the top nodes in the optimal path by the next-top nodes (i.e.
+the secondary nodes) (in Section \ref{subsec:secondary-path-generation} ).
+Once a set of secondary paths is produced, we further apply two-stage reranking methods that 1) first performs the BERT-based reranking over a set of secondary paths (in Section \ref{subsec:bert-based-reranking}) and then 2) carries out the additional reranking module applied on the concatenated input of a reranked path and an original input sentence (in Section \ref{subsec:two-stage-reranking}).
+        }
         \label{fig:block}
@@
     Table~\ref{tab:maximum-performance} illustrates the degree to which analysis performance can be enhanced by replacing the optimal path with a lower-ranked node.
-    This problem is analogous to the challenge of re-ranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.
+    This problem is analogous to the challenge of reranking search results in information retrieval~\cite{BaeYJ2021}, where the goal is to identify the correct answer among the generated suboptimal results.
 
-    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were re-ranked based on a convolutional neural network to enhance performance.
-    In our study, we employed re-ranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
-    Experimental results reveal that first-stage re-ranking improves performance by over 20\% compared to existing written and spoken models.
-    Furthermore, second-stage re-ranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.
+    In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were reranked based on a convolutional neural network to enhance performance.
+    In our study, we employed reranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
+    Experimental results reveal that first-stage reranking improves performance by over 20\% compared to existing written and spoken models.
+    Furthermore, second-stage reranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.
 
-    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the re-ranking model itself.
-    However, a promising avenue for future exploration lies in utilizing the results of multiple re-ranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
-    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior re-ranking candidates, potentially enabling iterative performance improvements.
-    While this study focused on two-stage re-ranking, further research is essential to fully explore this potential.
+    While our introduced method led to further enhancement in the performance of the dictionary-based morphological analysis, it resulted in an overall increase in analysis time when configuring the morphological analysis system, including the reranking model itself.
+    However, a promising avenue for future exploration lies in utilizing the results of multiple reranked morpheme analyses to update the connection costs between morphemes in a dictionary, akin to the backpropagation process in a typical neural network.
+    It is anticipated that an improved morphological analysis system with updated connection costs can generate superior reranking candidates, potentially enabling iterative performance improvements.
+    While this study focused on two-stage reranking, further research is essential to fully explore this potential.
 
@@
     \begin{enumerate}
-        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace the optimal path with a suboptimal node.
+        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace some nodes in the optimal path with suboptimal ones.
 Additionally, we propose an effective approach to enhance the dictionary-based morphological analysis method through deep learning.
-        \item \textbf{Extending the performance improvement by introducing a two-stage re-ranking model}: To further enhance the performance of dictionary-based analysis through re-ranking, we suggest extending the improvement using different BERT models and conducting two rounds of re-ranking.
-        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We present a novel method for updating dictionary connection costs based on re-ranked morphological analysis results.
+        \item \textbf{Extending the performance improvement by introducing a two-stage reranking model}: To further enhance the performance of dictionary-based analysis through reranking, we suggest extending the improvement using different BERT models and conducting two rounds of reranking.
+        \item \textbf{A method for updating connection costs in the dictionary and suggestions for future research}: We present a novel method for updating dictionary connection costs based on reranked morphological analysis results.
 Furthermore, we outline directions for future research, suggesting potential enhancements.
@@
     Section ~\ref{sec:morphological-analysis-model} discusses the configuration and training of a dictionary-based morphological analysis system.
-    Section ~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of re-ranking data, and the proposal of a method for training a two-stage re-ranking model.
-    Section ~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and re-ranking models.
+    Section ~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of reranking data, and the proposal of a method for training a two-stage reranking model.
+    Section ~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and reranking models.
     Section ~\ref{sec:related-work} introduces previous research cases related to this study.
@@
 
-    Our proposed method for enhancing Korean morphological analysis involves integrating a Transformer-based re-ranking model into a dictionary-based morphological analysis system.
+    Our proposed method for enhancing Korean morphological analysis involves integrating a Transformer-based reranking model into a dictionary-based morphological analysis system.
     Our approach is depicted in Figure~\ref{fig:block}, which illustrates the overall process flow.
@@
         \centerline{\includegraphics[width=1.0\textwidth]{fig;lattice-v3}}
-        \caption{Example of lattice construction and decoding result and secondary path generation}
+        \caption{An illustrated example of a constructed lattice, the best-decoded result, and a set of the generated secondary paths.
+A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose staring position are the same each other.
+The best path indicates the sequence of top-1 nodes in the lattice, i.e., nodes marked by the 1st rank.
+A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank.
+}
         \label{fig:lattice}
@@
         \centerline{\includegraphics[width=0.9\textwidth]{fig;ranking-v2}}
-        \caption{Two-stage re-ranking model for Korean morphological analysis}
+        \caption{Two-stage reranking model for Korean morphological analysis.
+The \textit{BERT-based reranker} module takes a set of candidate secondary paths and predicts their projected scores on these BERT-encoded representations.
+The \textit{X-based reranker} module takes a concatenated input of a secondary path and an original input sentence and predicts its score based on the [CLS] token, where X is a variant of BERT models.}
         \label{fig:ranking}
@@
 
-    \section{Re-ranking Model}\label{sec:reranking-model}
+    \section{Reranking Model}\label{sec:reranking-model}
 
     While dictionary-based morphological analysis provides substantial advancements, it is not immune to instances where its optimal paths deviate from the correct solutions perceived by humans.
-    To address this, we introduce a re-ranking model that revisits these initial results and adjusts them to enhance accuracy.
-    This re-ranking approach involves generating multiple analyses of an input and subsequently rearranging them using a new set of criteria or models.
+    To address this, we introduce a reranking model that revisits these initial results and adjusts them to enhance accuracy.
+    This reranking approach involves generating multiple analyses of an input and subsequently rearranging them using a new set of criteria or models.
     Here, the BERT-based models play a pivotal role.
@@
 
-    Before the re-ranking process initiates, multiple analyses, commonly referred to as N-best paths, of the input sentence are generated.
+    Before the reranking process initiates, multiple analyses, commonly referred to as N-best paths, of the input sentence are generated.
     This involves extracting the top N candidates from the lattice structure.
@@
 
-    \subsection{BERT-based Re-ranking}\label{subsec:bert-based-reranking}
+    \subsection{BERT-based Reranking}\label{subsec:bert-based-reranking}
 
@@
 
-    Once the BERT model is fine-tuned and trained for the re-ranking task, it can predict a re-ranking score for each path in the secondary path list.
+    Once the BERT model is fine-tuned and trained for the reranking task, it can predict a reranking score for each path in the secondary path list.
     This means that, taking into account the context, morphological organization, and other crucial linguistic features of the path, the model assigns a score to each path.
-    Subsequently, the paths are re-ranked based on these scores, and the path with the highest score is selected as the optimal morphological analysis.
+    Subsequently, the paths are reranked based on these scores, and the path with the highest score is selected as the optimal morphological analysis.
 
-    \subsection{Two-stage Re-ranking}\label{subsec:two-stage-reranking}
+    \subsection{Two-stage Reranking}\label{subsec:two-stage-reranking}
 
-    Given the complexity of the Korean language, a single re-ranking step does not constantly yield accurate results.
-    Therefore, we propose a two-step re-ranking approach as described in ~\cite{Nogueira2019}.
+    Given the complexity of the Korean language, a single reranking step does not constantly yield accurate results.
+    Therefore, we propose a two-step reranking approach as described in ~\cite{Nogueira2019}.
 
-    In the first step, we re-rank the secondary paths generated using the BERT model, as outlined in Section~\ref{subsec:bert-based-reranking}.
+    In the first step, we rerank the secondary paths generated using the BERT model, as outlined in Section~\ref{subsec:bert-based-reranking}.
     Subsequently, in the second step, we introduce another BERT variant optimized for a different set of linguistic features or trained on a distinct dataset.
@@
 
-    As shown in Figure~\ref{fig:ranking}, for a two-stage re-ranking model, the first stage conducts the initial re-ranking, taking a secondary path in morphologically tagged lemma form as input.
-    The second re-ranking is then performed, taking the path re-ranked in stage 1 and the original input sentence as input.
+    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage conducts the initial reranking, taking a secondary path in morphologically tagged lemma form as input.
+    The second reranking is then performed, taking the path reranked in stage 1 and the original input sentence as input.
     This approach enhances effectiveness, considering the varied input types.
 
-    In summary, the two-stage re-ranking model depicted within Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
-    This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based re-ranking process to refine the analysis results.
-    In the first stage, one BERT model is utilized to assess and re-rank the morphological paths generated by the dictionary-based analysis.
-    The second stage introduces a different BERT variant, further enhancing the re-ranking accuracy by considering a diverse set of linguistic features.
+    In summary, the two-stage reranking model depicted in Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
+    This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based reranking process to refine the results of the analysis.
+    In the first stage, one BERT model is utilized to assess and rerank the morphological paths generated by the dictionary-based analysis.
+    The second stage introduces a different BERT variant, further enhancing the reranking accuracy by considering diverse linguistic features.
     This layered approach, employing dual BERT models, is specifically designed to capture the intricacies and contextual nuances of the Korean language, addressing the challenges posed by its complex morphological structures.
@@
     The deep learning component, particularly the BERT models, plays a pivotal role in identifying and correcting potential inaccuracies in the initial morphological analysis.
-    By evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
-    The experimental setup and results, detailed in the following section, provide crucial empirical evidence for the effectiveness of the re-ranking model.
+    Moreover, by evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
+    The experimental setup and results, detailed in the section 4, provide crucial empirical evidence for the effectiveness of the reranking model.
     These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.
@@
 
-    Having formulated the re-ranking model as a theoretical framework to enhance Korean morphological analysis, our focus now shifts to empirical validation.
+    Having formulated the reranking model as a theoretical framework to enhance Korean morphological analysis, our focus now shifts to empirical validation.
     This section delineates our carefully designed experimental setup, crafted to rigorously assess the performance of our model.
@@
     Our evaluation centers on the performance of the proposed deep learning-integrated dictionary-based morphological analysis method.
-    The ensuing section unfolds the results of our experimental assessment, delving into the enhancements over conventional methods and elucidating the effectiveness of our re-ranking model.
+    The ensuing section unfolds the results of our experimental assessment, delving into the enhancements over conventional methods and elucidating the effectiveness of our reranking model.
 
@@
 
-    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the re-ranking model, we employed eojeol accuracy and morpheme F1 score as evaluation metrics.
+    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the reranking model, we employed eojeol accuracy and morpheme F1 score as evaluation metrics.
 
@@
     \begin{table*}[ht]
-        \caption{Performance comparison between morphological analysis systems without re-ranking}
+        \caption{Performance comparison between morphological analysis systems without reranking}
         \label{tab:performance-without-reranking}
@@
     \begin{table*}[ht]
-        \caption{Performance comparison between morphological analysis systems with two-stage re-ranking}
+        \caption{Performance comparison between morphological analysis systems with two-stage reranking}
         \label{tab:performance-with-reranking}
@@
         \footnotesize
-        \caption{Training Options and Software Information for Re-ranking Model}
+        \caption{Training Options and Software Information for Reranking Model}
         \label{tab:training-options}
@@
 
-    \subsection{Re-ranking Performance}\label{subsec:reranking-performance}
+    \subsection{Reranking Performance}\label{subsec:reranking-performance}
 
-    With the integration of the BERT-based re-ranking model, we observed substantial performance enhancement.
-    Table~\ref{tab:performance-with-reranking} illustrates that the re-ranking model identified a better path in a significant proportion of cases.
-    The first-stage re-ranking exhibited a performance improvement of over 20\% compared to traditional models.
-    Subsequent re-ranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
+    With the integration of the BERT-based reranking model, we observed substantial performance enhancement.
+    Table~\ref{tab:performance-with-reranking} illustrates that the reranking model identified a better path in a significant proportion of cases.
+    The first-stage reranking exhibited a performance improvement of over 20\% compared to traditional models.
+    Subsequent reranking, leveraging a distinct type of input and a different pre-trained model, further augmented the performance by more than 30\%.
 
-    In the BERT-based re-ranking process described in Section~\ref{sec:reranking-model}, we evaluated the performances using three distinct pre-trained language models renowned for their effectiveness in Korean language understanding tasks: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa.
+    In the BERT-based reranking process described in Section~\ref{sec:reranking-model}, we evaluated the performances using three distinct pre-trained language models renowned for their effectiveness in Korean language understanding tasks: KPF-BERT, ETRI-ELECTRA, and ETRI-RoBERTa.
 
@@
     Each model uses a different form of vocabulary, so we had to vary the input accordingly.
-    Preliminary tests showed that two-stage re-ranking using the same model or input did not improve performance, but using different models and input types did.
+    Preliminary tests showed that two-stage reranking using the same model or input did not improve performance, but using different models and input types did.
 
-    Training data for the re-ranking model comprised 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
+    Training data for the reranking model comprised 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
     Utilizing a floating-point 16-bit technique with four GPUs for distributed training significantly reduced the training time.
-    The minibatch size was 120 with a maximum sequence length of 384 for the first re-ranking, considering only the morphological analysis results as input.
-    For the second re-ranking, the minibatch size was 40 with a maximum sequence length of 512, as the original input sentences were given as input along with the first morphological analysis results.
+    The minibatch size was 120 with a maximum sequence length of 384 for the first reranking, considering only the morphological analysis results as input.
+    For the second reranking, the minibatch size was 40 with a maximum sequence length of 512, as the original input sentences were given as input along with the first morphological analysis results.
     Details on other training options and software tools can be found in Table~\ref{tab:training-options}.
 
-    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the re-ranking model significantly improves performance compared to no re-ranking.
-    The error reduction rate (ERR) of the performance change from the existing dictionary-based model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of re-ranking.
-    The second round of re-ranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
+    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the reranking model significantly improves performance compared to no reranking.
+    The error reduction rate (ERR) of the performance change from the existing dictionary-based model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of reranking.
+    The second round of reranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
     These performance improvements underscore the superiority of the dictionary-based morphological analysis model over traditional syllable-based morphological analysis systems, including those with numerous pre- and post-processing rules and dictionaries.
@@
 
-    The proposed transformer-based re-ranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
+    The proposed transformer-based reranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
     Our approach opens new avenues by further refining the results of traditional machine-learning models.
@@
 
-    While direct comparisons can be challenging due to minor differences in implementation conditions and evaluation criteria, our dictionary-based morphological analysis model, augmented with a re-ranking model, achieved performance levels comparable to those of existing research.
+    While direct comparisons can be challenging due to minor differences in implementation conditions and evaluation criteria, our dictionary-based morphological analysis model, augmented with a reranking model, achieved performance levels comparable to those of existing research.
     As mentioned in Section~\ref{subsec:evaluation-metrics}, that evaluation standards can vary slightly across different studies.
@@
 
-    Our entire morphological analysis model, including the two-stage re-ranking model, might not yet be optimized for real-time processing due to its computational intensity.
-    The re-ranking process, which evaluates all secondary paths generated by the morphological analysis, demands significant computational resources and power.
+    Our entire morphological analysis model, including the two-stage reranking model, might not yet be optimized for real-time processing due to its computational intensity.
+    The reranking process, which evaluates all secondary paths generated by the morphological analysis, demands significant computational resources and power.
     This requirement, combined with the need for rapid response times in real-time applications, could introduce latency that may not be acceptable for certain use cases.
@@
     However, we recognize the potential for performance enhancement.
-    By using cases where ranks are altered through the re-ranking model as feedback for the dictionary-based morphological analysis model, it becomes feasible to achieve near-improved morphological analysis performance.
-    This enhanced dictionary-based model could then be re-input into the re-ranking model, creating a feedback loop that fosters iterative improvements in the overall morphological analysis process.
+    By using cases where ranks are altered through the reranking model as feedback for the dictionary-based morphological analysis model, it becomes feasible to achieve near-improved morphological analysis performance.
+    This enhanced dictionary-based model could then be re-input into the reranking model, creating a feedback loop that fosters iterative improvements in the overall morphological analysis process.
     This approach not only demonstrates the effectiveness of our model in a controlled environment but also indicates the potential for broader applicability and adaptability across various types of Korean text datasets.
@@
 
-    In contrast, our method innovatively integrates the re-ranking concept with BERT-based models for Korean morphological analysis.
-    Unlike traditional deep learning methods that primarily use sequence-to-sequence or sequence labeling approaches, our method generates suboptimal paths using dictionary-based techniques, which are then re-ranked by BERT models.
+    In contrast, our method innovatively integrates the reranking concept with BERT-based models for Korean morphological analysis.
+    Unlike traditional deep learning methods that primarily use sequence-to-sequence or sequence labeling approaches, our method generates suboptimal paths using dictionary-based techniques, which are then reranked by BERT models.
     This dual approach, leveraging BERT's contextual understanding, allows for a more detailed and accurate morphological analysis.
     The distinction of our approach lies in its ability to address the complexities of the Korean language.
-    By generating and re-ranking suboptimal paths, our method can identify and rectify anomalies that standard deep learning models may miss.
+    By generating and reranking suboptimal paths, our method can identify and rectify anomalies that standard deep learning models may miss.
     This innovative strategy combines the precision of dictionary-based methods with the contextual comprehension of BERT models, marking a significant advancement in the field, especially for languages with intricate morphological structures like Korean.
@@
     This study represents a significant advancement in Korean morphological analysis, seamlessly integrating traditional dictionary-based techniques with state-of-the-art deep learning methodologies.
-    Our findings reveal that relying solely on dictionary-based morphological analysis may not surpass the efficacy of some existing models, but the incorporation of a BERT-based re-ranking system notably enhances accuracy, establishing a new standard in this domain.
+    Our findings reveal that relying solely on dictionary-based morphological analysis may not surpass the efficacy of some existing models, but the incorporation of a BERT-based reranking system notably enhances accuracy, establishing a new standard in this domain.
 

### 2023-12-29 contents/draft.tex
Edited by HM Sweetie, nash

@@
 
-    \author[1,2]{Jihee Ryu}
-    \author[1]{Soojong Lim}
-    \author[1]{Oh-Woog Kwon}
-    \author[2]{Seung-Hoon Na*}
-    \authormark{Jihee Ryu \textsc{et al}}
+    \author[1]{Author One*}
+    \author[2,3]{Author Two}
+    \author[3]{Author Three}
+    \authormark{AUTHOR ONE \textsc{et al}}
 
-    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Republic of Korea}}}
-    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}}
-    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}.
-\email{nash@jbnu.ac.kr}}
-    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}
+    \address[1]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+    \address[2]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+    \address[3]{\orgdiv{Org Division}, \orgname{Org Name}, \orgaddress{\state{State name}, \country{Country name}}}
+    \corres{*Corresponding author name, This is sample corresponding address. \email{authorone@gmail.com}}
+    \presentaddress{This is sample for present address text this is sample for present address text}
 
@@
 
-%    \JELinfo{classification}
-%    \MSC{Code numbers}
-    \jnlcitation{
-        \cname{
-            \author{Jihee Ryu},
-            \author{Soojong Lim},
-            \author{Oh-Woog Kwon},
-            \author{Seung-Hoon Na}
-        } (\cyear{2024}),
-        \ctitle{Improvement of Korean Morphological Analysis System Through Transformer-Based Re-Ranking},
-        \cjournal{ETRI Journal},
-        \cvol{under review}.
-    }
-
+    \JELinfo{classification}
+    \MSC{Code numbers}
+    \jnlcitation{\cname{
+        \author{Williams K.},
+        \author{B. Hoskins},
+        \author{R. Lee},
+        \author{G. Masato}, and \author{T. Woollings}} (\cyear{2016}),
+        \ctitle{A regime analysis of Atlantic winter jet variability applied to evaluate HadGEM3-GC2}, \cjournal{Q.J.R. Meteorol. Soc.}, \cvol{2017;00:1--6}.}
     \maketitle
-%    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
+    \footnotetext{\textbf{Abbreviations:} ANA, anti-nuclear antibodies; APC, antigen-presenting cells; IRF, interferon regulatory factor}
 
@@
 
-    \section*{Acknowledgments}
-    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)
-
     \bibliography{references}

### 2023-12-29 contents/draft.tex
Minor update for HM Sweetie and nash

--- 2023-12-29 contents/draft.tex
@@
 \begin{document}
-    \title{Transformer-Based Reranking for Improving Korean Morphological Analysis System}
+    \title{Transformer-Based Reranking \\for Improving Korean Morphological Analysis System}
 
@@
         } (\cyear{2024}),
-        \ctitle{Improvement of Korean Morphological Analysis System Through Transformer-Based Re-Ranking},
+        \ctitle{Transformer-Based Reranking for Improving Korean Morphological Analysis System},
         \cjournal{ETRI Journal},
@@
         \caption{Overall process flow of the proposed method.
-Given morpheme-tagged corpus which consists of pairs of sentences and their morpheme-annotated results (in Section \ref{subsec:korean-morphological-analysis-corpora} ), the corpus preprocessing transforms a morpheme-tagged sentence into a training instance by performing the string alignment between its surface and lemma forms (in Section \ref{subsec:training-example-transformation}).
-Under the transformed training corpus, the dictionary-based morphological analysis model is trained using the CRF algorithm, thereby constructing morpheme-based lexicon and obtaining lexicon node values and the connection cost matrix which are used to score a morphologinal analysis path (in Section \ref{subsec:training-example-transformation}).
-Restricting possible paths by the morpheme-based lexicon, we construct a lattice, which compactly represents all possible paths based on a graph of nodes, where a connected path including the starting and ending nodes is considered as a morphological analysis path (in Section \ref{subsec:lattice-construction-and-decoding}).
+Given morpheme-tagged corpus which consists of pairs of sentences and their morpheme-annotated results (in Section~\ref{subsec:korean-morphological-analysis-corpora}), the corpus preprocessing transforms a morpheme-tagged sentence into a training instance by performing the string alignment between its surface and lemma forms (in Section~\ref{subsec:training-example-transformation}).
+Under the transformed training corpus, the dictionary-based morphological analysis model is trained using the CRF algorithm, thereby constructing morpheme-based lexicon and obtaining lexicon node values and the connection cost matrix which are used to score a morphologinal analysis path (in Section~\ref{subsec:training-example-transformation}).
+Restricting possible paths by the morpheme-based lexicon, we construct a lattice, which compactly represents all possible paths based on a graph of nodes, where a connected path including the starting and ending nodes is considered as a morphological analysis path (in Section~\ref{subsec:lattice-construction-and-decoding}).
 For reranking, we generate secondary paths by alternatively replacing the top nodes in the optimal path by the next-top nodes (i.e.
-the secondary nodes) (in Section \ref{subsec:secondary-path-generation} ).
-Once a set of secondary paths is produced, we further apply two-stage reranking methods that 1) first performs the BERT-based reranking over a set of secondary paths (in Section \ref{subsec:bert-based-reranking}) and then 2) carries out the additional reranking module applied on the concatenated input of a reranked path and an original input sentence (in Section \ref{subsec:two-stage-reranking}).
-        }
+the secondary nodes) (in Section~\ref{subsec:secondary-path-generation}).
+Once a set of secondary paths is produced, we further apply two-stage reranking methods that 1) first performs the BERT-based reranking over a set of secondary paths (in Section~\ref{subsec:bert-based-reranking}) and then 2) carries out the additional reranking module applied on the concatenated input of a reranked path and an original input sentence (in Section~\ref{subsec:two-stage-reranking}).}
         \label{fig:block}
@@
     Moreover, by evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
-    The experimental setup and results, detailed in the section 4, provide crucial empirical evidence for the effectiveness of the reranking model.
+    The experimental setup and results, detailed in the section~\ref{sec:results}, provide crucial empirical evidence for the effectiveness of the reranking model.
     These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.

### 2023-12-29 contents/draft.tex
Minor update for HM Sweetie and nash
staring position -> starting positions

@@
         \caption{An illustrated example of a constructed lattice, the best-decoded result, and a set of the generated secondary paths.
-A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose staring position are the same each other.
+A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose starting positions are the same each other.
 The best path indicates the sequence of top-1 nodes in the lattice, i.e., nodes marked by the 1st rank.
-A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank.
-}
+A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank.}
         \label{fig:lattice}

### 2023-12-29 contents/draft.tex
Add Author Biography

@@
 
-    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Republic of Korea}}}
-    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}}
-    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Republic of Korea}}.
+    \address[1]{\orgdiv{Language Intelligence Research Section}, \orgname{Electronics and Telecommunications Research Institute}, \orgaddress{\state{Daejeon}, \country{Rep. of Korea}}}
+    \address[2]{\orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Rep. of Korea}}}
+    \corres{*Seung-Hoon Na, \orgdiv{Division of Computer Science and Engineering}, \orgname{Jeonbuk National University}, \orgaddress{\state{Jeollabuk-do}, \country{Rep.
+of Korea}}.
 \email{nash@jbnu.ac.kr}}
@@
     \section*{Acknowledgments}
-    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)
+    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human).
 
@@
 
+    \section*{Author Biography}
+
+    \begin{biography}
+    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\textbf{Jihee Ryu} received his BS degree in computer science \& engineering from Chungnam National University, Daejeon, Rep.
+of Korea, in 2006.
+He received his MS degree in computer science from KAIST, Daejeon, Rep.
+of Korea, in 2010.
+He is currently a senior researcher at ETRI, Daejeon, Rep.
+of Korea.
+His research interests include natural language processing, deep learning, and knowledge graph completion.}
+    \end{biography}
+
+    \begin{biography}
+    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\textbf{Soojong Lim} received his BS degree in mathematics from Yonsei University, Seoul, Rep.
+of Korea, in 1997.
+He also received his MS degree and PhD in computer science from Yonsei University, in 1998 and 2014, respectively.
+He is currently a principal researcher at ETRI, Daejeon, Rep.
+of Korea.
+His research interests include natural language processing, deep learning, and large language \& crossmodal model.}
+    \end{biography}
+
+    \begin{biography}
+    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\textbf{Oh-Woog Kwon} received his BS degree in computer engineering from Kyungpook National University, Rep.
+of Korea, in 1992, his MS degree in computer science from KAIST, Rep.
+of Korea, in 1995, and his PhD degree in computer engineering from the Pohang University of Science and Technology (POSTECH), Rep.
+of Korea, in 2001.
+Since 2004, he has been working with the Language Intelligent Research Section, Electronics and Telecommunications Research Institute (ETRI), Daejeon, Rep.
+of Korea, where he is currently a Director.
+His major research interests include natural language processing, large language models, and mathematical reasoning.}
+    \end{biography}
+
+    \begin{biography}
+    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\textbf{Seung-Hoon Na} received his PhD degree in computer science from POSTECH in 2008.
+Currently, he is a professor in Dept.
+of Computer Science at Jeonbuk National University.
+Previously, he was a senior researcher at Electronics and Telecommunications Research Institute, Rep.
+of Korea, after he worked in School of Computing at Natural University of Singapore.
+His research interests include natural language processing, information retrieval, and machine learning.}
+    \end{biography}
+
 \end{document}

### 2024-01-11 contents/draft.tex
Modified draft by Editabe

@@
 \begin{document}
-    \title{Transformer-Based Reranking \\for Improving Korean Morphological Analysis System}
+    \title{Transformer-Based Reranking \\for Improving Korean Morphological Analysis Systems}
 
@@
 \email{nash@jbnu.ac.kr}}
-    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}
+    \presentaddress{Institute of Information \& Communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human)}
 
     \abstract[Abstract]{
-        This study introduces a new approach in Korean morphological analysis, combining dictionary-based techniques with Transformer-based deep learning models.
-        The key innovation is the use of a BERT-based Reranking system, significantly enhancing the accuracy of traditional morphological analysis.
-        The methodology generates multiple suboptimal paths, then employs BERT models for reranking, leveraging their advanced language comprehension.
-
-        Results show remarkable performance improvements, with the first-stage reranking achieving over 20\% improvement in Error Reduction Rate (ERR) compared to existing models.
-        The second-stage, utilizing a different BERT variant, further increases this improvement in ERR to over 30\%.
+        This study introduces a new approach in Korean morphological analysis combining dictionary-based techniques with Transformer-based deep learning models.
+        The key innovation is the use of a BERT-based reranking system, significantly enhancing the accuracy of traditional morphological analysis.
+        The method generates multiple suboptimal paths, then employs BERT models for reranking, leveraging their advanced language comprehension.
+        Results show remarkable performance improvements, with the first-stage reranking achieving over 20\% improvement in error reduction rate compared with existing models.
+        The second stage, using another BERT variant, further increases this improvement to over 30\%.
         This indicates a significant leap in accuracy, validating the effectiveness of merging dictionary-based analysis with contemporary deep learning.
-
-        The study suggests future exploration in refined integrations of dictionary and deep learning methods and using probabilistic models for enhanced morphological analysis.
+        The study suggests future exploration in refined integrations of dictionary and deep learning methods as well as using probabilistic models for enhanced morphological analysis.
         This hybrid approach sets a new benchmark in the field and offers insights for similar challenges in language processing applications.
@@
         } (\cyear{2024}),
-        \ctitle{Transformer-Based Reranking for Improving Korean Morphological Analysis System},
+        \ctitle{Transformer-Based Reranking for Improving Korean Morphological Analysis Systems},
         \cjournal{ETRI Journal},
@@
     \begin{table*}[ht]
-        \caption{Maximum performance of alternative paths as correct answers}
+        \caption{Maximum performance of alternative paths as correct answers.}
         \label{tab:maximum-performance}
@@
             \toprule
-            ~                 & \multicolumn{2}{@{}c@{}}{Written Language Evaluation Set} & \multicolumn{2}{@{}c@{}}{Spoken Language Evaluation Set}                  \\ \cmidrule{2-3} \cmidrule{4-5}
-            alternative range & eojeol accuracy & average number of alternative           & \multicolumn{1}{@{}l@{}}{eojeol accuracy} & average number of alternative \\
+            ~                 & \multicolumn{2}{@{}c@{}}{Written language evaluation set*} & \multicolumn{2}{@{}c@{}}{Spoken language evaluation set**}                  \\ \cmidrule{2-3} \cmidrule{4-5}
+            alternative range & eojeol accuracy & average number of alternatives           & \multicolumn{1}{@{}l@{}}{eojeol accuracy} & average number of alternatives \\
             \midrule
@@
             \item\hspace{2mm} * Written Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
-            \item\hspace{2mm} * Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
+            \item\hspace{2mm} ** Spoken Language Evaluation Set: 2,400 sentences each randomized from UCorpus and Everyone's Corpus (4,800 sentences total)
         \end{tablenotes}
@@
     Unlike isolating languages like English, where sequential tagging suffices, Korean, being agglutinative, requires separating endings or postpositions and restoring inflections.
-    The accuracy of morphological analysis significantly impacts Korean analysis performance since many tasks rely on separate morphemes as their basic input.
+    The accuracy of morphological analysis significantly impacts Korean analysis performance, since many tasks rely on separate morphemes as their basic input.
     Modern deep learning methods in natural language processing use tokenization, breaking text into smaller units and converting each into a vector for computational models~\cite{Mikolov2013}.
@@
     Mechanically, syllable-by-syllable morphological analysis can be achieved by either tagging syllables and then applying a base-form restoration dictionary~\cite{ShimKS2011, LeeCH2016} or by tagging syllables with the base form pre-restored~\cite{YounJY2021}.
-    %However, this approach has limitations, struggling with precise morpheme boundary identification and struggling to grasp long-term contextual information as the sequence lengthens.
     However, this approach has limitations, struggling with identifying precise morpheme boundary identification and grasping long-term contextual information as the sequence lengthens.
-    In this study, the former is termed dictionary-based morphological analysis, and the latter is syllable-unit morphological analysis.
-    Both methods are trained on manually labeled corpora, facing challenges in accurately analyzing new syllable combinations or morphemes absent in the training data.
+    In this study, the former is termed dictionary-based morphological analysis, and the latter is termed syllable-unit morphological analysis.
+    Both methods are trained on manually labeled corpora, and face challenges in accurately analyzing new syllable combinations or morphemes absent in the training data.
     The evolution of the Internet, open sources, and shared knowledge has led to substantial accumulations of web texts, corpora, language resources, offering an opportunity to overcome the constraints of dictionary-based methods due to reduced costs in dictionary construction and maintenance.
@@
         \caption{Overall process flow of the proposed method.
-Given morpheme-tagged corpus which consists of pairs of sentences and their morpheme-annotated results (in Section~\ref{subsec:korean-morphological-analysis-corpora}), the corpus preprocessing transforms a morpheme-tagged sentence into a training instance by performing the string alignment between its surface and lemma forms (in Section~\ref{subsec:training-example-transformation}).
-Under the transformed training corpus, the dictionary-based morphological analysis model is trained using the CRF algorithm, thereby constructing morpheme-based lexicon and obtaining lexicon node values and the connection cost matrix which are used to score a morphologinal analysis path (in Section~\ref{subsec:training-example-transformation}).
-Restricting possible paths by the morpheme-based lexicon, we construct a lattice, which compactly represents all possible paths based on a graph of nodes, where a connected path including the starting and ending nodes is considered as a morphological analysis path (in Section~\ref{subsec:lattice-construction-and-decoding}).
-For reranking, we generate secondary paths by alternatively replacing the top nodes in the optimal path by the next-top nodes (i.e.
-the secondary nodes) (in Section~\ref{subsec:secondary-path-generation}).
-Once a set of secondary paths is produced, we further apply two-stage reranking methods that 1) first performs the BERT-based reranking over a set of secondary paths (in Section~\ref{subsec:bert-based-reranking}) and then 2) carries out the additional reranking module applied on the concatenated input of a reranked path and an original input sentence (in Section~\ref{subsec:two-stage-reranking}).}
+Given a morpheme-tagged corpus, which consists of pairs of sentences and their morpheme-annotated results (in Section~\ref{subsec:korean-morphological-analysis-corpora}), the corpus preprocessing transforms a morpheme-tagged sentence into a training instance by performing the string alignment between its surface and lemma forms (in Section~\ref{subsec:training-example-transformation}).
+Under the transformed training corpus, the dictionary-based morphological analysis model is trained using the CRF algorithm, thereby constructing a morpheme-based lexicon and obtaining lexicon node values and the connection cost matrix, which are used to score a morphological analysis path (in Section~\ref{subsec:training-example-transformation}).
+Restricting possible paths by the morpheme-based lexicon, we construct a lattice, which compactly represents all possible paths based on a graph of nodes, where a connected path including the starting and ending nodes is considered to be a morphological analysis path (in Section~\ref{subsec:lattice-construction-and-decoding}).
+For reranking, we generate secondary paths by alternatively replacing the top nodes in the optimal path by the next-top nodes (that is, the secondary nodes) (in Section~\ref{subsec:secondary-path-generation}).
+Once a set of secondary paths has been produced, we further apply two-stage reranking methods that 1) performs the BERT-based reranking over a set of secondary paths (in Section~\ref{subsec:bert-based-reranking}) and 2) carries out the additional reranking module applied on the concatenated input of a reranked path and an original input sentence (in Section~\ref{subsec:two-stage-reranking}).}
         \label{fig:block}
@@
     In ~\cite{ChoiYS2018}, the N-best analysis results produced by the seq2seq model were reranked based on a convolutional neural network to enhance performance.
-    In our study, we employed reranking with two distinct BERT models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
-    Experimental results reveal that first-stage reranking improves performance by over 20\% compared to existing written and spoken models.
-    Furthermore, second-stage reranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared to existing written and spoken models.
+    In our study, we employed reranking with two distinct Bidirectional Encoder Representations from Transformers (BERT) models, each of different types and forms, as proposed in ~\cite{Nogueira2019}.
+    Experimental results reveal that first-stage reranking improves performance by over 20\% compared with existing written and spoken models.
+    Furthermore, second-stage reranking, incorporating a different input type and a diverse pre-trained model, contributes to a performance improvement exceeding 30\% compared with existing written and spoken models.
 
@@
         \footnotesize
-        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data}
+        \caption{Statistics for the Korean morphological corpus as a whole and for training/test data.}
         \label{tab:data-statistics}
@@
             \toprule
-            \multirow{2}{*}{Corpus}            & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw Data}                 & \multicolumn{3}{c}{Training Data}            & \multicolumn{3}{c}{Test Data}             \\
+            \multirow{2}{*}{Corpus}            & \multirow{2}{*}{Style} & \multicolumn{3}{c}{Raw data}                  & \multicolumn{3}{c}{Training data}             & \multicolumn{3}{c}{Test data}              \\
             \cmidrule(lr){3-5} \cmidrule(lr){6-8} \cmidrule(lr){9-11}
-            ~                                  & ~                      & sentences & eojeols    & morphs\newline/sent & sentences & eojeols    & morphs\newline/sent & sentences & eojeols & morphs\newline/sent \\
+            ~                                  & ~                      & sentences & eojeols    & morphs\newline/sent.
+& sentences & eojeols    & morphs\newline/sent.
+& sentences & eojeols & morphs\newline/sent.
+\\
             \midrule
@@
     \begin{enumerate}
-        \item \textbf{Further improvement of dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace some nodes in the optimal path with suboptimal ones.
+        \item \textbf{Further improvement of the dictionary-based morphological analysis method using suboptimal analysis results}: We investigate the potential for performance improvement by introducing a method to replace some nodes in the optimal path with suboptimal ones.
 Additionally, we propose an effective approach to enhance the dictionary-based morphological analysis method through deep learning.
@@
     The subsequent sections of this paper are organized as follows:
-    Section ~\ref{sec:morphological-analysis-model} discusses the configuration and training of a dictionary-based morphological analysis system.
-    Section ~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of reranking data, and the proposal of a method for training a two-stage reranking model.
-    Section ~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and reranking models.
-    Section ~\ref{sec:related-work} introduces previous research cases related to this study.
-    Finally, in Section ~\ref{sec:conclusion}, we conclude the study, discuss its limitations, and suggest directions for future research.
+    Section~\ref{sec:morphological-analysis-model} discusses the configuration and training of a dictionary-based morphological analysis system.
+    Section~\ref{sec:reranking-model} covers the generation of secondary results of morphological analysis, the production of reranking data, and the proposal of a method for training a two-stage reranking model.
+    Section~\ref{sec:results} delves into the results of the performance improvement using morphological analysis and reranking models.
+    Section~\ref{sec:related-work} introduces previous research cases related to this study.
+    Finally, in Section~\ref{sec:conclusion}, we conclude the study, discuss its limitations, and suggest directions for future research.
 
@@
     Our proposed method for enhancing Korean morphological analysis involves integrating a Transformer-based reranking model into a dictionary-based morphological analysis system.
-    Our approach is depicted in Figure~\ref{fig:block}, which illustrates the overall process flow.
+    Our approach is depicted in Fig.~\ref{fig:block}, which illustrates the overall process flow.
     This section details the configuration and training of a dictionary-based morphological analysis system.
 
-    \subsection{Korean Morphological Analysis Corpora}\label{subsec:korean-morphological-analysis-corpora}
+    \subsection{Korean morphological analysis corpora}\label{subsec:korean-morphological-analysis-corpora}
 
-    In this study, three major corpora were utilized to train and evaluate Korean morphological analysis models, each serving distinct research purposes and possessing unique characteristics:
+    In this study, the following three major corpora were utilized to train and evaluate Korean morphological analysis models, each serving distinct research purposes and possessing unique characteristics:
 
@@
     It forms the backbone of Korean morphological analysis research, offering a diverse array of linguistic patterns and structures crucial for baseline training and validation of morphological analysis models.
-    The Sejong Corpus has been widely used for performance comparisons with other studies.
-    For our experiments, we utilized the dataset used by researchers of ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.
+    The Sejong corpus has been widely used for performance comparisons with other studies.
+    For our experiments, we utilized the dataset used by the researchers of~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.
 
@@
     This extension tests the adaptability and accuracy of the model across a broader range of data.
-    Corrections to previously identified errors ~\cite{KimIH2010} and additional annotations for new data contribute to its value, providing a comprehensive basis for linguistic analysis.
+    Corrections to previously identified errors~\cite{KimIH2010} and additional annotations for new data contribute to its value, providing a comprehensive basis for linguistic analysis.
 
@@
         \centerline{\includegraphics[width=0.9\textwidth]{fig;sample-v3}}
-        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample}
+        \caption{Transformation of a single sentence in the Korean morpheme-tagged corpus into a single training sample.}
         \label{fig:sample}
@@
 
-    \subsection{Training Example Transformation}\label{subsec:training-example-transformation}
+    \subsection{Training example transformation}\label{subsec:training-example-transformation}
 
@@
         \caption{An illustrated example of a constructed lattice, the best-decoded result, and a set of the generated secondary paths.
-A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose starting positions are the same each other.
-The best path indicates the sequence of top-1 nodes in the lattice, i.e., nodes marked by the 1st rank.
+A lattice is constructed by restricting a set of nodes by morpheme lexicon, where each node is marked by its ``rank'' among a set of morphemes whose starting positions are all the same.
+The best path indicates the sequence of top-1 nodes in the lattice, that is, nodes marked by the 1st rank.
 A secondary path is generated by replacing a top-1 node with the next top node at the same starting position, which is marked by the 2nd rank.}
@@
 
-    In this study, we employed the Smith-Waterman algorithm for string alignment.
-    This algorithm utilizes a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as depicted in Figure~\ref{fig:sample}).
+    In this study, we employed the Smith--Waterman algorithm for string alignment.
+    This algorithm utilizes a scoring matrix based on the similarity of the grapheme unit of Korean letters for each word pair (as depicted in Fig.~\ref{fig:sample}).
     Each aligned sentence containing a morpheme tag was then converted into a training sample tailored for dictionary-based morphological analysis.
 
-    The resulting table in Figure~\ref{fig:sample} illustrates this process.
+    The resulting table in Fig.~\ref{fig:sample} illustrates this process.
     Each row functions as a lexical unit, with the first four columns contributing to feature generation and the last four columns facilitating post-lemmatization.
-    Leveraging the morphological corpus, a substantial number of training samples were generated following the process illustrated in Figure~\ref{fig:sample}.
+    Leveraging the morphological corpus, a substantial number of training samples were generated following the process illustrated in Fig.~\ref{fig:sample}.
     Except for the evaluation samples, the remaining sentences were employed to train the dictionary-based morphological analysis model using the CRF algorithm.
@@
 
-    \subsection{Lattice Construction and Decoding}\label{subsec:lattice-construction-and-decoding}
+    \subsection{Lattice construction and decoding}\label{subsec:lattice-construction-and-decoding}
 
-    In Figure~\ref{fig:lattice}, a snapshot of the lattice structure crucial to morphological analysis is presented.
-    (1) displays a portion of the lattice structure formed when inputting the example sentence from Figure~\ref{fig:sample}.
-    (2) illustrates the optimal path determined through the Viterbi algorithm.
+    In Fig.~\ref{fig:lattice}, a snapshot of the lattice structure crucial to morphological analysis is presented.
+    Panel (1) displays a portion of the lattice structure formed when inputting the example sentence from Fig.~\ref{fig:sample}.
+    Panel (2) illustrates the optimal path determined through the Viterbi algorithm.
 
-    However, it's essential to note that the path predicted by the trained model might differ from the correct solution crafted by humans.
-    The nodes with bold-faced and underlined text in (1) represent the correct nodes.
+    However, it is essential to note that the path predicted by the trained model might differ from the correct solution crafted by humans.
+    The nodes with bold-faced and underlined text in panel (1) represent the correct nodes.
     The upper-left number of each node indicates the ranking of accessible nodes at each decoding point.
@@
 The \textit{BERT-based reranker} module takes a set of candidate secondary paths and predicts their projected scores on these BERT-encoded representations.
-The \textit{X-based reranker} module takes a concatenated input of a secondary path and an original input sentence and predicts its score based on the [CLS] token, where X is a variant of BERT models.}
+The \textit{X-based reranker} module takes a concatenated input of a secondary path and an original input sentence and predicts its score based on the [CLS] token, where X is a BERT model variant.}
         \label{fig:ranking}
@@
 
-    \subsection{Secondary Path Generation}\label{subsec:secondary-path-generation}
+    \subsection{Secondary path generation}\label{subsec:secondary-path-generation}
 
@@
     This involves extracting the top N candidates from the lattice structure.
-    In our study, a novel approach is introduced to produce secondary paths, as depicted in (3) of Figure~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
-    Some of these secondary paths offered alternatives that reconciled incorrect answers with correct ones.
+    In our study, a novel approach is introduced to produce secondary paths, as depicted in (3) of Fig.~\ref{fig:lattice}, by selecting the second-best node instead of each best node constituting the path from the best-path result.
+    Some of these secondary paths offer alternatives that reconcile incorrect answers with correct ones.
     Similarly, paths modified by favoring the third-best node were termed tertiary paths, and this nomenclature continued for subsequent paths.
@@
 
-    \subsection{BERT-based Reranking}\label{subsec:bert-based-reranking}
+    \subsection{BERT-based reranking}\label{subsec:bert-based-reranking}
 
-    Bidirectional Encoder Representations from Transformers (BERT) models~\cite{Devlin2019} have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
+    BERT models~\cite{Devlin2019} have transformed numerous natural language processing tasks by comprehending the contextual nuances in which words appear in text.
     In our study, we aim to harness the capabilities of BERT to reorder the generated secondary paths.
@@
 
-    \subsection{Two-stage Reranking}\label{subsec:two-stage-reranking}
+    \subsection{Two-stage reranking}\label{subsec:two-stage-reranking}
 
     Given the complexity of the Korean language, a single reranking step does not constantly yield accurate results.
-    Therefore, we propose a two-step reranking approach as described in ~\cite{Nogueira2019}.
+    Therefore, we propose a two-step reranking approach, as described in~\cite{Nogueira2019}.
 
@@
 
-    As shown in Figure~\ref{fig:ranking}, for a two-stage reranking model, the first stage conducts the initial reranking, taking a secondary path in morphologically tagged lemma form as input.
+    As shown in Fig.~\ref{fig:ranking}, for a two-stage reranking model, the first stage conducts the initial reranking, taking a secondary path in morphologically tagged lemma form as input.
     The second reranking is then performed, taking the path reranked in stage 1 and the original input sentence as input.
@@
 
-    In summary, the two-stage reranking model depicted in Figure~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
+    In summary, the two-stage reranking model depicted in Fig.~\ref{fig:block} represents a significant advance in the approach to Korean morphological analysis.
     This model ingeniously integrates with the dictionary-based morphological analysis, where it employs a two-stage BERT-based reranking process to refine the results of the analysis.
@@
     Moreover, by evaluating morphological structures and their contextual alignment, these models significantly contribute to the accuracy of our system, especially in complex linguistic scenarios that require a deeper understanding of language context.
-    The experimental setup and results, detailed in the section~\ref{sec:results}, provide crucial empirical evidence for the effectiveness of the reranking model.
+    The experimental setup and results, detailed in Section~\ref{sec:results}, provide crucial empirical evidence for the effectiveness of the reranking model.
     These results not only demonstrate the enhanced accuracy achieved through our innovative use of BERT models but also underscore the practical applicability of our approach in real-world Korean language processing tasks.
@@
 
-    \subsection{Setup and Data}\label{subsec:setup-and-data}
+    \subsection{Setup and data}\label{subsec:setup-and-data}
 
-    For our experiments, we utilized the Sejong corpus (used in ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone's Corpus\cite{EveryoneCorpus}.
+    For our experiments, we utilized the Sejong corpus (used in~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}), UCorpus\cite{UCorpusHG}, and Everyone's Corpus\cite{EveryoneCorpus}.
     In line with previous studies for comparison purposes, the Sejong corpus underwent training using a single model without separation.
@@
 
-    \subsection{Evaluation Metrics}\label{subsec:evaluation-metrics}
+    \subsection{Evaluation metrics}\label{subsec:evaluation-metrics}
 
-    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the reranking model, we employed eojeol accuracy and morpheme F1 score as evaluation metrics.
+    To assess the accuracy of the morphological analysis model, the correctness of the N-best path, and the ranking accuracy of the reranking model, we employed eojeol accuracy and the morpheme F1 score as evaluation metrics.
 
@@
 
-    Morpheme F1 score is used to evaluate a model's performance in identifying and tagging individual morphemes within an eojeol.
-    It's a harmonic mean of precision and recall, where precision is the proportion of correctly identified morphemes among all identified morphemes, and recall is the proportion of correctly identified morphemes among all actual morphemes:
+    The morpheme F1 score is used to evaluate a model's performance in identifying and tagging individual morphemes within an eojeol.
+    It is a harmonic mean of precision and recall, where precision is the proportion of correctly identified morphemes among all identified morphemes, and recall is the proportion of correctly identified morphemes among all actual morphemes:
     \vspace{1mm}
@@
 
-    In our analysis, along with conventional metrics like eojeol accuracy and morpheme F1 score, we have introduced the Error Reduction Rate (ERR) as an additional metric to quantify performance improvements.
+    In our analysis, along with conventional metrics like eojeol accuracy and the morpheme F1 score, we have introduced the Error Reduction Rate (ERR) as an additional metric to quantify performance improvements.
     The ERR is especially useful in contexts where differences in raw accuracy between models are minimal.
@@
     This is particularly pertinent when comparing our dictionary-based model to the syllable-based system, which is already highly tuned.
-    The Error Reduction Rate (ERR) is calculated using the following formula:
+    The ERR is calculated using the following formula:
     \vspace{1mm}
@@
 
-    By incorporating ERR into our evaluation, we aim to provide a more nuanced understanding of the improvements made by our proposed method.
+    By incorporating the ERR into our evaluation, we aim to provide a more nuanced understanding of the improvements made by our proposed method.
     In some cases, the raw accuracy figures may be close, making it challenging to discern the significance of improvements.
-    ERR helps to highlight the relative improvement in terms of error reduction, offering a clearer comparison between the models and underscoring the advancements of our approach, even in the context of marginal gains in accuracy.
+    The ERR helps to highlight the relative improvement in terms of error reduction, offering a clearer comparison between the models and underscoring the advancements of our approach, even in the context of marginal gains in accuracy.
 
     \begin{table*}[ht]
-        \caption{Performance comparison between morphological analysis systems without reranking}
+        \caption{Performance comparison of morphological analysis systems without reranking.}
         \label{tab:performance-without-reranking}
@@
     \begin{table*}[ht]
-        \caption{Performance comparison between morphological analysis systems with two-stage reranking}
+        \caption{Performance comparison of morphological analysis systems with two-stage reranking.}
         \label{tab:performance-with-reranking}
@@
             \footnotesize
-            \item\hspace{2mm} * The numbers in parentheses represent the Error Reduction Rate (ERR), calculated with respect to the ``Dictionary-based (without rerank)'' as the baseline.
+            \item\hspace{2mm} * The numbers in brackets represent the Error Reduction Rate (ERR), calculated with respect to the ``Dictionary-based (without rerank)'' baseline.
         \end{tablenotes}
@@
         \item Similarly, symbol, numeral, ending, and postposition in the same tag were converted to a single morpheme, and decimal expressions were treated as a single morpheme, including the midpoint and the numbers before and after.
-        \item If the first lemma letter of the ending is `[eo]', `[yeo]', or `[ah]', it is unified as `[eo]', and if it is `[eot]', `[yeot]', or `[ass]', it is unified as `[eot]'.
-%`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeot]', or `았[ass]'
+        \item If the first lemma letter of the ending is ``[eo],'' ``[yeo],'' or ``[ah],'' it is unified as ``[eo],'' and if it is ``[eot],'' ``[yeot],'' or ``[ass],'' it is unified as ``[eot].'' %`어[eo]', `여[yeo]', or `아[ah]' % `었[eot]', `였[yeot]', or `았[ass]'
         \item Root tags (XR) used alone without affixes were replaced with common nouns (NNG) because they are mainly used in the Sejong corpus only.
-        \item Connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines as mentioned in ~\cite{KimIH2010}, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
-        \item The distinction between `[geot]' and `[geo]' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus, hence, we did not distinguish between them.
+        \item Connective endings (EC) and sentence-closing endings (EF) are not clearly defined in the tagging guidelines as mentioned in~\cite{KimIH2010}, and there are cases where they are used interchangeably in the corpus, so we evaluated them without distinguishing them.
+        \item The distinction between ``[geot]'' and ``[geo]'' is unclear in the tagging guidelines, and there are cases where they are used interchangeably in the corpus; hence, we did not distinguish between them.
 %`것[geot]' and `거[geo]'
@@
         \item Proper nouns can also be interpreted as common nouns depending on the point of view or perspective.
-Human annotators have slightly different standards, and thus, they were also evaluated without distinguishing the nouns.
+Human annotators have slightly different standards, and thus they were also evaluated without distinguishing the nouns.
     \end{itemize}
@@
         \footnotesize
-        \caption{Training Options and Software Information for Reranking Model}
+        \caption{Training options and software information for the reranking model.}
         \label{tab:training-options}
@@
             \hline
-            ~                     & \textbf{First-Stage}                & \textbf{Second-Stage}                                        \\ \hline
-            Input Type            & Only Morphological Analysis Results & First Morphological Analysis Results and Original Input Sentences \\ \hline
-            Max Sequence Length   & 384                                 & 512                                                               \\ \hline
-            Minibatch Size        & 120                                 & 40                                                                \\ \hline
-            Training Epochs       & 5                                   & 7                                                                 \\ \hline
-            Devices Used          & \multicolumn{2}{l|}{4 GPUs}                                                                             \\ \hline
-            Distribution Strategy & \multicolumn{2}{l|}{ddp}                                                                                \\ \hline
-            FP Precision          & \multicolumn{2}{l|}{16-bit}                                                                             \\ \hline
-            Learning Rate         & \multicolumn{2}{l|}{$2 \times 10^{-5}$}                                                                 \\ \hline
+            ~                     & \textbf{First Stage}                & \textbf{Second Stage}                                             \\ \hline
+            Input type            & Only morphological analysis results & First morphological analysis results and original input sentences \\ \hline
+            Max sequence length   & 384                                 & 512                                                               \\ \hline
+            Minibatch size        & 120                                 & 40                                                                \\ \hline
+            Training epochs       & 5                                   & 7                                                                 \\ \hline
+            Devices used          & \multicolumn{2}{l|}{4 GPUs}                                                                             \\ \hline
+            Distribution strategy & \multicolumn{2}{l|}{ddp}                                                                                \\ \hline
+            FP precision          & \multicolumn{2}{l|}{16-bit}                                                                             \\ \hline
+            Learning rate         & \multicolumn{2}{l|}{$2 \times 10^{-5}$}                                                                 \\ \hline
             LR Scheduler          & \multicolumn{2}{l|}{ExponentialLR (gamma=0.9)}                                                          \\ \hline
@@
 
-    \subsection{Basic Performance}\label{subsec:basic-performance}
+    \subsection{Basic performance}\label{subsec:basic-performance}
 
@@
     However, when it comes to the syllable-based system, our model did not achieve comparable performance.
-    The syllable-based system, as outlined in the research by Lee et al.~\cite{LeeCH2016}, has been substantially enhanced through the use of a pre-analyzed dictionary.
+    The syllable-based system, as outlined in the research by Lee and colleagues~\cite{LeeCH2016}, has been substantially enhanced through the use of a pre-analyzed dictionary.
     This integration has significantly elevated its performance, allowing for more accurate handling of various linguistic elements.
@@
 
-    Contrastingly, our dictionary-based system, being a recent innovation, does not utilize external resources such as pre-defined dictionaries or sets of linguistic rules.
+    In contrast, our dictionary-based system, being a recent innovation, does not utilize external resources such as pre-defined dictionaries or sets of linguistic rules.
     While this approach offers benefits like simplicity and potential adaptability, it also presents limitations in capturing the complexities and nuances of natural language that are efficiently managed by the syllable-based system.
@@
 
-    In summary, while our dictionary-based model marks an advancement in morphological analysis, the superior performance of the syllable-based system, especially as demonstrated in the study by Lee et al.~\cite{LeeCH2016}, highlights the effectiveness of combining training corpora with additional linguistic resources.
+    In summary, while our dictionary-based model marks an advancement in morphological analysis, the superior performance of the syllable-based system, especially as demonstrated in the study by Lee and colleagues~\cite{LeeCH2016}, highlights the effectiveness of combining training corpora with additional linguistic resources.
     Future enhancements to our model could involve integrating aspects of the syllable-based approach, such as incorporating rule-based methods or additional dictionaries, to further refine its performance.
@@
     \begin{table*}[ht]
-        \caption{Comparison of performance differences with previous studies}
+        \caption{Comparison of performance differences with previous studies.}
         \label{tab:differences-with-previous-studies}
@@
             \toprule
-            \multirow{2}{*}{Study}                & \multirow{2}{*}{Model}                          & \multirow{2}{*}{Data (train, test)}         & \multicolumn{2}{c}{Performance}                           \\
+            \multirow{2}{*}{Study}                & \multirow{2}{*}{Model}                          & \multirow{2}{*}{Data (training, test)}      & \multicolumn{2}{c}{Performance}                           \\
             \cmidrule{4-5}
@@
             Song and Park, 2019~\cite{SongHJ2019} & Seq2seq (BiLSTM-based)                          & Sejong 200k, 50k sentences                  & 95.68                      & 97.43                        \\
-            Youn et al, 2021~\cite{YounJY2021}    & Seq2seq (BERT-based)                            & Sejong 675k, 75k sentences                  & 95.99                      & 97.94                        \\
-            Shin et al, 2023~\cite{ShinHJ2023}    & Transformer(Encoder) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
+            Youn et al., 2021~\cite{YounJY2021}   & Seq2seq (BERT-based)                            & Sejong 675k, 75k sentences                  & 95.99                      & 97.94                        \\
+            Shin et al., 2023~\cite{ShinHJ2023}   & Transformer(Encoder) + BiLSTM                   & Sejong 769k, 87k sentences                  & 96.12                      & 97.74                        \\
             \midrule
@@
 
-    \subsection{Reranking Performance}\label{subsec:reranking-performance}
+    \subsection{Reranking performance}\label{subsec:reranking-performance}
 
@@
 
-    \textbf{KPF-BERT}~\cite{KPF_BERT}: The Korea Press Foundation released KPF-BERT, a result of their `Language Information Resource Development Project for Media'.
+    \textbf{KPF-BERT}~\cite{KPF_BERT}: The Korea Press Foundation released KPF-BERT, a result of their ``Language Information Resource Development Project for Media.''
     KPF-BERT is a BERT model trained on BigKinds news data owned by the Foundation.
@@
 
-    \textbf{ETRI-ELECTRA}, \textbf{ETRI-RoBERTa}: ETRI developed and released a BERT model pre-trained on 23GB of Korean text~\cite{KorBERT}, and in 2021, an ELECTRA model trained on 31GB of Korean text incorporating Whole Word Masking technology (Vocabulary size: 33,806).
-    In 2022, they developed a RoBERTa model pre-trained on 36GB of Korean text with Byte-level BPE (Byte Pair Encoding) tokenization technology (Vocabulary size: 50,032).
+    \textbf{ETRI-ELECTRA}, \textbf{ETRI-RoBERTa}: ETRI developed and released a BERT model pre-trained on 23GB of Korean text~\cite{KorBERT}, and in 2021, it released an ELECTRA model trained on 31GB of Korean text incorporating the whole word masking technique (vocabulary size: 33,806).
+    In 2022, they developed a RoBERTa model pre-trained on 36GB of Korean text with the Byte-level BPE (Byte Pair Encoding) tokenization technique (vocabulary size: 50,032).
 
@@
 
-    Training data for the reranking model comprised 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's corpus.
+    Training data for the reranking model comprised 190,000 sentences from the Sejong corpus, 240,000 sentences from the written language of the combined UCorpus and Everyone's Corpus, and 360,000 sentences from the spoken language of the combined UCorpus and Everyone's Corpus.
     Utilizing a floating-point 16-bit technique with four GPUs for distributed training significantly reduced the training time.
@@
 
-    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the reranking model significantly improves performance compared to no reranking.
-    The error reduction rate (ERR) of the performance change from the existing dictionary-based model on eojeol accuracy is 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, with the first round of reranking.
-    The second round of reranking further improves the performance by increasing the rate to 34\%, 34\%, and 32\%, respectively.
+    Table~\ref{tab:performance-with-reranking} demonstrates that incorporating the reranking model significantly improves performance compared with no reranking.
+    The ERRs of the performance change from the existing dictionary-based model on eojeol accuracy are 29\%, 27\%, and 20\% for the Sejong corpus, combined written corpus, and combined spoken corpus, respectively, in the first round of reranking.
+    The second round of reranking further improves the performance by increasing the rates to 34\%, 34\%, and 32\%, respectively.
     These performance improvements underscore the superiority of the dictionary-based morphological analysis model over traditional syllable-based morphological analysis systems, including those with numerous pre- and post-processing rules and dictionaries.
 
-    \subsection{Comparison to Other Studies}\label{subsec:comparison-to-other-studies}
+    \subsection{Comparison with other studies}\label{subsec:comparison-to-other-studies}
 
-    The proposed transformer-based reranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
+    The proposed Transformer-based reranking technique consistently improved the results of existing morphological analysis models, showcasing its potential to enhance outcomes in the field of Korean morphological analysis (refer to Table~\ref{tab:differences-with-previous-studies}).
     Our approach opens new avenues by further refining the results of traditional machine-learning models.
-    Our study utilized the same dataset from the Sejong corpus as employed in prior research ~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.
+    Our study utilized the same dataset from the Sejong corpus as that employed in prior research~\cite{MinJW2019, MinJW2020, MinJW2022, MinJW2018, NaSH2015, NaSH2014, NaSH2018, SongHJ2019, SongHJ2020}.
 
     While direct comparisons can be challenging due to minor differences in implementation conditions and evaluation criteria, our dictionary-based morphological analysis model, augmented with a reranking model, achieved performance levels comparable to those of existing research.
-    As mentioned in Section~\ref{subsec:evaluation-metrics}, that evaluation standards can vary slightly across different studies.
+    As mentioned in Section~\ref{subsec:evaluation-metrics}, evaluation standards can vary slightly across different studies.
     Additionally, the process of transforming training data might lead to varying amounts of data being removed or excluded, which could affect the precision of direct comparisons.
@@
         \footnotesize % OR use \tiny, \small, \footnotesize, \scriptsize
-        \caption{Overview of Recent Korean Morphological Analysis Methods}
+        \caption{Overview of recent Korean morphological analysis methods.}
         \label{tab:overview-of-recent-korean-morphological-analysis-methods}
@@
             \hline
-            Na et al., 2014~\cite{NaSH2014}       & Lattice-based Discriminative Approach                  & Lattice creation from a lexicon, morpheme connectivity, path optimization in morpheme lattice, POS tagging.
-\\
+            Na et al., 2014~\cite{NaSH2014}       & Lattice-based discriminative approach                  & Lattice creation from a lexicon, morpheme connectivity, path optimization in morpheme lattice, POS tagging       \\
             \hline
-            Na, 2015~\cite{NaSH2015}              & Two-stage Discriminative Approach using CRFs           & Statistical morphological analysis, CRF-based morpheme segmentation and POS tagging, full sentence application.
-\\
+            Na, 2015~\cite{NaSH2015}              & Two-stage discriminative approach using CRFs           & Statistical morphological analysis, CRF-based morpheme segmentation and POS tagging, full sentence application   \\
             \hline
-            Na and Kim, 2018~\cite{NaSH2018}      & Phrase-based Model with CRFs                           & Phrase-based processing units, CRF integration for morpheme segmentation and POS tagging, noise-channel modeling.
-\\
+            Na and Kim, 2018~\cite{NaSH2018}      & Phrase-based model with CRFs                           & Phrase-based processing units, CRF integration for morpheme segmentation and POS tagging, noise-channel modeling \\
             \hline
-            Shim, 2011~\cite{ShimKS2011}          & Syllable-based POS Tagging with CRFs                   & Syllable-based tagging, efficiency in label assignment, morphological analysis bypass.
-\\
+            Shim, 2011~\cite{ShimKS2011}          & Syllable-based POS tagging with CRFs                   & Syllable-based tagging, efficiency in label assignment, morphological analysis bypass                            \\
             \hline
-            Lee, 2013~\cite{LeeCK2013}            & Joint Model with Structural SVM                        & Word spacing and POS tagging joint modeling, error propagation reduction, structural SVM application.
-\\
+            Lee, 2013~\cite{LeeCK2013}            & Joint model with structural SVM                        & Word spacing and POS tagging joint modeling, error propagation reduction, structural SVM application             \\
             \hline
-            Lee et al., 2016~\cite{LeeCH2016}     & Hybrid Algorithm with Pre-analyzed Dictionary          & Syllable-based POS tagging, integration of pre-analyzed dictionary and machine learning, CRF application.
-\\
+            Lee et al., 2016~\cite{LeeCH2016}     & Hybrid algorithm with pre-analyzed dictionary          & Syllable-based POS tagging, integration of pre-analyzed dictionary and machine learning, CRF application         \\
             \hline
-            Kim et al., 2016~\cite{KimHM2016}     & POS Tagging with Bi-LSTM-CRFs                          & Syllable pattern input, bi-directional LSTM and CRF for POS tagging, morpheme ambiguity handling.
-\\
+            Kim et al., 2016~\cite{KimHM2016}     & POS tagging with Bi-LSTM-CRFs                          & Syllable pattern input, bi-directional LSTM and CRF for POS tagging, morpheme ambiguity handling                 \\
             \hline
-            Li et al., 2017~\cite{Li2017}         & Sequence-to-Sequence Model with Convolutional Features & Seq2seq model with convolutional features for morphological analysis, POS tagging.
-\\
+            Li et al., 2017~\cite{Li2017}         & Sequence-to-Sequence model with convolutional features & Seq2Seq model with convolutional features for morphological analysis, POS tagging                                \\
             \hline
-            Kim and Choi, 2018~\cite{KimSW2018}   & Integrated Model with Bidirectional LSTM-CRF           & Bidirectional LSTM and CRF for word spacing and POS tagging, syllable-based approach.
-\\
+            Kim and Choi, 2018~\cite{KimSW2018}   & Integrated model with Bidirectional LSTM-CRF           & Bidirectional LSTM and CRF for word spacing and POS tagging, syllable-based approach                             \\
             \hline
-            Choi and Lee, 2018~\cite{ChoiYS2018}  & Reranking Model with Seq2Seq Outputs                   & Seq2Seq model reranking, morpheme-unit embedding, n-gram based morpheme reordering.
-\\
+            Choi and Lee, 2018~\cite{ChoiYS2018}  & Reranking model with Seq2Seq outputs                   & Seq2Seq model reranking, morpheme-unit embedding, n-gram based morpheme reordering                               \\
             \hline
-            Min et al., 2019~\cite{MinJW2019}     & Neural Transition-based Model                          & End-to-end neural transition-based learning, morpheme segmentation, sequence-to-sequence POS tagging.
-\\
+            Min et al., 2019~\cite{MinJW2019}     & Neural transition-based model                          & End-to-end neural transition-based learning, morpheme segmentation, Seq2Seq POS tagging                          \\
             \hline
-            Kim et al., 2019~\cite{KimHM2019}     & Syllable Distribution Patterns with Bi-LSTM-CRF        & Utilization of syllable distribution, Bi-LSTM-CRF for morphological analysis and POS tagging.
-\\
+            Kim et al., 2019~\cite{KimHM2019}     & Syllable distribution patterns with Bi-LSTM-CRF        & Utilization of syllable distribution, Bi-LSTM-CRF for morphological analysis and POS tagging                     \\
             \hline
-            Song and Park, 2019~\cite{SongHJ2019} & Tied Sequence-to-Sequence Multi-task Model             & Multi-task learning for morpheme processing and POS tagging, pointer-generator and CRF network integration.
-\\
+            Song and Park, 2019~\cite{SongHJ2019} & Tied Seq2Seq multi-task model                          & Multi-task learning for morpheme processing and POS tagging, pointer-generator and CRF network integration       \\
             \hline
-            Song and Park, 2020~\cite{SongHJ2020} & Two-step Korean POS Tagger with Encoder-Decoder        & Encoder-decoder architecture for morpheme generation, sequence labeling for POS tagging.
-\\
+            Song and Park, 2020~\cite{SongHJ2020} & Two-step Korean POS tagger with encoder--decoder       & Encoder--decoder architecture for morpheme generation, sequence labeling for POS tagging                         \\
             \hline
-            Youn and Lee, 2021~\cite{YounJY2021}  & Two-step Deep Learning-based Pipeline Model            & Deep learning sequence-to-sequence models, BERT for morpheme restoration and POS tagging.
-\\
+            Youn and Lee, 2021~\cite{YounJY2021}  & Two-step Deep Learning-based Pipeline Model            & Deep learning sequence-to-sequence models, BERT for morpheme restoration and POS tagging                         \\
             \hline
-            Shin and Lee, 2023~\cite{ShinHJ2023}  & Syllable-Based Multi-POSMORPH Annotation               & Syllable distribution patterns, Multi-POSMORPH tagging, Transformer encoder, BiLSTM usage.
-\\
+            Shin and Lee, 2023~\cite{ShinHJ2023}  & Syllable-based multi-POSMORPH annotation               & Syllable distribution patterns, multi-POSMORPH tagging, Transformer encoder, BiLSTM usage                        \\
             \hline
@@
 
-    \subsection{Traditional Dictionary-based Approaches}\label{subsec:traditional-dictionary-based-approaches}
+    \subsection{Traditional dictionary-based approaches}\label{subsec:traditional-dictionary-based-approaches}
     In the initial stages of Korean morphological analysis, the predominant methods leaned heavily on rule- and dictionary-based approaches~\cite{KwonHC1991}.
@@
 
-    \subsection{Syllable-unit Morphological Analysis}\label{subsec:syllable-unit-morphological-analysis}
+    \subsection{Syllable-unit morphological analysis}\label{subsec:syllable-unit-morphological-analysis}
     To address the drawbacks of dictionary dependence, syllable-by-syllable morphological analysis has emerged as an alternative~\cite{ShimKS2011, LeeCK2013, LeeCH2016, KimHM2016, Li2017, KimSW2018, ChoiYS2018, MinJW2019, KimHM2019, SongHJ2019, SongHJ2020, YounJY2021, ShinHJ2023}.
@@
 
-    \subsection{Recent Deep Learning Approaches}\label{subsec:recent-deep-learning-approaches}
+    \subsection{Recent deep learning approaches}\label{subsec:recent-deep-learning-approaches}
     The incorporation of deep learning into Korean morphological analysis has brought significant advancements to the field.
@@
 
-    \subsection{Integrating Dictionary-based and Deep Learning Approaches}\label{subsec:integrating-dictionary-based-and-deep-learning-approaches}
+    \subsection{Integrating dictionary-based and deep learning approaches}\label{subsec:integrating-dictionary-based-and-deep-learning-approaches}
     Tokenization, a fundamental process in NLP deep learning models, involves breaking down text into smaller units and converting these tokens into vectors for computational processing.
@@
     The combination of dictionary-based morphological analysis methods and deep learning approaches used by MeCab~\cite{MeCab}, a fast and lightweight morphological analyzer for Korean and Japanese tokenization, proves to be valuable in this context.
-    The dictionary-based morphological analysis employs a model trained with CRFs to form a lattice structure as in ~\cite{Kudo2004, NaSH2014, NaSH2018}, identifying the optimal path for morphological analysis.
+    The dictionary-based morphological analysis employs a model trained with CRFs to form a lattice structure as in~\cite{Kudo2004, NaSH2014, NaSH2018}, identifying the optimal path for morphological analysis.
     While this method provides a certain level of accuracy and speed, it falls short of the high accuracy achieved by modern deep learning.
@@
     \section*{Acknowledgments}
-    This work was supported by Institute of Information \& Communications Technology Planning \& Evaluation(IITP) grant funded by the Korea government(MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human).
+    This work was supported by an Institute of Information \& Communications Technology Planning \& Evaluation (IITP) grant funded by the Korea government (MSIT) (RS-2023-00216011, Development of artificial complex intelligence for conceptually understanding and inferring like human).
+    We would like to thank Editage (www.editage.co.kr) and Soomgo (soomgo.com) for English language editing.
 
@@
     {\includegraphics[width=60pt,height=70pt,draft]{empty}}
-    {\textbf{Jihee Ryu} received his BS degree in computer science \& engineering from Chungnam National University, Daejeon, Rep.
+    {\textbf{Jihee Ryu} received his B.S.
+degree in computer science \& engineering from Chungnam National University, Daejeon, Rep.
 of Korea, in 2006.
-He received his MS degree in computer science from KAIST, Daejeon, Rep.
+He received his M.S.
+degree in computer science from KAIST, Daejeon, Rep.
 of Korea, in 2010.
-He is currently a senior researcher at ETRI, Daejeon, Rep.
+He is currently a Senior Researcher at ETRI, Daejeon, Rep.
 of Korea.
@@
     {\includegraphics[width=60pt,height=70pt,draft]{empty}}
-    {\textbf{Soojong Lim} received his BS degree in mathematics from Yonsei University, Seoul, Rep.
+    {\textbf{Soojong Lim} received his B.S.
+degree in mathematics from Yonsei University, Seoul, Rep.
 of Korea, in 1997.
-He also received his MS degree and PhD in computer science from Yonsei University, in 1998 and 2014, respectively.
-He is currently a principal researcher at ETRI, Daejeon, Rep.
+He also received his M.S.
+degree and Ph.D.
+in computer science from Yonsei University, in 1998 and 2014, respectively.
+He is currently a Principal Researcher at ETRI, Daejeon, Rep.
 of Korea.
-His research interests include natural language processing, deep learning, and large language \& crossmodal model.}
+His research interests include natural language processing, deep learning, and large language \& crossmodal models.}
     \end{biography}
@@
     {\includegraphics[width=60pt,height=70pt,draft]{empty}}
-    {\textbf{Oh-Woog Kwon} received his BS degree in computer engineering from Kyungpook National University, Rep.
-of Korea, in 1992, his MS degree in computer science from KAIST, Rep.
-of Korea, in 1995, and his PhD degree in computer engineering from the Pohang University of Science and Technology (POSTECH), Rep.
+    {\textbf{Oh-Woog Kwon} received his B.S.
+degree in computer engineering from Kyungpook National University, Rep.
+of Korea, in 1992, his M.S.
+degree in computer science from KAIST, Rep.
+of Korea, in 1995, and his Ph.D.
+degree in computer engineering from the Pohang University of Science and Technology (POSTECH), Rep.
 of Korea, in 2001.
@@
     {\includegraphics[width=60pt,height=70pt,draft]{empty}}
-    {\textbf{Seung-Hoon Na} received his PhD degree in computer science from POSTECH in 2008.
-Currently, he is a professor in Dept.
+    {\textbf{Seung-Hoon Na} received his Ph.D.
+degree in computer science from POSTECH in 2008.
+Currently, he is a Professor at the Dept.
 of Computer Science at Jeonbuk National University.
-Previously, he was a senior researcher at Electronics and Telecommunications Research Institute, Rep.
-of Korea, after he worked in School of Computing at Natural University of Singapore.
+Previously, he was a Senior Researcher at the Electronics and Telecommunications Research Institute, Rep.
+of Korea, after working at the School of Computing at Natural University of Singapore.
 His research interests include natural language processing, information retrieval, and machine learning.}

### 2024-01-12 contents/draft.tex
Pictures added for Authors

@@
     \begin{biography}
-    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\includegraphics[width=60pt,height=70pt]{author1}}
     {\textbf{Jihee Ryu} received his B.S.
@@
     \begin{biography}
-    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\includegraphics[width=60pt,height=70pt]{author2}}
     {\textbf{Soojong Lim} received his B.S.
@@
     \begin{biography}
-    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\includegraphics[width=60pt,height=70pt]{author3}}
     {\textbf{Oh-Woog Kwon} received his B.S.
@@
     \begin{biography}
-    {\includegraphics[width=60pt,height=70pt,draft]{empty}}
+    {\includegraphics[width=60pt,height=70pt]{author4}}
     {\textbf{Seung-Hoon Na} received his Ph.D.
